### 2025-01-11 msconstraints-leo-temp.tex
Kickstarting slides.

%- HandOut Flag -----------------------------------------------------------------------------------------
\newif\ifHandout
%	\Handouttrue  %uncomment for the printable version

%- D0cum3nt ----------------------------------------------------------------------------------------------
\documentclass[beamer,handout,10pt]{standalone}   
\ifHandout
	\setbeameroption{show notes} %print notes   
\fi

%- Packages ----------------------------------------------------------------------------------------------
\usepackage{custom-style}

%--Beamer Style-----------------------------------------------------------------------------------------------
\usetheme{toninus}

%\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{tikz-cd}
\usepackage{tcolorbox}
\usepackage[all]{xy}
%\usepackage{quiver}
\usetikzlibrary{nfold}
\usetikzlibrary{decorations.pathmorphing}

\newcommand{\Ham}{\mathrm{Ham}}
\newcommand{\Der}{\mathrm{Der}}

%---------------------------------------------------------------------------------------------------------------------------------------------------
%- D0cum3nt ----------------------------------------------------------------------------------------------------------------------------------
\begin{document}
%------------------------------------------------------------------------------------------------

\section{LEOS}
% TEMP! All credit to Leonid Ryvkin www.ryvkin.eu

\section{Motivation: Symplectic reductions}
\subsection{Symplectic manifolds}
\begin{frame}

\begin{block}{Def. Symplectic manifold $(M,\omega)$}
	$M$ a smooth manifold, $\omega\in \Omega^{2}(M)$ closed and non-degenerate, i.e.:
\begin{itemize} 	
	\item $d\omega=0$
	\item $\omega^\flat:TM\to T^*M, v\mapsto \iota_v\omega$ is injective
\end{itemize}	
\end{block}

Examples:\pause
\begin{itemize}
	\item orientable 2-manifolds with volume, e.g. $S^2$, $T^2$, $\mathbb R^2$\pause
	\item cotangent bunlde $T^*Q$ of any manifold $Q$, with $\omega=d\theta$. $\theta_\eta(v)=\eta(T\pi_Q(v))$.\pause
	\item coadjoint orbits
\end{itemize}

\end{frame}

\begin{frame}
	\begin{block}{Def. Poisson algebra of observables} Let $(M,\omega)$ be symplectic.
		\begin{itemize}
			\item $X_f:=-(\omega^\flat)^{-1}(df)$  \emph{Hamiltonian vector field} of $f\in C^\infty(M)$.
			\item $\{f,g\}:=\omega(X_f,X_g)=L_{X_f}g$ \emph{Poisson bracket of observables}
		\end{itemize}
	\end{block}\pause
	Indeed $(C^{\infty}(M), \cdot, \{-,-\})$ Poisson algebra:
			\begin{itemize}
		\item $\cdot$ is a commutative, associative mutliplication
		\item $\{-,-\}$ is a Lie bracket
		\item $\{f,- \}$ is a derivation
	\end{itemize}\pause
	And $f\mapsto X_f$ is a Lie algebra map.

\end{frame}

\subsection{Marsden-Weinstein-Meyer reduction}
\begin{frame}[fragile]{Marsden-Weinstein-Meyer reduction}
Let $(M,\omega)$ symplectic, $G\circlearrowright M$ be a Lie group action\pause and $\mu:M\to \mathfrak g^*$ such that:\pause
\begin{itemize}
\item  $\mu$ is a momentum, i.e. the infinitesimal action $\xi\mapsto \underline\xi:\mathfrak g\to \mathfrak X(M)$ of $G$ satisfies $X_{\langle\mu,\xi\rangle}=\underline \xi$. \pause
\item $\mu$ is $G$-equivariant, i.e. $\mu(gm)=Ad^*_g\mu(m)$ \pause
\item The action of $G$ on $\mu^{-1}(0)$ is free and proper.\\ (This implies $0$ is reg. val. of $\mu$) \pause
\end{itemize}
Then $\exists!$ symplectic form $\omega_r$ on $M_r=\frac{\mu^{-1}(0)}{G}$ such that $\pi^*\omega_r=i^*\omega$.

% https://q.uiver.app/#q=WzAsMyxbMCwwLCJNIl0sWzMsMCwiXFxtdV57LTF9KDApIl0sWzYsMCwiTV9yIl0sWzEsMCwiaVxcXFwgXFxzdWJzdGFja3tpbmNsdXNpb25+b2Z+c3Vic3BhY2V9IiwyLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoiaG9vayIsInNpZGUiOiJib3R0b20ifX19XSxbMSwyLCJcXHBpXFxcXCBcXHN1YnN0YWNre3F1b3RpZW50fmJ5fnJlbGF0aW9ufSJdXQ==
\[\begin{tikzcd}
	M &&& {\mu^{-1}(0)} &&& {M_r}
	\arrow["\begin{array}{c} i\\ \substack{inclusion~of~subspace} \end{array}"', hook', from=1-4, to=1-1]
	\arrow["\begin{array}{c} \pi\\ \substack{quotient~by~relation} \end{array}", two heads, from=1-4, to=1-7]
\end{tikzcd}\]

\pause
Examples: $\mathbb CP^n$ from $S^1$-action on $\mathbb C^{n+1}$.

\end{frame}

\subsection{Attempting algebraic reduction}

\begin{frame}[fragile]
When the action is not 'free and proper', we can try to mimic this directly using the function algebras:
% https://q.uiver.app/#q=WzAsNixbMCwwLCJNIl0sWzEsMCwiXFxtdV57LTF9KDApPVMiXSxbMywwLCJNX3IiXSxbMCwxLCJDXlxcaW5mdHkoTSkiXSxbMSwxLCJDXntcXGluZnR5fShTKT1cXGZyYWN7Q157XFxpbmZ0eX0oTSl9e0lfe1N9fSJdLFszLDEsIkNee1xcaW5mdHl9KE1fcik9Q15cXGluZnR5KFMpXkciXSxbMSwyLCJcXHN1YnN0YWNre3F1b3RpZW50fSIsMCx7InN0eWxlIjp7ImhlYWQiOnsibmFtZSI6ImVwaSJ9fX1dLFszLDQsIlxcc3Vic3RhY2t7cXVvdGllbnR9IiwwLHsic3R5bGUiOnsiaGVhZCI6eyJuYW1lIjoiZXBpIn19fV0sWzAsMSwiXFxzdWJzdGFja3tyZXN0cmljdGlvbn0iLDAseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dLFs0LDUsIlxcc3Vic3RhY2t7cmVzdHJpY3Rpb259IiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoic3F1aWdnbHkifX19XV0=
\[\begin{tikzcd}
	M & {\mu^{-1}(0)=S} && {M_r} \\
	{C^\infty(M)} & {C^{\infty}(S):=\frac{C^{\infty}(M)}{I_{S}}} && {C^{\infty}(M_r)=C^\infty(S)^G}
	\arrow["{\substack{restriction}}", squiggly, from=1-1, to=1-2]
	\arrow["{\substack{quotient}}", two heads, from=1-2, to=1-4]
	\arrow["{\substack{quotient}}", two heads, from=2-1, to=2-2]
	\arrow["{\substack{restriction}}", squiggly, from=2-2, to=2-4]
\end{tikzcd}\]

where $I_S=\{f\in C^{\infty}(M)~|~f|_S=0\}$.\pause Equivalently:

% https://q.uiver.app/#q=WzAsMyxbMCwwLCJDXlxcaW5mdHkoTSkiXSxbMiwwLCJOX1M9XFx7Zn58fiBmXFxpbiBDXlxcaW5mdHkoTSl8X1N+fkdcXG1hdGhybXstaW52YXJpYW50fVxcfSJdLFs0LDAsIlxcZnJhY3tOX1N9e0lfU30iXSxbMCwxLCJcXHN1YnN0YWNre3Jlc3RyaWN0aW9ufSIsMCx7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6InNxdWlnZ2x5In19fV0sWzEsMiwiXFxzdWJzdGFja3txdW90aWVudH0iLDAseyJzdHlsZSI6eyJoZWFkIjp7Im5hbWUiOiJlcGkifX19XV0=
\[\small\begin{tikzcd}
	{C^\infty(M)} && {N_S=\{f~|~ f\in C^\infty(M)|_S~~G\mathrm{-invariant}\}} && {\frac{N_S}{I_S}}
	\arrow["{\substack{restriction}}", squiggly, from=1-1, to=1-3]
	\arrow["{\substack{quotient}}", two heads, from=1-3, to=1-5]
\end{tikzcd}\]
\pause

\begin{alertblock}{Problem}
	$C^\infty(S)^G=\frac{N_S}{I_S}$ is not a Poisson algebra in general.
\end{alertblock}
(when constraints not first class, cf. Dirac reduction)
\end{frame}

 \begin{frame}{Other approaches to reduction}

\begin{table}[]
	\begin{tabular}{l|l|l||l}
		algebra $\mathcal{A}_T$ & subalgebra $\mathcal{A}_N$ & ideal $\mathcal{A}_0$ & comment \\
		\hline

		$C^\infty(M)$&      $N_S$     &   $I_S$   &  $\substack{S=\mu^{-1}(0),~ I_S=\{f~|~f|_S=0\}}$ \\
			&&&  $\substack{N_S= \{ f | gf-f\in I_S \forall g\in G\}}$ \\
	& & & \color{red} not Poisson \\ 
	\hline	\pause
	$C^\infty(M)$&   $F_S$         &   $I_S$   &  $\substack{F_S=\{f~|~\{f,I_S\}\subset I_S\}}$ \\
	& & & \color{red} if $I_S\subset F_S$\\
	\hline \pause

	$C^\infty(M)$&   $C^\infty(M)^G$         &   $(I_S)^G$   &  $\substack{C^\infty(M)^G=\{f~|~gf=f\forall g\in G\}}$ \\
	\hline \pause
		$C^\infty(M)$&   $C^\infty(M)^G$         &   $(I_\mu)^G$   & $\substack{I_\mu=\{\sum_{i=1}^k f_i\langle \mu,\xi_i\rangle|~f_i\in C^\infty(M), \xi_i\in \mathfrak g\}}$\\
		\hline \pause
	$C^\infty(M)$&      $N_\mu$     &   $I_\mu$   & $\substack{N_\mu= \{ f | gf-f\in I_\mu \forall g\in G\}}$\\
	\hline

	\end{tabular}\pause
\end{table}
{\bf Remarks }names in order: 'naive' , Dirac, Sniatycki, Arms-Cushman-Gotay, Sniatycki-Weinstein.\pause \\
When $G$ connected $N_\mu=N(I_\mu):=\{f~|~\{f,I_\mu\}\subset I_\mu\}$. 
 \end{frame}

\subsection{Preview of our answer}
\begin{frame}
We will develop a multisymplectic reduction in this talk, symplectically it is:
\begin{block}{Construction: Multisymplectic reduction in the symplectic case}
Let $Q_S=\{f~|~ f|_S=0\rm{~and~} df|_S=0\}$ Then the $L_\infty$-reduction is:
$$
\frac{N(I_S)\cap N(I_\mu+Q)}{I_\mu+Q}
$$
\end{block}	\pause
Such a formula can be more generally applied to a Poisson algebra $P$ with associative ideals $I\subset J$ such that $\{I,I\}\subset I$ and $\{I,J\}\subset J$:
$$
\frac{N(J)\cap N(I+Q)}{I+Q}
$$
with $Q=\{f\in J|~\{f,P\}\subset J\}$
\end{frame}

\section{Multisymplectic manifolds and their observable algebras}
\subsection{Dramatis Personae}
\begin{frame}
\begin{block}{Def. Multisymplectic manifold $(M,\omega)$}
	$M$ a smooth manifold, $\omega\in \Omega^{n+1}(M)$ closed and non-deg., i.e.:
	\begin{itemize}
		\item $d\omega=0$
		\item $\omega^\flat:TM\to \Lambda^nT^*M, v\mapsto \iota_v\omega$ is injective
	\end{itemize}	\pause
\end{block}
Without the non-deg. condition we call it \emph{premultisymplectic}.	\pause
\begin{itemize} 
	\item orientable $n{+}1$-manifolds with volume, e.g. $S^{n+1}$, $T^{n+1}$, $\mathbb R^{n+1}$\pause
	\item multicotangent bunlde $\Lambda^nT^*Q$ of any manifold $Q$, with $\omega=d\theta$. $\theta_\eta(v_1,...,v_n)=\eta(T\pi_Q(v_n),...,T\pi_Q(v_n))$.\pause
	\item semisimple Lie groups, hyperKähler manifolds,...
\end{itemize}

\end{frame}

\subsection{Motivating example of $L_\infty$-algebra}

\begin{frame}{Back to the symplectic case, $M=\mathbb R^2$}
	Let $\omega=dx\wedge dy$, $\mathfrak X(\mathbb R^2,\omega)=\{X|~L_X\omega=0\}$.\pause

	\begin{itemize}
		\item {\bf Symplectic gradient}\\  $sgrad:C^\infty(\mathbb R^2)\to \mathfrak X(\mathbb R^2,\omega)$ (surjecive, kernel $\mathbb R$):\\ 
		$$f\mapsto sgrad(f)={-\partial^yf \choose \partial^xf}$$\pause 
		\item {\bf Poisson bracket} on $C^\infty(\mathbb R^2)$: $$\{f,g\}:=\partial^xf\partial^yg-\partial^xg\partial^yf$$ \\pause

		\item {\bf Preservation of the bracket} $$sgrad(\{f,g\})=[sgrad(f),sgrad(g)]$$
	\end{itemize}\pause
	{\color{teal} Conclusion: } One can use the nicer space $C^\infty(\mathbb R^2)$ instead of $\mathfrak X(\mathbb R^2,\omega)$!
\end{frame}

\begin{frame}{Let's try the same in $\mathbb R^3$}
	\begin{itemize}
		\item $\mathfrak X(\mathbb R^3)=\{(v_x,  v_y,  v_z)^T\}
		$\\ 
		\item {\bf Lie bracket :}
		$$[(v_x,  v_y,  v_z)^T,(w_x,  w_y,  w_z)^T]= (\sum_i v_i\partial^i(w_x) - w_i\partial^i(v_x) ,  \ldots ,\ldots)^T  $$
		\item {\bf volume form: }$\Omega=dx\wedge dy\wedge dz$ 
		\item {\bf volume-preserving fields: }$$\mathfrak X(\mathbb R^3,\Omega)=\{(v_x,v_y,v_z)^T~| \sum_i\partial^iv_i=0\}$$
	\end{itemize}\pause~\\
	This time the surjection is given by the {\bf Rotational}:

	$$rot:\mathfrak X (\mathbb R^3)\to \mathfrak X (\mathbb R^3,\Omega)$$
	$$
	rot((v_x,v_y,v_z)^T)= (\partial^yv_z-\partial^zv_y, \partial^z v_x-\partial^xv_z, \partial^x v_y-\partial^yv_x)^T
	$$

\end{frame}

\begin{frame}

	{\color{red} Problem: } $rot$ does not commute with the bracket: $[rot(X),rot(Y)]\neq rot([X,Y])$ in general\\
	~\\
	\pause
	{\color{teal} Solution: } New bracket $\{X,Y\}:=rot(X)\times rot(Y)$,\\ where $\times$ is the vector cross product on $\mathbb R^3$.\\~\\
	\pause
	We have $rot(\{X,Y\})=[rot(X), rot(Y)]$ \pause but no Jacobi identity. However: $$\{X,\{Y,Z\}\}-\{\{X,Y\},Z\}-\{Y,\{X,Z\}\}$$
	$$=- grad((rot(X)\times rot(Y))\cdot rot(Z))$$

\end{frame}

\begin{frame}
	$C^\infty(\mathbb R^3)\oplus \mathfrak X(\mathbb R^3)=:L_{-1}\oplus L_0$ form a \underline{\bf $L_\infty$ algebra} with:
	\begin{itemize} 	
		\item $l_1:L_{-1}\to L_0$, $l_1(f)=grad(f)$
		\item $l_2:L_{0}\times L_0\to L_0$, $l_2(X,Y)=\{X,Y\}$
		\item $l_3:L_{0}\times L_0\times L_0\to L_{-1}$, $l_3(X,Y,Z)=-(rot(X)\times rot(Y))\cdot rot(Z)$ 
	\end{itemize}~\\~\\ \pause
	In our case it means the following identities are satisfied:
	\begin{itemize} 	
		\item $l_2(l_1(f),Y)=0$
		\item $l_2(l_2(X,Y),Z) - cycl= l_1l_3(X,Y,Z)$
		\item $l_3(l_2(X,Y),Z,W)-cycl=0$
	\end{itemize}
\end{frame}

\subsection{The multisymplectic observable algebra}

\begin{frame}[fragile]
	\begin{block}{Def. Observable $L_\infty$ algebra [Rogers2012]}
		Let $(M,\omega)$ pre-multisymplectic. Set:
			\begin{itemize} 	
			\item $\Ham^0(M,\omega)=\{(\alpha,v)\in \Omega^{n-1}(M)\times \mathfrak X(M)~|~d\alpha=-\iota_v\omega  \}$
			\item $\Ham^{-i}(M,\omega)= \Omega^{n-1-i}(M)$, $1\leq i\leq n-1$.
			\item  $l_1=d:\Ham^{-i}(M,\omega)\to \Ham^{-i+1}(M,\omega)$,\\ (resp. $(d,0)$ for $i=1$)
			\item $l_k:\Lambda^k\Ham^0(M,\omega)\to \Ham^{2-k}(M,\omega),$
			\begin{align*}
			&l_k((\alpha_1,v_1),...,(\alpha_k,v_k))=-(-1)^{\frac{k(k+1)}{2}}\iota_{v_k}...\iota_{v_1}\omega & k\geq 3\\
			&l_2((\alpha_1,v_1),(\alpha_2,v_2))=(\iota_{v_2}\iota_{v_1}\omega, [v_1,v_2])
			\end{align*}
		\end{itemize}
	\end{block}
	\vspace{-15mm}
	\pause
	% https://q.uiver.app/#q=WzAsNixbMCwwLCJDXlxcaW5mdHkoTSkiXSxbMSwwLCJcXE9tZWdhXjEoTSkiXSxbMiwwLCIuLi4iXSxbMywwLCJcXE9tZWdhXntuLTN9KE0pIl0sWzQsMCwiXFxPbWVnYV57bi0yfShNKSJdLFs1LDAsIlxcSGFtXjAoTSkiXSxbMCwxLCJkIl0sWzEsMiwiZCJdLFsyLDMsImQiXSxbMyw0LCJkIl0sWzQsNSwiKGQsMCkiXSxbNSw1LCJsXzIiLDAseyJsYWJlbF9wb3NpdGlvbiI6NDAsIm9mZnNldCI6MSwiYW5nbGUiOjQ1LCJsZXZlbCI6Mn1dLFs1LDQsImxfMyIsMCx7ImN1cnZlIjotMywibGV2ZWwiOjN9XSxbNSwzLCJsXzQiLDIseyJjdXJ2ZSI6MywibGV2ZWwiOjR9XV0=
	\[\tiny\begin{tikzcd}
		{C^\infty(M)} & {\Omega^1(M)} & {...} & {\Omega^{n-3}(M)} & {\Omega^{n-2}(M)} & {\Ham^0(M)}
		\arrow["d", from=1-1, to=1-2]
		\arrow["d", from=1-2, to=1-3]
		\arrow["d", from=1-3, to=1-4]
		\arrow["d", from=1-4, to=1-5]
		\arrow["{(d,0)}", from=1-5, to=1-6]
		\arrow["{l_4}"', curve={height=18pt}, Rightarrow, scaling nfold=4, from=1-6, to=1-4]
		\arrow["{l_3}", curve={height=-18pt}, Rightarrow, scaling nfold=3, from=1-6, to=1-5]
		\arrow["{l_2}"{pos=0.4}, shift right, Rightarrow, from=1-6, to=1-6, loop, in=10, out=80, distance=10mm]
	\end{tikzcd}\]
\end{frame}

\begin{frame}
\begin{block}{Thm. $Ham^\bullet(M,\omega)$ is an $L_\infty$-algebra [Rogers2012]}
This means $
\substack{
l_1l_{m+1}(x_1,...,x_{m+1})=\sum_{i<j}(-1)^{i+j}l_m(l_2(x_{i},x_j),x_1,...,\widehat{x_i},...,\widehat{x_j},...,x_{m+1})}
$ for all $m$ and all possible $x_i$, where $l_0:=0$ and $l_{m+2}:=0$.
\end{block}\pause

{\bf Remark:} We could instead turn $\Ham^0(M,\omega)$ into a Left-Leibniz algebra by $[(\alpha,v)(\beta, w)]:=(L_v\beta,[v,w])$. This satisfies (left-)Jacobi, but is not skew-symmetric.\pause

\begin{block}{Remark}
 The above also works if we replace $(C^\infty(M),\mathfrak X(M))$ with any Lie-Rinehart algebra $(A, L)$ and $\omega$ with a cocycle in $(\Lambda^{n+1}_AL)^*$.
\end{block}\pause
A Lie Rinehart algebra is: 
\begin{itemize} 
	\item A commutative algebra $A$ and an A-module $L$
	\item A Lie algebra structure on $L$
	\item A Lie algebra and module homomorphism $\rho:L\to \Der(A)$
\end{itemize}
such that $[\ell, a\tilde \ell]=a[\ell,\tilde \ell]+\rho(\ell)(a) \cdot \tilde\ell$
\end{frame}

\section{Reduction using Constraint triples}

\subsection{General idea}
\begin{frame}
\begin{exampleblock}{Idea of multisymplectic observable reduction:}
	Mimic the above construction of $\Ham^\bullet$\\ with triples of the type (algebra , subalgebra, ideal).
\end{exampleblock}\pause
After [Dippel2023] we call such triples { \bf constraint triples} and their parts \emph{total space, normal space, zero space}.\\~

Let $S$ be a closed set. We describe $C^\infty(S)$ by $\frac{C^\infty(M)}{I_S}$.\\ We think of it as the constraint triple:
$$
\mathcal A=(\mathcal A_T,\mathcal A_N,\mathcal A_0)=(C^\infty(M),C^\infty(M), I_S)
$$
It is a (strong) constraint algebra,\\ i.e. $\mathcal A_0\subset \mathcal A_N\subset \mathcal A_T$ subalgebras and $\mathcal A_0\subset \mathcal A_T$ ideal.

\end{frame}

\subsection{A dictionary between algebra and geometry}
\begin{frame}{Translating geometry to algebra}

\begin{table}[]
	\begin{tabular}{l|l|l}
	 geometry & algebra & translation \\
		\hline	
	smooth manifold $M$ & comm. algebra $\mathcal A_T$  	& $\mathcal A_T=C^{\infty}(M)$\\ \hline\pause
	vector fields $\mathfrak X(M)$ & derivations $\Der(\mathcal A_T)$ &  $\Der(C^\infty(M))=\mathfrak X(M)$\\ \hline\pause
	closed subset $S\subset M$ & ideals $\mathcal A_0\subset \mathcal A_T$ & $\mathcal A_0=I_S=\{f~|~f|_S=0\}$ \\ \hline\pause
	action $G\circlearrowleft M$ & Lie algebra map & infinitesimal generators\\
	 of connected group &$\underline{\cdot}:\mathfrak g\to \Der(\mathcal A_T)$ & of the action \\ \hline \pause
	 $G$ action preserves $S$ & $\underline \xi(I_S)\subset I_S$ $\forall \xi\in\mathfrak g$& \color{red} Careful! Not equivalent! \\ \hline
	\end{tabular}\pause
\end{table}
	\begin{alertblock}{Warning}
	$\partial_x$ is algebraically preserving $S=[0,1]\subset \mathbb R=M$, even though the flow leads out of the set.
\end{alertblock}
\end{frame}

\begin{frame}{Derivations of constraint algebras}
	$\mathcal A=(\mathcal A_T,\mathcal A_N,\mathcal A_0)=(C^\infty(M),C^\infty(M), I_S)$\\~
\begin{itemize} 
	\item $\Der(\mathcal A)_T:=\Der(\mathcal A)_T$ corresponds to all vector fields\pause
	\item  $\Der(\mathcal A)_N:=\{v\in \Der(\mathcal A)~|~v(\mathcal A_N)\subset \mathcal A_N, ~v(\mathcal A_0)\subset \mathcal A_0\}$\\
	corresponds to vector fields ({\color{red}algebraically}) tangent to $S$.\\ \pause

	\item  $\Der(\mathcal A)_0:=\{v\in \Der(\mathcal A)~|~v(\mathcal A_N)\subset \mathcal A_0\}$\\
	are vector fields vanishing on $S$.\pause
		\begin{block}{Lemma: Algebraic vanishing = geometric vanishing}
		$\Der(\mathcal A)_0=\{v ~| ~v|_S=0\}=I_S\cdot \mathfrak X(M)$.
	\end{block}\pause
\end{itemize}	
\end{frame}

\begin{frame}
	$\mathcal A=(C^\infty(M),C^\infty(M), I_S)$\\
	$\Der(\mathcal A)=(\mathfrak X(M),~~\{v| v(I_S)\subset I_S\},~~ I_S\mathfrak X(M))$
		\begin{block}{Lemma: $\mathfrak L:=\Der(\mathcal A)$ is a constraint Lie-Rinehart algebra over $\mathcal A$}
			This means 
	\begin{itemize} 
		\item $\mathfrak L_T$ is a Lie Rinehart algebra over $\mathcal A_T$.
		\item $\mathfrak L$ is a strong constraint module over $\mathcal A$, i.e.\\ $\mathcal A_N\mathfrak L_N\subset \mathfrak L_N$ and $\mathcal A_0\mathfrak L_T+\mathcal A_T\mathfrak L_0\subset \mathfrak L_0$.
		\item $[\mathfrak L_N,\mathfrak L_N]\subset \mathfrak L_N$ and  $[\mathfrak L_N,\mathfrak L_0]\subset \mathfrak L_0$
	\end{itemize}

\end{block}\pause

\begin{exampleblock}{Corollary: $(\Lambda \mathfrak L)^*$ has a constraint Cartan calculus $d, \iota, L$}
	\begin{itemize} 
	\item $(\Lambda^k \mathfrak L)^*_T=\Omega^k(M)$
	\item $(\Lambda^k \mathfrak L)^*_N=\{\alpha~|~\alpha(v_1,...,v_k)\in \mathcal A_N~\forall v_i\in \mathfrak L_N , $ \\ ~~~~~~~~~~~~~~~~~~~~$ \alpha(v_1,...,v_{k-1},w)\in \mathcal A_0~\forall v_i\in \mathfrak L_N , w\in \mathfrak L_0 \}$
	\item $(\Lambda^k \mathfrak L)^*_0=\{\alpha~|~\alpha(v_1,...,v_k)\in \mathcal A_0~\forall v_i\in \mathfrak L_N\}$
	\end{itemize}

\end{exampleblock}

\end{frame}

\subsection{Introducing symmetry}
\begin{frame}
Let $F\subset \Der(\mathcal A)_N$ a Lie subalgebra  (typically $F=\underline{\mathfrak g}$). Consider:
\begin{itemize} 
	\item the constraint algebra $\mathcal B= (C^\infty(M),~~~~ \{f~|~F(f)\subset I_S\},~~~ I_S)$\pause
	\item the constraint Lie-Rinehart algebra $\mathcal L$  \[ (\mathfrak X(M),~~~~\{v ~|~ [v,F]\subset C^\infty(M)F+I_S\mathfrak X(M)\}, ~~~~ C^\infty(M)F+I_S\mathfrak X(M) )\]
	\item \pause the constaint differential forms 
	\[
	\mathcal W=(\Omega(M),~~~, \{\alpha |\iota_\xi\alpha,L_\xi\alpha\in (\Lambda \mathfrak L)^*_0 ~~\forall \xi\in F \},~~~~(\Lambda \mathfrak L)^*_0  )
	\]
	where $(\Lambda^k \mathfrak L)^*_0=\{\alpha~|~\alpha(v_1,...,v_k)\in \mathcal A_0~\forall v_i\in \mathfrak L_N\}$
\end{itemize}
\begin{block}{'Lemma': $\mathcal L$ has a Cartan calculus on $\mathcal W$}
	In particular, from the premultisymplectic form $\omega$ we obtain a constraint $L_{\infty}$-algebra.
\end{block}
\end{frame}

\subsection{The reduced $L_\infty$-algebra}
\begin{frame}[fragile]
Let $(M,\omega)$ premultisymplectic, $S\subset M$ closed and \\ $F\subset \mathfrak X(M)$ a Lie subalgebra s.th. $F(I_S)\subset I_S$\\ ~\\
The following subquotient $\frac{\Ham(M,\omega)_N}{\Ham(M,\omega)_0}$\\ of $\Ham(M,\omega)_T=\Ham(M,\omega)$ forms an $L_\infty$-algebra:

	\[\small
		\frac{
			\left\lbrace
			\begin{array}{l}
				\alpha\in \Omega^{\leq n-2}(M) ~\mathrm{, respectively}\\	
				(\alpha,X) \in \Omega^{n{-}1}(M) \oplus\mathfrak X(M)
			\end{array}
			~\left\vert~
			\begin{array}{l l}
				\iota_\xi \alpha \in (\Lambda \mathfrak L)^*_0 &\\
				L_\xi\alpha \in (\Lambda \mathfrak L)^*_0&~\forall \xi \in F\\
				\hline
				\iota_X \omega = -d \alpha &\\
				X(I_S)\subset I_S &\\
				L_\xi X \in C^{\infty}(M) F + I_S\mathfrak X(M)
				&~\forall \xi \in F\\
			\end{array}
			\right.
			\right\rbrace
		}{
			\left\lbrace
			\begin{array}{l}
				\alpha\in \Omega^{\leq n-2}(M) ~\mathrm{, respectively}\\	
				(\alpha,X) \in \Omega^{n{-}1}(M) \oplus \mathfrak X(M)
			\end{array}
			~\left\vert~
			\begin{array}{l}
				\alpha \in (\Lambda \mathfrak L)^*_0\\
				\hline
				\iota_X \omega = -d \alpha\\
				X \in C^{\infty}(M) F + I_S\mathfrak X(M)
			\end{array}
			\right.
			\right\rbrace
		}
\]
where $(\Lambda^k \mathfrak L)^*_0=\{\alpha~|~\alpha(v_1,...,v_k)\in \mathcal A_0~\forall v_i\in \mathfrak L_N\}$
\end{frame}

\subsection{Main application}
\begin{frame}[fragile]
Let $(M,\omega)$ premultisymplectic, $\underline{\cdot}:\mathfrak g\to \mathfrak X(M)$ an action and\\
 $\mu:\mathfrak g\to \Omega^{n-1}(M)$ a Leibniz momentum, i.e.
\[
X_{\mu(\xi)}=\underline \xi ~~\forall \xi ~~~~~~~\mu([\xi,\zeta])=L_{\underline \xi}\mu(\zeta)~\forall \xi,\zeta
\]
Then $F=\underline {\mathfrak g}$ and $S=\{p\in M~|~\mu(\xi)_p=0\forall \xi\in\mathfrak g\}$ satisfy the necessary condition. \pause  Moreover:
\begin{block}{Thm: The geometric case [Blacker21]}
If in the above $S$ is smooth and the foliation spannd by $\underline{\mathfrak g}|_S$ is simple, then $M_{r}=\frac{S}{\underline{\mathfrak g}|_S}$ is premultisymplectic with $\omega_r$ unique, satisfying $\pi^*\omega_r=i^*\omega$.
\[\begin{tikzcd}
	M &&& S &&& {M_r}
	\arrow["\begin{array}{c} i \end{array}"', hook', from=1-4, to=1-1]
	\arrow["\begin{array}{c} \pi \end{array}", two heads, from=1-4, to=1-7]
\end{tikzcd}\]
\end{block}
\end{frame}

\begin{frame}
\begin{block}{Lemma: Relating the reductions}	
There is a natural injection $R:\frac{\Ham(M,\omega)_N}{\Ham(M,\omega)_0}\hookrightarrow \Ham(M_r,\omega_r)$.
\end{block}
\pause 
\begin{exampleblock}{Non-surjectivity in general}
	\begin{itemize} 
	\item 	$M=\mathbb R^5$, $\omega=dt\wedge (dx_1\wedge dy_1+dx_2\wedge dy_2)$\pause 
	\item $\mathfrak g=\langle\xi\rangle, \underline{\xi}=\partial_{x_1}$, $\mu(\xi)=-y_1dt$\pause 
	\item $S=\{y_1=0\}$, $M_r\cong \mathbb R^3$ with $t,x_2,y_2$ and $\omega_r=dt\wedge dx_2\wedge dy_2$\pause 
	\item $(\alpha,v)=(x_2tdy_2,x_2\partial_t-t\partial_{x_2})$ is not in the image of $R$.\pause 
	\end{itemize}
\end{exampleblock}
{\bf Reason for non-surjectivity:} From the perspective of $M_r$ it does not make sense to require $d\alpha=-\iota_v\omega$ on all of $M$.\pause \\
{\bf Remark:} We can easily construct examples where $\omega_r$ degenerates.
\end{frame}

\subsection{Lessons learned}
\begin{frame}{Lessons learned}
	\begin{itemize} 
\item Constraint triples permit to do differential geometry/ Cartan calculus on singular subquotients,\\ ... in particular constructing observable algebras on them.\pause
\item Even if $\omega$ is non-degenerate, $\omega_r$ could degenerate, forcing us to pull along the Hamiltonian vector fields explicitly\pause
\item Coomentum maps in the sense of the Leibniz structure seem better for reducing than $L_\infty$-comomenta \pause
\item The algebraic approach can treat algebroid / singular foliation symmetries and remembers vanishing orders a the singularities. \pause
\item The reduction seems to give something novel even in the symplectic case \pause
\item A 'softer' notion of constraint $L_\infty$ algebra is necessary to obtain all observables of the reduced space.

	\end{itemize}
\end{frame}

%------------------------------------------------------------------------------------------------
\end{document}

### 2025-01-11 msconstraints-short.tex
Kickstarting slides.

%+----------------------------------------------------------------------------+
%| SLIDES: Constraint Algebras of multisymplectic Observables (Follow-up talk)
%| Contents:	- 25 minutes (extimated duration ~2 minutes per slide, ~12 slides )
%|
%| Author: Antonio miti
%| Event: 19th International Young Researchers Workshop on Geometry, Dynamics and Field Theory
%| Place: Verona
%| Date: 20/01/25
%+----------------------------------------------------------------------------+

%- HandOut Flag -----------------------------------------------------------------------------------------
	\newif\ifHandout
	%\Handouttrue  %uncomment for the printable version
	%Handling of flags it is not preserved when passing to standalone-subfiles!

%- D0cum3nt ----------------------------------------------------------------------------------------------
\ifHandout
	\documentclass[handout,10pt]{beamer}   
	\setbeameroption{show notes} %print notes   
\else
	\documentclass[10pt]{beamer}
\fi

%- Packages ----------------------------------------------------------------------------------------------
\usepackage{custom-style}
\usepackage{math}
\usepackage{multicol}
\usepackage{xfrac}

\renewcommand{\action}{\curvearrowright} 
\makeatletter
\def\blfootnote{\gdef\@thefnmark{}\@footnotetext}
\makeatother

\newcommand{\fgmodule}{\mathfrak{X}_{\g}}
\newcommand{\tgtvanform}{I_{\Omega}(N)}
\newcommand{\tgtvf}{\mathfrak X_N(M)}
\newcommand{\vanvf}{I_{\mathfrak{X}}(N)}%{I_N^{\mathfrak X}}
\newcommand{\Ham}{\mathsf{Ham}}
\renewcommand{\ham}{\text{ham}}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{amssymb}

%--Beamer Style-----------------------------------------------------------------------------------------------
\usetheme{toninus}

\usetikzlibrary{backgrounds}
  \tikzset{
    invisible/.style={opacity=0},
    visible on/.style={alt=#1{}{invisible}},
    alt/.code args={<#1>#2#3}{%
      \alt<#1>{\pgfkeysalso{#2}}{\pgfkeysalso{#3}} % \pgfkeysalso doesn't change the path
    },
  }

%- T1tle P4g3 -------------------------------------------------------------------------------------------
\title{ Constraint Algebras \\ of Multisymplectic Observables } 
\subtitle{\href{https://sites.google.com/view/xix-yrw-verona/home?authuser=0}{19th International Young Researchers Workshop on Geometry, Dynamics and Field Theory}}
\author[AMM]{
	\href{https://www.antoniomiti.it/}{Antonio Michele Miti}
	{\small joint work w/ Leonid Ryvkin}
}
\institute[SUR]{
	Sapienza Università di Roma \\
	Rome, Italy 	\\
	\vspace{.5em}
  \begin{tabular}[h]{ccc}
      \href{https://www.mat.uniroma1.it/en}{\includegraphics[width=6cm]{./Logos/Sur_logo}} & & 
      \href{https://civis3i.univ-amu.fr/en/civis3i-alliance-programme}{\includegraphics[width=3cm]{Logos/Civis_logo}}
  \end{tabular}    
}
\date[YGMC] % (optional, should be abbreviation of conference name)
{	
	{\vskip 1ex}
	University of Verona, Italy, January 2025
}

%---------------------------------------------------------------------------------------------------------------------------------------------------
%- D0cum3nt ----------------------------------------------------------------------------------------------------------------------------------
\begin{document}
%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}  % Alternative: \maketitle outside of frame
	\titlepage
	\ifHandout
		\tikz[overlay,remember picture]
		{
	    	%	\node at ($(current page.west)+(1.5,0)$) [rotate=90] {\Huge\textcolor{gray}{\today}};
	    	\node[        
	    		draw,
	    		shape border rotate=90,
			isosceles triangle,
			isosceles triangle apex angle=90,
			fill=yellow]
	        		at ($(current page.north east)-(1,1)$) [rotate=-45] {\textcolor{red}{Handout version}};
		}
	\fi
	\end{frame}
	\addtocounter{framenumber}{-1}
\note{
	%\textbf{\underline{OUTLINE}}:
	%\tableofcontents
	\textbf{Abstract:}
	\\
%
This talk explores key algebraic structures in multisymplectic geometry, a generalization of symplectic geometry where higher-degree $k$-forms replace 2-forms. A central theme is the interplay between symmetries (group actions preserving the differential form) and reduction, which constructs a lower-dimensional space inheriting the geometric structure of the original manifold.

The Marsden--Weinstein--Meyer theorem in symplectic geometry connects this reduction process to regular-level sets of momentum maps, with extensions to singular cases by Śniatycki and Weinstein. Marvin Dippel, Chiara Esposito, and Stephan Waldmann (\href{https://arxiv.org/abs/2310.05613}{\texttt{arXiv:2310.05613}}) developed a framework for constraint algebras of observables in the context of coisotropic reduction in Poisson geometry.

Our research builds on previous work by adapting and implementing algebraic reduction schemes within multisymplectic geometry, providing a higher-dimensional perspective on the relationship between symmetries and reduction.

This talk reviews higher versions of observable algebras and moment maps in multisymplectic geometry and examines how regular and singular reduction schemes extend to this framework. The presentation is based on ongoing joint work with Leonid Ryvkin.

}
%---------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{Keywords}
\tikzstyle{every picture}+=[remember picture]
	\begin{columns}
    	\begin{column}{.45\textwidth}
    		\onslide<4->{
			\tikz[baseline]{
		            \node[draw=orange!40,anchor=base,text width=5cm] (s1)
		            {Algebraic structure encoding informations necessary for defining coisotropic reduction in Poisson geometry.};
			}
		}
	\end{column}
    	\begin{column}{.45\textwidth}
    		\onslide<5->{
			 \tikz[baseline]{
		            \node[draw=blue!40,anchor=base, text width=5cm] (s2)
		            {Mathematical formalization of classical measurable quantities.};
			}
		}
	\end{column}
	\end{columns}

	\vfill

	\begin{center}
		\large
		 \tikz[baseline]{
		            \node[fill=orange!20,anchor=base] (t1)
		            {Constraint Algebra};
			}
		\\
		of 
		\\
		 \tikz[baseline]{
	            \node[fill=green!20,anchor=base] (t3)
	            {Multi};
		}
		\kern-3pt - \kern-3pt
		 \tikz[baseline]{
	            \node[fill=red!20,anchor=base] (t4)
	            {Symplectic};
		}		
		  \tikz[baseline]{
		            \node[fill=blue!20,anchor=base] (t2)
		            {Observables};
		        }

	\end{center}

	\vfill

	\begin{columns}
    	\begin{column}{.45\textwidth}
    		\onslide<3->{
	 		 \tikz[baseline]{
	            \node[draw=green!40,anchor=base,text width=5cm] (s3)
	            {A certain higher version \\(involving differential forms in degree $\geq 2$)};
	         }
		}		   	
		\end{column}
    	\begin{column}{.45\textwidth}
    		\onslide<2->{
				\tikz[baseline]{
	            \node[draw=red!40,anchor=base,text width=5cm] (s4)
	            {Closed $2$-form on a smooth manifold, providing a geometric framework for classical mechanics};
	           }	
			}
		\end{column}
	\end{columns}

	\begin{tikzpicture}[overlay]
        \path[->,draw=orange!40]<4-> (s1) edge [bend right] (t1);
        \path[->,draw=blue!40]<5-> (s2) edge [bend left] (t2);
        \path[->,draw=green!40]<3-> (s3) edge [bend left] (t3);
        \path[->,draw=red!40]<2-> (s4) edge [bend left] (t4);
	\end{tikzpicture}

	\vfill
	\onslide<1->{
	\begin{block}{Based on:}
%		 \emph{ \small
%			 Blacker, M, Ryvkin;
%			\textbf{Reduction of $L_\infty$-algebra of observables on multisymplectic manifolds}; 
%			\href{https://arxiv.org/abs/2206.03137}{arXiv:2206.03137}.
%		}
%		\\
		 \emph{ \small
			 M. , Ryvkin;
			\textbf{Constraint algebras of multisyplectic observables}; 
			\href{https://www.antoniomiti.it/teaching/Obs-Constraint-2024/}{In preparation}.
		}		
	\end{block}
	}

\end{frame}
\note[itemize]{
	\item Provide a vague idea of the words that make up the title.
	\item \cite{Dippell2023}
	\item Conventions:
	\\- $M$ and $G$ are connected,
	\\- actions $\theta:G \curvearrowright M$ are always smooth
	\\- $\xi,\eta\in\g$,
	\\- for $\mu\in\Omega^*(M,\g^*)$ and $\xi\in\g$, write
			\[
				\mu_\xi := \langle\mu,\xi\rangle \;{\color{black!50}\in\Omega^*(M)}
			\]
			for the ``$\xi$th component'' of $\mu$.
}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\section{Symplectic Reduction}
\checkpoint	
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}{Symplectic geometry (mechanics flavour)}
\begin{columns}[T]
	\begin{column}{.50\linewidth}
		\centering
		\textit{ "geometric approach" to mechanics \dots}
		%
		\begin{columns}
			\begin{column}{.60\linewidth}
				\begin{center}
					\includegraphics[width=0.6\linewidth]{Pictures/pendulum13}			
				\end{center}
			\end{column}	
			\begin{column}{.40\linewidth}
				\begin{center}
					\includegraphics[width=0.45\linewidth]{Pictures/pendulum-phase-space}			
				\end{center}
			\end{column}	
		\end{columns}
		%
		\begin{defblock}[Symplectic Manifold]
			\vspace{-1em}
			\includestandalone[width=1\textwidth]{Pictures/Figure_sym}	
		\end{defblock}
		%
		\pause
		\begin{exblock}[$M = T^\ast Q$ is symplectic]
			with $\omega = d \theta $ given by
			$$ \left.\theta\right\vert_{(q,p)} (v) = p (\pi_\ast v) ~.$$
		\end{exblock}
		%
		\pause
		\vspace{1.2em}
		\centering
		\textit{ based on the notion of \\"states".}		
	\end{column}
	\onslide<1->{\vrule{}}
	\pause
	\begin{column}{.50\linewidth}
		\centering
		\textit{ "algebraic approach" to mechanics \dots}
		\vspace{.5em}	
		\begin{defblock}[Classical Observables]
			Unital, associative, commutative algebra $C^\infty(M)$.
		\end{defblock}
		%
		\vspace{.1em}
		\pause
		\begin{defblock}[Hamiltonian vector fields]
			$\vHam_f \in \mathfrak{X}(M)$ such that:
			$$\iota_{\vHam_f} \omega = -df \quad$$ %$\in B^1(M)$
			%
			\footnotetext{	$\vHam_f$ = \emph{Ham.v.f. pertaining to $f\in C^\infty(M)$}.}
		\end{defblock}
		\vspace{.1em}
		%
		\begin{defblock}[Poisson Algebra of Observables]
			$C^\infty(M)$ is a Poisson algebra with
			$$\{f,g\} = \iota_{\vHam_g} \iota_{\vHam_f} \omega = \omega(\vHam_f,\vHam_g) ~.$$
		\end{defblock}
		%
		\pause
		\vspace{.15em}
		\centering
		\textit{ based on the notion of \\"measurable quantities".}						
	\end{column}
\end{columns}
\end{frame}
\note[itemize]{
	\footnotesize

	\item We work in the framework of multisymplectic geometry which is one of the possible generalizations of the well-established field of symplectic geometry.

	\item To recall what symplectic geometry is let me assume a particular point of view: mechanics.
	\\
	Idea:"
	Symplectic geometry is a branch of differential geometry studying symplectic manifolds; it originated as a formalization of the mathematical apparatus of classical mechanics and geometric optics."{\href{https://ncatlab.org/nlab/show/symplectic+geometry}{nlab}}

	Namely, a sym. mfd. is the geometric structure encoding the phase space of conservative, ordinary, classical, mechanical systems.

	\item $\theta$ = \emph{tautological 1-form}.
		$\theta$ evaluated at $p\in T^*Q$ in the fibre of $q\in Q$ and contracted with $v$ coincides with the form $p$ evaluated at $q$ and contracted with the push forward of $v$.

	\item We identify a special class of vector fields.
		Out of them one can define a Lie bracket.

	\item Poisson is a Lie algebra with the extra property of compatibility with the associative product (Leibniz rule)

	\item take away message: geometric (based on "states") vs algebraic (based on "measurable quantities").7
}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%------------------------------------------------------------------------------------------------
\begin{frame}{Reminder: momentum maps in symplectic geometry}\label{frame:symplecticmomaps}
	Consider $\theta:G\curvearrowright M$ symplectic,~~ $\underline{\cdot}:\mathfrak{g}\to \mathfrak{X}(M)$ infinitesimal action.
	\vfill

	\begin{columns}[T]
		\setlength{\belowdisplayskip}{5pt}
		\begin{column}{.50\linewidth}
			%
			\centering \it
			\onslide<2->{
				\begin{defblock}[Equivariant moment map]
					Smooth map $$\mu:M\to \mathfrak{g}^\ast$$
					such that:
					\begin{itemize}
						\item[i.] $d\langle \mu,\xi\rangle = -\iota_{\underline{\xi}}\omega$ 
						~\qquad, $\forall \xi \in \mathfrak{g}$
						\item[ii.] $\mu \circ \theta_g = Ad_g^\ast \circ \mu$
						 \qquad\small, $\forall g \in G$
					\end{itemize}
				\end{defblock}
			}
		\end{column}	
		%
		\onslide<2->{\vrule{}}
		%
		\begin{column}{.50\linewidth}
			\onslide<3->{			
				\begin{defblock}[Comoment map]
					Linear map $$\widetilde{\mu}: \mathfrak{g}\to C^\infty(M,\omega)$$
					such that:
					\begin{itemize}
						\item[i.] $d\widetilde{\mu}(\xi) = -\iota_{\underline{\xi}}\omega$ 
						\qquad~\small, $\forall \xi \in \mathfrak{g}$
						\item[ii.] $\widetilde{\mu}([\xi,\eta]) = \lbrace\widetilde{\mu}(\xi),\widetilde{\mu}(\eta)\rbrace$ \small, $\forall \xi,\eta \in \mathfrak{g}$
					\end{itemize}
				\end{defblock}
			}
		\end{column}	
	\end{columns}	
	%
	\pause
	\vspace{1em}
	%
	\begin{columns}[]
		\setlength{\belowdisplayskip}{5pt}
		\begin{column}{.40\linewidth}
			%
			\centering \it
			\onslide<5->{
				\begin{upshotblocktitle}[Duality]
					\begin{displaymath}
						\mu(x) : \mathfrak{\xi} \mapsto \widetilde{\mu}(\xi)\big\vert_x
					\end{displaymath}
					%
					\emph{
					\small
					"duality wrt. the currying operation"					
					}
				\end{upshotblocktitle}
			}
		\end{column}	
		%
		%
		\begin{column}{.60\linewidth}
			\onslide<4->{			
				\begin{upshotblocktitle}[$\widetilde{\mu}$ as a lift]
					\begin{displaymath}
						\begin{tikzcd}[ampersand replacement = \&]
						 \& C^\infty(M,\omega) \ar[d,"\vHam"]
						 \\
						 \mathfrak{g} \ar[ur,dashed,sloped,"\widetilde{\mu}"]\ar[r,"\underline{\cdot}"'] \& \mathfrak{X}(M)
						\end{tikzcd}
					\end{displaymath}
					%
					\emph{
					\small
					"it is a lift (in the Lie category) of the infinitesimal action by the assigment of hamiltonian v.fields."					
					}
				\end{upshotblocktitle}
			}
		\end{column}	
	\end{columns}		
\end{frame}
\note[itemize]{
	\item consider an action preserving the symplectic form.
	\item[-] $\langle \cdot, \cdot \rangle$ is the natural pairing of $\mathfrak{g}$ and $\mathfrak{g}^\ast$.
		\item[-] $\theta_g$ is the diffeomorphism associated to $g\in G$ via $\theta:G\curvearrowright M$
		\item[-] $Ad^\ast_g$ is the coadjoint action $G\curvearrowright \mathfrak{g}^\ast$
	\item The moment map can be reexpressed as a comomentum map.
	\item Observe that ii. on the left always implies ii. on the right. The converse is trure only if $G$ is connected.
	\item $G\curvearrowright M$ is said "Hamiltonian" (see slide \ref{frame:gisthamaction} in appendix) iff $\exists$ comoment map $\widetilde{\mu}$.
	\item \emph{moment map: Describe ${\color{orange}G\curvearrowright M}$ in terms of $\color{blue}C^\infty(M)\to\X(M)$.}
	\begin{center}
	\begin{tikzpicture}[scale=1.5]
		\node[orange] (A) at (0,0) {$\g$};
		\node[gray] (A1) at (0,-.3) {$\xi$};
		\node[blue] (B) at (1,1) {$C^\infty(M)$};
		\node[gray] (B2) at (1.55,1) {$f$};
		\node[orange] (C) at (1,0) {$\X(M)$};
		\node[gray] (C1) at (1,-.3) {$\underline\xi$};
		\node[gray] (C2) at (1.55,0) {$X_f$};

		\path[->,blue,dashed] (A) edge node[above left] {$\langle\mu,\cdot\,\rangle$} (B);
		\path[->,orange] (A) edge (C);
		\path[->] (B) edge (C);
		\path[|->,gray] (A1) edge (C1);
		\path[|->,gray] (B2) edge (C2);

		\begin{scope}[xshift=3cm]
			\node at (-.32,.8) {as Lie algebras};
			\node at (-.13,.2) {i.e., {\color{blue}$\mu_\xi$} generates {\color{orange}$\underline\xi$}};
		\end{scope}
	\end{tikzpicture}

		\footnotesize		(\emph{moment map:} ${\color{blue}\mu:M\to\g^*}$, 
	 \emph{Hamiltonian $G$-space:} 	$(M,\omega,G,\mu)$)
	\end{center}
	\item
	 $\alpha\mapsto X_\alpha$ is a homomorphism of Leibniz algebras:
	$$\d\{\alpha,\beta\} = \d\L_{X_\alpha}\beta = \L_{X_\alpha}\iota_{X_\beta}\omega = \iota_{[X_\alpha,X_\beta]}\omega ~{\color{black!80} \implies}~
	X_{\{\alpha,\beta\}} = [X_\alpha,X_\beta]$$
}
%------------------------------------------------------------------------------------------------

\subsection{Regular reduction}
%------------------------------------------------------------------------------------------------
\begin{frame}{Regular reduction in symplectic geometry}
	\textbf{\color{UniGreen}Symplectic reduction:}~~
	\\ 
	{\it \small
	Procedure associating to any (suitably regular) pair of symplectic manifold and Hamiltonian action another symplectic manifold of smaller dimension.}
	\vfill
	\pause
	\begin{thmblock}[Marsden-Weinstein reduction \cite{MarsdenWeinstein74}]
		\vspace{-.4em}\hspace{-1em}
		\begin{tabular}{l p{14cm}}
		    Given: & $(M,\omega)$ symplectic
		    \\
		    & $G\curvearrowright M$ symplectic with equivariant momap. $\mu:M\to \mathfrak{g}^*$
		    \\[.2em]
		    Assume: & $\phi \in \mathfrak{g}^*$ regular value of $\mu$ 
		    \qquad\quad \footnotesize \textcolor{gray}{($\Rightarrow$ $\mu^{-1}(\phi)\hookrightarrow M$ smooth embedding)}
		    \\
			& $G_\phi\curvearrowright \mu^{-1}(\phi)$ free and proper
			\quad \footnotesize \textcolor{gray}{($\Rightarrow$ $\mu^{-1}(\phi)/G_\phi$ smooth manifold)}
			\\[.4em]
			Then: & $\exists!$ symplectic structure $\omega_\phi$ in $M_\phi:= \mu^{-1}(\phi)/G_\phi$ \\
			& s.t. $\pi^\ast \omega_\phi = j^\ast \omega$ 
			\qquad {\footnotesize with $j:\mu^{-1}(\phi) \hookrightarrow M$ and $\pi:\mu^{-1}(\phi)\twoheadrightarrow M_\mu$}
		\end{tabular}
		\vspace{-.4em}
	\end{thmblock}
	%
	\vfill
	\pause
	\begin{columns}
		\begin{column}{0.40\textwidth}
			\includegraphics[width=\textwidth]{Pictures/Reduction}
		\end{column}

		\begin{column}{0.6\textwidth}
				\textbf{\color{UniGreen}In mechanics:}~~
				\\
			{\it \small
				it embodies the process of restricting the dynamics of the system to the level sets of the conserved quantities pertaining to the symmetry group.		
			}
			\\[.2em]
			\color{gray}\small( e.g. restricting to studying a point-like particle in a central potential by studying it in radial coordinates)
		\end{column}	
	\end{columns}	
\end{frame}
\note[itemize]{
	\item {Symplectic Reduction} takes two inputs:
	\\ 1. Hamiltonian $G$-space $(M,\omega,{\color{orange}G},{\color{blue}\mu})$
	\\ 2. parameter ${\color{blue}\phi}\in\g^*$
	\item The \emph{reduced space} is $M_\phi:={\color{blue}\mu^{-1}(\phi)}{\color{orange}/G_\phi}$.
	\item (Marsden--Weinstein '74, Meyer '73) THM:\\
		If $\mu^{-1}(\phi)\subset M$ is smooth and $G_\phi\curvearrowright \mu^{-1}(\phi)$ is free and proper, then there is a \textbf{unique symplectic form} $\omega_\phi\in\Omega^2(M_\phi)$ such that $\pi^*\omega_\phi = i^*\omega$.

	\begin{center}
	\begin{tikzpicture}[scale=2]
		\node[blue] (A) at (0,0) {$\mu^{-1}(\phi)$};
		\node[gray] (A1) at (0,.3) {$i^*\omega$};
		\node[gray] (A2) at (-.6,0) {$\pi^*\omega_\phi$};
		\node[blue] (B) at (1,0) {$M$};
		\node[gray] (B1) at (1,.3) {$\omega$};
		\node[orange] (C) at (0,-.8) {$M_\phi$};
		\node[gray] (C2) at (-.6,-.8) {$\omega_\phi$};

		\path[right hook->,blue] (A) edge node[above] {$i$} (B);
		\path[orange,->] (A) edge node[left] {$\pi$} (C);
		\begin{scope}[xshift=-1.8cm]
			\node[blue] at (0,0) {\small restrict to $\{\mu=\phi\}$};
			\node[orange] at (.15,-.4) {\small quotient by $G_\phi$};
		\end{scope}
	\end{tikzpicture}
	\end{center}
	\item Heuristic Approach to Reduction:
	\\1. describe $G\curvearrowright M$ in terms of $\omega$ 	\hspace{1cm}
	({\color{green}moment map $\mu$})
	\\2. identify a distinguished reduced space \hspace{1cm}
	({\color{green}reduction at $\mu=0$})
	\\3. use the ambiguity in 1.\ to obtain a family of reduced spaces \hspace{1cm}
	({\color{green}reduction at $\mu-\phi=0$, i.e.\ reduction at $\mu=\phi$}
	\\
	{\tiny Note: If $G_\phi\neq G$, then $\mu-\phi:M\to\g^*$ is not a moment map for either $G\curvearrowright M$ or $G_\phi\curvearrowright M$.}

}
%------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Singular reduction}
\begin{frame}{Symplectic singular reduction schemes}
	\begin{block}{The gist of singular reduction}
 		\begin{itemize}
 			\item[-] when $\mu$ is singular (i.e. $\mu^{-1}(0)$ is not a mfd.), the (geometrically) reduced space may not exist.
 			\item[-] a \emph{singular reduction scheme} is a procedure to construct a "reduced" algebra of observable out of the given data
 			\item[-] such that it corresponds to the algebra of observable of the reduced manifold in the regular case.
 		\end{itemize}
	\end{block}
 	%
 	\pause
 	%
	\begin{thmblock}[Sniatycki-Weinstein reduction \cite{SniatyckiWeinstein83}]
		\vspace{-.4em}\hspace{-1em}
		\begin{tabular}{l p{14cm}}
		    Given: & $(M,\omega)$ symplectic
		    \\
		    & $G\curvearrowright M$ symplectic with equivariant momap. $\mu:M\to \mathfrak{g}^*$
			\\[.4em]
			Then: & 
			$\displaystyle \left[\sfrac{C^\infty(M)}{I_\mu}\right]^G$
			admits a Poisson algebra structure 
			\blfootnote{$I_\mu$ = associative ideal generated by $\widetilde{\mu}(\g)$}			
			\\
			& it agrees with the M--W reduction in the regular case.		
		\end{tabular}
		\vspace{-.4em}
	\end{thmblock}

\end{frame}
\note[itemize]{
 \item Let $(M,\omega,G,\mu)$ be a symplectic Hamiltonian $G$-space.
 \item The \emph{momentum ideal} is the associative ideal $I_\mu\subset C^\infty(M)$ generated by the momenta $\mu_{\xi}$ for any $\xi\in \mathfrak{g}$.
		Namely
		\[
			I_\mu 
			= 
			\Big\langle \mu_\xi \Big\rangle_{\xi \in \mathfrak{g}}^{\text{\tiny asso.}} 
			=
			\left\{
				\left.
					\sum_{i=1}^n f_i ~ \mu_{\xi_i}
				\right|~
					f_i \in C^\infty(M),~ \xi_i\in \mathfrak{g},~  1 \leq i \leq n
			\right\}
		\]

 \item The \emph{\'Sniatycki--Weinstein reduction} is the Poisson algebra
		\[
			\left(C^\infty(M)/I_\mu\right)^G.
		\]

}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\section{Multisymplectic Geometry}
\checkpoint	
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}{From symplectic to {multi}symplectic} 
	%
	\begin{center}
		$-$ \emph{multisymplectic means \textbf{going higher} in the degree of $\omega$} $-$
	\end{center}
	\pause
	\begin{defblock}[$n$-plectic manifold ~\emph{(Cantrijn, Ibort, De Le\'on)} \cite{Cantrun2017}]
		\includestandalone[width=0.95\textwidth]{Pictures/Figure_multisym}	
	\end{defblock}
	%
	\pause
		\begin{table}
			\begin{tabular}{c c c}
				symplectic forms \small($n=1$) & $\leftrightsquigarrow$ & volume forms \small($n= \text{dim}(M)-1$)
			\end{tabular}
		\end{table}

	\vfill
	\pause
	\begin{block}{Historical motivation}
		Mechanics: geometrical foundations of \textit{(first-order)} field theories.
	\end{block}
	%
	\begin{table}
		\ifHandout
		%
		\else
		\only<4>{
		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
            \hline
            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
            \hline
            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold &  \\[.25em]
            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra &  \\[.25em]
            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map &  
            \\
            \hline
  \multicolumn{1}{c}{}
            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
            &  \multicolumn{1}{@{}c@{}}{}              \\
		\end{tabular}
		}
		\fi
		\onslide<5->{
		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
            \hline
            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
            \hline
            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold & multisymplectic manifold \\[.25em]
            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra & $L_\infty$-algebra \\[.25em]
            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map & group actions admitting (homotopy) comomentum map
            \\
            \hline
  			\multicolumn{1}{c}{}
            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
            &
            \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{field-theoretic systems}}$} 
               \\
		\end{tabular}
		}
	\end{table}

\end{frame}
\note[itemize]{
	\item Historically, the interest in multisymplectic manifolds, has been motivated by the need for understanding the geometrical foundations of first-order classical field theories.
	The key point is that, just as one can associate a symplectic manifold to an ordinary classical mechanical system (e.g. a single
point-like particle constrained to some manifold), it is possible to associate a multisymplectic
manifold to any classical field system (e.g. a continuous medium like a filament or a fluid). See frame Extra-\ref{Frame:Ms-Field-Mechanics}

	\item General ideas basic parallelisms with caveats
	\item caveat: points in multiphase spaces are not states
	\item the table hides the duality between geometric and algebraic approaches to the problem.
	\item	Mechanics: geometrical foundations of \textit{(first-order)} field theories.
		\begin{itemize}
		 \item[-] Kijowski, W. Tulczyjew \cite{Kijowski1979}; %(1979)
		 \item[-] Cariñena, Crampin, Ibort \cite{Carinena1991b};% (1991)
		 \item[-] Gotay, Isenberg, Marsden, Montgomery \cite{Gimmsy1};%(1998)
		 \\ $\cdots$
		\end{itemize}
}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}{Observables in $n$-plectic geometry}
	%
	\begin{defblock}[Hamiltonian $(n-1)$-forms]
		\begin{displaymath}
			\Omega^{n-1}_{ham}(M,\omega) 	:=
			\biggr\{ \sigma \in  \Omega^{n-1}(M) \; \biggr\vert \; 
				\exists \vHam_\sigma \in \mathfrak{X}(M) ~:~ 
				\tikz[baseline,remember picture]{\node[rounded corners,
                        fill=orange!5,draw=orange!30,anchor=base]            
            			(target) {$d \sigma = -\iota_{\vHam_\sigma} \omega$ };
            	}				
				~\biggr\} 
			\end{displaymath}
	\end{defblock}

	\pause
		\tikz[overlay,remember picture]
		{
			\node[rounded corners,
                 fill=orange!5,draw=orange!30,anchor=base]
            	 (base) at ($(current page.north east)-(2,1)$) [rotate=-0,text width=3.5cm,align=center] {\footnotesize{\textcolor{red}{Hamilton-DeDonder-Weyl \\equation}}};
		}	
	\begin{tikzpicture}[overlay,remember picture]
    	\path[->] (base.south) edge[bend right,red](target.north);
    \end{tikzpicture}
	%
	\vfill
	\begin{columns}[T]
		\pause
		\setlength{\belowdisplayskip}{5pt}
		\begin{column}{.50\linewidth}
			%
			\vspace{-1em}
			\begin{thmblock}[Observables $L_\infty$-algebra]
				$\Omega^{n-1}_{ham}(M,\omega)$ endowed with
				\vspace{-.5em}
				\begin{displaymath}
					\lbrace \sigma_1, \sigma_2 \rbrace =			
					~ - \iota_{\vHam_1}\iota_{\vHam_2} \omega 
				\end{displaymath}			
				can be "completed" to a \\ $L_\infty-algebra$.
			\end{thmblock}
			%	
		\end{column}	
		%
		\pause
		\begin{column}{.50\linewidth}
		%
			\begin{itemize}
				\item[\cmark] Skew-symmetric;
				\item[\xmark] multiplication of observables;
				\item[\xmark] Jacobi equation;
				%\\ \hspace*{4.25em} full-fledged Jacobi equation;
				\item[\smark] Jacobi equation \emph{up to homotopies}.
			\end{itemize}			
			%
				\[
					\small
					\{\alpha,\{\beta,\gamma\}\} + \text{\it cyc. perm.}
					= {\color{orange}\d \iota_{X_\alpha} \iota_{X_\beta} \iota_{X_\gamma}\omega}
				\]
		\end{column}	
	\end{columns}
	%
	\vfill
	\pause
	Interesting alternatives:
	\begin{itemize}
		\item  descend to $\Omega^{k-1}_{ham}(M) / {\color{orange}\d\hspace{1pt}\Omega^{k-2}(M)}$, hence getting a Lie algebra;
		\item Incorporate the {\color{orange}discrepancy} as part of the data of the space of observables $ 
				L_\infty(M,\omega) = \Omega_{ham}^{k-1}(M)\oplus{\color{orange}\Omega^{\leq k-2}(M)}$
			%a \textbf{homotopy Lie algebra} or \textbf{$L_\infty$-algebra}.
	\end{itemize}

\end{frame}
\note[itemize]{
	\item
}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%---------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{$L_\infty$-algebra of Observables}
\begin{frame}[fragile,t]{$L_\infty$-algebra of Observables (higher observables) }
	Let be $(M,\omega)$ a $n$-plectic manifold.
	\begin{defblock}[$L_\infty$-algebra of observables ~\emph{(Rogers)} ~\cite{Rogers2010}]

		\hspace{.25em} $L\infty(M,\omega)$ is given by:

		\begin{itemize}
			\item[•] a cochain-complex $(L,\{\cdot\}_1)$ 
		\end{itemize}
		\begin{center}
		\ifHandout
			\includestandalone{Pictures/Figure_Observables}	
		\else
			\includestandalone{Pictures/Frame_Observables}
		\fi				
		\end{center}
		\onslide<2->{
			\begin{itemize}
				\item[•] with $n$ (skew-symmetric) multibrackets $(2 \leq k \leq n+1)$
			\end{itemize}
			\begin{center}
				\includestandalone{Pictures/Equation_Multibracket}	
			\end{center}
		}
		%
	\end{defblock}
  \end{frame}
 \note[itemize]{
	\item if symplectic manifolds are the symmetric take on mechanics, Poisson algebras are the algebraic counterpart.
 	\item A Lie algebra is associated to an ordinary symplectic manifold (its Poisson algebra).
	%(Underlying this is a Lie algebra, whose Lie bracket is the Poisson bracket.)
	Similarly, one associates an Lie-$n$ algebra to any $n$-plectic manifold.
 	% https://ncatlab.org/nlab/show/n-plectic+geometry 	 
 	 %https://ncatlab.org/nlab/show/Poisson+bracket+Lie+n-algebra
	 \item Basically, the higher observables algebra is a chunk of the de Rham complex of $M$ with inverted grading( convention employed here) and an extra structure called "multibrackets".
 	\item ( In the 1-plectic case it reduces to the corresponding Poisson algebra of classical observables)
 	\item Rogers associated to any n-plectic mfd a $L\-\infty$ algebra, Zambon generalized it to the pre-n-plectic case.
 	\item Recognize in the definition of $\{\cdot,\ldots,\cdot\}_k$ the contraction with hamiltonian fields $v_\sigma$ w.r.t. $\sigma$.
  	\item Note $	\iota_{v_{\sigma_1}}\cdots\iota_{v_{\sigma_k}} = (-)^{(k-1)+(k-2)+\dots+1}\iota_{v_{\sigma_k}}\cdots\iota_{v_{\sigma_1}} = (-)^{\frac{k(k-1)}{2}}\iota_{v_{\sigma_k}}\cdots\iota_{v_{\sigma_1}}$ 
 	The definition usually find in literature of Rogers multibrackets involves the coefficient $ (-)^{\frac{k(k-1)}{2}} = -\varsigma(k-1) = (-)^{k+1} \varsigma(k)$.
  \item higher observables is Special instance of a more general object  called $L\-\infty$ Algebra...
 }
%------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\section{Multisymplectic observables reduction}
\checkpoint	
%-------------------------------------------------------------------------------------------------------------------------------------------------
%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}{Singular Reduction: Roadmap}
	%
	\begin{block}{Data:}
			\begin{itemize}
				\item A \emph{constraint set} $N$ (possibly singular),
				\item An infinitesimal action preserving $N$.
			\end{itemize}
	\end{block}
	%
	\vfill
	\pause
	%
	\begin{block}{Goal:}
		\begin{itemize}
			\item Obtain a "reduced" observables algebra out of the data.
		\end{itemize}
	\end{block}
	%
	\vfill
	\pause
	%
	\begin{block}{Strategy:}
		\begin{enumerate}
			\item Define smooth fields/forms \emph{tangent to $N$},
			\item define smooth fields/forms \emph{vanishing along $N$},
			\item define \emph{reducible fields} requiring the preservation of the vanishing objects,
			\item define \emph{reducible forms} requiring their conservation w.r.t. the infinitesimal action,
			\item define \emph{reducible and vanishing observables},
			\item \textbf{quotient}
		\end{enumerate}
	\end{block}

\end{frame}
\note[itemize]{
	\item
}

%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[shrink]{Smooth objects on a singular set}
	Consider $N$ closed subset of $M$.
	\vfill
	\pause
	\begin{defblock}
	 $I_N$ = ideal of smooth functions vanishing over $N$.
	\end{defblock}
	\vfill
	\pause

	\begin{columns}[T]
		\setlength{\belowdisplayskip}{5pt}
		\begin{column}{.65\linewidth}
			%
			\centering \it
				\begin{defblock}[v.f tangent to $N$]
					\begin{displaymath}
						\X_N(M):=
						\left\lbrace
							v \in \X(M)
						~\Big\vert~
							\L_v(I_N) \subseteq I_N
						\right\rbrace
					\end{displaymath}
				\end{defblock}
				\begin{defblock}[v.f vanishing on $N$]
					\begin{displaymath}
						I_\X(N):=
						\left\lbrace
							v \in \X(M)
						~\Big\vert~
							\L_v(C^\infty(M)) \subseteq I_N
						\right\rbrace
					\end{displaymath}				
				\end{defblock}				
		\end{column}	
		%
		%
		\begin{column}{.35\linewidth}
			\centering 
			\includestandalone[width=0.8\textwidth]{Pictures/Figure_VfTangentN}			
		\end{column}	
	\end{columns}			
	%	
	\pause

				%

				%	
		\begin{tcolorbox}[
		enhanced,frame hidden,borderline={0.5pt}{0pt}{blue},
		arc=5pt,colback=white,
		colbacktitle=white,]
			\color{blue}{\textbf{Lem}:} If $N$ is smoothly embedded,  $\X(N)\cong {X_N(M)}/{I_\X}$.
		\end{tcolorbox}

		\pause

		\begin{defblock}[Differential form vanishing on $N$]
			\begin{displaymath}
				I_{\Omega(N)}:=
				\left\lbrace
					\alpha\in\Omega^k(M
				~\left\vert~
					\begin{array}{l r}
						k\geq 0,~		\\		
						\alpha(u_1,\ldots,u_k) \in I_N & \forall u_i \in\X_N(M)
					\end{array}
				\right\rbrace\right.
			\end{displaymath}
		\end{defblock}

\end{frame}
\note[itemize]{
 \item $N$ is not a submanifold in general. An example is $N=\mu^{-1}(0)$ for a certain smooth map $N$.
 \item observe that if $N$ is a smooth embedded submanifold, one has that $\X(N)\cong \frac{X_N(M)}{I_\X}$

}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Multisymplectic singular reduction}
\begin{frame}{Reducible smooth objects \quad \small (w.r.t. $N$ and $\g\action M$)}
	Consider $\g \action M$ by vector fields tangent to $N$ % \hfill( fond. distribution $\underline{\g}\subseteq \X_N(M)$)
	\\
	\vfill
	Denote by :  
	\hspace{1em} $\underline{\g}\subseteq \X_N(M)$ the fundamental distribution,
	\\
	\hspace{6.5em}  $\X_g$ the $C^\infty$-module generated by $\underline{\g}$.
	\\
	\vfill
	\begin{defblock}[Reducible v.fields ]
			\begin{displaymath}
				\X(M)_{[N]} :=
				\left\lbrace
					v \in \X(M)
				~\left\vert~
					\begin{array}{l}
						\L_v (I_N) \subseteq I_N	\\		
						\L_v (\X_g) \subseteq \X_g + I_\X
					\end{array}
				\right\rbrace\right.
			\end{displaymath}
%			\blfootnote{
%			 $\X_g$ = $C^\infty(M)$-module generated by the fundamental distribution.
%			}

	\end{defblock}	
	%
	\pause
	%
	\begin{defblock}[Reducible forms ]
		\begin{displaymath}
			\Omega(M)_{[N]} :=
			\left\lbrace
				\alpha \in \Omega(M)
			~\left\vert~
				\begin{array}{l r}
					\L_\underline{\xi} \,\alpha \in I_{\Omega(N)}	\\		
					\iota_\underline{\xi} \,\alpha \in I_{\Omega(N)}	& \forall \xi \in \g				\end{array}
			\right\rbrace\right.
		\end{displaymath}	
	\end{defblock}	
	%
	\pause
	\vfill
	%
	Let $(M,\omega)$ be a $k$-plectic manifold
	\begin{defblock}[Reducible Hamiltonian forms]
		\begin{displaymath}
			(\Omega(M)_{ham}^{n-1})_{[N]} :=
			\left\lbrace
				\alpha \in \Omega(M)_{ham}^{n-1}
			~\left\vert~
				\begin{array}{l r}
					\alpha \text{ is a reducible form} \\
					\vHam_\alpha \text{ is a reducible v.field}
				\end{array}
			\right\rbrace\right.
		\end{displaymath}	
	\end{defblock}

\end{frame}
\note[itemize]{
 \item $\g\action M$ by vector field tangent to $N$ means that $\underline{\xi}\in\X_n(M) \forall \xi \in \g$
 \item Spelling out the definition: reducible vector fields are 
 \\i) v.f. tangent to N 
 \\ii) such that their commutator with any $\underline{\xi}$ lies in $\X_\g$ along $N$.
 \item more algebraically, they stabilize both $I_N$ and $\X_g + I_\X$.
 \item observe that $\L_v I_\X \subseteq I_\X$ since , $\forall u \in I_\X$ $\forall f \in C^\infty(M)$ one has\\
 $(\L_v u) f = \L_{[v,u]} f = \L_v\L_u f - \L_u\L_v f \in I_N$
 \item
}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}\frametitle{Hierarchy of auxiliary constructions}
	\begin{minipage}{\textwidth}
	\centering
	\scalebox{.65}{
	\begin{tikzpicture}
		\node (A) at (0,10.0) {\fbox{\parbox{5.6cm}{\centering Ideal of functions vanishing on $N$ \\ $I_N$}}};
		\node (B) at (0,8.3) {\fbox{\parbox{4.4cm}{\centering Vector fields tangent to $N$ \\ $\X_N(M)$}}};
		\node (C) at (3,6.5) {\fbox{\parbox{4.2cm}{\centering Forms vanishing along $N$ \\ $I_\Omega(N)$}}};
		\node (D) at (3,4.2) {\fbox{\parbox{2.7cm}{\centering Reducible forms \\ $\Omega(M)_{[N]}$}}};
		\node (E) at (-3,6.3) {\fbox{\parbox{5.3cm}{\centering Fundamental $C^\infty$-module \emph{plus} \\ vector fields vanishing along $N$ \\ $\X_\g(M)+I_\X(N)$}}};
		\node (E') at (-3,4.2) {\fbox{\parbox{3.8cm}{\centering Reducible vector fields \\ $\X(M)_{[N]}$}}};
		\node (F) at (0,2.4) {\fbox{\parbox{3.7cm}{\centering Reducible observables \\ $L_\infty(M,\omega)_{[N]}$}}};
		\node (G) at (0,0.6) {\fbox{\parbox{5.0cm}{\centering Vanishing ideal of observables \\ $I_{L_\infty}(N)$}}};
		\node (H) at (0,-1.05) {\fbox{\parbox{4.3cm}{\centering Observable reduced space \\ $L_\infty(M,\omega)_N$}}};

		\draw[->] (A)-- node[right=1pt]{{\scriptsize used to define}} (B);
		\draw[->] (B)-- (C);
		\draw[->] (C)-- node[right=.25cm]{\rotatebox{-90}{\small $\subset$}} (D);
		\draw[->] (B)-- (E);
		\draw[->] (D)-- (F);
		\draw[->] (E)-- node[left=.25cm]{\rotatebox{-90}{\small $\subset$}} (E');
		\draw[->] (E')-- (F);
		\draw[->] (F)-- node[right=.25cm]{\rotatebox{90}{\small $\subset$}} (G);
		\draw[->] (G)-- (H);

		\node[right=2.95cm] at (A) {\scriptsize\emph{associative ideal}};
		\node[right=2.30cm] at (B) {\scriptsize\emph{Lie algebra}};
		\node[right=2.25cm] at (C) {\scriptsize\emph{differential ideal}};
		\node[right=1.5cm] at (D) {\scriptsize\emph{differential graded subalgebra}};
		\node[left=2cm] at (E') {\scriptsize\emph{Lie subalgebra}};
		\node[left=2.8cm] at (E) {\scriptsize\emph{Lie ideal}};
		\node[right=2cm] at (F) {\scriptsize\emph{$L_\infty$-subalgebra}};
		\node[right=2.65cm] at (G) {\scriptsize\emph{$L_\infty$-ideal}};
		\node[right=2.3cm] at (H) {\scriptsize\emph{$L_\infty$-algebra}};
	\end{tikzpicture}
	}
	\end{minipage}
\end{frame}
\note[itemize]{
 \item
}

%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}{Multisymplectic observable reduction}
	\begin{defpropblock}[Reducible $L_\infty$-observables]
		Is the {\color{blue!70!black}$L_\infty$-subalgebra} of $L_\infty(M,\omega)$ given by
		\begin{displaymath}
			L_\infty(M,\omega)_{[N]}^k :=
			\begin{cases}
				\Omega^{n-1-k}(M)_{[N]} 
				\qquad\text{\color{gray}\small (reducible forms) }
				& \text{if } n-1\leq k < 0 \\
				(\Omega(M)_{ham}^{n-1})_{[N]} 
				\quad
				\text{\color{gray}\small (reducible hamiltonians) }
				& \text{if } k = 0 \\
				0 & \text{if } k > 0
			\end{cases}
		\end{displaymath}
	\end{defpropblock}
	%
	\pause
	%
	\begin{defpropblock}[Vanishing $L_\infty$-observables]
		Is the {\color{blue!70!black}$L_\infty$-ideal} of $L_\infty(M,\omega)_{[N]}$ given by
		\begin{displaymath}
			I_{L_\infty(M,\omega)} :=
			\left\lbrace
				\alpha \in L_\infty(M,\omega)_{[N]}
			~\left\vert~
				\begin{array}{l l}
					\alpha(v_1,\dots,v_k) \in I_N  \quad \forall v_i \in \X_N &
					\text{if}~ \alpha \in \Omega^k \\
					\vHam_\alpha \in \X_\g + I_\X &
					\text{if}~ \alpha \in \Omega^{n-1}
				\end{array}
			\right\rbrace\right.
		\end{displaymath}
	\end{defpropblock}
	%
	\pause
	%
	\begin{thmblock}[Blacker - M. - Ryvkin]%[Reduced $L_\infty$-algebra of observables]
		The reduction of $L_\infty(M,\omega)$  with respect to $\g\curvearrowright (N\subset M)$ is the %$L_\infty$-algebra
		quotient
		\begin{displaymath}
					L_\infty(M,\omega)_N = \frac{L_\infty(M,\omega)_{[N]}}{I_{\L_\infty}(N)}~.		
		\end{displaymath}
	\end{thmblock}

\end{frame}
\note[itemize]{
 \item The graded vector space underlying the reduced $L_\infty$-algebra $\Ham_\infty(M,\omega)_N$ is explicitly given by
\begin{displaymath}
	\Ham_\infty(M,\omega)_N =
	\frac{
		\left\lbrace
			(\alpha,v) \in \Omega(M){[n{-}1]}\oplus\X(M)
		~\left\vert~
			\begin{array}{l l}
				\iota_v \omega = -\d \alpha^{(0)} &
				\\
				\iota_\xi \alpha \in I_{\Omega}(N) &
				\\
				\L_\xi\alpha \in I_{\Omega}(N)
				&
				\\
				\L_\xi v \in \fgmodule +\vanvf
				&~\forall \xi \in \g 
				\\
				v \in \X_N(M)
				&
			\end{array}
		\right.
		\right\rbrace
	}{
		\left\lbrace
			(\alpha,v) \in \Omega(M){[n{-}1]}\oplus\X(M)
		~\left\vert~
			\begin{array}{l}
				\alpha \in I_{\Omega}(N)
				\\
				v \in \fgmodule +\vanvf
			\end{array}
		\right.
		\right\rbrace
	}~.
\end{displaymath}
}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}{Singular reduction (Conclusions)}
		  \centering 
	\emph{Reduction of states vs.\ reduction of observables}
	\vfill
	\begin{minipage}{.7\textwidth}
	\hspace{-.4cm}
	\begin{tikzpicture}
		\draw (-4,-2.5) rectangle (4,2.5);
		\draw (-4,0) -- (4,0);
		\draw (0,-2.5) -- (0,2.5);

		\draw node[align=center] at (-2,1.25) {symplectic\\ reduction};
		\draw node[align=center] at (2,1.25) {multisymplectic\\ reduction};
		\draw node[align=center] at (-2,-1.25) {\'{S}niatycki--Weinstein,\\Dirac,\\Arms--Gotay--Jennings\\ reduction};
		\draw node[align=center] at (2,-1.25) {\color{UniGreen}$L_\infty$ reduction};

		\draw node[align=center] at (2,2.85) {\color{UniGreen}\emph{higher}};
		\draw node[align=center] at (-2,2.85) {\emph{lower}};

		\draw node[align=right] at (-4.7,1.25) {\emph{states}};
		\draw node[align=right] at (-5.13,-1.25) {\color{UniGreen}\emph{observables}};
	\end{tikzpicture}
	\end{minipage}

	\pause
			\vfill
		  \centering 
		  {\Huge\color{red} 
		  \emph{Thank you for your attention!}}
\end{frame}
\note[itemize]{
 \item Consider $N=\mu^{-1}(0)$ to be regular (smooth embedding)
		\vspace{.5em}
		\begin{table}[]
			\begin{tabular}{ccc}
			Multisymplectic               &                      & Multisymplectic                  \\
			regular                       & $\equiv$             & singular                \\
			reduction & & reduction
			\end{tabular}
		\end{table}

		\item
			Consider $\omega$ to be $1$-plectic
			\vspace{.5em}
			\begin{table}[]
				\begin{tabular}{ccc}
				Multisymplectic               &                      &  Sniaticky--Weinstein                  \\
				singular                       & $\cancel\equiv$             & singular                \\
				reduction & & reduction
				\end{tabular}
			\end{table}

			(but $\exists$ a canonical Poisson algebra morphism)

}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%------------------------------------------------------------------------------------------------
% APPENDIX
%------------------------------------------------------------------------------------------------
\appendix
%-------------------------------------------------------------------------------------------------------------------------------------------------
\section{Complementary Material}
%##################################################################################
\begin{frame}
	\begin{center}
	\Huge\emph{Supplementary Material}
	\end{center}
\end{frame}
\note[itemize]{
	\item
}
\addtocounter{framenumber}{-1}
%##################################################################################

%------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{MS geometry and classical field mechanics}\label{Frame:Ms-Field-Mechanics}
		Consider a smooth manifold $Y$,
		\begin{columns}
			\hfill
			\begin{column}{.5\linewidth}
				\emph{Multicotangent bundle} $\bigwedge = \bigwedge^n T^\ast Y$\\
				is naturally $n$-plectic
			\end{column}
			\begin{column}{.4\linewidth}
				\[
				\begin{tikzcd}
					\Lambda \ar[d,"\pi"'] & T \Lambda \ar[d,"T \pi"] \ar[l] \\
					Y								& T Y \ar[l]
				\end{tikzcd}	
				\]
			\end{column}
		\end{columns}
	\pause
	\begin{defblock}[Tautological $n$-form]
		$\theta \in \Omega^n(\Lambda)$ such that:
		\begin{displaymath}
		\begin{split}
			\left[ \iota_{u_1 \wedge \ldots \wedge u_n} \theta \right]_\eta 
			&= \iota_{(T \pi)_\ast u_1 \wedge \ldots \wedge (T \pi)_\ast u_n} \eta \\
			&= \iota_{u_1 \wedge \ldots \wedge u_n} \pi^\ast \eta 
			\qquad \qquad \forall \eta \in \Lambda \, , \: \forall u_i \in T_\eta \Lambda 		
		\end{split}
		\end{displaymath}
	\end{defblock}
	\vfill
	\begin{columns}
		\begin{column}{.6\linewidth}
			\begin{defblock}[Tautological (multisymplectic) (n+1)-form]
				$$\omega := d \theta$$
			\end{defblock}
		\end{column}
		\begin{column}{.4\linewidth}
		 	\begin{claimblock}$\omega$ is not degenerate.\end{claimblock}	
		\end{column}
	\end{columns}	
	\pause
	\begin{keywordblock}
		\begin{tabular}{|c|c|c|}
			\hline 
			point-particles mechanics & $\rightsquigarrow$ & classical fields mechanics \\
			%(finite discrete DOF) & & (finite dimensional continuous DOF) \\
			\hline 
			symplectic & $\rightsquigarrow$ & multisymplectic \\ 
			\hline 
			Observables (Poisson) algebra & $\rightsquigarrow$ & Observables $L-\infty$ algebra
			 \\ 
			\hline 
			Co-moment map & $\rightsquigarrow$ & Homotopy co-momentum map \\ 
			\hline 
		\end{tabular} 
	\end{keywordblock}

\end{frame}
\note[itemize]{
	\item This example is significant from the perspective of geometric classical field theory:
		\begin{displaymath}
			\frac{\text{classical mechanics}}{\text{symplectic geo.}} =
			\frac{\text{classical field mechanics}}{\text{multisymplectic geo.}}
		\end{displaymath}
	\item Multicotangent bundle is the \emph{Higher analogue} of the cotangent bundle.
	(but it is not yet the analogue of a \emph{phase space}.)
\item The multiphase space is the sub-bundle of $n$-forms vanishing when contracted with 2 vertical fields.
  	\item The reason why this sub-bundle has a particular role is that it can be proved to be isomorphic to a suitable dual of the first Jet bundle.
  	\item For further details see Gotay et al. \href{https://arxiv.org/abs/physics/9801019}{arXiv:physics/9801019}. For a pictorial representation of all the structures involved in the geometric mechanics of I order classical field theories see appendix, pag: \ref{frame:Gimmsy}.
}
%------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[t]{Symmetries in \textbf{multisymplectic geometry}}
	Consider a Lie algebra action $v:\mathfrak{g} \to \mathfrak{X}(M)$  preserving the $n$-plectic form $\omega$,
	\vfill

	\vspace{-1em}
	\begin{columns}[T]
		\setlength{\belowdisplayskip}{5pt}
		\begin{column}{.50\linewidth}
			%
			\centering \it
			\onslide<2->{
				$-$ symplectic case $-$
				\begin{defblock}[Comoment map pertaining to $v$]
					Lie algebra morphism
					$$ f: \mathfrak{g} \to C^\infty(M) $$
					such that
					$$ d~f (x) = -\iota_{v_x} \omega \qquad \forall x \in \mathfrak{g}~.$$
				\end{defblock}
			}
		\end{column}	
		%
		\onslide<2->{\vrule{}}
		%
		\begin{column}{.50\linewidth}
			\centering \it
			\onslide<3->{			
				$-$ $n$-plectic case $-$
				\begin{defblock}[Homotopy comoment map \tiny (HCMM)]
					$L_\infty$-morphism 
					$$ (f_k) : \mathfrak{g} \to L_\infty (M,\omega)$$
					such that
					$$ d~f_1(x) = -\iota_{v_x} \omega \qquad \forall x \in \mathfrak{g}~.$$
				\end{defblock}	
			}
		\end{column}	
	\end{columns}	
	%
	\pause
	\vfill
	\centering 
	\onslide<4->{\textbf{-- Conserved quantities --}}
	%
	\vspace{-.5em}
	\begin{columns}[T]
		\setlength{\belowdisplayskip}{5pt}
		\begin{column}{.50\linewidth}
			%
			\centering \it
			\onslide<4->{
			\begin{propblock}[Noether Theorem]
				\small Fixed $H\in C^\infty_{\text{Ham}}(M)$ ($\mathfrak{g}$-invariant) ,
				$$\mathcal{L}_{v_H} f(x) = 0 \qquad \forall x \in \mathfrak{g}$$
			\end{propblock}
			}
		\end{column}	
		%
		\onslide<5->{\vrule{}}
		%
		\begin{column}{.50\linewidth}
			\centering \it
			\onslide<5->{			
			\begin{propblock}[RWZ16 Theorem]
				\small Fixed $H\in \Omega^{n-1}_{\text{Ham}}(M)$ ($\mathfrak{g}$-invariant),
				$$\mathcal{L}_{v_H} f_k(p) \in B^k(M) \qquad \forall p \in Z_k(\mathfrak{g})$$			
			\end{propblock}
			}
		\end{column}	
	\end{columns}		
\end{frame}
\note{
}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%------------------------------------------------------------------------------------------------
\begin{frame}{Reminder: $L_\infty$ Algebras}

		\emph{
			$L_\infty$-algebra is the notion that one obtains from a Lie algebra when one requires the Jacobi identity to be satisfied only up to a higher coherent chain homotopy.
		}
		\\
		\vspace{.5em}
		\begin{defblock}[$L_\infty$-algebra ~\emph{(Lada, Markl)} ~\cite{Lada1995}]
			\includestandalone{Pictures/Figure_Linfinitydef}
		\end{defblock}	
		%
		%
	\pause
	\vfill
	\begin{thmblock}[Rogers \cite{Rogers2010}]
		The \emph{higher observable algebra} $L_{\infty}(M,\omega)$ 	forms an honest $L_\infty$ algebra.
		\footnotetext{ Take $\mu_1 = \text{d}$, $\mu_k=\lbrace\dots\rbrace_k$, $L$ is a shifted truncation of the de Rham complex.}
	\end{thmblock}
\end{frame}
\note[itemize]{
	\item $L_\infty$-algebra is the notion obtained from a Lie algebra requiring that the Jacobi identity is satisfied only up to a higher coherent chain homotopy.
	\item The Lie-n algebra mentioned before is a $L_\infty$ algebra with underlying graded vector space concentrated in degrees $0,1...n$.

	\item Definition. We say that a permutation $\sigma \in S_n$ is a $(j,n-j)$-unshuffle, $0\leq j \le1 n$  if $\sigma(1)< \dots < \sigma(j)$ and $\sigma(j+1)<\dots<\sigma(n)$.
	\\
	You can also say that $\sigma$ is a $(j,n-j)$-unshuffle if $\sigma(i)< \sigma(i+1)$ when $i\neq j$.

	\item 	Alternatively, the Jacobiators can be also denoted as $$\displaystyle J_m=\sum_{i+j=m+1} 	\mu_i \triangleleft \mu_j = 0$$
	employing the so-called \emph{ Richardson-Nijenhuis product}
		 $$\mu_i\circ \mu_j := (-)^{i(j+1)}\frac{1}{j!(i-1)!}\mu_i \triangleleft \mu_j\otimes \mathbb{1}_{i-1} \circ \mathcal{A}~,$$
		 where $\mathcal{A}$ denotes the (graded) total skew-symmetrizator.

	\item see frame extra-\ref{Frame:unwapping-Jacobi} for a slightly demystification of the higher Jacobi equations.

	\item more precisely this statement is a proposition/definition

}
%------------------------------------------------------------------------------------------------

	%\input{msconstraints-aknowledgements}
%------------------------------------------------------------------------------------------------

%------------------------------------------------------------------------------------------------
\end{document}

### 2025-01-11 msconstraints-short.tex
Old slides still not working...

@@
 
-%- D0cum3nt ----------------------------------------------------------------------------------------------
+%- Document ----------------------------------------------------------------------------------------------
 \ifHandout
@@
 \usepackage{xfrac}
+\usepackage{graphicx}
+\usepackage{enumitem}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{tikz}
+\usetikzlibrary{backgrounds}
 
@@
 \renewcommand{\ham}{\text{ham}}
-\usepackage{graphicx}
-\usepackage{enumitem}
-\usepackage{amsmath}
-\usepackage{amssymb}
 
@@
 
-%- T1tle P4g3 -------------------------------------------------------------------------------------------
+%- Title Page -------------------------------------------------------------------------------------------
 \title{ Constraint Algebras \\ of Multisymplectic Observables } 
@@
 %---------------------------------------------------------------------------------------------------------------------------------------------------
-%- D0cum3nt ----------------------------------------------------------------------------------------------------------------------------------
+%- Document ----------------------------------------------------------------------------------------------------------------------------------
 \begin{document}
@@
 
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\section{Symplectic Reduction}
-\checkpoint	
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}{Symplectic geometry (mechanics flavour)}
-\begin{columns}[T]
-	\begin{column}{.50\linewidth}
-		\centering
-		\textit{ "geometric approach" to mechanics \dots}
-		%
-		\begin{columns}
-			\begin{column}{.60\linewidth}
-				\begin{center}
-					\includegraphics[width=0.6\linewidth]{Pictures/pendulum13}			
-				\end{center}
-			\end{column}	
-			\begin{column}{.40\linewidth}
-				\begin{center}
-					\includegraphics[width=0.45\linewidth]{Pictures/pendulum-phase-space}			
-				\end{center}
-			\end{column}	
-		\end{columns}
-		%
-		\begin{defblock}[Symplectic Manifold]
-			\vspace{-1em}
-			\includestandalone[width=1\textwidth]{Pictures/Figure_sym}	
-		\end{defblock}
-		%
-		\pause
-		\begin{exblock}[$M = T^\ast Q$ is symplectic]
-			with $\omega = d \theta $ given by
-			$$ \left.\theta\right\vert_{(q,p)} (v) = p (\pi_\ast v) ~.$$
-		\end{exblock}
-		%
-		\pause
-		\vspace{1.2em}
-		\centering
-		\textit{ based on the notion of \\"states".}		
-	\end{column}
-	\onslide<1->{\vrule{}}
-	\pause
-	\begin{column}{.50\linewidth}
-		\centering
-		\textit{ "algebraic approach" to mechanics \dots}
-		\vspace{.5em}	
-		\begin{defblock}[Classical Observables]
-			Unital, associative, commutative algebra $C^\infty(M)$.
-		\end{defblock}
-		%
-		\vspace{.1em}
-		\pause
-		\begin{defblock}[Hamiltonian vector fields]
-			$\vHam_f \in \mathfrak{X}(M)$ such that:
-			$$\iota_{\vHam_f} \omega = -df \quad$$ %$\in B^1(M)$
-			%
-			\footnotetext{	$\vHam_f$ = \emph{Ham.v.f. pertaining to $f\in C^\infty(M)$}.}
-		\end{defblock}
-		\vspace{.1em}
-		%
-		\begin{defblock}[Poisson Algebra of Observables]
-			$C^\infty(M)$ is a Poisson algebra with
-			$$\{f,g\} = \iota_{\vHam_g} \iota_{\vHam_f} \omega = \omega(\vHam_f,\vHam_g) ~.$$
-		\end{defblock}
-		%
-		\pause
-		\vspace{.15em}
-		\centering
-		\textit{ based on the notion of \\"measurable quantities".}						
-	\end{column}
-\end{columns}
-\end{frame}
-\note[itemize]{
-	\footnotesize
-
-	\item We work in the framework of multisymplectic geometry which is one of the possible generalizations of the well-established field of symplectic geometry.
-
-	\item To recall what symplectic geometry is let me assume a particular point of view: mechanics.
-	\\
-	Idea:"
-	Symplectic geometry is a branch of differential geometry studying symplectic manifolds; it originated as a formalization of the mathematical apparatus of classical mechanics and geometric optics."{\href{https://ncatlab.org/nlab/show/symplectic+geometry}{nlab}}
-
-	Namely, a sym. mfd. is the geometric structure encoding the phase space of conservative, ordinary, classical, mechanical systems.
-
-	\item $\theta$ = \emph{tautological 1-form}.
-		$\theta$ evaluated at $p\in T^*Q$ in the fibre of $q\in Q$ and contracted with $v$ coincides with the form $p$ evaluated at $q$ and contracted with the push forward of $v$.
-
-	\item We identify a special class of vector fields.
-		Out of them one can define a Lie bracket.
-
-	\item Poisson is a Lie algebra with the extra property of compatibility with the associative product (Leibniz rule)
-
-	\item take away message: geometric (based on "states") vs algebraic (based on "measurable quantities").7
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%------------------------------------------------------------------------------------------------
-\begin{frame}{Reminder: momentum maps in symplectic geometry}\label{frame:symplecticmomaps}
-	Consider $\theta:G\curvearrowright M$ symplectic,~~ $\underline{\cdot}:\mathfrak{g}\to \mathfrak{X}(M)$ infinitesimal action.
-	\vfill
-
-	\begin{columns}[T]
-		\setlength{\belowdisplayskip}{5pt}
-		\begin{column}{.50\linewidth}
-			%
-			\centering \it
-			\onslide<2->{
-				\begin{defblock}[Equivariant moment map]
-					Smooth map $$\mu:M\to \mathfrak{g}^\ast$$
-					such that:
-					\begin{itemize}
-						\item[i.] $d\langle \mu,\xi\rangle = -\iota_{\underline{\xi}}\omega$ 
-						~\qquad, $\forall \xi \in \mathfrak{g}$
-						\item[ii.] $\mu \circ \theta_g = Ad_g^\ast \circ \mu$
-						 \qquad\small, $\forall g \in G$
-					\end{itemize}
-				\end{defblock}
-			}
-		\end{column}	
-		%
-		\onslide<2->{\vrule{}}
-		%
-		\begin{column}{.50\linewidth}
-			\onslide<3->{			
-				\begin{defblock}[Comoment map]
-					Linear map $$\widetilde{\mu}: \mathfrak{g}\to C^\infty(M,\omega)$$
-					such that:
-					\begin{itemize}
-						\item[i.] $d\widetilde{\mu}(\xi) = -\iota_{\underline{\xi}}\omega$ 
-						\qquad~\small, $\forall \xi \in \mathfrak{g}$
-						\item[ii.] $\widetilde{\mu}([\xi,\eta]) = \lbrace\widetilde{\mu}(\xi),\widetilde{\mu}(\eta)\rbrace$ \small, $\forall \xi,\eta \in \mathfrak{g}$
-					\end{itemize}
-				\end{defblock}
-			}
-		\end{column}	
-	\end{columns}	
-	%
-	\pause
-	\vspace{1em}
-	%
-	\begin{columns}[]
-		\setlength{\belowdisplayskip}{5pt}
-		\begin{column}{.40\linewidth}
-			%
-			\centering \it
-			\onslide<5->{
-				\begin{upshotblocktitle}[Duality]
-					\begin{displaymath}
-						\mu(x) : \mathfrak{\xi} \mapsto \widetilde{\mu}(\xi)\big\vert_x
-					\end{displaymath}
-					%
-					\emph{
-					\small
-					"duality wrt. the currying operation"					
-					}
-				\end{upshotblocktitle}
-			}
-		\end{column}	
-		%
-		%
-		\begin{column}{.60\linewidth}
-			\onslide<4->{			
-				\begin{upshotblocktitle}[$\widetilde{\mu}$ as a lift]
-					\begin{displaymath}
-						\begin{tikzcd}[ampersand replacement = \&]
-						 \& C^\infty(M,\omega) \ar[d,"\vHam"]
-						 \\
-						 \mathfrak{g} \ar[ur,dashed,sloped,"\widetilde{\mu}"]\ar[r,"\underline{\cdot}"'] \& \mathfrak{X}(M)
-						\end{tikzcd}
-					\end{displaymath}
-					%
-					\emph{
-					\small
-					"it is a lift (in the Lie category) of the infinitesimal action by the assigment of hamiltonian v.fields."					
-					}
-				\end{upshotblocktitle}
-			}
-		\end{column}	
-	\end{columns}		
-\end{frame}
-\note[itemize]{
-	\item consider an action preserving the symplectic form.
-	\item[-] $\langle \cdot, \cdot \rangle$ is the natural pairing of $\mathfrak{g}$ and $\mathfrak{g}^\ast$.
-		\item[-] $\theta_g$ is the diffeomorphism associated to $g\in G$ via $\theta:G\curvearrowright M$
-		\item[-] $Ad^\ast_g$ is the coadjoint action $G\curvearrowright \mathfrak{g}^\ast$
-	\item The moment map can be reexpressed as a comomentum map.
-	\item Observe that ii. on the left always implies ii. on the right. The converse is trure only if $G$ is connected.
-	\item $G\curvearrowright M$ is said "Hamiltonian" (see slide \ref{frame:gisthamaction} in appendix) iff $\exists$ comoment map $\widetilde{\mu}$.
-	\item \emph{moment map: Describe ${\color{orange}G\curvearrowright M}$ in terms of $\color{blue}C^\infty(M)\to\X(M)$.}
-	\begin{center}
-	\begin{tikzpicture}[scale=1.5]
-		\node[orange] (A) at (0,0) {$\g$};
-		\node[gray] (A1) at (0,-.3) {$\xi$};
-		\node[blue] (B) at (1,1) {$C^\infty(M)$};
-		\node[gray] (B2) at (1.55,1) {$f$};
-		\node[orange] (C) at (1,0) {$\X(M)$};
-		\node[gray] (C1) at (1,-.3) {$\underline\xi$};
-		\node[gray] (C2) at (1.55,0) {$X_f$};
-
-		\path[->,blue,dashed] (A) edge node[above left] {$\langle\mu,\cdot\,\rangle$} (B);
-		\path[->,orange] (A) edge (C);
-		\path[->] (B) edge (C);
-		\path[|->,gray] (A1) edge (C1);
-		\path[|->,gray] (B2) edge (C2);
-
-		\begin{scope}[xshift=3cm]
-			\node at (-.32,.8) {as Lie algebras};
-			\node at (-.13,.2) {i.e., {\color{blue}$\mu_\xi$} generates {\color{orange}$\underline\xi$}};
-		\end{scope}
-	\end{tikzpicture}
-
-		\footnotesize		(\emph{moment map:} ${\color{blue}\mu:M\to\g^*}$, 
-	 \emph{Hamiltonian $G$-space:} 	$(M,\omega,G,\mu)$)
-	\end{center}
-	\item
-	 $\alpha\mapsto X_\alpha$ is a homomorphism of Leibniz algebras:
-	$$\d\{\alpha,\beta\} = \d\L_{X_\alpha}\beta = \L_{X_\alpha}\iota_{X_\beta}\omega = \iota_{[X_\alpha,X_\beta]}\omega ~{\color{black!80} \implies}~
-	X_{\{\alpha,\beta\}} = [X_\alpha,X_\beta]$$
-}
-%------------------------------------------------------------------------------------------------
-
-\subsection{Regular reduction}
-%------------------------------------------------------------------------------------------------
-\begin{frame}{Regular reduction in symplectic geometry}
-	\textbf{\color{UniGreen}Symplectic reduction:}~~
-	\\ 
-	{\it \small
-	Procedure associating to any (suitably regular) pair of symplectic manifold and Hamiltonian action another symplectic manifold of smaller dimension.}
-	\vfill
-	\pause
-	\begin{thmblock}[Marsden-Weinstein reduction \cite{MarsdenWeinstein74}]
-		\vspace{-.4em}\hspace{-1em}
-		\begin{tabular}{l p{14cm}}
-		    Given: & $(M,\omega)$ symplectic
-		    \\
-		    & $G\curvearrowright M$ symplectic with equivariant momap. $\mu:M\to \mathfrak{g}^*$
-		    \\[.2em]
-		    Assume: & $\phi \in \mathfrak{g}^*$ regular value of $\mu$ 
-		    \qquad\quad \footnotesize \textcolor{gray}{($\Rightarrow$ $\mu^{-1}(\phi)\hookrightarrow M$ smooth embedding)}
-		    \\
-			& $G_\phi\curvearrowright \mu^{-1}(\phi)$ free and proper
-			\quad \footnotesize \textcolor{gray}{($\Rightarrow$ $\mu^{-1}(\phi)/G_\phi$ smooth manifold)}
-			\\[.4em]
-			Then: & $\exists!$ symplectic structure $\omega_\phi$ in $M_\phi:= \mu^{-1}(\phi)/G_\phi$ \\
-			& s.t. $\pi^\ast \omega_\phi = j^\ast \omega$ 
-			\qquad {\footnotesize with $j:\mu^{-1}(\phi) \hookrightarrow M$ and $\pi:\mu^{-1}(\phi)\twoheadrightarrow M_\mu$}
-		\end{tabular}
-		\vspace{-.4em}
-	\end{thmblock}
-	%
-	\vfill
-	\pause
-	\begin{columns}
-		\begin{column}{0.40\textwidth}
-			\includegraphics[width=\textwidth]{Pictures/Reduction}
-		\end{column}
-
-		\begin{column}{0.6\textwidth}
-				\textbf{\color{UniGreen}In mechanics:}~~
-				\\
-			{\it \small
-				it embodies the process of restricting the dynamics of the system to the level sets of the conserved quantities pertaining to the symmetry group.		
-			}
-			\\[.2em]
-			\color{gray}\small( e.g. restricting to studying a point-like particle in a central potential by studying it in radial coordinates)
-		\end{column}	
-	\end{columns}	
-\end{frame}
-\note[itemize]{
-	\item {Symplectic Reduction} takes two inputs:
-	\\ 1. Hamiltonian $G$-space $(M,\omega,{\color{orange}G},{\color{blue}\mu})$
-	\\ 2. parameter ${\color{blue}\phi}\in\g^*$
-	\item The \emph{reduced space} is $M_\phi:={\color{blue}\mu^{-1}(\phi)}{\color{orange}/G_\phi}$.
-	\item (Marsden--Weinstein '74, Meyer '73) THM:\\
-		If $\mu^{-1}(\phi)\subset M$ is smooth and $G_\phi\curvearrowright \mu^{-1}(\phi)$ is free and proper, then there is a \textbf{unique symplectic form} $\omega_\phi\in\Omega^2(M_\phi)$ such that $\pi^*\omega_\phi = i^*\omega$.
-
-	\begin{center}
-	\begin{tikzpicture}[scale=2]
-		\node[blue] (A) at (0,0) {$\mu^{-1}(\phi)$};
-		\node[gray] (A1) at (0,.3) {$i^*\omega$};
-		\node[gray] (A2) at (-.6,0) {$\pi^*\omega_\phi$};
-		\node[blue] (B) at (1,0) {$M$};
-		\node[gray] (B1) at (1,.3) {$\omega$};
-		\node[orange] (C) at (0,-.8) {$M_\phi$};
-		\node[gray] (C2) at (-.6,-.8) {$\omega_\phi$};
-
-		\path[right hook->,blue] (A) edge node[above] {$i$} (B);
-		\path[orange,->] (A) edge node[left] {$\pi$} (C);
-		\begin{scope}[xshift=-1.8cm]
-			\node[blue] at (0,0) {\small restrict to $\{\mu=\phi\}$};
-			\node[orange] at (.15,-.4) {\small quotient by $G_\phi$};
-		\end{scope}
-	\end{tikzpicture}
-	\end{center}
-	\item Heuristic Approach to Reduction:
-	\\1. describe $G\curvearrowright M$ in terms of $\omega$ 	\hspace{1cm}
-	({\color{green}moment map $\mu$})
-	\\2. identify a distinguished reduced space \hspace{1cm}
-	({\color{green}reduction at $\mu=0$})
-	\\3. use the ambiguity in 1.\ to obtain a family of reduced spaces \hspace{1cm}
-	({\color{green}reduction at $\mu-\phi=0$, i.e.\ reduction at $\mu=\phi$}
-	\\
-	{\tiny Note: If $G_\phi\neq G$, then $\mu-\phi:M\to\g^*$ is not a moment map for either $G\curvearrowright M$ or $G_\phi\curvearrowright M$.}
-
-}
-%------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Singular reduction}
-\begin{frame}{Symplectic singular reduction schemes}
-	\begin{block}{The gist of singular reduction}
- 		\begin{itemize}
- 			\item[-] when $\mu$ is singular (i.e. $\mu^{-1}(0)$ is not a mfd.), the (geometrically) reduced space may not exist.
- 			\item[-] a \emph{singular reduction scheme} is a procedure to construct a "reduced" algebra of observable out of the given data
- 			\item[-] such that it corresponds to the algebra of observable of the reduced manifold in the regular case.
- 		\end{itemize}
-	\end{block}
- 	%
- 	\pause
- 	%
-	\begin{thmblock}[Sniatycki-Weinstein reduction \cite{SniatyckiWeinstein83}]
-		\vspace{-.4em}\hspace{-1em}
-		\begin{tabular}{l p{14cm}}
-		    Given: & $(M,\omega)$ symplectic
-		    \\
-		    & $G\curvearrowright M$ symplectic with equivariant momap. $\mu:M\to \mathfrak{g}^*$
-			\\[.4em]
-			Then: & 
-			$\displaystyle \left[\sfrac{C^\infty(M)}{I_\mu}\right]^G$
-			admits a Poisson algebra structure 
-			\blfootnote{$I_\mu$ = associative ideal generated by $\widetilde{\mu}(\g)$}			
-			\\
-			& it agrees with the M--W reduction in the regular case.		
-		\end{tabular}
-		\vspace{-.4em}
-	\end{thmblock}
-
-\end{frame}
-\note[itemize]{
- \item Let $(M,\omega,G,\mu)$ be a symplectic Hamiltonian $G$-space.
- \item The \emph{momentum ideal} is the associative ideal $I_\mu\subset C^\infty(M)$ generated by the momenta $\mu_{\xi}$ for any $\xi\in \mathfrak{g}$.
-		Namely
-		\[
-			I_\mu 
-			= 
-			\Big\langle \mu_\xi \Big\rangle_{\xi \in \mathfrak{g}}^{\text{\tiny asso.}} 
-			=
-			\left\{
-				\left.
-					\sum_{i=1}^n f_i ~ \mu_{\xi_i}
-				\right|~
-					f_i \in C^\infty(M),~ \xi_i\in \mathfrak{g},~  1 \leq i \leq n
-			\right\}
-		\]
-
- \item The \emph{\'Sniatycki--Weinstein reduction} is the Poisson algebra
-		\[
-			\left(C^\infty(M)/I_\mu\right)^G.
-		\]
-
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\section{Multisymplectic Geometry}
-\checkpoint	
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}{From symplectic to {multi}symplectic} 
-	%
-	\begin{center}
-		$-$ \emph{multisymplectic means \textbf{going higher} in the degree of $\omega$} $-$
-	\end{center}
-	\pause
-	\begin{defblock}[$n$-plectic manifold ~\emph{(Cantrijn, Ibort, De Le\'on)} \cite{Cantrun2017}]
-		\includestandalone[width=0.95\textwidth]{Pictures/Figure_multisym}	
-	\end{defblock}
-	%
-	\pause
-		\begin{table}
-			\begin{tabular}{c c c}
-				symplectic forms \small($n=1$) & $\leftrightsquigarrow$ & volume forms \small($n= \text{dim}(M)-1$)
-			\end{tabular}
-		\end{table}
-
-	\vfill
-	\pause
-	\begin{block}{Historical motivation}
-		Mechanics: geometrical foundations of \textit{(first-order)} field theories.
-	\end{block}
-	%
-	\begin{table}
-		\ifHandout
-		%
-		\else
-		\only<4>{
-		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
-            \hline
-            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
-            \hline
-            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold &  \\[.25em]
-            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra &  \\[.25em]
-            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map &  
-            \\
-            \hline
-  \multicolumn{1}{c}{}
-            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
-            &  \multicolumn{1}{@{}c@{}}{}              \\
-		\end{tabular}
-		}
-		\fi
-		\onslide<5->{
-		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
-            \hline
-            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
-            \hline
-            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold & multisymplectic manifold \\[.25em]
-            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra & $L_\infty$-algebra \\[.25em]
-            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map & group actions admitting (homotopy) comomentum map
-            \\
-            \hline
-  			\multicolumn{1}{c}{}
-            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
-            &
-            \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{field-theoretic systems}}$} 
-               \\
-		\end{tabular}
-		}
-	\end{table}
-
-\end{frame}
-\note[itemize]{
-	\item Historically, the interest in multisymplectic manifolds, has been motivated by the need for understanding the geometrical foundations of first-order classical field theories.
-	The key point is that, just as one can associate a symplectic manifold to an ordinary classical mechanical system (e.g. a single
-point-like particle constrained to some manifold), it is possible to associate a multisymplectic
-manifold to any classical field system (e.g. a continuous medium like a filament or a fluid). See frame Extra-\ref{Frame:Ms-Field-Mechanics}
-
-	\item General ideas basic parallelisms with caveats
-	\item caveat: points in multiphase spaces are not states
-	\item the table hides the duality between geometric and algebraic approaches to the problem.
-	\item	Mechanics: geometrical foundations of \textit{(first-order)} field theories.
-		\begin{itemize}
-		 \item[-] Kijowski, W. Tulczyjew \cite{Kijowski1979}; %(1979)
-		 \item[-] Cariñena, Crampin, Ibort \cite{Carinena1991b};% (1991)
-		 \item[-] Gotay, Isenberg, Marsden, Montgomery \cite{Gimmsy1};%(1998)
-		 \\ $\cdots$
-		\end{itemize}
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}{Observables in $n$-plectic geometry}
-	%
-	\begin{defblock}[Hamiltonian $(n-1)$-forms]
-		\begin{displaymath}
-			\Omega^{n-1}_{ham}(M,\omega) 	:=
-			\biggr\{ \sigma \in  \Omega^{n-1}(M) \; \biggr\vert \; 
-				\exists \vHam_\sigma \in \mathfrak{X}(M) ~:~ 
-				\tikz[baseline,remember picture]{\node[rounded corners,
-                        fill=orange!5,draw=orange!30,anchor=base]            
-            			(target) {$d \sigma = -\iota_{\vHam_\sigma} \omega$ };
-            	}				
-				~\biggr\} 
-			\end{displaymath}
-	\end{defblock}
-
-	\pause
-		\tikz[overlay,remember picture]
-		{
-			\node[rounded corners,
-                 fill=orange!5,draw=orange!30,anchor=base]
-            	 (base) at ($(current page.north east)-(2,1)$) [rotate=-0,text width=3.5cm,align=center] {\footnotesize{\textcolor{red}{Hamilton-DeDonder-Weyl \\equation}}};
-		}	
-	\begin{tikzpicture}[overlay,remember picture]
-    	\path[->] (base.south) edge[bend right,red](target.north);
-    \end{tikzpicture}
-	%
-	\vfill
-	\begin{columns}[T]
-		\pause
-		\setlength{\belowdisplayskip}{5pt}
-		\begin{column}{.50\linewidth}
-			%
-			\vspace{-1em}
-			\begin{thmblock}[Observables $L_\infty$-algebra]
-				$\Omega^{n-1}_{ham}(M,\omega)$ endowed with
-				\vspace{-.5em}
-				\begin{displaymath}
-					\lbrace \sigma_1, \sigma_2 \rbrace =			
-					~ - \iota_{\vHam_1}\iota_{\vHam_2} \omega 
-				\end{displaymath}			
-				can be "completed" to a \\ $L_\infty-algebra$.
-			\end{thmblock}
-			%	
-		\end{column}	
-		%
-		\pause
-		\begin{column}{.50\linewidth}
-		%
-			\begin{itemize}
-				\item[\cmark] Skew-symmetric;
-				\item[\xmark] multiplication of observables;
-				\item[\xmark] Jacobi equation;
-				%\\ \hspace*{4.25em} full-fledged Jacobi equation;
-				\item[\smark] Jacobi equation \emph{up to homotopies}.
-			\end{itemize}			
-			%
-				\[
-					\small
-					\{\alpha,\{\beta,\gamma\}\} + \text{\it cyc. perm.}
-					= {\color{orange}\d \iota_{X_\alpha} \iota_{X_\beta} \iota_{X_\gamma}\omega}
-				\]
-		\end{column}	
-	\end{columns}
-	%
-	\vfill
-	\pause
-	Interesting alternatives:
-	\begin{itemize}
-		\item  descend to $\Omega^{k-1}_{ham}(M) / {\color{orange}\d\hspace{1pt}\Omega^{k-2}(M)}$, hence getting a Lie algebra;
-		\item Incorporate the {\color{orange}discrepancy} as part of the data of the space of observables $ 
-				L_\infty(M,\omega) = \Omega_{ham}^{k-1}(M)\oplus{\color{orange}\Omega^{\leq k-2}(M)}$
-			%a \textbf{homotopy Lie algebra} or \textbf{$L_\infty$-algebra}.
-	\end{itemize}
-
-\end{frame}
-\note[itemize]{
-	\item
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%---------------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{$L_\infty$-algebra of Observables}
-\begin{frame}[fragile,t]{$L_\infty$-algebra of Observables (higher observables) }
-	Let be $(M,\omega)$ a $n$-plectic manifold.
-	\begin{defblock}[$L_\infty$-algebra of observables ~\emph{(Rogers)} ~\cite{Rogers2010}]
-
-		\hspace{.25em} $L\infty(M,\omega)$ is given by:
-
-		\begin{itemize}
-			\item[•] a cochain-complex $(L,\{\cdot\}_1)$ 
-		\end{itemize}
-		\begin{center}
-		\ifHandout
-			\includestandalone{Pictures/Figure_Observables}	
-		\else
-			\includestandalone{Pictures/Frame_Observables}
-		\fi				
-		\end{center}
-		\onslide<2->{
-			\begin{itemize}
-				\item[•] with $n$ (skew-symmetric) multibrackets $(2 \leq k \leq n+1)$
-			\end{itemize}
-			\begin{center}
-				\includestandalone{Pictures/Equation_Multibracket}	
-			\end{center}
-		}
-		%
-	\end{defblock}
-  \end{frame}
- \note[itemize]{
-	\item if symplectic manifolds are the symmetric take on mechanics, Poisson algebras are the algebraic counterpart.
- 	\item A Lie algebra is associated to an ordinary symplectic manifold (its Poisson algebra).
-	%(Underlying this is a Lie algebra, whose Lie bracket is the Poisson bracket.)
-	Similarly, one associates an Lie-$n$ algebra to any $n$-plectic manifold.
- 	% https://ncatlab.org/nlab/show/n-plectic+geometry 	 
- 	 %https://ncatlab.org/nlab/show/Poisson+bracket+Lie+n-algebra
-	 \item Basically, the higher observables algebra is a chunk of the de Rham complex of $M$ with inverted grading( convention employed here) and an extra structure called "multibrackets".
- 	\item ( In the 1-plectic case it reduces to the corresponding Poisson algebra of classical observables)
- 	\item Rogers associated to any n-plectic mfd a $L\-\infty$ algebra, Zambon generalized it to the pre-n-plectic case.
- 	\item Recognize in the definition of $\{\cdot,\ldots,\cdot\}_k$ the contraction with hamiltonian fields $v_\sigma$ w.r.t. $\sigma$.
-  	\item Note $	\iota_{v_{\sigma_1}}\cdots\iota_{v_{\sigma_k}} = (-)^{(k-1)+(k-2)+\dots+1}\iota_{v_{\sigma_k}}\cdots\iota_{v_{\sigma_1}} = (-)^{\frac{k(k-1)}{2}}\iota_{v_{\sigma_k}}\cdots\iota_{v_{\sigma_1}}$
- 	The definition usually find in literature of Rogers multibrackets involves the coefficient $ (-)^{\frac{k(k-1)}{2}} = -\varsigma(k-1) = (-)^{k+1} \varsigma(k)$.
-  \item higher observables is Special instance of a more general object  called $L\-\infty$ Algebra...
- }
-%------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\section{Multisymplectic observables reduction}
-\checkpoint	
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}{Singular Reduction: Roadmap}
-	%
-	\begin{block}{Data:}
-			\begin{itemize}
-				\item A \emph{constraint set} $N$ (possibly singular),
-				\item An infinitesimal action preserving $N$.
-			\end{itemize}
-	\end{block}
-	%
-	\vfill
-	\pause
-	%
-	\begin{block}{Goal:}
-		\begin{itemize}
-			\item Obtain a "reduced" observables algebra out of the data.
-		\end{itemize}
-	\end{block}
-	%
-	\vfill
-	\pause
-	%
-	\begin{block}{Strategy:}
-		\begin{enumerate}
-			\item Define smooth fields/forms \emph{tangent to $N$},
-			\item define smooth fields/forms \emph{vanishing along $N$},
-			\item define \emph{reducible fields} requiring the preservation of the vanishing objects,
-			\item define \emph{reducible forms} requiring their conservation w.r.t. the infinitesimal action,
-			\item define \emph{reducible and vanishing observables},
-			\item \textbf{quotient}
-		\end{enumerate}
-	\end{block}
-
-\end{frame}
-\note[itemize]{
-	\item
-}
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[shrink]{Smooth objects on a singular set}
-	Consider $N$ closed subset of $M$.
-	\vfill
-	\pause
-	\begin{defblock}
-	 $I_N$ = ideal of smooth functions vanishing over $N$.
-	\end{defblock}
-	\vfill
-	\pause
-
-	\begin{columns}[T]
-		\setlength{\belowdisplayskip}{5pt}
-		\begin{column}{.65\linewidth}
-			%
-			\centering \it
-				\begin{defblock}[v.f tangent to $N$]
-					\begin{displaymath}
-						\X_N(M):=
-						\left\lbrace
-							v \in \X(M)
-						~\Big\vert~
-							\L_v(I_N) \subseteq I_N
-						\right\rbrace
-					\end{displaymath}
-				\end{defblock}
-				\begin{defblock}[v.f vanishing on $N$]
-					\begin{displaymath}
-						I_\X(N):=
-						\left\lbrace
-							v \in \X(M)
-						~\Big\vert~
-							\L_v(C^\infty(M)) \subseteq I_N
-						\right\rbrace
-					\end{displaymath}				
-				\end{defblock}				
-		\end{column}	
-		%
-		%
-		\begin{column}{.35\linewidth}
-			\centering 
-			\includestandalone[width=0.8\textwidth]{Pictures/Figure_VfTangentN}			
-		\end{column}	
-	\end{columns}			
-	%	
-	\pause
-
-				%
-
-				%	
-		\begin{tcolorbox}[
-		enhanced,frame hidden,borderline={0.5pt}{0pt}{blue},
-		arc=5pt,colback=white,
-		colbacktitle=white,]
-			\color{blue}{\textbf{Lem}:} If $N$ is smoothly embedded,  $\X(N)\cong {X_N(M)}/{I_\X}$.
-		\end{tcolorbox}
-
-		\pause
-
-		\begin{defblock}[Differential form vanishing on $N$]
-			\begin{displaymath}
-				I_{\Omega(N)}:=
-				\left\lbrace
-					\alpha\in\Omega^k(M
-				~\left\vert~
-					\begin{array}{l r}
-						k\geq 0,~		\\		
-						\alpha(u_1,\ldots,u_k) \in I_N & \forall u_i \in\X_N(M)
-					\end{array}
-				\right\rbrace\right.
-			\end{displaymath}
-		\end{defblock}
-
-\end{frame}
-\note[itemize]{
- \item $N$ is not a submanifold in general. An example is $N=\mu^{-1}(0)$ for a certain smooth map $N$.
- \item observe that if $N$ is a smooth embedded submanifold, one has that $\X(N)\cong \frac{X_N(M)}{I_\X}$
-
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Multisymplectic singular reduction}
-\begin{frame}{Reducible smooth objects \quad \small (w.r.t. $N$ and $\g\action M$)}
-	Consider $\g \action M$ by vector fields tangent to $N$ % \hfill( fond. distribution $\underline{\g}\subseteq \X_N(M)$)
-	\\
-	\vfill
-	Denote by :  
-	\hspace{1em} $\underline{\g}\subseteq \X_N(M)$ the fundamental distribution,
-	\\
-	\hspace{6.5em}  $\X_g$ the $C^\infty$-module generated by $\underline{\g}$.
-	\\
-	\vfill
-	\begin{defblock}[Reducible v.fields ]
-			\begin{displaymath}
-				\X(M)_{[N]} :=
-				\left\lbrace
-					v \in \X(M)
-				~\left\vert~
-					\begin{array}{l}
-						\L_v (I_N) \subseteq I_N	\\		
-						\L_v (\X_g) \subseteq \X_g + I_\X
-					\end{array}
-				\right\rbrace\right.
-			\end{displaymath}
-%			\blfootnote{
-%			 $\X_g$ = $C^\infty(M)$-module generated by the fundamental distribution.
-%			}
-
-	\end{defblock}	
-	%
-	\pause
-	%
-	\begin{defblock}[Reducible forms ]
-		\begin{displaymath}
-			\Omega(M)_{[N]} :=
-			\left\lbrace
-				\alpha \in \Omega(M)
-			~\left\vert~
-				\begin{array}{l r}
-					\L_\underline{\xi} \,\alpha \in I_{\Omega(N)}	\\		
-					\iota_\underline{\xi} \,\alpha \in I_{\Omega(N)}	& \forall \xi \in \g				\end{array}
-			\right\rbrace\right.
-		\end{displaymath}	
-	\end{defblock}	
-	%
-	\pause
-	\vfill
-	%
-	Let $(M,\omega)$ be a $k$-plectic manifold
-	\begin{defblock}[Reducible Hamiltonian forms]
-		\begin{displaymath}
-			(\Omega(M)_{ham}^{n-1})_{[N]} :=
-			\left\lbrace
-				\alpha \in \Omega(M)_{ham}^{n-1}
-			~\left\vert~
-				\begin{array}{l r}
-					\alpha \text{ is a reducible form} \\
-					\vHam_\alpha \text{ is a reducible v.field}
-				\end{array}
-			\right\rbrace\right.
-		\end{displaymath}	
-	\end{defblock}
-
-\end{frame}
-\note[itemize]{
- \item $\g\action M$ by vector field tangent to $N$ means that $\underline{\xi}\in\X_n(M) \forall \xi \in \g$
- \item Spelling out the definition: reducible vector fields are 
- \\i) v.f. tangent to N 
- \\ii) such that their commutator with any $\underline{\xi}$ lies in $\X_\g$ along $N$.
- \item more algebraically, they stabilize both $I_N$ and $\X_g + I_\X$.
- \item observe that $\L_v I_\X \subseteq I_\X$ since , $\forall u \in I_\X$ $\forall f \in C^\infty(M)$ one has\\
- $(\L_v u) f = \L_{[v,u]} f = \L_v\L_u f - \L_u\L_v f \in I_N$
- \item
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}\frametitle{Hierarchy of auxiliary constructions}
-	\begin{minipage}{\textwidth}
-	\centering
-	\scalebox{.65}{
-	\begin{tikzpicture}
-		\node (A) at (0,10.0) {\fbox{\parbox{5.6cm}{\centering Ideal of functions vanishing on $N$ \\ $I_N$}}};
-		\node (B) at (0,8.3) {\fbox{\parbox{4.4cm}{\centering Vector fields tangent to $N$ \\ $\X_N(M)$}}};
-		\node (C) at (3,6.5) {\fbox{\parbox{4.2cm}{\centering Forms vanishing along $N$ \\ $I_\Omega(N)$}}};
-		\node (D) at (3,4.2) {\fbox{\parbox{2.7cm}{\centering Reducible forms \\ $\Omega(M)_{[N]}$}}};
-		\node (E) at (-3,6.3) {\fbox{\parbox{5.3cm}{\centering Fundamental $C^\infty$-module \emph{plus} \\ vector fields vanishing along $N$ \\ $\X_\g(M)+I_\X(N)$}}};
-		\node (E') at (-3,4.2) {\fbox{\parbox{3.8cm}{\centering Reducible vector fields \\ $\X(M)_{[N]}$}}};
-		\node (F) at (0,2.4) {\fbox{\parbox{3.7cm}{\centering Reducible observables \\ $L_\infty(M,\omega)_{[N]}$}}};
-		\node (G) at (0,0.6) {\fbox{\parbox{5.0cm}{\centering Vanishing ideal of observables \\ $I_{L_\infty}(N)$}}};
-		\node (H) at (0,-1.05) {\fbox{\parbox{4.3cm}{\centering Observable reduced space \\ $L_\infty(M,\omega)_N$}}};
-
-		\draw[->] (A)-- node[right=1pt]{{\scriptsize used to define}} (B);
-		\draw[->] (B)-- (C);
-		\draw[->] (C)-- node[right=.25cm]{\rotatebox{-90}{\small $\subset$}} (D);
-		\draw[->] (B)-- (E);
-		\draw[->] (D)-- (F);
-		\draw[->] (E)-- node[left=.25cm]{\rotatebox{-90}{\small $\subset$}} (E');
-		\draw[->] (E')-- (F);
-		\draw[->] (F)-- node[right=.25cm]{\rotatebox{90}{\small $\subset$}} (G);
-		\draw[->] (G)-- (H);
-
-		\node[right=2.95cm] at (A) {\scriptsize\emph{associative ideal}};
-		\node[right=2.30cm] at (B) {\scriptsize\emph{Lie algebra}};
-		\node[right=2.25cm] at (C) {\scriptsize\emph{differential ideal}};
-		\node[right=1.5cm] at (D) {\scriptsize\emph{differential graded subalgebra}};
-		\node[left=2cm] at (E') {\scriptsize\emph{Lie subalgebra}};
-		\node[left=2.8cm] at (E) {\scriptsize\emph{Lie ideal}};
-		\node[right=2cm] at (F) {\scriptsize\emph{$L_\infty$-subalgebra}};
-		\node[right=2.65cm] at (G) {\scriptsize\emph{$L_\infty$-ideal}};
-		\node[right=2.3cm] at (H) {\scriptsize\emph{$L_\infty$-algebra}};
-	\end{tikzpicture}
-	}
-	\end{minipage}
-\end{frame}
-\note[itemize]{
- \item
-}
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}{Multisymplectic observable reduction}
-	\begin{defpropblock}[Reducible $L_\infty$-observables]
-		Is the {\color{blue!70!black}$L_\infty$-subalgebra} of $L_\infty(M,\omega)$ given by
-		\begin{displaymath}
-			L_\infty(M,\omega)_{[N]}^k :=
-			\begin{cases}
-				\Omega^{n-1-k}(M)_{[N]} 
-				\qquad\text{\color{gray}\small (reducible forms) }
-				& \text{if } n-1\leq k < 0 \\
-				(\Omega(M)_{ham}^{n-1})_{[N]} 
-				\quad
-				\text{\color{gray}\small (reducible hamiltonians) }
-				& \text{if } k = 0 \\
-				0 & \text{if } k > 0
-			\end{cases}
-		\end{displaymath}
-	\end{defpropblock}
-	%
-	\pause
-	%
-	\begin{defpropblock}[Vanishing $L_\infty$-observables]
-		Is the {\color{blue!70!black}$L_\infty$-ideal} of $L_\infty(M,\omega)_{[N]}$ given by
-		\begin{displaymath}
-			I_{L_\infty(M,\omega)} :=
-			\left\lbrace
-				\alpha \in L_\infty(M,\omega)_{[N]}
-			~\left\vert~
-				\begin{array}{l l}
-					\alpha(v_1,\dots,v_k) \in I_N  \quad \forall v_i \in \X_N &
-					\text{if}~ \alpha \in \Omega^k \\
-					\vHam_\alpha \in \X_\g + I_\X &
-					\text{if}~ \alpha \in \Omega^{n-1}
-				\end{array}
-			\right\rbrace\right.
-		\end{displaymath}
-	\end{defpropblock}
-	%
-	\pause
-	%
-	\begin{thmblock}[Blacker - M. - Ryvkin]%[Reduced $L_\infty$-algebra of observables]
-		The reduction of $L_\infty(M,\omega)$  with respect to $\g\curvearrowright (N\subset M)$ is the %$L_\infty$-algebra
-		quotient
-		\begin{displaymath}
-					L_\infty(M,\omega)_N = \frac{L_\infty(M,\omega)_{[N]}}{I_{\L_\infty}(N)}~.		
-		\end{displaymath}
-	\end{thmblock}
-
-\end{frame}
-\note[itemize]{
- \item The graded vector space underlying the reduced $L_\infty$-algebra $\Ham_\infty(M,\omega)_N$ is explicitly given by
-\begin{displaymath}
-	\Ham_\infty(M,\omega)_N =
-	\frac{
-		\left\lbrace
-			(\alpha,v) \in \Omega(M){[n{-}1]}\oplus\X(M)
-		~\left\vert~
-			\begin{array}{l l}
-				\iota_v \omega = -\d \alpha^{(0)} &
-				\\
-				\iota_\xi \alpha \in I_{\Omega}(N) &
-				\\
-				\L_\xi\alpha \in I_{\Omega}(N)
-				&
-				\\
-				\L_\xi v \in \fgmodule +\vanvf
-				&~\forall \xi \in \g 
-				\\
-				v \in \X_N(M)
-				&
-			\end{array}
-		\right.
-		\right\rbrace
-	}{
-		\left\lbrace
-			(\alpha,v) \in \Omega(M){[n{-}1]}\oplus\X(M)
-		~\left\vert~
-			\begin{array}{l}
-				\alpha \in I_{\Omega}(N)
-				\\
-				v \in \fgmodule +\vanvf
-			\end{array}
-		\right.
-		\right\rbrace
-	}~.
-\end{displaymath}
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}{Singular reduction (Conclusions)}
-		  \centering 
-	\emph{Reduction of states vs.\ reduction of observables}
-	\vfill
-	\begin{minipage}{.7\textwidth}
-	\hspace{-.4cm}
-	\begin{tikzpicture}
-		\draw (-4,-2.5) rectangle (4,2.5);
-		\draw (-4,0) -- (4,0);
-		\draw (0,-2.5) -- (0,2.5);
-
-		\draw node[align=center] at (-2,1.25) {symplectic\\ reduction};
-		\draw node[align=center] at (2,1.25) {multisymplectic\\ reduction};
-		\draw node[align=center] at (-2,-1.25) {\'{S}niatycki--Weinstein,\\Dirac,\\Arms--Gotay--Jennings\\ reduction};
-		\draw node[align=center] at (2,-1.25) {\color{UniGreen}$L_\infty$ reduction};
-
-		\draw node[align=center] at (2,2.85) {\color{UniGreen}\emph{higher}};
-		\draw node[align=center] at (-2,2.85) {\emph{lower}};
-
-		\draw node[align=right] at (-4.7,1.25) {\emph{states}};
-		\draw node[align=right] at (-5.13,-1.25) {\color{UniGreen}\emph{observables}};
-	\end{tikzpicture}
-	\end{minipage}
-
-	\pause
-			\vfill
-		  \centering 
-		  {\Huge\color{red} 
-		  \emph{Thank you for your attention!}}
-\end{frame}
-\note[itemize]{
- \item Consider $N=\mu^{-1}(0)$ to be regular (smooth embedding)
-		\vspace{.5em}
-		\begin{table}[]
-			\begin{tabular}{ccc}
-			Multisymplectic               &                      & Multisymplectic                  \\
-			regular                       & $\equiv$             & singular                \\
-			reduction & & reduction
-			\end{tabular}
-		\end{table}
-
-		\item
-			Consider $\omega$ to be $1$-plectic
-			\vspace{.5em}
-			\begin{table}[]
-				\begin{tabular}{ccc}
-				Multisymplectic               &                      &  Sniaticky--Weinstein                  \\
-				singular                       & $\cancel\equiv$             & singular                \\
-				reduction & & reduction
-				\end{tabular}
-			\end{table}
-
-			(but $\exists$ a canonical Poisson algebra morphism)
-
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%------------------------------------------------------------------------------------------------
-% APPENDIX
-%------------------------------------------------------------------------------------------------
-\appendix
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\section{Complementary Material}
-%##################################################################################
-\begin{frame}
-	\begin{center}
-	\Huge\emph{Supplementary Material}
-	\end{center}
-\end{frame}
-\note[itemize]{
-	\item
-}
-\addtocounter{framenumber}{-1}
-%##################################################################################
-
-%------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{MS geometry and classical field mechanics}\label{Frame:Ms-Field-Mechanics}
-		Consider a smooth manifold $Y$,
-		\begin{columns}
-			\hfill
-			\begin{column}{.5\linewidth}
-				\emph{Multicotangent bundle} $\bigwedge = \bigwedge^n T^\ast Y$\\
-				is naturally $n$-plectic
-			\end{column}
-			\begin{column}{.4\linewidth}
-				\[
-				\begin{tikzcd}
-					\Lambda \ar[d,"\pi"'] & T \Lambda \ar[d,"T \pi"] \ar[l] \\
-					Y								& T Y \ar[l]
-				\end{tikzcd}	
-				\]
-			\end{column}
-		\end{columns}
-	\pause
-	\begin{defblock}[Tautological $n$-form]
-		$\theta \in \Omega^n(\Lambda)$ such that:
-		\begin{displaymath}
-		\begin{split}
-			\left[ \iota_{u_1 \wedge \ldots \wedge u_n} \theta \right]_\eta 
-			&= \iota_{(T \pi)_\ast u_1 \wedge \ldots \wedge (T \pi)_\ast u_n} \eta \\
-			&= \iota_{u_1 \wedge \ldots \wedge u_n} \pi^\ast \eta 
-			\qquad \qquad \forall \eta \in \Lambda \, , \: \forall u_i \in T_\eta \Lambda 		
-		\end{split}
-		\end{displaymath}
-	\end{defblock}
-	\vfill
-	\begin{columns}
-		\begin{column}{.6\linewidth}
-			\begin{defblock}[Tautological (multisymplectic) (n+1)-form]
-				$$\omega := d \theta$$
-			\end{defblock}
-		\end{column}
-		\begin{column}{.4\linewidth}
-		 	\begin{claimblock}$\omega$ is not degenerate.\end{claimblock}	
-		\end{column}
-	\end{columns}	
-	\pause
-	\begin{keywordblock}
-		\begin{tabular}{|c|c|c|}
-			\hline 
-			point-particles mechanics & $\rightsquigarrow$ & classical fields mechanics \\
-			%(finite discrete DOF) & & (finite dimensional continuous DOF) \\
-			\hline 
-			symplectic & $\rightsquigarrow$ & multisymplectic \\ 
-			\hline 
-			Observables (Poisson) algebra & $\rightsquigarrow$ & Observables $L-\infty$ algebra
-			 \\ 
-			\hline 
-			Co-moment map & $\rightsquigarrow$ & Homotopy co-momentum map \\ 
-			\hline 
-		\end{tabular} 
-	\end{keywordblock}
-
-\end{frame}
-\note[itemize]{
-	\item This example is significant from the perspective of geometric classical field theory:
-		\begin{displaymath}
-			\frac{\text{classical mechanics}}{\text{symplectic geo.}} =
-			\frac{\text{classical field mechanics}}{\text{multisymplectic geo.}}
-		\end{displaymath}
-	\item Multicotangent bundle is the \emph{Higher analogue} of the cotangent bundle.
-	(but it is not yet the analogue of a \emph{phase space}.)
-\item The multiphase space is the sub-bundle of $n$-forms vanishing when contracted with 2 vertical fields.
-  	\item The reason why this sub-bundle has a particular role is that it can be proved to be isomorphic to a suitable dual of the first Jet bundle.
-  	\item For further details see Gotay et al.
-\href{https://arxiv.org/abs/physics/9801019}{arXiv:physics/9801019}.
-For a pictorial representation of all the structures involved in the geometric mechanics of I order classical field theories see appendix, pag: \ref{frame:Gimmsy}.
-}
-%------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[t]{Symmetries in \textbf{multisymplectic geometry}}
-	Consider a Lie algebra action $v:\mathfrak{g} \to \mathfrak{X}(M)$  preserving the $n$-plectic form $\omega$,
-	\vfill
-
-	\vspace{-1em}
-	\begin{columns}[T]
-		\setlength{\belowdisplayskip}{5pt}
-		\begin{column}{.50\linewidth}
-			%
-			\centering \it
-			\onslide<2->{
-				$-$ symplectic case $-$
-				\begin{defblock}[Comoment map pertaining to $v$]
-					Lie algebra morphism
-					$$ f: \mathfrak{g} \to C^\infty(M) $$
-					such that
-					$$ d~f (x) = -\iota_{v_x} \omega \qquad \forall x \in \mathfrak{g}~.$$
-				\end{defblock}
-			}
-		\end{column}	
-		%
-		\onslide<2->{\vrule{}}
-		%
-		\begin{column}{.50\linewidth}
-			\centering \it
-			\onslide<3->{			
-				$-$ $n$-plectic case $-$
-				\begin{defblock}[Homotopy comoment map \tiny (HCMM)]
-					$L_\infty$-morphism 
-					$$ (f_k) : \mathfrak{g} \to L_\infty (M,\omega)$$
-					such that
-					$$ d~f_1(x) = -\iota_{v_x} \omega \qquad \forall x \in \mathfrak{g}~.$$
-				\end{defblock}	
-			}
-		\end{column}	
-	\end{columns}	
-	%
-	\pause
-	\vfill
-	\centering 
-	\onslide<4->{\textbf{-- Conserved quantities --}}
-	%
-	\vspace{-.5em}
-	\begin{columns}[T]
-		\setlength{\belowdisplayskip}{5pt}
-		\begin{column}{.50\linewidth}
-			%
-			\centering \it
-			\onslide<4->{
-			\begin{propblock}[Noether Theorem]
-				\small Fixed $H\in C^\infty_{\text{Ham}}(M)$ ($\mathfrak{g}$-invariant) ,
-				$$\mathcal{L}_{v_H} f(x) = 0 \qquad \forall x \in \mathfrak{g}$$
-			\end{propblock}
-			}
-		\end{column}	
-		%
-		\onslide<5->{\vrule{}}
-		%
-		\begin{column}{.50\linewidth}
-			\centering \it
-			\onslide<5->{			
-			\begin{propblock}[RWZ16 Theorem]
-				\small Fixed $H\in \Omega^{n-1}_{\text{Ham}}(M)$ ($\mathfrak{g}$-invariant),
-				$$\mathcal{L}_{v_H} f_k(p) \in B^k(M) \qquad \forall p \in Z_k(\mathfrak{g})$$			
-			\end{propblock}
-			}
-		\end{column}	
-	\end{columns}		
-\end{frame}
-\note{
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%------------------------------------------------------------------------------------------------
-\begin{frame}{Reminder: $L_\infty$ Algebras}
-
-		\emph{
-			$L_\infty$-algebra is the notion that one obtains from a Lie algebra when one requires the Jacobi identity to be satisfied only up to a higher coherent chain homotopy.
-		}
-		\\
-		\vspace{.5em}
-		\begin{defblock}[$L_\infty$-algebra ~\emph{(Lada, Markl)} ~\cite{Lada1995}]
-			\includestandalone{Pictures/Figure_Linfinitydef}
-		\end{defblock}	
-		%
-		%
-	\pause
-	\vfill
-	\begin{thmblock}[Rogers \cite{Rogers2010}]
-		The \emph{higher observable algebra} $L_{\infty}(M,\omega)$ 	forms an honest $L_\infty$ algebra.
-		\footnotetext{ Take $\mu_1 = \text{d}$, $\mu_k=\lbrace\dots\rbrace_k$, $L$ is a shifted truncation of the de Rham complex.}
-	\end{thmblock}
-\end{frame}
-\note[itemize]{
-	\item $L_\infty$-algebra is the notion obtained from a Lie algebra requiring that the Jacobi identity is satisfied only up to a higher coherent chain homotopy.
-	\item The Lie-n algebra mentioned before is a $L_\infty$ algebra with underlying graded vector space concentrated in degrees $0,1...n$.
-
-	\item Definition. We say that a permutation $\sigma \in S_n$ is a $(j,n-j)$-unshuffle, $0\leq j \le1 n$  if $\sigma(1)< \dots < \sigma(j)$ and $\sigma(j+1)<\dots<\sigma(n)$.
-	\\
-	You can also say that $\sigma$ is a $(j,n-j)$-unshuffle if $\sigma(i)< \sigma(i+1)$ when $i\neq j$.
-
-	\item 	Alternatively, the Jacobiators can be also denoted as $$\displaystyle J_m=\sum_{i+j=m+1} 	\mu_i \triangleleft \mu_j = 0$$
-	employing the so-called \emph{ Richardson-Nijenhuis product}
-		 $$\mu_i\circ \mu_j := (-)^{i(j+1)}\frac{1}{j!(i-1)!}\mu_i \triangleleft \mu_j\otimes \mathbb{1}_{i-1} \circ \mathcal{A}~,$$
-		 where $\mathcal{A}$ denotes the (graded) total skew-symmetrizator.
-
-	\item see frame extra-\ref{Frame:unwapping-Jacobi} for a slightly demystification of the higher Jacobi equations.
-
-	\item more precisely this statement is a proposition/definition
-
-}
-%------------------------------------------------------------------------------------------------
-
-	%\input{msconstraints-aknowledgements}
-%------------------------------------------------------------------------------------------------
-
 %------------------------------------------------------------------------------------------------
 \end{document}
+
+	\includestandalone{msconstraints-aknowledgements}>

### 2025-01-16 msconstraints-symplectic-reduction.tex
Solved compilation errors.

%- HandOut Flag -----------------------------------------------------------------------------------------
\newif\ifHandout
%	\Handouttrue  %uncomment for the printable version

%- D0cum3nt ----------------------------------------------------------------------------------------------
\documentclass[beamer,handout,10pt]{standalone}   
\ifHandout
	\setbeameroption{show notes} %print notes   
\fi

%- Packages ----------------------------------------------------------------------------------------------
\usepackage{custom-style}
\usepackage{math}

%--Beamer Style-----------------------------------------------------------------------------------------------
\usetheme{toninus}

\renewcommand{\action}{\curvearrowright} 
\makeatletter
\def\blfootnote{\gdef\@thefnmark{}\@footnotetext}
\makeatother

%--------------------------------------------------------------------------------------------------
%- D0cum3nt ----------------------------------------------------------------------------------------------------------------------------------
\begin{document}
%------------------------------------------------------------------------------------------------

%------------------------------------------------------------------------------------------------
\begin{frame}{Symplectic geometry (mechanics flavour)}
	\begin{columns}[T]
		\begin{column}{.50\linewidth}
			\centering
			\textit{ "geometric approach" to mechanics \dots}
			%
			\begin{columns}
				\begin{column}{.60\linewidth}
					\begin{center}
						\includegraphics[width=0.6\linewidth]{Pictures/pendulum13}			
					\end{center}
				\end{column}	
				\begin{column}{.40\linewidth}
					\begin{center}
						\includegraphics[width=0.45\linewidth]{Pictures/pendulum-phase-space}			
					\end{center}
				\end{column}	
			\end{columns}
			%
			\begin{defblock}[Symplectic Manifold]
				\vspace{-1em}
				\includestandalone[width=1\textwidth]{Pictures/Figure_sym}	
			\end{defblock}
			%
			\pause
			\begin{exblock}[$M = T^\ast Q$ is symplectic]
				with $\omega = d \theta $ given by
				$$ \left.\theta\right\vert_{(q,p)} (v) = p (\pi_\ast v) ~.$$
			\end{exblock}
			%
			\pause
			\vspace{1.2em}
			\centering
			\textit{ based on the notion of \\"states".}		
		\end{column}
		\onslide<1->{\vrule{}}
		\pause
		\begin{column}{.50\linewidth}
			\centering
			\textit{ "algebraic approach" to mechanics \dots}
			\vspace{.5em}	
			\begin{defblock}[Classical Observables]
				Unital, associative, commutative algebra $C^\infty(M)$.
			\end{defblock}
			%
			\vspace{.1em}
			\pause
			\begin{defblock}[Hamiltonian vector fields]
				$\vHam_f \in \mathfrak{X}(M)$ such that:
				$$\iota_{\vHam_f} \omega = -df \quad$$ %$\in B^1(M)$
				%
				\footnotetext{	$\vHam_f$ = \emph{Ham.v.f. pertaining to $f\in C^\infty(M)$}.}
			\end{defblock}
			\vspace{.1em}
			%
			\begin{defblock}[Poisson Algebra of Observables]
				$C^\infty(M)$ is a Poisson algebra with
				$$\{f,g\} = \iota_{\vHam_g} \iota_{\vHam_f} \omega = \omega(\vHam_f,\vHam_g) ~.$$
			\end{defblock}
			%
			\pause
			\vspace{.15em}
			\centering
			\textit{ based on the notion of \\"measurable quantities".}						
		\end{column}
	\end{columns}
	\end{frame}
	\note[itemize]{
		\footnotesize

		\item We work in the framework of multisymplectic geometry which is one of the possible generalizations of the well-established field of symplectic geometry.

		\item To recall what symplectic geometry is let me assume a particular point of view: mechanics.
		\\
		Idea:"
		Symplectic geometry is a branch of differential geometry studying symplectic manifolds; it originated as a formalization of the mathematical apparatus of classical mechanics and geometric optics."{\href{https://ncatlab.org/nlab/show/symplectic+geometry}{nlab}}

		Namely, a sym. mfd. is the geometric structure encoding the phase space of conservative, ordinary, classical, mechanical systems.

		\item $\theta$ = \emph{tautological 1-form}.
			$\theta$ evaluated at $p\in T^*Q$ in the fibre of $q\in Q$ and contracted with $v$ coincides with the form $p$ evaluated at $q$ and contracted with the push forward of $v$.

		\item We identify a special class of vector fields.
			Out of them one can define a Lie bracket.

		\item Poisson is a Lie algebra with the extra property of compatibility with the associative product (Leibniz rule)

		\item take away message: geometric (based on "states") vs algebraic (based on "measurable quantities").7
	}
	%------------------------------------------------------------------------------------------------

	%------------------------------------------------------------------------------------------------
	\begin{frame}{Reminder: momentum maps in symplectic geometry}\label{frame:symplecticmomaps}
		Consider $\theta:G\curvearrowright M$ symplectic,~~ $\underline{\cdot}:\mathfrak{g}\to \mathfrak{X}(M)$ infinitesimal action.
		\vfill

		\begin{columns}[T]
			\setlength{\belowdisplayskip}{5pt}
			\begin{column}{.50\linewidth}
				%
				\centering \it
				\onslide<2->{
					\begin{defblock}[Equivariant moment map]
						Smooth map $$\mu:M\to \mathfrak{g}^\ast$$
						such that:
						\begin{itemize}
							\item[i.] $d\langle \mu,\xi\rangle = -\iota_{\underline{\xi}}\omega$ 
							~\qquad, $\forall \xi \in \mathfrak{g}$
							\item[ii.] $\mu \circ \theta_g = Ad_g^\ast \circ \mu$
							 \qquad\small, $\forall g \in G$
						\end{itemize}
					\end{defblock}
				}
			\end{column}	
			%
			\onslide<2->{\vrule{}}
			%
			\begin{column}{.50\linewidth}
				\onslide<3->{			
					\begin{defblock}[Comoment map]
						Linear map $$\widetilde{\mu}: \mathfrak{g}\to C^\infty(M,\omega)$$
						such that:
						\begin{itemize}
							\item[i.] $d\widetilde{\mu}(\xi) = -\iota_{\underline{\xi}}\omega$ 
							\qquad~\small, $\forall \xi \in \mathfrak{g}$
							\item[ii.] $\widetilde{\mu}([\xi,\eta]) = \lbrace\widetilde{\mu}(\xi),\widetilde{\mu}(\eta)\rbrace$ \small, $\forall \xi,\eta \in \mathfrak{g}$
						\end{itemize}
					\end{defblock}
				}
			\end{column}	
		\end{columns}	
		%
		\pause
		\vspace{1em}
		%
		\begin{columns}[]
			\setlength{\belowdisplayskip}{5pt}
			\begin{column}{.40\linewidth}
				%
				\centering \it
				\onslide<5->{
					\begin{upshotblocktitle}[Duality]
						\begin{displaymath}
							\mu(x) : \mathfrak{\xi} \mapsto \widetilde{\mu}(\xi)\big\vert_x
						\end{displaymath}
						%
						\emph{
						\small
						"duality wrt. the currying operation"					
						}
					\end{upshotblocktitle}
				}
			\end{column}	
			%
			%
			\begin{column}{.60\linewidth}
				\onslide<4->{			
					\begin{upshotblocktitle}[$\widetilde{\mu}$ as a lift]
						\begin{displaymath}
							\begin{tikzcd}[ampersand replacement = \&]
							 \& C^\infty(M,\omega) \ar[d,"\vHam"]
							 \\
							 \mathfrak{g} \ar[ur,dashed,sloped,"\widetilde{\mu}"]\ar[r,"\underline{\cdot}"'] \& \mathfrak{X}(M)
							\end{tikzcd}
						\end{displaymath}
						%
						\emph{
						\small
						"it is a lift (in the Lie category) of the infinitesimal action by the assigment of hamiltonian v.fields."					
						}
					\end{upshotblocktitle}
				}
			\end{column}	
		\end{columns}		
	\end{frame}
	\note[itemize]{
		\item consider an action preserving the symplectic form.
		\item[-] $\langle \cdot, \cdot \rangle$ is the natural pairing of $\mathfrak{g}$ and $\mathfrak{g}^\ast$.
			\item[-] $\theta_g$ is the diffeomorphism associated to $g\in G$ via $\theta:G\curvearrowright M$
			\item[-] $Ad^\ast_g$ is the coadjoint action $G\curvearrowright \mathfrak{g}^\ast$
		\item The moment map can be reexpressed as a comomentum map.
		\item Observe that ii. on the left always implies ii. on the right. The converse is trure only if $G$ is connected.
		\item $G\curvearrowright M$ is said "Hamiltonian" (see slide \ref{frame:gisthamaction} in appendix) iff $\exists$ comoment map $\widetilde{\mu}$.
		\item \emph{moment map: Describe ${\color{orange}G\curvearrowright M}$ in terms of $\color{blue}C^\infty(M)\to\X(M)$.}
		\begin{center}
		\begin{tikzpicture}[scale=1.5]
			\node[orange] (A) at (0,0) {$\g$};
			\node[gray] (A1) at (0,-.3) {$\xi$};
			\node[blue] (B) at (1,1) {$C^\infty(M)$};
			\node[gray] (B2) at (1.55,1) {$f$};
			\node[orange] (C) at (1,0) {$\X(M)$};
			\node[gray] (C1) at (1,-.3) {$\underline\xi$};
			\node[gray] (C2) at (1.55,0) {$X_f$};

			\path[->,blue,dashed] (A) edge node[above left] {$\langle\mu,\cdot\,\rangle$} (B);
			\path[->,orange] (A) edge (C);
			\path[->] (B) edge (C);
			\path[|->,gray] (A1) edge (C1);
			\path[|->,gray] (B2) edge (C2);

			\begin{scope}[xshift=3cm]
				\node at (-.32,.8) {as Lie algebras};
				\node at (-.13,.2) {i.e., {\color{blue}$\mu_\xi$} generates {\color{orange}$\underline\xi$}};
			\end{scope}
		\end{tikzpicture}

			\footnotesize		(\emph{moment map:} ${\color{blue}\mu:M\to\g^*}$, 
		 \emph{Hamiltonian $G$-space:} 	$(M,\omega,G,\mu)$)
		\end{center}
		\item
		 $\alpha\mapsto X_\alpha$ is a homomorphism of Leibniz algebras:
		$$\d\{\alpha,\beta\} = \d\L_{X_\alpha}\beta = \L_{X_\alpha}\iota_{X_\beta}\omega = \iota_{[X_\alpha,X_\beta]}\omega ~{\color{black!80} \implies}~
		X_{\{\alpha,\beta\}} = [X_\alpha,X_\beta]$$
	}
	%------------------------------------------------------------------------------------------------

	\subsection{Regular reduction}
	%------------------------------------------------------------------------------------------------
	\begin{frame}{Regular reduction in symplectic geometry}
		\textbf{\color{UniGreen}Symplectic reduction:}~~
		\\ 
		{\it \small
		Procedure associating to any (suitably regular) pair of symplectic manifold and Hamiltonian action another symplectic manifold of smaller dimension.}
		\vfill
		\pause
		\begin{thmblock}[Marsden-Weinstein reduction \cite{MarsdenWeinstein74}]
			\vspace{-.4em}\hspace{-1em}
			\begin{tabular}{l p{14cm}}
				Given: & $(M,\omega)$ symplectic
				\\
				& $G\curvearrowright M$ symplectic with equivariant momap. $\mu:M\to \mathfrak{g}^*$
				\\[.2em]
				Assume: & $\phi \in \mathfrak{g}^*$ regular value of $\mu$ 
				\qquad\quad \footnotesize \textcolor{gray}{($\Rightarrow$ $\mu^{-1}(\phi)\hookrightarrow M$ smooth embedding)}
				\\
				& $G_\phi\curvearrowright \mu^{-1}(\phi)$ free and proper
				\quad \footnotesize \textcolor{gray}{($\Rightarrow$ $\mu^{-1}(\phi)/G_\phi$ smooth manifold)}
				\\[.4em]
				Then: & $\exists!$ symplectic structure $\omega_\phi$ in $M_\phi:= \mu^{-1}(\phi)/G_\phi$ \\
				& s.t. $\pi^\ast \omega_\phi = j^\ast \omega$ 
				\qquad {\footnotesize with $j:\mu^{-1}(\phi) \hookrightarrow M$ and $\pi:\mu^{-1}(\phi)\twoheadrightarrow M_\mu$}
			\end{tabular}
			\vspace{-.4em}
		\end{thmblock}
		%
		\vfill
		\pause
		\begin{columns}
			\begin{column}{0.40\textwidth}
				\includegraphics[width=\textwidth]{Pictures/Reduction}
			\end{column}

			\begin{column}{0.6\textwidth}
					\textbf{\color{UniGreen}In mechanics:}~~
					\\
				{\it \small
					it embodies the process of restricting the dynamics of the system to the level sets of the conserved quantities pertaining to the symmetry group.		
				}
				\\[.2em]
				\color{gray}\small( e.g. restricting to studying a point-like particle in a central potential by studying it in radial coordinates)
			\end{column}	
		\end{columns}	
	\end{frame}
	\note[itemize]{
		\item {Symplectic Reduction} takes two inputs:
		\\ 1. Hamiltonian $G$-space $(M,\omega,{\color{orange}G},{\color{blue}\mu})$
		\\ 2. parameter ${\color{blue}\phi}\in\g^*$
		\item The \emph{reduced space} is $M_\phi:={\color{blue}\mu^{-1}(\phi)}{\color{orange}/G_\phi}$.
		\item (Marsden--Weinstein '74, Meyer '73) THM:\\
			If $\mu^{-1}(\phi)\subset M$ is smooth and $G_\phi\curvearrowright \mu^{-1}(\phi)$ is free and proper, then there is a \textbf{unique symplectic form} $\omega_\phi\in\Omega^2(M_\phi)$ such that $\pi^*\omega_\phi = i^*\omega$.

		\begin{center}
		\begin{tikzpicture}[scale=2]
			\node[blue] (A) at (0,0) {$\mu^{-1}(\phi)$};
			\node[gray] (A1) at (0,.3) {$i^*\omega$};
			\node[gray] (A2) at (-.6,0) {$\pi^*\omega_\phi$};
			\node[blue] (B) at (1,0) {$M$};
			\node[gray] (B1) at (1,.3) {$\omega$};
			\node[orange] (C) at (0,-.8) {$M_\phi$};
			\node[gray] (C2) at (-.6,-.8) {$\omega_\phi$};

			\path[right hook->,blue] (A) edge node[above] {$i$} (B);
			\path[orange,->] (A) edge node[left] {$\pi$} (C);
			\begin{scope}[xshift=-1.8cm]
				\node[blue] at (0,0) {\small restrict to $\{\mu=\phi\}$};
				\node[orange] at (.15,-.4) {\small quotient by $G_\phi$};
			\end{scope}
		\end{tikzpicture}
		\end{center}
		\item Heuristic Approach to Reduction:
		\\1. describe $G\curvearrowright M$ in terms of $\omega$ 	\hspace{1cm}
		({\color{green}moment map $\mu$})
		\\2. identify a distinguished reduced space \hspace{1cm}
		({\color{green}reduction at $\mu=0$})
		\\3. use the ambiguity in 1.\ to obtain a family of reduced spaces \hspace{1cm}
		({\color{green}reduction at $\mu-\phi=0$, i.e.\ reduction at $\mu=\phi$}
		\\
		{\tiny Note: If $G_\phi\neq G$, then $\mu-\phi:M\to\g^*$ is not a moment map for either $G\curvearrowright M$ or $G_\phi\curvearrowright M$.}

	}
	%------------------------------------------------------------------------------------------------

	%------------------------------------------------------------------------------------------------
	\subsection{Singular reduction}
	\begin{frame}{Symplectic singular reduction schemes}
		\begin{block}{The gist of singular reduction}
			 \begin{itemize}
				 \item[-] when $\mu$ is singular (i.e. $\mu^{-1}(0)$ is not a mfd.), the (geometrically) reduced space may not exist.
				 \item[-] a \emph{singular reduction scheme} is a procedure to construct a "reduced" algebra of observable out of the given data
				 \item[-] such that it corresponds to the algebra of observable of the reduced manifold in the regular case.
			 \end{itemize}
		\end{block}
		 %
		 \pause
		 %
		\begin{thmblock}[Sniatycki-Weinstein reduction \cite{SniatyckiWeinstein83}]
			\vspace{-.4em}\hspace{-1em}
			\begin{tabular}{l p{14cm}}
				Given: & $(M,\omega)$ symplectic
				\\
				& $G\curvearrowright M$ symplectic with equivariant momap. $\mu:M\to \mathfrak{g}^*$
				\\[.4em]
				Then: & 
				$\displaystyle \left[\sfrac{C^\infty(M)}{I_\mu}\right]^G$
				admits a Poisson algebra structure 
				\blfootnote{$I_\mu$ = associative ideal generated by $\widetilde{\mu}(\g)$}			
				\\
				& it agrees with the M--W reduction in the regular case.		
			\end{tabular}
			\vspace{-.4em}
		\end{thmblock}

	\end{frame}
	\note[itemize]{
	 \item Let $(M,\omega,G,\mu)$ be a symplectic Hamiltonian $G$-space.
	 \item The \emph{momentum ideal} is the associative ideal $I_\mu\subset C^\infty(M)$ generated by the momenta $\mu_{\xi}$ for any $\xi\in \mathfrak{g}$.
			Namely
			\[
				I_\mu 
				= 
				\Big\langle \mu_\xi \Big\rangle_{\xi \in \mathfrak{g}}^{\text{\tiny asso.}} 
				=
				\left\{
					\left.
						\sum_{i=1}^n f_i ~ \mu_{\xi_i}
					\right|~
						f_i \in C^\infty(M),~ \xi_i\in \mathfrak{g},~  1 \leq i \leq n
				\right\}
			\]

	 \item The \emph{\'Sniatycki--Weinstein reduction} is the Poisson algebra
			\[
				\left(C^\infty(M)/I_\mu\right)^G.
			\]

	}
	%------------------------------------------------------------------------------------------------

%------------------------------------------------------------------------------------------------
\end{document}

### 2025-01-17 msconstraints-appendix.tex

%- HandOut Flag -----------------------------------------------------------------------------------------
\newif\ifHandout
%	\Handouttrue  %uncomment for the printable version

%- D0cum3nt ----------------------------------------------------------------------------------------------
\documentclass[beamer,handout,10pt]{standalone}   
\ifHandout
	\setbeameroption{show notes} %print notes   
\fi

%- Packages ----------------------------------------------------------------------------------------------
\usepackage{custom-style}

%--Beamer Style-----------------------------------------------------------------------------------------------
\usetheme{toninus}

%--------------------------------------------------------------------------------------------------
%- D0cum3nt ----------------------------------------------------------------------------------------------------------------------------------
\begin{document}
%------------------------------------------------------------------------------------------------

\section{Complementary Material}
%##################################################################################
\begin{frame}
	\begin{center}
	\Huge\emph{Supplementary Material}
	\end{center}
\end{frame}
\note[itemize]{
	\item
}
\addtocounter{framenumber}{-1}
%##################################################################################

%------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{MS geometry and classical field mechanics}\label{Frame:Ms-Field-Mechanics}
		Consider a smooth manifold $Y$,
		\begin{columns}
			\hfill
			\begin{column}{.5\linewidth}
				\emph{Multicotangent bundle} $\bigwedge = \bigwedge^n T^\ast Y$\\
				is naturally $n$-plectic
			\end{column}
			\begin{column}{.4\linewidth}
				\[
				\begin{tikzcd}
					\Lambda \ar[d,"\pi"'] & T \Lambda \ar[d,"T \pi"] \ar[l] \\
					Y								& T Y \ar[l]
				\end{tikzcd}	
				\]
			\end{column}
		\end{columns}
	\pause
	\begin{defblock}[Tautological $n$-form]
		$\theta \in \Omega^n(\Lambda)$ such that:
		\begin{displaymath}
		\begin{split}
			\left[ \iota_{u_1 \wedge \ldots \wedge u_n} \theta \right]_\eta 
			&= \iota_{(T \pi)_\ast u_1 \wedge \ldots \wedge (T \pi)_\ast u_n} \eta \\
			&= \iota_{u_1 \wedge \ldots \wedge u_n} \pi^\ast \eta 
			\qquad \qquad \forall \eta \in \Lambda \, , \: \forall u_i \in T_\eta \Lambda 		
		\end{split}
		\end{displaymath}
	\end{defblock}
	\vfill
	\begin{columns}
		\begin{column}{.6\linewidth}
			\begin{defblock}[Tautological (multisymplectic) (n+1)-form]
				$$\omega := d \theta$$
			\end{defblock}
		\end{column}
		\begin{column}{.4\linewidth}
		 	\begin{claimblock}$\omega$ is not degenerate.\end{claimblock}	
		\end{column}
	\end{columns}	
	\pause
	\begin{keywordblock}
		\begin{tabular}{|c|c|c|}
			\hline 
			point-particles mechanics & $\rightsquigarrow$ & classical fields mechanics \\
			%(finite discrete DOF) & & (finite dimensional continuous DOF) \\
			\hline 
			symplectic & $\rightsquigarrow$ & multisymplectic \\ 
			\hline 
			Observables (Poisson) algebra & $\rightsquigarrow$ & Observables $L-\infty$ algebra
			 \\ 
			\hline 
			Co-moment map & $\rightsquigarrow$ & Homotopy co-momentum map \\ 
			\hline 
		\end{tabular} 
	\end{keywordblock}

\end{frame}
\note[itemize]{
	\item This example is significant from the perspective of geometric classical field theory:
		\begin{displaymath}
			\frac{\text{classical mechanics}}{\text{symplectic geo.}} =
			\frac{\text{classical field mechanics}}{\text{multisymplectic geo.}}
		\end{displaymath}
	\item Multicotangent bundle is the \emph{Higher analogue} of the cotangent bundle.
	(but it is not yet the analogue of a \emph{phase space}.)
\item The multiphase space is the sub-bundle of $n$-forms vanishing when contracted with 2 vertical fields.
  	\item The reason why this sub-bundle has a particular role is that it can be proved to be isomorphic to a suitable dual of the first Jet bundle.
  	\item For further details see Gotay et al. \href{https://arxiv.org/abs/physics/9801019}{arXiv:physics/9801019}. For a pictorial representation of all the structures involved in the geometric mechanics of I order classical field theories see appendix, pag: \ref{frame:Gimmsy}.
}
%------------------------------------------------------------------------------------------------

%------------------------------------------------------------------------------------------------
\begin{frame}[t]{Symmetries in \textbf{multisymplectic geometry}}
	Consider a Lie algebra action $v:\mathfrak{g} \to \mathfrak{X}(M)$  preserving the $n$-plectic form $\omega$,
	\vfill

	\vspace{-1em}
	\begin{columns}[T]
		\setlength{\belowdisplayskip}{5pt}
		\begin{column}{.50\linewidth}
			%
			\centering \it
			\onslide<2->{
				$-$ symplectic case $-$
				\begin{defblock}[Comoment map pertaining to $v$]
					Lie algebra morphism
					$$ f: \mathfrak{g} \to C^\infty(M) $$
					such that
					$$ d~f (x) = -\iota_{v_x} \omega \qquad \forall x \in \mathfrak{g}~.$$
				\end{defblock}
			}
		\end{column}	
		%
		\onslide<2->{\vrule{}}
		%
		\begin{column}{.50\linewidth}
			\centering \it
			\onslide<3->{			
				$-$ $n$-plectic case $-$
				\begin{defblock}[Homotopy comoment map \tiny (HCMM)]
					$L_\infty$-morphism 
					$$ (f_k) : \mathfrak{g} \to L_\infty (M,\omega)$$
					such that
					$$ d~f_1(x) = -\iota_{v_x} \omega \qquad \forall x \in \mathfrak{g}~.$$
				\end{defblock}	
			}
		\end{column}	
	\end{columns}	
	%
	\pause
	\vfill
	\centering 
	\onslide<4->{\textbf{-- Conserved quantities --}}
	%
	\vspace{-.5em}
	\begin{columns}[T]
		\setlength{\belowdisplayskip}{5pt}
		\begin{column}{.50\linewidth}
			%
			\centering \it
			\onslide<4->{
			\begin{propblock}[Noether Theorem]
				\small Fixed $H\in C^\infty_{\text{Ham}}(M)$ ($\mathfrak{g}$-invariant) ,
				$$\mathcal{L}_{v_H} f(x) = 0 \qquad \forall x \in \mathfrak{g}$$
			\end{propblock}
			}
		\end{column}	
		%
		\onslide<5->{\vrule{}}
		%
		\begin{column}{.50\linewidth}
			\centering \it
			\onslide<5->{			
			\begin{propblock}[RWZ16 Theorem]
				\small Fixed $H\in \Omega^{n-1}_{\text{Ham}}(M)$ ($\mathfrak{g}$-invariant),
				$$\mathcal{L}_{v_H} f_k(p) \in B^k(M) \qquad \forall p \in Z_k(\mathfrak{g})$$			
			\end{propblock}
			}
		\end{column}	
	\end{columns}		
\end{frame}
\note{
}
%------------------------------------------------------------------------------------------------

%------------------------------------------------------------------------------------------------
\begin{frame}{Reminder: $L_\infty$ Algebras}

		\emph{
			$L_\infty$-algebra is the notion that one obtains from a Lie algebra when one requires the Jacobi identity to be satisfied only up to a higher coherent chain homotopy.
		}
		\\
		\vspace{.5em}
		\begin{defblock}[$L_\infty$-algebra ~\emph{(Lada, Markl)} ~\cite{Lada1995}]
			\includestandalone{Pictures/Figure_Linfinitydef}
		\end{defblock}	
		%
		%
	\pause
	\vfill
	\begin{thmblock}[Rogers \cite{Rogers2010}]
		The \emph{higher observable algebra} $L_{\infty}(M,\omega)$ 	forms an honest $L_\infty$ algebra.
		\footnotetext{ Take $\mu_1 = \text{d}$, $\mu_k=\lbrace\dots\rbrace_k$, $L$ is a shifted truncation of the de Rham complex.}
	\end{thmblock}
\end{frame}
\note[itemize]{
	\item $L_\infty$-algebra is the notion obtained from a Lie algebra requiring that the Jacobi identity is satisfied only up to a higher coherent chain homotopy.
	\item The Lie-n algebra mentioned before is a $L_\infty$ algebra with underlying graded vector space concentrated in degrees $0,1...n$.

	\item Definition. We say that a permutation $\sigma \in S_n$ is a $(j,n-j)$-unshuffle, $0\leq j \le1 n$  if $\sigma(1)< \dots < \sigma(j)$ and $\sigma(j+1)<\dots<\sigma(n)$.
	\\
	You can also say that $\sigma$ is a $(j,n-j)$-unshuffle if $\sigma(i)< \sigma(i+1)$ when $i\neq j$.

	\item 	Alternatively, the Jacobiators can be also denoted as $$\displaystyle J_m=\sum_{i+j=m+1} 	\mu_i \triangleleft \mu_j = 0$$
	employing the so-called \emph{ Richardson-Nijenhuis product}
		 $$\mu_i\circ \mu_j := (-)^{i(j+1)}\frac{1}{j!(i-1)!}\mu_i \triangleleft \mu_j\otimes \mathbb{1}_{i-1} \circ \mathcal{A}~,$$
		 where $\mathcal{A}$ denotes the (graded) total skew-symmetrizator.

	\item see frame extra-\ref{Frame:unwapping-Jacobi} for a slightly demystification of the higher Jacobi equations.

	\item more precisely this statement is a proposition/definition

}
%------------------------------------------------------------------------------------------------

%------------------------------------------------------------------------------------------------
\end{document}

### 2025-01-17 msconstraints-multisym-basics.tex

%- HandOut Flag -----------------------------------------------------------------------------------------
\newif\ifHandout
%	\Handouttrue  %uncomment for the printable version

%- D0cum3nt ----------------------------------------------------------------------------------------------
\documentclass[beamer,handout,10pt]{standalone}   
\ifHandout
	\setbeameroption{show notes} %print notes   
\fi

%- Packages ----------------------------------------------------------------------------------------------
\usepackage{custom-style}
\usepackage{math}

%--Beamer Style-----------------------------------------------------------------------------------------------
\usetheme{toninus}
\usepackage{math}

%--------------------------------------------------------------------------------------------------
%- D0cum3nt ----------------------------------------------------------------------------------------------------------------------------------
\begin{document}
%------------------------------------------------------------------------------------------------

%------------------------------------------------------------------------------------------------
\begin{frame}{From symplectic to {multi}symplectic} 
	%
	\begin{center}
		$-$ \emph{multisymplectic means \textbf{going higher} in the degree of $\omega$} $-$
	\end{center}
	\pause
	\begin{defblock}[$n$-plectic manifold ~\emph{(Cantrijn, Ibort, De Le\'on)} \cite{Cantrun2017}]
		\includestandalone[width=0.95\textwidth]{Pictures/Figure_multisym}	
	\end{defblock}
	%
	\pause
		\begin{table}
			\begin{tabular}{c c c}
				symplectic forms \small($n=1$) & $\leftrightsquigarrow$ & volume forms \small($n= \text{dim}(M)-1$)
			\end{tabular}
		\end{table}

	\vfill
	\pause
	\begin{block}{Historical motivation}
		Mechanics: geometrical foundations of \textit{(first-order)} field theories.
	\end{block}
	%
	\begin{table}
		\ifHandout
		%
		\else
		\only<4>{
		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
            \hline
            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
            \hline
            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold &  \\[.25em]
            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra &  \\[.25em]
            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map &  
            \\
            \hline
  \multicolumn{1}{c}{}
            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
            &  \multicolumn{1}{@{}c@{}}{}              \\
		\end{tabular}
		}
		\fi
		\onslide<5->{
		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
            \hline
            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
            \hline
            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold & multisymplectic manifold \\[.25em]
            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra & $L_\infty$-algebra \\[.25em]
            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map & group actions admitting (homotopy) comomentum map
            \\
            \hline
  			\multicolumn{1}{c}{}
            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
            &
            \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{field-theoretic systems}}$} 
               \\
		\end{tabular}
		}
	\end{table}

\end{frame}
\note[itemize]{
	\item Historically, the interest in multisymplectic manifolds, has been motivated by the need for understanding the geometrical foundations of first-order classical field theories.
	The key point is that, just as one can associate a symplectic manifold to an ordinary classical mechanical system (e.g. a single
point-like particle constrained to some manifold), it is possible to associate a multisymplectic
manifold to any classical field system (e.g. a continuous medium like a filament or a fluid). See frame Extra-\ref{Frame:Ms-Field-Mechanics}

	\item General ideas basic parallelisms with caveats
	\item caveat: points in multiphase spaces are not states
	\item the table hides the duality between geometric and algebraic approaches to the problem.
	\item	Mechanics: geometrical foundations of \textit{(first-order)} field theories.
		\begin{itemize}
		 \item[-] Kijowski, W. Tulczyjew \cite{Kijowski1979}; %(1979)
		 \item[-] Cariñena, Crampin, Ibort \cite{Carinena1991b};% (1991)
		 \item[-] Gotay, Isenberg, Marsden, Montgomery \cite{Gimmsy1};%(1998)
		 \\ $\cdots$
		\end{itemize}
}
%------------------------------------------------------------------------------------------------

%------------------------------------------------------------------------------------------------
\begin{frame}{Observables in $n$-plectic geometry}
	%
	\begin{defblock}[Hamiltonian $(n-1)$-forms]
		\begin{displaymath}
			\Omega^{n-1}_{ham}(M,\omega) 	:=
			\biggr\{ \sigma \in  \Omega^{n-1}(M) \; \biggr\vert \; 
				\exists \vHam_\sigma \in \mathfrak{X}(M) ~:~ 
				\tikz[baseline,remember picture]{\node[rounded corners,
                        fill=orange!5,draw=orange!30,anchor=base]            
            			(target) {$d \sigma = -\iota_{\vHam_\sigma} \omega$ };
            	}				
				~\biggr\} 
			\end{displaymath}
	\end{defblock}

	\pause
		\tikz[overlay,remember picture]
		{
			\node[rounded corners,
                 fill=orange!5,draw=orange!30,anchor=base]
            	 (base) at ($(current page.north east)-(2,1)$) [rotate=-0,text width=3.5cm,align=center] {\footnotesize{\textcolor{red}{Hamilton-DeDonder-Weyl \\equation}}};
		}	
	\begin{tikzpicture}[overlay,remember picture]
    	\path[->] (base.south) edge[bend right,red](target.north);
    \end{tikzpicture}
	%
	\vfill
	\begin{columns}[T]
		\pause
		\setlength{\belowdisplayskip}{5pt}
		\begin{column}{.50\linewidth}
			%
			\vspace{-1em}
			\begin{thmblock}[Observables $L_\infty$-algebra]
				$\Omega^{n-1}_{ham}(M,\omega)$ endowed with
				\vspace{-.5em}
				\begin{displaymath}
					\lbrace \sigma_1, \sigma_2 \rbrace =			
					~ - \iota_{\vHam_1}\iota_{\vHam_2} \omega 
				\end{displaymath}			
				can be "completed" to a \\ $L_\infty-algebra$.
			\end{thmblock}
			%	
		\end{column}	
		%
		\pause
		\begin{column}{.50\linewidth}
		%
			\begin{itemize}
				\item[\cmark] Skew-symmetric;
				\item[\xmark] multiplication of observables;
				\item[\xmark] Jacobi equation;
				%\\ \hspace*{4.25em} full-fledged Jacobi equation;
				\item[\smark] Jacobi equation \emph{up to homotopies}.
			\end{itemize}			
			%
				\[
					\small
					\{\alpha,\{\beta,\gamma\}\} + \text{\it cyc. perm.}
					= {\color{orange}\d \iota_{X_\alpha} \iota_{X_\beta} \iota_{X_\gamma}\omega}
				\]
		\end{column}	
	\end{columns}
	%
	\vfill
	\pause
	Interesting alternatives:
	\begin{itemize}
		\item  descend to $\Omega^{k-1}_{ham}(M) / {\color{orange}\d\hspace{1pt}\Omega^{k-2}(M)}$, hence getting a Lie algebra;
		\item Incorporate the {\color{orange}discrepancy} as part of the data of the space of observables $ 
				L_\infty(M,\omega) = \Omega_{ham}^{k-1}(M)\oplus{\color{orange}\Omega^{\leq k-2}(M)}$
			%a \textbf{homotopy Lie algebra} or \textbf{$L_\infty$-algebra}.
	\end{itemize}

\end{frame}
\note[itemize]{
	\item
}
%------------------------------------------------------------------------------------------------

%--------------------------------------------------------------------------------------------------
\subsection{$L_\infty$-algebra of Observables}
\begin{frame}[fragile,t]{$L_\infty$-algebra of Observables (higher observables) }
	Let be $(M,\omega)$ a $n$-plectic manifold.
	\begin{defblock}[$L_\infty$-algebra of observables ~\emph{(Rogers)} ~\cite{Rogers2010}]

		\hspace{.25em} $L\infty(M,\omega)$ is given by:

		\begin{itemize}
			\item[•] a cochain-complex $(L,\{\cdot\}_1)$ 
		\end{itemize}
		\begin{center}
		\ifHandout
			\includestandalone{Pictures/Figure_Observables}	
		\else
			\includestandalone{Pictures/Frame_Observables}
		\fi				
		\end{center}
		\onslide<2->{
			\begin{itemize}
				\item[•] with $n$ (skew-symmetric) multibrackets $(2 \leq k \leq n+1)$
			\end{itemize}
			\begin{center}
				\includestandalone{Pictures/Equation_Multibracket}	
			\end{center}
		}
		%
	\end{defblock}
  \end{frame}
 \note[itemize]{
	\item if symplectic manifolds are the symmetric take on mechanics, Poisson algebras are the algebraic counterpart.
 	\item A Lie algebra is associated to an ordinary symplectic manifold (its Poisson algebra).
	%(Underlying this is a Lie algebra, whose Lie bracket is the Poisson bracket.)
	Similarly, one associates an Lie-$n$ algebra to any $n$-plectic manifold.
 	% https://ncatlab.org/nlab/show/n-plectic+geometry 	 
 	 %https://ncatlab.org/nlab/show/Poisson+bracket+Lie+n-algebra
	 \item Basically, the higher observables algebra is a chunk of the de Rham complex of $M$ with inverted grading( convention employed here) and an extra structure called "multibrackets".
 	\item ( In the 1-plectic case it reduces to the corresponding Poisson algebra of classical observables)
 	\item Rogers associated to any n-plectic mfd a $L\-\infty$ algebra, Zambon generalized it to the pre-n-plectic case.
 	\item Recognize in the definition of $\{\cdot,\ldots,\cdot\}_k$ the contraction with hamiltonian fields $v_\sigma$ w.r.t. $\sigma$.
  	\item Note $	\iota_{v_{\sigma_1}}\cdots\iota_{v_{\sigma_k}} = (-)^{(k-1)+(k-2)+\dots+1}\iota_{v_{\sigma_k}}\cdots\iota_{v_{\sigma_1}} = (-)^{\frac{k(k-1)}{2}}\iota_{v_{\sigma_k}}\cdots\iota_{v_{\sigma_1}}$ 
 	The definition usually find in literature of Rogers multibrackets involves the coefficient $ (-)^{\frac{k(k-1)}{2}} = -\varsigma(k-1) = (-)^{k+1} \varsigma(k)$.
  \item higher observables is Special instance of a more general object  called $L\-\infty$ Algebra...
 }
%------------------------------------------------------------------------------------------------

%------------------------------------------------------------------------------------------------
\end{document}

### 2025-01-18 Spunti/Marvin-intro.tex
Improved referencing to Leo and Marvin.

\documentclass{memoir}
%
% some macro packages
%
\usepackage[utf8]{inputenc}    % smart input of funny chars
\usepackage[T1]{fontenc}       % also for the font encoding
\usepackage{longtable}         % tables longer than one page
\usepackage{calc}
\usepackage{exscale}           % large summation signs in 11pt
\usepackage{array}             % nice tables
\usepackage{subcaption} %For subfigures
\usepackage{wrapfig} % for wrapping text around figures
\usepackage{xspace}            % better spacing after macros
\usepackage{stackengine} 	%for stacking text in diagrams
\setstackEOL{\\}
\usepackage{ifdraft}           % to determine whether draft mode
\usepackage{xparse} %for macros with more than one optional argument
\usepackage{imakeidx} %for index
\usepackage{appendix}
\usepackage[symbols, record]{glossaries-extra}
\usepackage[expansion=false    % no font expansion
           ]{microtype}        % only protrusion
\usepackage[backend = biber,
backref = true,
style = alphabetic,
maxcitenames = 99,
maxbibnames = 99,
mincitenames = 5]{biblatex}

\usepackage[
draft,		%no links
final,                    % treat as final
plainpages=false,              % whatever that means
pdfpagelabels=true,            % strange options
pdfencoding=auto,              % getting worse
unicode=true,                  % unicode is always nice
hypertexnames=true,            % needs both to get index *and*
naturalnames=true,              % crossrefs correct
colorlinks,
linkcolor={blue!70!black},
citecolor={blue!50!black},
urlcolor={blue!80!black}
]{hyperref}                    % hyperrefs are cool!

%
% Bibliography with BibLaTex
%
%\DeclareNameAlias{default}{last-first}

\addbibresource{phd-thesis.bib}

%
% Index
%
%\makeindex[intoc,options= {-s phd-index.ist}]

%
% Text starts here
%

% Macros imported from macros-phd-thesis.tex
\newcommand{\Ann}{\operatorname{Ann}}
% Orbit space functor

\newcommand{\Total}{{\scriptscriptstyle\script{T}}}
% Normalizer

\newcommand{\Wobs}{{\scriptscriptstyle\script{N}}}
% Null

\newcommand{\Null}{{\scriptscriptstyle\script{0}}}
% Total

\newcommand{\TOTAL}{\script{T}}
% Normalizer

\newcommand{\WOBS}{\script{N}}
% Null

\newcommand{\NULL}{\script{0}}
% Index for strong constraint objects

\newcommand{\ConAlg}{{\Con\Algebras}}

\newcommand{\ConMfld}{{\Con\Manifolds}}

\newcommand{\ConCinfty}{\Con\Cinfty}
% Smooth strong constraint functions

\newcommand{\strtensor}[1][{}]{\mathbin{\boxtimes_{\scriptscriptstyle{#1}}}}
% Strong tensor product for embedded things

% Vanishing ideal
\newcommand{\vanishing}{\spacename{I}}
% Poisson Normalizer
\newcommand{\Pnormalizer}{\mathcal{B}}
% Constraint prefix
\newcommand{\Con}{\categoryname{C}}
% Categories of constraint Modules
\newcommand{\ConMod}{\Con\Modules}

%Copy ChairXthesis

\let\footruleskip\undefined
\usepackage{fancyhdr}          % cool headers
\usepackage{xkeyval}           % key-value options
\usepackage[multiuser]{fixme}  % correction notes, warnings etc.
\usepackage{enumitem}
\usepackage{tikz}              % for commutative diagrams and

\usepackage{nchairx} % additional packages

%
% tikz libraries to be loaded, feel free to add more...
%
\usetikzlibrary{cd,arrows,intersections,matrix,calc,fadings,decorations.pathreplacing,positioning,patterns,decorations.markings,decorations.pathmorphing,calc}
\usetikzlibrary[patterns,patterns.meta]

%
% TikzCD Settings
%
\tikzcdset{
	row sep/normal=2.7em,
	column sep/normal=3.6em}

%
% List environments
%

\newlist{propertieslist}{enumerate}{1}
\setlist[propertieslist, 1]{topsep = 0.2em,
	partopsep = 0em,
	itemsep = 0.2em,
	parsep = 0.1em,
	label=\textit{\alph*.)}}

\newlist{structurelist}{enumerate}{1}
\setlist[structurelist, 1]{topsep = 0.2em,
	partopsep = 0em,
	itemsep = 0.2em,
	parsep = 0.1em,
	label=\textit{\Alph*.)}}

\begin{document}

\paragraph{Geometric Reduction}
In classical mechanics symmetry reduction plays an important role.
Mathematically, this is usually phrased in terms of Marsden-Weinstein reduction \cite{marsden.weinstein:1974a} on a symplectic manifold $(M,\omega)$.
For this assume that a connected Lie group $\group{G}$ acts on $M$ in a Hamiltonian fashion, i.e.
there exists a momentum map $J \colon M \to \liealg{g}^*$, with $\liealg{g}$ denoting the Lie algebra of $\group{G}$,
such that
\begin{equation}
	\phi(\xi) = X_{J_\xi}
\end{equation}
for $\xi \in \liealg{g}$, and $\phi$ denoting the infinitesimal action of $\liealg{g}$.
If $0 \in \liealg{g}$ is a value and regular value of $J$, then $C \coloneqq J^{-1}(\{0\})$
is a closed submanifold of $M$.
Moreover, suppose that $\group{G}$ acts freely and properly on $C$, then
\begin{equation}
	M_\red \coloneqq C / \group{G}
\end{equation}
is a symplectic manifold with symplectic form $\omega_\red$ fulfilling $\pi^*\omega_\red = \iota^*\omega$,
with $\iota \colon C \to M$ the inclusion and $\pi \colon C \to M_\red$ the canonical projection.
It turns out that $C$ is a coisotropic submanifold of $M$ and that the above reduction procedure can actually be done for any coisotropic submanifold of a Poisson manifold.
Such coisotropic submanifolds and their reduction were introduced by Weinstein in \cite{weinstein:1988a} based on ideas
of Poisson reduction from \cite{marsden.ratiu:1086a}, see also \cite{stasheff:1997a}.
For this consider a Poisson manifold $(M,\pi)$, with $\argument^\sharp \colon T^*M \to TM$ denoting the corresponding musical homomorphism.
Then a submanifold $C$ of $M$ is coisotropic if and only if 
\begin{equation}
	\Ann(T_pC)^\# \subseteq T_pC
\end{equation}
for all $p \in C$.
Every such coisotropic submanifold carries a so-called characteristic distribution $D \subseteq TC$ spanned by the 
Hamiltonian vector fields $X_f$ for all functions $f$ vanishing on $C$.
\begin{figure}[t]
	\centering
	\includegraphics{constraintmanifold-Dippel.pdf}
	\caption{Reduction of coisotropic submanifold $C \subseteq M$ with characteristic distribution $D$.}
	\label{fig:ConstraintManifold}
\end{figure}
In the above case of the Marsden-Weinstein reduction of a symplectic manifold the leaves of this distribution
are given by the orbits of the group action on $C$.
If the characteristic distribution is nice enough, we can construct a reduced manifold
\begin{equation}
	M_\red \coloneqq C / D,
\end{equation}
see \cite[fig:ConstraintManifold]{Dippell2023}, which carries a Poisson structure $\pi_\red$ induced by the Poisson structure $\pi$ on $M$.

\paragraph{Algebraic Reduction}
The general strategy is now to reformulate the geometric situation of a coisotropic submanifold equipped with its characteristic distributions in algebraic terms, similar to the way the algebra of observables $\Cinfty(M)$ is used to algebraically describe the manifold $M$.
Any closed submanifold $C \subseteq M$ can be described in terms of functions by its vanishing ideal
 {vanishingIdeal}
\begin{equation}
	\vanishing_C = \left\{ f \in \Cinfty(M) \bigm| f\at{C} = 0 \right\} \subseteq \Cinfty(M).
\end{equation}
Similarly, the foliation induced by any distribution $D \subseteq TM$ can be encoded by the subalgebra
 {invariantFunctions}
\begin{equation}
	\Cinfty(M)^D = \{ f \in \Cinfty(M) \mid \Lie_X f = 0 \text{ for all } X \in \Secinfty(D) \} \subseteq \Cinfty(M).
\end{equation}
Now for a coisotropic submanifold $C \subseteq (M,\pi)$ the characteristic distribution $D$ is only defined on $C$.
This leads us to consider the subalgebra
 {locallyInvariantFunctions}
\begin{equation}
	\Cinfty_D(M) = \{ f \in \Cinfty(M) \mid \Lie_X f\at{C} = 0 \text{ for all } X \in \Secinfty(D) \} \subseteq \Cinfty(M)
\end{equation}
instead.
Note that the vanishing ideal $\vanishing_C$ is contained in $\Cinfty_D(M)$.
Thus we have established a correspondence
\begin{equation} \label{eq:GeometryAlgebraCorrespondenceConstraint}
	(M,C,D)  \leftrightsquigarrow (\Cinfty(M), \Cinfty_D(M), \vanishing_C)
\end{equation}
between a manifold $M$ equipped with a closed submanifold $C$ on one side and a distribution $D$ on $C$ and
its algebra of functions $\Cinfty(M)$ equipped with the subalgebra $\Cinfty_D(M)$
of functions which are invariant on $C$ and the vanishing ideal $\vanishing_C$ on the other side.
Motivated by coisotropic reduction there is a reduction procedure for both sides of this correspondence.
Namely, on the geometric side, under the assumption of a simple distribution, 
we can construct the reduced manifold $M_\red \coloneqq C / D$ as before, 
while on the algebraic side we can always construct the reduced algebra
\begin{equation}
	\Cinfty(M)_\red = \Cinfty_D(M) / \vanishing_C.
\end{equation}
It is then easy to see that $\Cinfty(M)_\red \simeq \Cinfty(M_\red)$
is just the algebra of functions on the reduced manifold.
If we consider again the setting of a coisotropic submanifold $C \subseteq M$
then one can show that $\vanishing_C$ is a Poisson subalgebra of $(\Cinfty(M), \{\argument, \argument\})$
and that $\Cinfty_D(M)$ coincides with the Poisson normalizer
\begin{equation}
	\Pnormalizer_C = \{ f \in \Cinfty(M) \mid \{f,g\} \in \vanishing_C \text{ for all } g \in \vanishing_C\}	
\end{equation}
of $\vanishing_C$.
In particular, $\vanishing_C$ becomes a Poisson ideal in the Poisson subalgebra $\Pnormalizer_C$, and
therefore $\Cinfty(M)_\red$ carries itself a Poisson bracket, which turns
$M_\red$ into a Poisson manifold.

\paragraph{Constraint Algebras and their Deformations}
We now seek to carry over the basic ideas of deformation quantization to this more structured situation.
This means we want to treat the triple $(\Cinfty(M), \Cinfty_D(M),\vanishing_C)$
as a single algebraic entity and study deformations of it.
Thus we use $(\Cinfty(M), \Cinfty_D(M),\vanishing_C)$ as the motivating example to define an (embedded)
\emph{constraint algebra} $\algebra{A}$ as consisting of a unital associative algebra $\algebra{A}_\Total$
together with a unital subalgebra $\algebra{A}_\Wobs$ and an ideal $\algebra{A}_\Null \subseteq \algebra{A}_\Wobs$.
The subscript $\WOBS$ is supposed to remind the reader of the coisotropic situation, where $\algebra{A}_\Wobs$ is given as 
the Poisson normalizer of the Poisson subalgebra $\algebra{A}_\Null$.

In a next step we can try to define formal deformations of constraint algebras by taking the classical definition of a formal deformation and formally replace algebras by constraint algebras.
In particular, replacing $\Cinfty(M)$ by the constraint algebra $(\Cinfty(M), \Cinfty_D(M), \vanishing_C)$
To make sense of this we first need to clarify some notions:
\begin{cptitem}
	\item What are modules over constraint algebras and their tensor products?
	\item What are constraint multidifferential operators?
	\item Is there a cohomology theory governing the deformation problem of constraint algebras?
\end{cptitem}
We will answer these questions by taking a categorical point of view:
constraint algebras can be realized as monoid objects internal to a certain monoidal category 
$\ConMod_\field{k}$ equipped with a tensor product $\tensor[\field{k}]$, whose objects will be called
constraint $\field{k}$-modules.
By abstract categorical considerations, the definition and some first properties
of constraint modules over constraint algebras, as well as their tensor products, are then fixed.
In contrast to classical categories of modules, the categories of constraint modules will not form abelian categories.
This will lead to effects not present in classical module theory, and forces us to thoroughly examine even the most basic constructions of constraint modules.

This categorical approach will immediately allow us to find constraint analogues of many other classical algebraic concepts, such as derivations, groups, vector spaces, Lie algebras etc.
All these constraint notions will consist of a classical object as $\TOTAL$-component, together with a subobject as
$\WOBS$-component and an equivalence relation or ideal as $\NULL$-component.
Then, by construction, there is always a reduction procedure, defined by taking the quotient of the $\WOBS$-component by the $\NULL$-component, which by definition always yields a classical object.
It should be noted that the motivating example $(\Cinfty(M), \Cinfty_D(M),\vanishing_C)$
has additional properties not accounted for in the definition of constraint algebras, namely that
$\vanishing_C$ is an ideal not only in $\Cinfty_D(M)$ but in all of $\Cinfty(M)$.
Such constraint algebras will be called strong, and their modules will allow for two different canonical tensor products
$\tensor$ and $\strtensor$, whose interplay will be an important piece of study.
Note however that, since we are interested in non-commutative deformations of constraint algebras we should not expect
$\algebra{A}_\Null$ to stay a two-sided ideal in $\algebra{A}_\Total$ after deformation, see Lu's coisotropic creed \cite{lu:1993a}.
Even in the classical geometric situation we will encounter examples of honest non-strong constraint algebras.

\paragraph{Constraint Manifolds and Vector Bundles}
Consider again the correspondence \eqref{eq:GeometryAlgebraCorrespondenceConstraint}.
Here, on the algebraic side, we have a subobject together with an equivalence relation on the subobject which is compatible with the structure of the subobject in a suitable sense.
In our example we have a subalgebra and an ideal inside this subalgebra.
On the geometric side, the triple $(M,C,D)$ carries the same underlying structure:
A subobject $C \subseteq M$, i.e. a submanifold, together with an equivalence relation on $C$, which in our case comes from a distribution $D$ on $C$.
We will understand in the course of this thesis that both the geometric and the algebraic side of \eqref{eq:GeometryAlgebraCorrespondenceConstraint} can be derived from the notion of constraint sets.
In particular, $(M,C,D)$ can be understood as a constraint set equipped with geometric structure, while the constraint algebra
$(\Cinfty(M), \Cinfty_D(M), \vanishing_C)$ can be seen as a constraint set equipped with algebraic structure.
Therefore we will call $\mathcal{M} = (M,C,D)$ a constraint manifold.
From this point of view we can reformulate the correspondence \eqref{eq:GeometryAlgebraCorrespondenceConstraint}
as a functor
\begin{equation} \label{eq:ConstraintFunctionsFunctor}
\begin{split}
	\ConCinfty &\colon \ConMfld \to \ConAlg, \\
	\ConCinfty(\mathcal{M}) &\coloneqq (\Cinfty(M), \Cinfty_D(M),\vanishing_C),
\end{split}
\end{equation}
from the category of constraint manifolds to the category of constraint algebras.

The notion of constraint manifolds encompasses two extreme, but important cases, namely that of a submanifold 
$C \subseteq M$ without a distribution, described by $(M,C,0)$, and that of a distribution $D$ on $M$ without an additional submanifold, described by $(M,M,D)$.
When applying the functor $\ConCinfty$ we obtain
\begin{align}
	\ConCinfty(M,C,0) &= (\Cinfty(M), \Cinfty(M), \vanishing_C)\\
	\shortintertext{and}
	\ConCinfty(M,M,D) &= (\Cinfty(M), \Cinfty(M)^D, 0).
\end{align}
Thus we see that the information of the $\WOBS$-component on the geometric side, i.e. the submanifold $C$, is encoded in the $\NULL$-component on the algebraic side.
Conversely, the geometric $\NULL$-component, i.e. the distribution $D$, is described by the $\WOBS$-component of the algebra of functions.
Therefore, if we are searching for a common framework including both the geometric and algebraic information, even if we are only interested in submanifolds \emph{or} in distributions, we have to consider the full constraint triple.
In particular, we can \emph{not} expect to be able to separate the reduction problem into two independent problems taking care of restriction and quotients separately.

The notion of constraint manifolds suggests to also introduce constraint versions of other geometric concepts,
such as constraint vector bundles and, in particular, constraint tangent and cotangent bundles.

%************************************
\subsubsection*{Bibliographical Notes}
%**************************************

This thesis is based on three publications \cite{dippell.esposito.waldmann:2019a}, \cite{dippell.menke.waldmann:2022a}
and \cite{dippell.esposito.waldmann:2022a}.
Since the basic notions used there have somewhat changed over time, let us comment a bit on their relation to the current thesis.

A first version of the notion of constraint algebra was introduced in \cite{dippell:2018a} and \cite{dippell.esposito.waldmann:2019a}
under the name of \emph{coisotropic triple of algebras} as a tool to study the behaviour of Morita equivalence under reduction.
These coisotropic triples would now be called embedded constraint algebras, with the additional property of
$\algebra{A}_\Null$ being a left ideal in $\algebra{A}_\Total$.
The notion of bimodules over coisotropic triples of algebras as used in
\cite{dippell.esposito.waldmann:2019a} already coincides with the notion of constraint bimodules over constraint algebras,
and reduction functors for constraint algebras and modules were already defined.
Thus the bicategory of bimodules over coisotropic triples of algebras as constructed in
\cite{dippell.esposito.waldmann:2019a} can be understood as a subbicategory of the bicategory of constraint bimodules over constraint algebras.
The proofs can easily be carried over to the more general situation of constraint algebras.

In \cite{dippell.menke.waldmann:2022a} the notions of coisotropic triples of algebras and modules were replaced by
\emph{coisotropic algebras} and \emph{coisotropic modules}, which agree with what we call constraint algebras and constraint modules in this thesis.
Here also coisotropic index sets, now called constraint index sets, were introduced in order to study
free and projective coisotropic modules.
These results can be found in \cite[sec:ConIndSets]{Dippell2023}, \cite[sec:FreeConMod]{Dippell2023} and
\cite[sec:ProjectiveConModules]{Dippell2023}.
The goal of \cite{dippell.menke.waldmann:2022a} was then to find a suitable notion of vector bundles
over what we would now call a constraint manifold, such that sections of these vector bundles correspond to 
constraint modules by some sort of Serre-Swan Theorem.
These vector bundles are similar to the constraint vector bundles we introduce in
\cite[sec:ConVectorBundles]{Dippell2023}, but they do still differ in important aspects.
In particular, there seems to be no good notion of tangent bundles or dual bundles.
We will see in the course of this thesis that these deficiencies come from the fact that the algebraic analogue of constraint manifolds
is given by \emph{strong} constraint algebras, and hence when searching for the correct notion of vector bundles one should also consider \emph{strong} constraint modules.
Although the vector bundles introduced in \cite{dippell.menke.waldmann:2022a} do not agree with our objects of study many ideas and smaller results used in \cite[chap:ConstraintGeometricStructures]{Dippell2023} are based on \cite{dippell.menke.waldmann:2022a}.

Finally, in \cite{dippell.esposito.waldmann:2022a} the formal deformation theory of what was still called coisotropic algebras was studied.
The introduction of constraint Hochschild cohomology and the deformation functor based on constraint DGLAs is based on
\cite{dippell.esposito.waldmann:2022a}.

Even though this thesis is based on these three publications, a considerable amount does appear here for the first time.
In particular the notions of \emph{strong} constraint algebras and related objects, together with the strong tensor product, as well as the notion of constraint vector bundles have not been studied before.
Also the three main results as introduced above have not appeared elsewhere.

\end{document}

### 2025-01-19 msconstraints-short-main.tex
Troubleshooting on windows.
Repo simplified due to compilation errors with standalone.

--- 2025-01-11 msconstraints-short.tex
@@
 	\newif\ifHandout
-	%\Handouttrue  %uncomment for the printable version
+	\Handouttrue  %uncomment for the printable version
 	%Handling of flags it is not preserved when passing to standalone-subfiles!
@@
 \usepackage{math}
-\usepackage{multicol}
-\usepackage{xfrac}
-
-\renewcommand{\action}{\curvearrowright} 
-\makeatletter
-\def\blfootnote{\gdef\@thefnmark{}\@footnotetext}
-\makeatother
-
-\newcommand{\fgmodule}{\mathfrak{X}_{\g}}
-\newcommand{\tgtvanform}{I_{\Omega}(N)}
-\newcommand{\tgtvf}{\mathfrak X_N(M)}
-\newcommand{\vanvf}{I_{\mathfrak{X}}(N)}%{I_N^{\mathfrak X}}
-\newcommand{\Ham}{\mathsf{Ham}}
-\renewcommand{\ham}{\text{ham}}
-\usepackage{graphicx}
-\usepackage{enumitem}
-\usepackage{amsmath}
-\usepackage{amssymb}
+
+%- Bibliography (Biber) ----------------------------------------------------------------------------------
+\usepackage[backend=biber,style=alphabetic,maxnames=2]{biblatex}
+\bibliography{bibfile.bib}
+
+%- L30's ----------------------------------------------------------------------------------------------
+\usepackage{quiver} %https://q.uiver.app/ % Not in Miktex!
+\usetikzlibrary{nfold}
+\usetikzlibrary{decorations.pathmorphing} 
+\renewcommand{\Ham}{\mathrm{Ham}}
+\newcommand{\Der}{\mathrm{Der}}
 
@@
 
-%---------------------------------------------------------------------------------------------------------------------------------------------------
+%--------------------------------------------------------------------------------------------------
 %- D0cum3nt ----------------------------------------------------------------------------------------------------------------------------------
 \begin{document}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
+%------------------------------------------------------------------------------------------------
 \begin{frame}  % Alternative: \maketitle outside of frame
@@
 }
-%---------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
+%--------------------------------------------------------------------------------------------------
+
+%------------------------------------------------------------------------------------------------
 \begin{frame}[fragile]{Keywords}
@@
 }
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
+%------------------------------------------------------------------------------------------------
+
+%------------------------------------------------------------------------------------------------
 \section{Symplectic Reduction}
 \checkpoint	
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
+%------------------------------------------------------------------------------------------------
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}{Reduction in Classical Mechanics}
+
+\end{frame}
+\note[itemize]{
+	\item  In classical mechanics symmetry reduction plays an important role.
+	\item Mathematically, this is usually phrased in terms of Marsden-Weinstein reduction
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}{Geometric Reduction} 
+	{Def. Symplectic manifold $(M,\omega)$} $M$ a smooth manifold, $\omega\in \Omega^{2}(M)$ closed and non-degenerate, i.e.:
+		\begin{itemize} 	
+			\item $d\omega=0$
+			\item $\omega^\flat:TM\to T^*M, v\mapsto \iota_v\omega$ is injective
+		\end{itemize}
+
+\end{frame}
+\note[itemize]{
+	\item   Examples:
+		\begin{itemize}
+			\item orientable 2-manifolds with volume, e.g. $S^2$, $T^2$, $\mathbb R^2$
+			\item cotangent bunlde $T^*Q$ of any manifold $Q$, with $\omega=d\theta$. $\theta_\eta(v)=\eta(T\pi_Q(v))$.
+			\item coadjoint orbits
+		\end{itemize}
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}{Poisson Reduction} 
+{Def. Poisson algebra of observables} Let $(M,\omega)$ be symplectic.
+		\begin{itemize}
+			\item $X_f:=-(\omega^\flat)^{-1}(df)$  \emph{Hamiltonian vector field} of $f\in C^\infty(M)$.
+			\item $\{f,g\}:=\omega(X_f,X_g)=L_{X_f}g$ \emph{Poisson bracket of observables}
+		\end{itemize}
+	Indeed $(C^{\infty}(M), \cdot, \{-,-\})$ Poisson algebra:
+			\begin{itemize}
+		\item $\cdot$ is a commutative, associative mutliplication
+		\item $\{-,-\}$ is a Lie bracket
+		\item $\{f,- \}$ is a derivation
+	\end{itemize}\pause
+	And $f\mapsto X_f$ is a Lie algebra map. 
+\end{frame}
+\note[itemize]{
+	\item  
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\subsection{Marsden-Weinstein-Meyer reduction}
+\begin{frame}[fragile]{Marsden-Weinstein-Meyer reduction}
+Let $(M,\omega)$ symplectic, $G\circlearrowright M$ be a Lie group action\pause and $\mu:M\to \mathfrak g^*$ such that:\pause
+\begin{itemize}
+\item  $\mu$ is a momentum, i.e. the infinitesimal action $\xi\mapsto \underline\xi:\mathfrak g\to \mathfrak X(M)$ of $G$ satisfies $X_{\langle\mu,\xi\rangle}=\underline \xi$. \pause
+\item $\mu$ is $G$-equivariant, i.e. $\mu(gm)=Ad^*_g\mu(m)$ \pause
+\item The action of $G$ on $\mu^{-1}(0)$ is free and proper.\\ (This implies $0$ is reg. val. of $\mu$) \pause
+\end{itemize}
+Then $\exists!$ symplectic form $\omega_r$ on $M_r=\frac{\mu^{-1}(0)}{G}$ such that $\pi^*\omega_r=i^*\omega$.
+
+% https://q.uiver.app/#q=WzAsMyxbMCwwLCJNIl0sWzMsMCwiXFxtdV57LTF9KDApIl0sWzYsMCwiTV9yIl0sWzEsMCwiaVxcXFwgXFxzdWJzdGFja3tpbmNsdXNpb25+b2Z+c3Vic3BhY2V9IiwyLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoiaG9vayIsInNpZGUiOiJib3R0b20ifX19XSxbMSwyLCJcXHBpXFxcXCBcXHN1YnN0YWNre3F1b3RpZW50fmJ5fnJlbGF0aW9ufSJdXQ==
+\[\begin{tikzcd}
+	M &&& {\mu^{-1}(0)} &&& {M_r}
+	\arrow["\begin{array}{c} i\\ \substack{inclusion~of~subspace} \end{array}"', hook', from=1-4, to=1-1]
+	\arrow["\begin{array}{c} \pi\\ \substack{quotient~by~relation} \end{array}", two heads, from=1-4, to=1-7]
+\end{tikzcd}\]
+
+\pause
+Examples: $\mathbb CP^n$ from $S^1$-action on $\mathbb C^{n+1}$.
+
+\end{frame}
+
+\subsection{Attempting algebraic reduction}
+
+\begin{frame}[fragile]
+When the action is not 'free and proper', we can try to mimic this directly using the function algebras:
+% https://q.uiver.app/#q=WzAsNixbMCwwLCJNIl0sWzEsMCwiXFxtdV57LTF9KDApPVMiXSxbMywwLCJNX3IiXSxbMCwxLCJDXlxcaW5mdHkoTSkiXSxbMSwxLCJDXntcXGluZnR5fShTKT1cXGZyYWN7Q157XFxpbmZ0eX0oTSl9e0lfe1N9fSJdLFszLDEsIkNee1xcaW5mdHl9KE1fcik9Q15cXGluZnR5KFMpXkciXSxbMSwyLCJcXHN1YnN0YWNre3F1b3RpZW50fSIsMCx7InN0eWxlIjp7ImhlYWQiOnsibmFtZSI6ImVwaSJ9fX1dLFszLDQsIlxcc3Vic3RhY2t7cXVvdGllbnR9IiwwLHsic3R5bGUiOnsiaGVhZCI6eyJuYW1lIjoiZXBpIn19fV0sWzAsMSwiXFxzdWJzdGFja3tyZXN0cmljdGlvbn0iLDAseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dLFs0LDUsIlxcc3Vic3RhY2t7cmVzdHJpY3Rpb259IiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoic3F1aWdnbHkifX19XV0=
+\[\begin{tikzcd}
+	M & {\mu^{-1}(0)=S} && {M_r} \\
+	{C^\infty(M)} & {C^{\infty}(S):=\frac{C^{\infty}(M)}{I_{S}}} && {C^{\infty}(M_r)=C^\infty(S)^G}
+	\arrow["{\substack{restriction}}", squiggly, from=1-1, to=1-2]
+	\arrow["{\substack{quotient}}", two heads, from=1-2, to=1-4]
+	\arrow["{\substack{quotient}}", two heads, from=2-1, to=2-2]
+	\arrow["{\substack{restriction}}", squiggly, from=2-2, to=2-4]
+\end{tikzcd}\]
+
+where $I_S=\{f\in C^{\infty}(M)~|~f|_S=0\}$.\pause Equivalently:
+
+% https://q.uiver.app/#q=WzAsMyxbMCwwLCJDXlxcaW5mdHkoTSkiXSxbMiwwLCJOX1M9XFx7Zn58fiBmXFxpbiBDXlxcaW5mdHkoTSl8X1N+fkdcXG1hdGhybXstaW52YXJpYW50fVxcfSJdLFs0LDAsIlxcZnJhY3tOX1N9e0lfU30iXSxbMCwxLCJcXHN1YnN0YWNre3Jlc3RyaWN0aW9ufSIsMCx7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6InNxdWlnZ2x5In19fV0sWzEsMiwiXFxzdWJzdGFja3txdW90aWVudH0iLDAseyJzdHlsZSI6eyJoZWFkIjp7Im5hbWUiOiJlcGkifX19XV0=
+\[\small\begin{tikzcd}
+	{C^\infty(M)} && {N_S=\{f~|~ f\in C^\infty(M)|_S~~G\mathrm{-invariant}\}} && {\frac{N_S}{I_S}}
+	\arrow["{\substack{restriction}}", squiggly, from=1-1, to=1-3]
+	\arrow["{\substack{quotient}}", two heads, from=1-3, to=1-5]
+\end{tikzcd}\]
+\pause
+
+\begin{alertblock}{Problem}
+	$C^\infty(S)^G=\frac{N_S}{I_S}$ is not a Poisson algebra in general.
+\end{alertblock}
+(when constraints not first class, cf. Dirac reduction)
+\end{frame}
+
+ \begin{frame}{Other approaches to reduction}
+
+\begin{table}[]
+	\begin{tabular}{l|l|l||l}
+		algebra $\mathcal{A}_T$ & subalgebra $\mathcal{A}_N$ & ideal $\mathcal{A}_0$ & comment \\
+		\hline
+
+		$C^\infty(M)$&      $N_S$     &   $I_S$   &  $\substack{S=\mu^{-1}(0),~ I_S=\{f~|~f|_S=0\}}$ \\
+			&&&  $\substack{N_S= \{ f | gf-f\in I_S \forall g\in G\}}$ \\
+	& & & \color{red} not Poisson \\ 
+	\hline	\pause
+	$C^\infty(M)$&   $F_S$         &   $I_S$   &  $\substack{F_S=\{f~|~\{f,I_S\}\subset I_S\}}$ \\
+	& & & \color{red} if $I_S\subset F_S$\\
+	\hline \pause
+
+	$C^\infty(M)$&   $C^\infty(M)^G$         &   $(I_S)^G$   &  $\substack{C^\infty(M)^G=\{f~|~gf=f\forall g\in G\}}$ \\
+	\hline \pause
+		$C^\infty(M)$&   $C^\infty(M)^G$         &   $(I_\mu)^G$   & $\substack{I_\mu=\{\sum_{i=1}^k f_i\langle \mu,\xi_i\rangle|~f_i\in C^\infty(M), \xi_i\in \mathfrak g\}}$\\
+		\hline \pause
+	$C^\infty(M)$&      $N_\mu$     &   $I_\mu$   & $\substack{N_\mu= \{ f | gf-f\in I_\mu \forall g\in G\}}$\\
+	\hline
+
+	\end{tabular}\pause
+\end{table}
+{\bf Remarks }names in order: 'naive' , Dirac, Sniatycki, Arms-Cushman-Gotay, Sniatycki-Weinstein.\pause \\
+When $G$ connected $N_\mu=N(I_\mu):=\{f~|~\{f,I_\mu\}\subset I_\mu\}$. 
+ \end{frame}
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}{Algebraic Reduction} 
+ a
+
+\end{frame}
+\note[itemize]{
+	\item  
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}{Constraint Algebras} 
+ a
+
+\end{frame}
+\note[itemize]{
+	\item  
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%------------------------------------------------------------------------------------------------
+\section{Multisymplectic Geometry}
+\checkpoint	
+%------------------------------------------------------------------------------------------------
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}{From symplectic to {multi}symplectic} 
+	%
+	\begin{center}
+		$-$ \emph{multisymplectic means \textbf{going higher} in the degree of $\omega$} $-$
+	\end{center}
+	\pause
+	\begin{defblock}[$n$-plectic manifold ~\emph{(Cantrijn, Ibort, De Le\'on)} \cite{Cantrun2017}]
+		\includestandalone[width=0.95\textwidth]{Pictures/Figure_multisym}	
+	\end{defblock}
+	%
+	\pause
+		\begin{table}
+			\begin{tabular}{c c c}
+				symplectic forms \small($n=1$) & $\leftrightsquigarrow$ & volume forms \small($n= \text{dim}(M)-1$)
+			\end{tabular}
+		\end{table}
+
+	\vfill
+	\pause
+	\begin{block}{Historical motivation}
+		Mechanics: geometrical foundations of \textit{(first-order)} field theories.
+	\end{block}
+	%
+	\begin{table}
+		\ifHandout
+		%
+		\else
+		\only<4>{
+		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
+            \hline
+            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
+            \hline
+            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold &  \\[.25em]
+            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra &  \\[.25em]
+            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map &  
+            \\
+            \hline
+  \multicolumn{1}{c}{}
+            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
+            &  \multicolumn{1}{@{}c@{}}{}              \\
+		\end{tabular}
+		}
+		\fi
+		\onslide<5->{
+		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
+            \hline
+            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
+            \hline
+            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold & multisymplectic manifold \\[.25em]
+            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra & $L_\infty$-algebra \\[.25em]
+            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map & group actions admitting (homotopy) comomentum map
+            \\
+            \hline
+  			\multicolumn{1}{c}{}
+            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
+            &
+            \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{field-theoretic systems}}$} 
+               \\
+		\end{tabular}
+		}
+	\end{table}
+
+\end{frame}
+\note[itemize]{
+	\item Historically, the interest in multisymplectic manifolds, has been motivated by the need for understanding the geometrical foundations of first-order classical field theories.
+	The key point is that, just as one can associate a symplectic manifold to an ordinary classical mechanical system (e.g. a single
+point-like particle constrained to some manifold), it is possible to associate a multisymplectic
+manifold to any classical field system (e.g. a continuous medium like a filament or a fluid). See frame Extra-\ref{Frame:Ms-Field-Mechanics}
+
+	\item General ideas basic parallelisms with caveats
+	\item caveat: points in multiphase spaces are not states
+	\item the table hides the duality between geometric and algebraic approaches to the problem.
+	\item	Mechanics: geometrical foundations of \textit{(first-order)} field theories.
+		\begin{itemize}
+		 \item[-] Kijowski, W. Tulczyjew \cite{Kijowski1979}; %(1979)
+		 \item[-] Cariñena, Crampin, Ibort \cite{Carinena1991b};% (1991)
+		 \item[-] Gotay, Isenberg, Marsden, Montgomery \cite{Gimmsy1};%(1998)
+		 \\ $\cdots$
+		\end{itemize}
+	\item {Def. Multisymplectic manifold $(M,\omega)$}
+	$M$ a smooth manifold, $\omega\in \Omega^{n+1}(M)$ closed and non-deg., i.e.:
+	\begin{itemize}
+		\item $d\omega=0$
+		\item $\omega^\flat:TM\to \Lambda^nT^*M, v\mapsto \iota_v\omega$ is injective
+	\end{itemize} 
+	\item Without the non-deg. condition we call it \emph{premultisymplectic}. 
+	\item Examples:
+		\begin{itemize} 
+			\item orientable $n{+}1$-manifolds with volume, e.g. $S^{n+1}$, $T^{n+1}$, $\mathbb R^{n+1}$ 
+			\item multicotangent bunlde $\Lambda^nT^*Q$ of any manifold $Q$, with $\omega=d\theta$. $\theta_\eta(v_1,...,v_n)=\eta(T\pi_Q(v_n),...,T\pi_Q(v_n))$. 
+			\item semisimple Lie groups, hyperKähler manifolds,...
+		\end{itemize}
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}{Geometric Multisymplectic Reduction} 
+ a
+
+\end{frame}
+\note[itemize]{
+	\item  
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%------------------------------------------------------------------------------------------------
+\section{Multisymplectic observables reduction}
+\checkpoint	
+%------------------------------------------------------------------------------------------------
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}{Observables in $n$-plectic geometry}
+	%
+	\begin{defblock}[Hamiltonian $(n-1)$-forms]
+		\begin{displaymath}
+			\Omega^{n-1}_{ham}(M,\omega) 	:=
+			\biggr\{ \sigma \in  \Omega^{n-1}(M) \; \biggr\vert \; 
+				\exists \vHam_\sigma \in \mathfrak{X}(M) ~:~ 
+				\tikz[baseline,remember picture]{\node[rounded corners,
+                        fill=orange!5,draw=orange!30,anchor=base]            
+            			(target) {$d \sigma = -\iota_{\vHam_\sigma} \omega$ };
+            	}				
+				~\biggr\} 
+			\end{displaymath}
+	\end{defblock}
+
+	\pause
+		\tikz[overlay,remember picture]
+		{
+			\node[rounded corners,
+                 fill=orange!5,draw=orange!30,anchor=base]
+            	 (base) at ($(current page.north east)-(2,1)$) [rotate=-0,text width=3.5cm,align=center] {\footnotesize{\textcolor{red}{Hamilton-DeDonder-Weyl \\equation}}};
+		}	
+	\begin{tikzpicture}[overlay,remember picture]
+    	\path[->] (base.south) edge[bend right,red](target.north);
+    \end{tikzpicture}
+	%
+	\vfill
+	\begin{columns}[T]
+		\pause
+		\setlength{\belowdisplayskip}{5pt}
+		\begin{column}{.50\linewidth}
+			%
+			\vspace{-1em}
+			\begin{thmblock}[Observables $L_\infty$-algebra]
+				$\Omega^{n-1}_{ham}(M,\omega)$ endowed with
+				\vspace{-.5em}
+				\begin{displaymath}
+					\lbrace \sigma_1, \sigma_2 \rbrace =			
+					~ - \iota_{\vHam_1}\iota_{\vHam_2} \omega 
+				\end{displaymath}			
+				can be "completed" to a \\ $L_\infty-algebra$.
+			\end{thmblock}
+			%	
+		\end{column}	
+		%
+		\pause
+		\begin{column}{.50\linewidth}
+		%
+			\begin{itemize}
+				\item[\cmark] Skew-symmetric;
+				\item[\xmark] multiplication of observables;
+				\item[\xmark] Jacobi equation;
+				%\\ \hspace*{4.25em} full-fledged Jacobi equation;
+				\item[\smark] Jacobi equation \emph{up to homotopies}.
+			\end{itemize}			
+			%
+				\[
+					\small
+					\{\alpha,\{\beta,\gamma\}\} + \text{\it cyc. perm.}
+					= {\color{orange}\d \iota_{X_\alpha} \iota_{X_\beta} \iota_{X_\gamma}\omega}
+				\]
+		\end{column}	
+	\end{columns}
+	%
+	\vfill
+	\pause
+	Interesting alternatives:
+	\begin{itemize}
+		\item  descend to $\Omega^{k-1}_{ham}(M) / {\color{orange}\d\hspace{1pt}\Omega^{k-2}(M)}$, hence getting a Lie algebra;
+		\item Incorporate the {\color{orange}discrepancy} as part of the data of the space of observables $ 
+				L_\infty(M,\omega) = \Omega_{ham}^{k-1}(M)\oplus{\color{orange}\Omega^{\leq k-2}(M)}$
+			%a \textbf{homotopy Lie algebra} or \textbf{$L_\infty$-algebra}.
+	\end{itemize}
+
+\end{frame}
+\note[itemize]{
+	\item
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\subsection{$L_\infty$-algebra of Observables}
+\begin{frame}[fragile,t]{$L_\infty$-algebra of Observables (higher observables) }
+	Let be $(M,\omega)$ a $n$-plectic manifold.
+	\begin{defblock}[$L_\infty$-algebra of observables ~\emph{(Rogers)} ~\cite{Rogers2010}]
+
+		\hspace{.25em} $L\infty(M,\omega)$ is given by:
+
+		\begin{itemize}
+			\item[•] a cochain-complex $(L,\{\cdot\}_1)$ 
+		\end{itemize}
+		\begin{center}
+		\ifHandout
+			\includestandalone{Pictures/Figure_Observables}	
+		\else
+			\includestandalone{Pictures/Frame_Observables}
+		\fi				
+		\end{center}
+		\onslide<2->{
+			\begin{itemize}
+				\item[•] with $n$ (skew-symmetric) multibrackets $(2 \leq k \leq n+1)$
+			\end{itemize}
+			\begin{center}
+				\includestandalone{Pictures/Equation_Multibracket}	
+			\end{center}
+		}
+		%
+	\end{defblock}
+  \end{frame}
+ \note[itemize]{
+	\item if symplectic manifolds are the symmetric take on mechanics, Poisson algebras are the algebraic counterpart.
+ 	\item A Lie algebra is associated to an ordinary symplectic manifold (its Poisson algebra).
+	%(Underlying this is a Lie algebra, whose Lie bracket is the Poisson bracket.)
+	Similarly, one associates an Lie-$n$ algebra to any $n$-plectic manifold.
+ 	% https://ncatlab.org/nlab/show/n-plectic+geometry 	 
+ 	 %https://ncatlab.org/nlab/show/Poisson+bracket+Lie+n-algebra
+	 \item Basically, the higher observables algebra is a chunk of the de Rham complex of $M$ with inverted grading( convention employed here) and an extra structure called "multibrackets".
+ 	\item ( In the 1-plectic case it reduces to the corresponding Poisson algebra of classical observables)
+ 	\item Rogers associated to any n-plectic mfd a $L\-\infty$ algebra, Zambon generalized it to the pre-n-plectic case.
+ 	\item Recognize in the definition of $\{\cdot,\ldots,\cdot\}_k$ the contraction with hamiltonian fields $v_\sigma$ w.r.t. $\sigma$.
+  	\item Note $	\iota_{v_{\sigma_1}}\cdots\iota_{v_{\sigma_k}} = (-)^{(k-1)+(k-2)+\dots+1}\iota_{v_{\sigma_k}}\cdots\iota_{v_{\sigma_1}} = (-)^{\frac{k(k-1)}{2}}\iota_{v_{\sigma_k}}\cdots\iota_{v_{\sigma_1}}$
+ 	The definition usually find in literature of Rogers multibrackets involves the coefficient $ (-)^{\frac{k(k-1)}{2}} = -\varsigma(k-1) = (-)^{k+1} \varsigma(k)$.
+  \item higher observables is Special instance of a more general object  called $L\-\infty$ Algebra...
+ }
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%------------------------------------------------------------------------------------------------
+% APPENDIX
+%------------------------------------------------------------------------------------------------
+\appendix
+%------------------------------------------------------------------------------------------------
+
+\section{Supplementary Material}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}
+	\begin{center}
+	\Huge\emph{Supplementary Material}
+	\end{center}
+\end{frame}
+\note[itemize]{
+	\item
+}
+\addtocounter{framenumber}{-1}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}[fragile]{MS geometry and classical field mechanics}\label{Frame:Ms-Field-Mechanics}
+		Consider a smooth manifold $Y$,
+		\begin{columns}
+			\hfill
+			\begin{column}{.5\linewidth}
+				\emph{Multicotangent bundle} $\bigwedge = \bigwedge^n T^\ast Y$\\
+				is naturally $n$-plectic
+			\end{column}
+			\begin{column}{.4\linewidth}
+				\[
+				\begin{tikzcd}
+					\Lambda \ar[d,"\pi"'] & T \Lambda \ar[d,"T \pi"] \ar[l] \\
+					Y								& T Y \ar[l]
+				\end{tikzcd}	
+				\]
+			\end{column}
+		\end{columns}
+	\pause
+	\begin{defblock}[Tautological $n$-form]
+		$\theta \in \Omega^n(\Lambda)$ such that:
+		\begin{displaymath}
+		\begin{split}
+			\left[ \iota_{u_1 \wedge \ldots \wedge u_n} \theta \right]_\eta 
+			&= \iota_{(T \pi)_\ast u_1 \wedge \ldots \wedge (T \pi)_\ast u_n} \eta \\
+			&= \iota_{u_1 \wedge \ldots \wedge u_n} \pi^\ast \eta 
+			\qquad \qquad \forall \eta \in \Lambda \, , \: \forall u_i \in T_\eta \Lambda 		
+		\end{split}
+		\end{displaymath}
+	\end{defblock}
+	\vfill
+	\begin{columns}
+		\begin{column}{.6\linewidth}
+			\begin{defblock}[Tautological (multisymplectic) (n+1)-form]
+				$$\omega := d \theta$$
+			\end{defblock}
+		\end{column}
+		\begin{column}{.4\linewidth}
+		 	\begin{claimblock}$\omega$ is not degenerate.\end{claimblock}	
+		\end{column}
+	\end{columns}	
+	\pause
+	\begin{keywordblock}
+		\begin{tabular}{|c|c|c|}
+			\hline 
+			point-particles mechanics & $\rightsquigarrow$ & classical fields mechanics \\
+			%(finite discrete DOF) & & (finite dimensional continuous DOF) \\
+			\hline 
+			symplectic & $\rightsquigarrow$ & multisymplectic \\ 
+			\hline 
+			Observables (Poisson) algebra & $\rightsquigarrow$ & Observables $L-\infty$ algebra
+			 \\ 
+			\hline 
+			Co-moment map & $\rightsquigarrow$ & Homotopy co-momentum map \\ 
+			\hline 
+		\end{tabular} 
+	\end{keywordblock}
+
+\end{frame}
+\note[itemize]{
+	\item This example is significant from the perspective of geometric classical field theory:
+		\begin{displaymath}
+			\frac{\text{classical mechanics}}{\text{symplectic geo.}} =
+			\frac{\text{classical field mechanics}}{\text{multisymplectic geo.}}
+		\end{displaymath}
+	\item Multicotangent bundle is the \emph{Higher analogue} of the cotangent bundle.
+	(but it is not yet the analogue of a \emph{phase space}.)
+\item The multiphase space is the sub-bundle of $n$-forms vanishing when contracted with 2 vertical fields.
+  	\item The reason why this sub-bundle has a particular role is that it can be proved to be isomorphic to a suitable dual of the first Jet bundle.
+  	\item For further details see Gotay et al.
+\href{https://arxiv.org/abs/physics/9801019}{arXiv:physics/9801019}.
+For a pictorial representation of all the structures involved in the geometric mechanics of I order classical field theories see appendix, pag: \ref{frame:Gimmsy}.
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}[t]{Symmetries in \textbf{multisymplectic geometry}}
+	Consider a Lie algebra action $v:\mathfrak{g} \to \mathfrak{X}(M)$  preserving the $n$-plectic form $\omega$,
+	\vfill
+
+	\vspace{-1em}
+	\begin{columns}[T]
+		\setlength{\belowdisplayskip}{5pt}
+		\begin{column}{.50\linewidth}
+			%
+			\centering \it
+			\onslide<2->{
+				$-$ symplectic case $-$
+				\begin{defblock}[Comoment map pertaining to $v$]
+					Lie algebra morphism
+					$$ f: \mathfrak{g} \to C^\infty(M) $$
+					such that
+					$$ d~f (x) = -\iota_{v_x} \omega \qquad \forall x \in \mathfrak{g}~.$$
+				\end{defblock}
+			}
+		\end{column}	
+		%
+		\onslide<2->{\vrule{}}
+		%
+		\begin{column}{.50\linewidth}
+			\centering \it
+			\onslide<3->{			
+				$-$ $n$-plectic case $-$
+				\begin{defblock}[Homotopy comoment map \tiny (HCMM)]
+					$L_\infty$-morphism 
+					$$ (f_k) : \mathfrak{g} \to L_\infty (M,\omega)$$
+					such that
+					$$ d~f_1(x) = -\iota_{v_x} \omega \qquad \forall x \in \mathfrak{g}~.$$
+				\end{defblock}	
+			}
+		\end{column}	
+	\end{columns}	
+	%
+	\pause
+	\vfill
+	\centering 
+	\onslide<4->{\textbf{-- Conserved quantities --}}
+	%
+	\vspace{-.5em}
+	\begin{columns}[T]
+		\setlength{\belowdisplayskip}{5pt}
+		\begin{column}{.50\linewidth}
+			%
+			\centering \it
+			\onslide<4->{
+			\begin{propblock}[Noether Theorem]
+				\small Fixed $H\in C^\infty_{\text{Ham}}(M)$ ($\mathfrak{g}$-invariant) ,
+				$$\mathcal{L}_{v_H} f(x) = 0 \qquad \forall x \in \mathfrak{g}$$
+			\end{propblock}
+			}
+		\end{column}	
+		%
+		\onslide<5->{\vrule{}}
+		%
+		\begin{column}{.50\linewidth}
+			\centering \it
+			\onslide<5->{			
+			\begin{propblock}[RWZ16 Theorem]
+				\small Fixed $H\in \Omega^{n-1}_{\text{Ham}}(M)$ ($\mathfrak{g}$-invariant),
+				$$\mathcal{L}_{v_H} f_k(p) \in B^k(M) \qquad \forall p \in Z_k(\mathfrak{g})$$			
+			\end{propblock}
+			}
+		\end{column}	
+	\end{columns}		
+\end{frame}
+\note{
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}{Reminder: $L_\infty$ Algebras}
+
+		\emph{
+			$L_\infty$-algebra is the notion that one obtains from a Lie algebra when one requires the Jacobi identity to be satisfied only up to a higher coherent chain homotopy.
+		}
+		\\
+		\vspace{.5em}
+		\begin{defblock}[$L_\infty$-algebra ~\emph{(Lada, Markl)} ~\cite{Lada1995}]
+			\includestandalone{Pictures/Figure_Linfinitydef}
+		\end{defblock}	
+		%
+		%
+	\pause
+	\vfill
+	\begin{thmblock}[Rogers \cite{Rogers2010}]
+		The \emph{higher observable algebra} $L_{\infty}(M,\omega)$ 	forms an honest $L_\infty$ algebra.
+		\footnotetext{ Take $\mu_1 = \text{d}$, $\mu_k=\lbrace\dots\rbrace_k$, $L$ is a shifted truncation of the de Rham complex.}
+	\end{thmblock}
+\end{frame}
+\note[itemize]{
+	\item $L_\infty$-algebra is the notion obtained from a Lie algebra requiring that the Jacobi identity is satisfied only up to a higher coherent chain homotopy.
+	\item The Lie-n algebra mentioned before is a $L_\infty$ algebra with underlying graded vector space concentrated in degrees $0,1...n$.
+
+	\item Definition. We say that a permutation $\sigma \in S_n$ is a $(j,n-j)$-unshuffle, $0\leq j \le1 n$  if $\sigma(1)< \dots < \sigma(j)$ and $\sigma(j+1)<\dots<\sigma(n)$.
+	\\
+	You can also say that $\sigma$ is a $(j,n-j)$-unshuffle if $\sigma(i)< \sigma(i+1)$ when $i\neq j$.
+
+	\item 	Alternatively, the Jacobiators can be also denoted as $$\displaystyle J_m=\sum_{i+j=m+1} 	\mu_i \triangleleft \mu_j = 0$$
+	employing the so-called \emph{ Richardson-Nijenhuis product}
+		 $$\mu_i\circ \mu_j := (-)^{i(j+1)}\frac{1}{j!(i-1)!}\mu_i \triangleleft \mu_j\otimes \mathbb{1}_{i-1} \circ \mathcal{A}~,$$
+		 where $\mathcal{A}$ denotes the (graded) total skew-symmetrizator.
+
+	\item see frame extra-\ref{Frame:unwapping-Jacobi} for a slightly demystification of the higher Jacobi equations.
+
+	\item more precisely this statement is a proposition/definition
+
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%------------------------------------------------------------------------------------------------
 \begin{frame}{Symplectic geometry (mechanics flavour)}
@@
 	}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
+	%------------------------------------------------------------------------------------------------
 
@@
 
-%-------------------------------------------------------------------------------------------------------------------------------------------------
+	%------------------------------------------------------------------------------------------------
 	\subsection{Singular reduction}
@@
 				admits a Poisson algebra structure 
-			\blfootnote{$I_\mu$ = associative ideal generated by $\widetilde{\mu}(\g)$}			
+				\footnote{$I_\mu$ = associative ideal generated by $\widetilde{\mu}(\g)$}			
 				\\
@@
 	}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\section{Multisymplectic Geometry}
-\checkpoint	
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}{From symplectic to {multi}symplectic} 
-	%
-	\begin{center}
-		$-$ \emph{multisymplectic means \textbf{going higher} in the degree of $\omega$} $-$
-	\end{center}
-	\pause
-	\begin{defblock}[$n$-plectic manifold ~\emph{(Cantrijn, Ibort, De Le\'on)} \cite{Cantrun2017}]
-		\includestandalone[width=0.95\textwidth]{Pictures/Figure_multisym}	
-	\end{defblock}
-	%
-	\pause
-		\begin{table}
-			\begin{tabular}{c c c}
-				symplectic forms \small($n=1$) & $\leftrightsquigarrow$ & volume forms \small($n= \text{dim}(M)-1$)
-			\end{tabular}
+	%------------------------------------------------------------------------------------------------
+
+%------------------------------------------------------------------------------------------------
+\subsection{References \& Aknowledgments}
+%------------------------------------------------------------------------------------------------
+
+%TODO aknowledgiare Leonid (sue slides) e Marvin (sua Tesi su Arxiv
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}[t,allowframebreaks]{Aknowledgments}
+	\begin{itemize}
+		\item MW reduction as "restriction to level sets", C. Lessig,
+			\href{https://arxiv.org/abs/1206.3302}{arXiv:1206.3302}
+
+	\end{itemize}
+\end{frame}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%TODO Modificare il Readme ricordando che questo si compila con Biber
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+% https://en.wikibooks.org/wiki/LaTeX/Bibliographies_with_biblatex_and_biber
+\begin{frame}[t,allowframebreaks]{Bibliography}
+	%\nocite{*}
+	\printbibliography
+\end{frame}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+% TEMP! All credit to Leonid Ryvkin www.ryvkin.eu
+\section{Leos}
+
+\subsection{Motivating example of $L_\infty$-algebra}
+%TODO All credits to Leo 
+\begin{frame}{Back to the symplectic case, $M=\mathbb R^2$}
+	Let $\omega=dx\wedge dy$, $\mathfrak X(\mathbb R^2,\omega)=\{X|~L_X\omega=0\}$.\pause
+
+	\begin{itemize}
+		\item {\bf Symplectic gradient}\\  $sgrad:C^\infty(\mathbb R^2)\to \mathfrak X(\mathbb R^2,\omega)$ (surjecive, kernel $\mathbb R$):\\ 
+		$$f\mapsto sgrad(f)={-\partial^yf \choose \partial^xf}$$\pause 
+		\item {\bf Poisson bracket} on $C^\infty(\mathbb R^2)$: $$\{f,g\}:=\partial^xf\partial^yg-\partial^xg\partial^yf$$ \\pause
+
+		\item {\bf Preservation of the bracket} $$sgrad(\{f,g\})=[sgrad(f),sgrad(g)]$$
+	\end{itemize}\pause
+	{\color{teal} Conclusion: } One can use the nicer space $C^\infty(\mathbb R^2)$ instead of $\mathfrak X(\mathbb R^2,\omega)$!
+\end{frame}
+
+\begin{frame}{Let's try the same in $\mathbb R^3$}
+	\begin{itemize}
+		\item $\mathfrak X(\mathbb R^3)=\{(v_x,  v_y,  v_z)^T\}
+		$\\ 
+		\item {\bf Lie bracket :}
+		$$[(v_x,  v_y,  v_z)^T,(w_x,  w_y,  w_z)^T]= (\sum_i v_i\partial^i(w_x) - w_i\partial^i(v_x) ,  \ldots ,\ldots)^T  $$
+		\item {\bf volume form: }$\Omega=dx\wedge dy\wedge dz$ 
+		\item {\bf volume-preserving fields: }$$\mathfrak X(\mathbb R^3,\Omega)=\{(v_x,v_y,v_z)^T~| \sum_i\partial^iv_i=0\}$$
+	\end{itemize}\pause~\\
+	This time the surjection is given by the {\bf Rotational}:
+
+	$$rot:\mathfrak X (\mathbb R^3)\to \mathfrak X (\mathbb R^3,\Omega)$$
+	$$
+	rot((v_x,v_y,v_z)^T)= (\partial^yv_z-\partial^zv_y, \partial^z v_x-\partial^xv_z, \partial^x v_y-\partial^yv_x)^T
+	$$
+\end{frame}
+
+\begin{frame}
+
+	{\color{red} Problem: } $rot$ does not commute with the bracket: $[rot(X),rot(Y)]\neq rot([X,Y])$ in general\\
+	~\\
+	\pause
+	{\color{teal} Solution: } New bracket $\{X,Y\}:=rot(X)\times rot(Y)$,\\ where $\times$ is the vector cross product on $\mathbb R^3$.\\~\\
+	\pause
+	We have $rot(\{X,Y\})=[rot(X), rot(Y)]$ \pause but no Jacobi identity. However: $$\{X,\{Y,Z\}\}-\{\{X,Y\},Z\}-\{Y,\{X,Z\}\}$$
+	$$=- grad((rot(X)\times rot(Y))\cdot rot(Z))$$
+
+\end{frame}
+
+\begin{frame}
+	$C^\infty(\mathbb R^3)\oplus \mathfrak X(\mathbb R^3)=:L_{-1}\oplus L_0$ form a \underline{\bf $L_\infty$ algebra} with:
+	\begin{itemize} 	
+		\item $l_1:L_{-1}\to L_0$, $l_1(f)=grad(f)$
+		\item $l_2:L_{0}\times L_0\to L_0$, $l_2(X,Y)=\{X,Y\}$
+		\item $l_3:L_{0}\times L_0\times L_0\to L_{-1}$, $l_3(X,Y,Z)=-(rot(X)\times rot(Y))\cdot rot(Z)$ 
+	\end{itemize}~\\~\\ \pause
+	In our case it means the following identities are satisfied:
+	\begin{itemize} 	
+		\item $l_2(l_1(f),Y)=0$
+		\item $l_2(l_2(X,Y),Z) - cycl= l_1l_3(X,Y,Z)$
+		\item $l_3(l_2(X,Y),Z,W)-cycl=0$
+	\end{itemize}
+\end{frame}
+
+\subsection{The multisymplectic observable algebra}
+
+\begin{frame}[fragile]
+	\begin{block}{Def. Observable $L_\infty$ algebra [Rogers2012]}
+		Let $(M,\omega)$ pre-multisymplectic. Set:
+			\begin{itemize} 	
+			\item $\Ham^0(M,\omega)=\{(\alpha,v)\in \Omega^{n-1}(M)\times \mathfrak X(M)~|~d\alpha=-\iota_v\omega  \}$
+			\item $\Ham^{-i}(M,\omega)= \Omega^{n-1-i}(M)$, $1\leq i\leq n-1$.
+			\item  $l_1=d:\Ham^{-i}(M,\omega)\to \Ham^{-i+1}(M,\omega)$,\\ (resp. $(d,0)$ for $i=1$)
+			\item $l_k:\Lambda^k\Ham^0(M,\omega)\to \Ham^{2-k}(M,\omega),$
+			\begin{align*}
+			&l_k((\alpha_1,v_1),...,(\alpha_k,v_k))=-(-1)^{\frac{k(k+1)}{2}}\iota_{v_k}...\iota_{v_1}\omega & k\geq 3\\
+			&l_2((\alpha_1,v_1),(\alpha_2,v_2))=(\iota_{v_2}\iota_{v_1}\omega, [v_1,v_2])
+			\end{align*}
+		\end{itemize}
+	\end{block}
+	\vspace{-15mm}
+	\pause
+	% https://q.uiver.app/#q=WzAsNixbMCwwLCJDXlxcaW5mdHkoTSkiXSxbMSwwLCJcXE9tZWdhXjEoTSkiXSxbMiwwLCIuLi4iXSxbMywwLCJcXE9tZWdhXntuLTN9KE0pIl0sWzQsMCwiXFxPbWVnYV57bi0yfShNKSJdLFs1LDAsIlxcSGFtXjAoTSkiXSxbMCwxLCJkIl0sWzEsMiwiZCJdLFsyLDMsImQiXSxbMyw0LCJkIl0sWzQsNSwiKGQsMCkiXSxbNSw1LCJsXzIiLDAseyJsYWJlbF9wb3NpdGlvbiI6NDAsIm9mZnNldCI6MSwiYW5nbGUiOjQ1LCJsZXZlbCI6Mn1dLFs1LDQsImxfMyIsMCx7ImN1cnZlIjotMywibGV2ZWwiOjN9XSxbNSwzLCJsXzQiLDIseyJjdXJ2ZSI6MywibGV2ZWwiOjR9XV0=
+	\[\tiny\begin{tikzcd}
+		{C^\infty(M)} & {\Omega^1(M)} & {...} & {\Omega^{n-3}(M)} & {\Omega^{n-2}(M)} & {\Ham^0(M)}
+		\arrow["d", from=1-1, to=1-2]
+		\arrow["d", from=1-2, to=1-3]
+		\arrow["d", from=1-3, to=1-4]
+		\arrow["d", from=1-4, to=1-5]
+		\arrow["{(d,0)}", from=1-5, to=1-6]
+		\arrow["{l_4}"', curve={height=18pt}, Rightarrow, scaling nfold=4, from=1-6, to=1-4]
+		\arrow["{l_3}", curve={height=-18pt}, Rightarrow, scaling nfold=3, from=1-6, to=1-5]
+		\arrow["{l_2}"{pos=0.4}, shift right, Rightarrow, from=1-6, to=1-6, loop, in=10, out=80, distance=10mm]
+	\end{tikzcd}\]
+\end{frame}
+
+\begin{frame}
+\begin{block}{Thm. $Ham^\bullet(M,\omega)$ is an $L_\infty$-algebra [Rogers2012]}
+This means $
+\substack{
+l_1l_{m+1}(x_1,...,x_{m+1})=\sum_{i<j}(-1)^{i+j}l_m(l_2(x_{i},x_j),x_1,...,\widehat{x_i},...,\widehat{x_j},...,x_{m+1})}
+$ for all $m$ and all possible $x_i$, where $l_0:=0$ and $l_{m+2}:=0$.
+\end{block}\pause
+
+{\bf Remark:} We could instead turn $\Ham^0(M,\omega)$ into a Left-Leibniz algebra by $[(\alpha,v)(\beta, w)]:=(L_v\beta,[v,w])$. This satisfies (left-)Jacobi, but is not skew-symmetric.\pause
+
+\begin{block}{Remark}
+ The above also works if we replace $(C^\infty(M),\mathfrak X(M))$ with any Lie-Rinehart algebra $(A, L)$ and $\omega$ with a cocycle in $(\Lambda^{n+1}_AL)^*$.
+\end{block}\pause
+A Lie Rinehart algebra is: 
+\begin{itemize} 
+	\item A commutative algebra $A$ and an A-module $L$
+	\item A Lie algebra structure on $L$
+	\item A Lie algebra and module homomorphism $\rho:L\to \Der(A)$
+\end{itemize}
+such that $[\ell, a\tilde \ell]=a[\ell,\tilde \ell]+\rho(\ell)(a) \cdot \tilde\ell$
+\end{frame}
+
+\subsection{Preview of our answer}
+\begin{frame}
+We will develop a multisymplectic reduction in this talk, symplectically it is:
+\begin{block}{Construction: Multisymplectic reduction in the symplectic case}
+Let $Q_S=\{f~|~ f|_S=0\rm{~and~} df|_S=0\}$ Then the $L_\infty$-reduction is:
+$$
+\frac{N(I_S)\cap N(I_\mu+Q)}{I_\mu+Q}
+$$
+\end{block}	\pause
+Such a formula can be more generally applied to a Poisson algebra $P$ with associative ideals $I\subset J$ such that $\{I,I\}\subset I$ and $\{I,J\}\subset J$:
+$$
+\frac{N(J)\cap N(I+Q)}{I+Q}
+$$
+with $Q=\{f\in J|~\{f,P\}\subset J\}$
+\end{frame}
+
+\section{Reduction using Constraint triples}
+
+\subsection{General idea}
+\begin{frame}
+\begin{exampleblock}{Idea of multisymplectic observable reduction:}
+	Mimic the above construction of $\Ham^\bullet$\\ with triples of the type (algebra , subalgebra, ideal).
+\end{exampleblock}\pause
+After [Dippel2023] we call such triples { \bf constraint triples} and their parts \emph{total space, normal space, zero space}.\\~
+
+Let $S$ be a closed set. We describe $C^\infty(S)$ by $\frac{C^\infty(M)}{I_S}$.\\ We think of it as the constraint triple:
+$$
+\mathcal A=(\mathcal A_T,\mathcal A_N,\mathcal A_0)=(C^\infty(M),C^\infty(M), I_S)
+$$
+It is a (strong) constraint algebra,\\ i.e. $\mathcal A_0\subset \mathcal A_N\subset \mathcal A_T$ subalgebras and $\mathcal A_0\subset \mathcal A_T$ ideal.
+
+\end{frame}
+
+\subsection{A dictionary between algebra and geometry}
+\begin{frame}{Translating geometry to algebra}
+
+\begin{table}[]
+	\begin{tabular}{l|l|l}
+	 geometry & algebra & translation \\
+		\hline	
+	smooth manifold $M$ & comm. algebra $\mathcal A_T$  	& $\mathcal A_T=C^{\infty}(M)$\\ \hline\pause
+	vector fields $\mathfrak X(M)$ & derivations $\Der(\mathcal A_T)$ &  $\Der(C^\infty(M))=\mathfrak X(M)$\\ \hline\pause
+	closed subset $S\subset M$ & ideals $\mathcal A_0\subset \mathcal A_T$ & $\mathcal A_0=I_S=\{f~|~f|_S=0\}$ \\ \hline\pause
+	action $G\circlearrowleft M$ & Lie algebra map & infinitesimal generators\\
+	 of connected group &$\underline{\cdot}:\mathfrak g\to \Der(\mathcal A_T)$ & of the action \\ \hline \pause
+	 $G$ action preserves $S$ & $\underline \xi(I_S)\subset I_S$ $\forall \xi\in\mathfrak g$& \color{red} Careful! Not equivalent! \\ \hline
+	\end{tabular}\pause
 \end{table}
-
-	\vfill
-	\pause
-	\begin{block}{Historical motivation}
-		Mechanics: geometrical foundations of \textit{(first-order)} field theories.
+	\begin{alertblock}{Warning}
+	$\partial_x$ is algebraically preserving $S=[0,1]\subset \mathbb R=M$, even though the flow leads out of the set.
+\end{alertblock}
+\end{frame}
+
+\begin{frame}{Derivations of constraint algebras}
+	$\mathcal A=(\mathcal A_T,\mathcal A_N,\mathcal A_0)=(C^\infty(M),C^\infty(M), I_S)$\\~
+\begin{itemize} 
+	\item $\Der(\mathcal A)_T:=\Der(\mathcal A)_T$ corresponds to all vector fields\pause
+	\item  $\Der(\mathcal A)_N:=\{v\in \Der(\mathcal A)~|~v(\mathcal A_N)\subset \mathcal A_N, ~v(\mathcal A_0)\subset \mathcal A_0\}$\\
+	corresponds to vector fields ({\color{red}algebraically}) tangent to $S$.\\ \pause
+
+	\item  $\Der(\mathcal A)_0:=\{v\in \Der(\mathcal A)~|~v(\mathcal A_N)\subset \mathcal A_0\}$\\
+	are vector fields vanishing on $S$.\pause
+		\begin{block}{Lemma: Algebraic vanishing = geometric vanishing}
+		$\Der(\mathcal A)_0=\{v ~| ~v|_S=0\}=I_S\cdot \mathfrak X(M)$.
+	\end{block}\pause
+\end{itemize}	
+\end{frame}
+
+\begin{frame}
+	$\mathcal A=(C^\infty(M),C^\infty(M), I_S)$\\
+	$\Der(\mathcal A)=(\mathfrak X(M),~~\{v| v(I_S)\subset I_S\},~~ I_S\mathfrak X(M))$
+		\begin{block}{Lemma: $\mathfrak L:=\Der(\mathcal A)$ is a constraint Lie-Rinehart algebra over $\mathcal A$}
+			This means 
+	\begin{itemize} 
+		\item $\mathfrak L_T$ is a Lie Rinehart algebra over $\mathcal A_T$.
+		\item $\mathfrak L$ is a strong constraint module over $\mathcal A$, i.e.\\ $\mathcal A_N\mathfrak L_N\subset \mathfrak L_N$ and $\mathcal A_0\mathfrak L_T+\mathcal A_T\mathfrak L_0\subset \mathfrak L_0$.
+		\item $[\mathfrak L_N,\mathfrak L_N]\subset \mathfrak L_N$ and  $[\mathfrak L_N,\mathfrak L_0]\subset \mathfrak L_0$
+	\end{itemize}
+
+\end{block}\pause
+
+\begin{exampleblock}{Corollary: $(\Lambda \mathfrak L)^*$ has a constraint Cartan calculus $d, \iota, L$}
+	\begin{itemize} 
+	\item $(\Lambda^k \mathfrak L)^*_T=\Omega^k(M)$
+	\item $(\Lambda^k \mathfrak L)^*_N=\{\alpha~|~\alpha(v_1,...,v_k)\in \mathcal A_N~\forall v_i\in \mathfrak L_N , $ \\ ~~~~~~~~~~~~~~~~~~~~$ \alpha(v_1,...,v_{k-1},w)\in \mathcal A_0~\forall v_i\in \mathfrak L_N , w\in \mathfrak L_0 \}$
+	\item $(\Lambda^k \mathfrak L)^*_0=\{\alpha~|~\alpha(v_1,...,v_k)\in \mathcal A_0~\forall v_i\in \mathfrak L_N\}$
+	\end{itemize}
+
+\end{exampleblock}
+
+\end{frame}
+
+\subsection{Introducing symmetry}
+\begin{frame}
+Let $F\subset \Der(\mathcal A)_N$ a Lie subalgebra  (typically $F=\underline{\mathfrak g}$). Consider:
+\begin{itemize} 
+	\item the constraint algebra $\mathcal B= (C^\infty(M),~~~~ \{f~|~F(f)\subset I_S\},~~~ I_S)$\pause
+	\item the constraint Lie-Rinehart algebra $\mathcal L$  \[ (\mathfrak X(M),~~~~\{v ~|~ [v,F]\subset C^\infty(M)F+I_S\mathfrak X(M)\}, ~~~~ C^\infty(M)F+I_S\mathfrak X(M) )\]
+	\item \pause the constaint differential forms 
+	\[
+	\mathcal W=(\Omega(M),~~~, \{\alpha |\iota_\xi\alpha,L_\xi\alpha\in (\Lambda \mathfrak L)^*_0 ~~\forall \xi\in F \},~~~~(\Lambda \mathfrak L)^*_0  )
+	\]
+	where $(\Lambda^k \mathfrak L)^*_0=\{\alpha~|~\alpha(v_1,...,v_k)\in \mathcal A_0~\forall v_i\in \mathfrak L_N\}$
+\end{itemize}
+\begin{block}{'Lemma': $\mathcal L$ has a Cartan calculus on $\mathcal W$}
+	In particular, from the premultisymplectic form $\omega$ we obtain a constraint $L_{\infty}$-algebra.
 \end{block}
-	%
-	\begin{table}
-		\ifHandout
-		%
-		\else
-		\only<4>{
-		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
-            \hline
-            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
-            \hline
-            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold &  \\[.25em]
-            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra &  \\[.25em]
-            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map &  
-            \\
-            \hline
-  \multicolumn{1}{c}{}
-            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
-            &  \multicolumn{1}{@{}c@{}}{}              \\
-		\end{tabular}
-		}
-		\fi
-		\onslide<5->{
-		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
-            \hline
-            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
-            \hline
-            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold & multisymplectic manifold \\[.25em]
-            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra & $L_\infty$-algebra \\[.25em]
-            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map & group actions admitting (homotopy) comomentum map
-            \\
-            \hline
-  			\multicolumn{1}{c}{}
-            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
-            &
-            \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{field-theoretic systems}}$} 
-               \\
-		\end{tabular}
-		}
-	\end{table}
-
-\end{frame}
-\note[itemize]{
-	\item Historically, the interest in multisymplectic manifolds, has been motivated by the need for understanding the geometrical foundations of first-order classical field theories.
-	The key point is that, just as one can associate a symplectic manifold to an ordinary classical mechanical system (e.g. a single
-point-like particle constrained to some manifold), it is possible to associate a multisymplectic
-manifold to any classical field system (e.g. a continuous medium like a filament or a fluid). See frame Extra-\ref{Frame:Ms-Field-Mechanics}
-
-	\item General ideas basic parallelisms with caveats
-	\item caveat: points in multiphase spaces are not states
-	\item the table hides the duality between geometric and algebraic approaches to the problem.
-	\item	Mechanics: geometrical foundations of \textit{(first-order)} field theories.
-		\begin{itemize}
-		 \item[-] Kijowski, W. Tulczyjew \cite{Kijowski1979}; %(1979)
-		 \item[-] Cariñena, Crampin, Ibort \cite{Carinena1991b};% (1991)
-		 \item[-] Gotay, Isenberg, Marsden, Montgomery \cite{Gimmsy1};%(1998)
-		 \\ $\cdots$
-		\end{itemize}
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}{Observables in $n$-plectic geometry}
-	%
-	\begin{defblock}[Hamiltonian $(n-1)$-forms]
-		\begin{displaymath}
-			\Omega^{n-1}_{ham}(M,\omega) 	:=
-			\biggr\{ \sigma \in  \Omega^{n-1}(M) \; \biggr\vert \; 
-				\exists \vHam_\sigma \in \mathfrak{X}(M) ~:~ 
-				\tikz[baseline,remember picture]{\node[rounded corners,
-                        fill=orange!5,draw=orange!30,anchor=base]            
-            			(target) {$d \sigma = -\iota_{\vHam_\sigma} \omega$ };
-            	}				
-				~\biggr\} 
-			\end{displaymath}
-	\end{defblock}
-
-	\pause
-		\tikz[overlay,remember picture]
-		{
-			\node[rounded corners,
-                 fill=orange!5,draw=orange!30,anchor=base]
-            	 (base) at ($(current page.north east)-(2,1)$) [rotate=-0,text width=3.5cm,align=center] {\footnotesize{\textcolor{red}{Hamilton-DeDonder-Weyl \\equation}}};
-		}	
-	\begin{tikzpicture}[overlay,remember picture]
-    	\path[->] (base.south) edge[bend right,red](target.north);
-    \end{tikzpicture}
-	%
-	\vfill
-	\begin{columns}[T]
-		\pause
-		\setlength{\belowdisplayskip}{5pt}
-		\begin{column}{.50\linewidth}
-			%
-			\vspace{-1em}
-			\begin{thmblock}[Observables $L_\infty$-algebra]
-				$\Omega^{n-1}_{ham}(M,\omega)$ endowed with
-				\vspace{-.5em}
-				\begin{displaymath}
-					\lbrace \sigma_1, \sigma_2 \rbrace =			
-					~ - \iota_{\vHam_1}\iota_{\vHam_2} \omega 
-				\end{displaymath}			
-				can be "completed" to a \\ $L_\infty-algebra$.
-			\end{thmblock}
-			%	
-		\end{column}	
-		%
-		\pause
-		\begin{column}{.50\linewidth}
-		%
-			\begin{itemize}
-				\item[\cmark] Skew-symmetric;
-				\item[\xmark] multiplication of observables;
-				\item[\xmark] Jacobi equation;
-				%\\ \hspace*{4.25em} full-fledged Jacobi equation;
-				\item[\smark] Jacobi equation \emph{up to homotopies}.
-			\end{itemize}			
-			%
-				\[
-					\small
-					\{\alpha,\{\beta,\gamma\}\} + \text{\it cyc. perm.}
-					= {\color{orange}\d \iota_{X_\alpha} \iota_{X_\beta} \iota_{X_\gamma}\omega}
-				\]
-		\end{column}	
-	\end{columns}
-	%
-	\vfill
-	\pause
-	Interesting alternatives:
-	\begin{itemize}
-		\item  descend to $\Omega^{k-1}_{ham}(M) / {\color{orange}\d\hspace{1pt}\Omega^{k-2}(M)}$, hence getting a Lie algebra;
-		\item Incorporate the {\color{orange}discrepancy} as part of the data of the space of observables $ 
-				L_\infty(M,\omega) = \Omega_{ham}^{k-1}(M)\oplus{\color{orange}\Omega^{\leq k-2}(M)}$
-			%a \textbf{homotopy Lie algebra} or \textbf{$L_\infty$-algebra}.
-	\end{itemize}
-
-\end{frame}
-\note[itemize]{
-	\item
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%---------------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{$L_\infty$-algebra of Observables}
-\begin{frame}[fragile,t]{$L_\infty$-algebra of Observables (higher observables) }
-	Let be $(M,\omega)$ a $n$-plectic manifold.
-	\begin{defblock}[$L_\infty$-algebra of observables ~\emph{(Rogers)} ~\cite{Rogers2010}]
-
-		\hspace{.25em} $L\infty(M,\omega)$ is given by:
-
-		\begin{itemize}
-			\item[•] a cochain-complex $(L,\{\cdot\}_1)$ 
-		\end{itemize}
-		\begin{center}
-		\ifHandout
-			\includestandalone{Pictures/Figure_Observables}	
-		\else
-			\includestandalone{Pictures/Frame_Observables}
-		\fi				
-		\end{center}
-		\onslide<2->{
-			\begin{itemize}
-				\item[•] with $n$ (skew-symmetric) multibrackets $(2 \leq k \leq n+1)$
-			\end{itemize}
-			\begin{center}
-				\includestandalone{Pictures/Equation_Multibracket}	
-			\end{center}
-		}
-		%
-	\end{defblock}
-  \end{frame}
- \note[itemize]{
-	\item if symplectic manifolds are the symmetric take on mechanics, Poisson algebras are the algebraic counterpart.
- 	\item A Lie algebra is associated to an ordinary symplectic manifold (its Poisson algebra).
-	%(Underlying this is a Lie algebra, whose Lie bracket is the Poisson bracket.)
-	Similarly, one associates an Lie-$n$ algebra to any $n$-plectic manifold.
- 	% https://ncatlab.org/nlab/show/n-plectic+geometry 	 
- 	 %https://ncatlab.org/nlab/show/Poisson+bracket+Lie+n-algebra
-	 \item Basically, the higher observables algebra is a chunk of the de Rham complex of $M$ with inverted grading( convention employed here) and an extra structure called "multibrackets".
- 	\item ( In the 1-plectic case it reduces to the corresponding Poisson algebra of classical observables)
- 	\item Rogers associated to any n-plectic mfd a $L\-\infty$ algebra, Zambon generalized it to the pre-n-plectic case.
- 	\item Recognize in the definition of $\{\cdot,\ldots,\cdot\}_k$ the contraction with hamiltonian fields $v_\sigma$ w.r.t. $\sigma$.
-  	\item Note $	\iota_{v_{\sigma_1}}\cdots\iota_{v_{\sigma_k}} = (-)^{(k-1)+(k-2)+\dots+1}\iota_{v_{\sigma_k}}\cdots\iota_{v_{\sigma_1}} = (-)^{\frac{k(k-1)}{2}}\iota_{v_{\sigma_k}}\cdots\iota_{v_{\sigma_1}}$
- 	The definition usually find in literature of Rogers multibrackets involves the coefficient $ (-)^{\frac{k(k-1)}{2}} = -\varsigma(k-1) = (-)^{k+1} \varsigma(k)$.
-  \item higher observables is Special instance of a more general object  called $L\-\infty$ Algebra...
- }
-%------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\section{Multisymplectic observables reduction}
-\checkpoint	
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}{Singular Reduction: Roadmap}
-	%
-	\begin{block}{Data:}
-			\begin{itemize}
-				\item A \emph{constraint set} $N$ (possibly singular),
-				\item An infinitesimal action preserving $N$.
-			\end{itemize}
-	\end{block}
-	%
-	\vfill
-	\pause
-	%
-	\begin{block}{Goal:}
-		\begin{itemize}
-			\item Obtain a "reduced" observables algebra out of the data.
-		\end{itemize}
-	\end{block}
-	%
-	\vfill
-	\pause
-	%
-	\begin{block}{Strategy:}
-		\begin{enumerate}
-			\item Define smooth fields/forms \emph{tangent to $N$},
-			\item define smooth fields/forms \emph{vanishing along $N$},
-			\item define \emph{reducible fields} requiring the preservation of the vanishing objects,
-			\item define \emph{reducible forms} requiring their conservation w.r.t. the infinitesimal action,
-			\item define \emph{reducible and vanishing observables},
-			\item \textbf{quotient}
-		\end{enumerate}
-	\end{block}
-
-\end{frame}
-\note[itemize]{
-	\item
-}
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[shrink]{Smooth objects on a singular set}
-	Consider $N$ closed subset of $M$.
-	\vfill
-	\pause
-	\begin{defblock}
-	 $I_N$ = ideal of smooth functions vanishing over $N$.
-	\end{defblock}
-	\vfill
-	\pause
-
-	\begin{columns}[T]
-		\setlength{\belowdisplayskip}{5pt}
-		\begin{column}{.65\linewidth}
-			%
-			\centering \it
-				\begin{defblock}[v.f tangent to $N$]
-					\begin{displaymath}
-						\X_N(M):=
+\end{frame}
+
+\subsection{The reduced $L_\infty$-algebra}
+\begin{frame}[fragile]
+Let $(M,\omega)$ premultisymplectic, $S\subset M$ closed and \\ $F\subset \mathfrak X(M)$ a Lie subalgebra s.th. $F(I_S)\subset I_S$\\ ~\\
+The following subquotient $\frac{\Ham(M,\omega)_N}{\Ham(M,\omega)_0}$\\ of $\Ham(M,\omega)_T=\Ham(M,\omega)$ forms an $L_\infty$-algebra:
+
+	\[\small
+		\frac{
 			\left\lbrace
-							v \in \X(M)
-						~\Big\vert~
-							\L_v(I_N) \subseteq I_N
-						\right\rbrace
-					\end{displaymath}
-				\end{defblock}
-				\begin{defblock}[v.f vanishing on $N$]
-					\begin{displaymath}
-						I_\X(N):=
-						\left\lbrace
-							v \in \X(M)
-						~\Big\vert~
-							\L_v(C^\infty(M)) \subseteq I_N
-						\right\rbrace
-					\end{displaymath}				
-				\end{defblock}				
-		\end{column}	
-		%
-		%
-		\begin{column}{.35\linewidth}
-			\centering 
-			\includestandalone[width=0.8\textwidth]{Pictures/Figure_VfTangentN}			
-		\end{column}	
-	\end{columns}			
-	%	
-	\pause
-
-				%
-
-				%	
-		\begin{tcolorbox}[
-		enhanced,frame hidden,borderline={0.5pt}{0pt}{blue},
-		arc=5pt,colback=white,
-		colbacktitle=white,]
-			\color{blue}{\textbf{Lem}:} If $N$ is smoothly embedded,  $\X(N)\cong {X_N(M)}/{I_\X}$.
-		\end{tcolorbox}
-
-		\pause
-
-		\begin{defblock}[Differential form vanishing on $N$]
-			\begin{displaymath}
-				I_{\Omega(N)}:=
-				\left\lbrace
-					\alpha\in\Omega^k(M
-				~\left\vert~
-					\begin{array}{l r}
-						k\geq 0,~		\\		
-						\alpha(u_1,\ldots,u_k) \in I_N & \forall u_i \in\X_N(M)
+			\begin{array}{l}
+				\alpha\in \Omega^{\leq n-2}(M) ~\mathrm{, respectively}\\	
+				(\alpha,X) \in \Omega^{n{-}1}(M) \oplus\mathfrak X(M)
 			\end{array}
-				\right\rbrace\right.
-			\end{displaymath}
-		\end{defblock}
-
-\end{frame}
-\note[itemize]{
- \item $N$ is not a submanifold in general. An example is $N=\mu^{-1}(0)$ for a certain smooth map $N$.
- \item observe that if $N$ is a smooth embedded submanifold, one has that $\X(N)\cong \frac{X_N(M)}{I_\X}$
-
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Multisymplectic singular reduction}
-\begin{frame}{Reducible smooth objects \quad \small (w.r.t. $N$ and $\g\action M$)}
-	Consider $\g \action M$ by vector fields tangent to $N$ % \hfill( fond. distribution $\underline{\g}\subseteq \X_N(M)$)
-	\\
-	\vfill
-	Denote by :  
-	\hspace{1em} $\underline{\g}\subseteq \X_N(M)$ the fundamental distribution,
-	\\
-	\hspace{6.5em}  $\X_g$ the $C^\infty$-module generated by $\underline{\g}$.
-	\\
-	\vfill
-	\begin{defblock}[Reducible v.fields ]
-			\begin{displaymath}
-				\X(M)_{[N]} :=
-				\left\lbrace
-					v \in \X(M)
-				~\left\vert~
-					\begin{array}{l}
-						\L_v (I_N) \subseteq I_N	\\		
-						\L_v (\X_g) \subseteq \X_g + I_\X
-					\end{array}
-				\right\rbrace\right.
-			\end{displaymath}
-%			\blfootnote{
-%			 $\X_g$ = $C^\infty(M)$-module generated by the fundamental distribution.
-%			}
-
-	\end{defblock}	
-	%
-	\pause
-	%
-	\begin{defblock}[Reducible forms ]
-		\begin{displaymath}
-			\Omega(M)_{[N]} :=
-			\left\lbrace
-				\alpha \in \Omega(M)
-			~\left\vert~
-				\begin{array}{l r}
-					\L_\underline{\xi} \,\alpha \in I_{\Omega(N)}	\\		
-					\iota_\underline{\xi} \,\alpha \in I_{\Omega(N)}	& \forall \xi \in \g				\end{array}
-			\right\rbrace\right.
-		\end{displaymath}	
-	\end{defblock}	
-	%
-	\pause
-	\vfill
-	%
-	Let $(M,\omega)$ be a $k$-plectic manifold
-	\begin{defblock}[Reducible Hamiltonian forms]
-		\begin{displaymath}
-			(\Omega(M)_{ham}^{n-1})_{[N]} :=
-			\left\lbrace
-				\alpha \in \Omega(M)_{ham}^{n-1}
-			~\left\vert~
-				\begin{array}{l r}
-					\alpha \text{ is a reducible form} \\
-					\vHam_\alpha \text{ is a reducible v.field}
-				\end{array}
-			\right\rbrace\right.
-		\end{displaymath}	
-	\end{defblock}
-
-\end{frame}
-\note[itemize]{
- \item $\g\action M$ by vector field tangent to $N$ means that $\underline{\xi}\in\X_n(M) \forall \xi \in \g$
- \item Spelling out the definition: reducible vector fields are 
- \\i) v.f. tangent to N 
- \\ii) such that their commutator with any $\underline{\xi}$ lies in $\X_\g$ along $N$.
- \item more algebraically, they stabilize both $I_N$ and $\X_g + I_\X$.
- \item observe that $\L_v I_\X \subseteq I_\X$ since , $\forall u \in I_\X$ $\forall f \in C^\infty(M)$ one has\\
- $(\L_v u) f = \L_{[v,u]} f = \L_v\L_u f - \L_u\L_v f \in I_N$
- \item
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}\frametitle{Hierarchy of auxiliary constructions}
-	\begin{minipage}{\textwidth}
-	\centering
-	\scalebox{.65}{
-	\begin{tikzpicture}
-		\node (A) at (0,10.0) {\fbox{\parbox{5.6cm}{\centering Ideal of functions vanishing on $N$ \\ $I_N$}}};
-		\node (B) at (0,8.3) {\fbox{\parbox{4.4cm}{\centering Vector fields tangent to $N$ \\ $\X_N(M)$}}};
-		\node (C) at (3,6.5) {\fbox{\parbox{4.2cm}{\centering Forms vanishing along $N$ \\ $I_\Omega(N)$}}};
-		\node (D) at (3,4.2) {\fbox{\parbox{2.7cm}{\centering Reducible forms \\ $\Omega(M)_{[N]}$}}};
-		\node (E) at (-3,6.3) {\fbox{\parbox{5.3cm}{\centering Fundamental $C^\infty$-module \emph{plus} \\ vector fields vanishing along $N$ \\ $\X_\g(M)+I_\X(N)$}}};
-		\node (E') at (-3,4.2) {\fbox{\parbox{3.8cm}{\centering Reducible vector fields \\ $\X(M)_{[N]}$}}};
-		\node (F) at (0,2.4) {\fbox{\parbox{3.7cm}{\centering Reducible observables \\ $L_\infty(M,\omega)_{[N]}$}}};
-		\node (G) at (0,0.6) {\fbox{\parbox{5.0cm}{\centering Vanishing ideal of observables \\ $I_{L_\infty}(N)$}}};
-		\node (H) at (0,-1.05) {\fbox{\parbox{4.3cm}{\centering Observable reduced space \\ $L_\infty(M,\omega)_N$}}};
-
-		\draw[->] (A)-- node[right=1pt]{{\scriptsize used to define}} (B);
-		\draw[->] (B)-- (C);
-		\draw[->] (C)-- node[right=.25cm]{\rotatebox{-90}{\small $\subset$}} (D);
-		\draw[->] (B)-- (E);
-		\draw[->] (D)-- (F);
-		\draw[->] (E)-- node[left=.25cm]{\rotatebox{-90}{\small $\subset$}} (E');
-		\draw[->] (E')-- (F);
-		\draw[->] (F)-- node[right=.25cm]{\rotatebox{90}{\small $\subset$}} (G);
-		\draw[->] (G)-- (H);
-
-		\node[right=2.95cm] at (A) {\scriptsize\emph{associative ideal}};
-		\node[right=2.30cm] at (B) {\scriptsize\emph{Lie algebra}};
-		\node[right=2.25cm] at (C) {\scriptsize\emph{differential ideal}};
-		\node[right=1.5cm] at (D) {\scriptsize\emph{differential graded subalgebra}};
-		\node[left=2cm] at (E') {\scriptsize\emph{Lie subalgebra}};
-		\node[left=2.8cm] at (E) {\scriptsize\emph{Lie ideal}};
-		\node[right=2cm] at (F) {\scriptsize\emph{$L_\infty$-subalgebra}};
-		\node[right=2.65cm] at (G) {\scriptsize\emph{$L_\infty$-ideal}};
-		\node[right=2.3cm] at (H) {\scriptsize\emph{$L_\infty$-algebra}};
-	\end{tikzpicture}
-	}
-	\end{minipage}
-\end{frame}
-\note[itemize]{
- \item
-}
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}{Multisymplectic observable reduction}
-	\begin{defpropblock}[Reducible $L_\infty$-observables]
-		Is the {\color{blue!70!black}$L_\infty$-subalgebra} of $L_\infty(M,\omega)$ given by
-		\begin{displaymath}
-			L_\infty(M,\omega)_{[N]}^k :=
-			\begin{cases}
-				\Omega^{n-1-k}(M)_{[N]} 
-				\qquad\text{\color{gray}\small (reducible forms) }
-				& \text{if } n-1\leq k < 0 \\
-				(\Omega(M)_{ham}^{n-1})_{[N]} 
-				\quad
-				\text{\color{gray}\small (reducible hamiltonians) }
-				& \text{if } k = 0 \\
-				0 & \text{if } k > 0
-			\end{cases}
-		\end{displaymath}
-	\end{defpropblock}
-	%
-	\pause
-	%
-	\begin{defpropblock}[Vanishing $L_\infty$-observables]
-		Is the {\color{blue!70!black}$L_\infty$-ideal} of $L_\infty(M,\omega)_{[N]}$ given by
-		\begin{displaymath}
-			I_{L_\infty(M,\omega)} :=
-			\left\lbrace
-				\alpha \in L_\infty(M,\omega)_{[N]}
 			~\left\vert~
 			\begin{array}{l l}
-					\alpha(v_1,\dots,v_k) \in I_N  \quad \forall v_i \in \X_N &
-					\text{if}~ \alpha \in \Omega^k \\
-					\vHam_\alpha \in \X_\g + I_\X &
-					\text{if}~ \alpha \in \Omega^{n-1}
-				\end{array}
-			\right\rbrace\right.
-		\end{displaymath}
-	\end{defpropblock}
-	%
-	\pause
-	%
-	\begin{thmblock}[Blacker - M. - Ryvkin]%[Reduced $L_\infty$-algebra of observables]
-		The reduction of $L_\infty(M,\omega)$  with respect to $\g\curvearrowright (N\subset M)$ is the %$L_\infty$-algebra
-		quotient
-		\begin{displaymath}
-					L_\infty(M,\omega)_N = \frac{L_\infty(M,\omega)_{[N]}}{I_{\L_\infty}(N)}~.		
-		\end{displaymath}
-	\end{thmblock}
-
-\end{frame}
-\note[itemize]{
- \item The graded vector space underlying the reduced $L_\infty$-algebra $\Ham_\infty(M,\omega)_N$ is explicitly given by
-\begin{displaymath}
-	\Ham_\infty(M,\omega)_N =
-	\frac{
-		\left\lbrace
-			(\alpha,v) \in \Omega(M){[n{-}1]}\oplus\X(M)
-		~\left\vert~
-			\begin{array}{l l}
-				\iota_v \omega = -\d \alpha^{(0)} &
-				\\
-				\iota_\xi \alpha \in I_{\Omega}(N) &
-				\\
-				\L_\xi\alpha \in I_{\Omega}(N)
-				&
-				\\
-				\L_\xi v \in \fgmodule +\vanvf
-				&~\forall \xi \in \g 
-				\\
-				v \in \X_N(M)
-				&
+				\iota_\xi \alpha \in (\Lambda \mathfrak L)^*_0 &\\
+				L_\xi\alpha \in (\Lambda \mathfrak L)^*_0&~\forall \xi \in F\\
+				\hline
+				\iota_X \omega = -d \alpha &\\
+				X(I_S)\subset I_S &\\
+				L_\xi X \in C^{\infty}(M) F + I_S\mathfrak X(M)
+				&~\forall \xi \in F\\
 			\end{array}
@@
 			\left\lbrace
-			(\alpha,v) \in \Omega(M){[n{-}1]}\oplus\X(M)
+			\begin{array}{l}
+				\alpha\in \Omega^{\leq n-2}(M) ~\mathrm{, respectively}\\	
+				(\alpha,X) \in \Omega^{n{-}1}(M) \oplus \mathfrak X(M)
+			\end{array}
 			~\left\vert~
 			\begin{array}{l}
-				\alpha \in I_{\Omega}(N)
-				\\
-				v \in \fgmodule +\vanvf
+				\alpha \in (\Lambda \mathfrak L)^*_0\\
+				\hline
+				\iota_X \omega = -d \alpha\\
+				X \in C^{\infty}(M) F + I_S\mathfrak X(M)
 			\end{array}
@@
 			\right\rbrace
-	}~.
-\end{displaymath}
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}{Singular reduction (Conclusions)}
-		  \centering 
-	\emph{Reduction of states vs.\ reduction of observables}
-	\vfill
-	\begin{minipage}{.7\textwidth}
-	\hspace{-.4cm}
-	\begin{tikzpicture}
-		\draw (-4,-2.5) rectangle (4,2.5);
-		\draw (-4,0) -- (4,0);
-		\draw (0,-2.5) -- (0,2.5);
-
-		\draw node[align=center] at (-2,1.25) {symplectic\\ reduction};
-		\draw node[align=center] at (2,1.25) {multisymplectic\\ reduction};
-		\draw node[align=center] at (-2,-1.25) {\'{S}niatycki--Weinstein,\\Dirac,\\Arms--Gotay--Jennings\\ reduction};
-		\draw node[align=center] at (2,-1.25) {\color{UniGreen}$L_\infty$ reduction};
-
-		\draw node[align=center] at (2,2.85) {\color{UniGreen}\emph{higher}};
-		\draw node[align=center] at (-2,2.85) {\emph{lower}};
-
-		\draw node[align=right] at (-4.7,1.25) {\emph{states}};
-		\draw node[align=right] at (-5.13,-1.25) {\color{UniGreen}\emph{observables}};
-	\end{tikzpicture}
-	\end{minipage}
-
-	\pause
-			\vfill
-		  \centering 
-		  {\Huge\color{red} 
-		  \emph{Thank you for your attention!}}
-\end{frame}
-\note[itemize]{
- \item Consider $N=\mu^{-1}(0)$ to be regular (smooth embedding)
-		\vspace{.5em}
-		\begin{table}[]
-			\begin{tabular}{ccc}
-			Multisymplectic               &                      & Multisymplectic                  \\
-			regular                       & $\equiv$             & singular                \\
-			reduction & & reduction
-			\end{tabular}
-		\end{table}
-
-		\item
-			Consider $\omega$ to be $1$-plectic
-			\vspace{.5em}
-			\begin{table}[]
-				\begin{tabular}{ccc}
-				Multisymplectic               &                      &  Sniaticky--Weinstein                  \\
-				singular                       & $\cancel\equiv$             & singular                \\
-				reduction & & reduction
-				\end{tabular}
-			\end{table}
-
-			(but $\exists$ a canonical Poisson algebra morphism)
-
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%------------------------------------------------------------------------------------------------
-% APPENDIX
-%------------------------------------------------------------------------------------------------
-\appendix
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\section{Complementary Material}
-%##################################################################################
+		}
+\]
+where $(\Lambda^k \mathfrak L)^*_0=\{\alpha~|~\alpha(v_1,...,v_k)\in \mathcal A_0~\forall v_i\in \mathfrak L_N\}$
+\end{frame}
+
+\subsection{Main application}
+\begin{frame}[fragile]
+Let $(M,\omega)$ premultisymplectic, $\underline{\cdot}:\mathfrak g\to \mathfrak X(M)$ an action and\\
+ $\mu:\mathfrak g\to \Omega^{n-1}(M)$ a Leibniz momentum, i.e.
+\[
+X_{\mu(\xi)}=\underline \xi ~~\forall \xi ~~~~~~~\mu([\xi,\zeta])=L_{\underline \xi}\mu(\zeta)~\forall \xi,\zeta
+\]
+Then $F=\underline {\mathfrak g}$ and $S=\{p\in M~|~\mu(\xi)_p=0\forall \xi\in\mathfrak g\}$ satisfy the necessary condition. \pause  Moreover:
+\begin{block}{Thm: The geometric case [Blacker21]}
+If in the above $S$ is smooth and the foliation spannd by $\underline{\mathfrak g}|_S$ is simple, then $M_{r}=\frac{S}{\underline{\mathfrak g}|_S}$ is premultisymplectic with $\omega_r$ unique, satisfying $\pi^*\omega_r=i^*\omega$.
+\[\begin{tikzcd}
+	M &&& S &&& {M_r}
+	\arrow["\begin{array}{c} i \end{array}"', hook', from=1-4, to=1-1]
+	\arrow["\begin{array}{c} \pi \end{array}", two heads, from=1-4, to=1-7]
+\end{tikzcd}\]
+\end{block}
+\end{frame}
+
 \begin{frame}
-	\begin{center}
-	\Huge\emph{Supplementary Material}
-	\end{center}
-\end{frame}
-\note[itemize]{
-	\item
-}
-\addtocounter{framenumber}{-1}
-%##################################################################################
-
-%------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{MS geometry and classical field mechanics}\label{Frame:Ms-Field-Mechanics}
-		Consider a smooth manifold $Y$,
-		\begin{columns}
-			\hfill
-			\begin{column}{.5\linewidth}
-				\emph{Multicotangent bundle} $\bigwedge = \bigwedge^n T^\ast Y$\\
-				is naturally $n$-plectic
-			\end{column}
-			\begin{column}{.4\linewidth}
-				\[
-				\begin{tikzcd}
-					\Lambda \ar[d,"\pi"'] & T \Lambda \ar[d,"T \pi"] \ar[l] \\
-					Y								& T Y \ar[l]
-				\end{tikzcd}	
-				\]
-			\end{column}
-		\end{columns}
-	\pause
-	\begin{defblock}[Tautological $n$-form]
-		$\theta \in \Omega^n(\Lambda)$ such that:
-		\begin{displaymath}
-		\begin{split}
-			\left[ \iota_{u_1 \wedge \ldots \wedge u_n} \theta \right]_\eta 
-			&= \iota_{(T \pi)_\ast u_1 \wedge \ldots \wedge (T \pi)_\ast u_n} \eta \\
-			&= \iota_{u_1 \wedge \ldots \wedge u_n} \pi^\ast \eta 
-			\qquad \qquad \forall \eta \in \Lambda \, , \: \forall u_i \in T_\eta \Lambda 		
-		\end{split}
-		\end{displaymath}
-	\end{defblock}
-	\vfill
-	\begin{columns}
-		\begin{column}{.6\linewidth}
-			\begin{defblock}[Tautological (multisymplectic) (n+1)-form]
-				$$\omega := d \theta$$
-			\end{defblock}
-		\end{column}
-		\begin{column}{.4\linewidth}
-		 	\begin{claimblock}$\omega$ is not degenerate.\end{claimblock}	
-		\end{column}
-	\end{columns}	
-	\pause
-	\begin{keywordblock}
-		\begin{tabular}{|c|c|c|}
-			\hline 
-			point-particles mechanics & $\rightsquigarrow$ & classical fields mechanics \\
-			%(finite discrete DOF) & & (finite dimensional continuous DOF) \\
-			\hline 
-			symplectic & $\rightsquigarrow$ & multisymplectic \\ 
-			\hline 
-			Observables (Poisson) algebra & $\rightsquigarrow$ & Observables $L-\infty$ algebra
-			 \\ 
-			\hline 
-			Co-moment map & $\rightsquigarrow$ & Homotopy co-momentum map \\ 
-			\hline 
-		\end{tabular} 
-	\end{keywordblock}
-
-\end{frame}
-\note[itemize]{
-	\item This example is significant from the perspective of geometric classical field theory:
-		\begin{displaymath}
-			\frac{\text{classical mechanics}}{\text{symplectic geo.}} =
-			\frac{\text{classical field mechanics}}{\text{multisymplectic geo.}}
-		\end{displaymath}
-	\item Multicotangent bundle is the \emph{Higher analogue} of the cotangent bundle.
-	(but it is not yet the analogue of a \emph{phase space}.)
-\item The multiphase space is the sub-bundle of $n$-forms vanishing when contracted with 2 vertical fields.
-  	\item The reason why this sub-bundle has a particular role is that it can be proved to be isomorphic to a suitable dual of the first Jet bundle.
-  	\item For further details see Gotay et al.
-\href{https://arxiv.org/abs/physics/9801019}{arXiv:physics/9801019}.
-For a pictorial representation of all the structures involved in the geometric mechanics of I order classical field theories see appendix, pag: \ref{frame:Gimmsy}.
-}
-%------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[t]{Symmetries in \textbf{multisymplectic geometry}}
-	Consider a Lie algebra action $v:\mathfrak{g} \to \mathfrak{X}(M)$  preserving the $n$-plectic form $\omega$,
-	\vfill
-
-	\vspace{-1em}
-	\begin{columns}[T]
-		\setlength{\belowdisplayskip}{5pt}
-		\begin{column}{.50\linewidth}
-			%
-			\centering \it
-			\onslide<2->{
-				$-$ symplectic case $-$
-				\begin{defblock}[Comoment map pertaining to $v$]
-					Lie algebra morphism
-					$$ f: \mathfrak{g} \to C^\infty(M) $$
-					such that
-					$$ d~f (x) = -\iota_{v_x} \omega \qquad \forall x \in \mathfrak{g}~.$$
-				\end{defblock}
-			}
-		\end{column}	
-		%
-		\onslide<2->{\vrule{}}
-		%
-		\begin{column}{.50\linewidth}
-			\centering \it
-			\onslide<3->{			
-				$-$ $n$-plectic case $-$
-				\begin{defblock}[Homotopy comoment map \tiny (HCMM)]
-					$L_\infty$-morphism 
-					$$ (f_k) : \mathfrak{g} \to L_\infty (M,\omega)$$
-					such that
-					$$ d~f_1(x) = -\iota_{v_x} \omega \qquad \forall x \in \mathfrak{g}~.$$
-				\end{defblock}	
-			}
-		\end{column}	
-	\end{columns}	
-	%
-	\pause
-	\vfill
-	\centering 
-	\onslide<4->{\textbf{-- Conserved quantities --}}
-	%
-	\vspace{-.5em}
-	\begin{columns}[T]
-		\setlength{\belowdisplayskip}{5pt}
-		\begin{column}{.50\linewidth}
-			%
-			\centering \it
-			\onslide<4->{
-			\begin{propblock}[Noether Theorem]
-				\small Fixed $H\in C^\infty_{\text{Ham}}(M)$ ($\mathfrak{g}$-invariant) ,
-				$$\mathcal{L}_{v_H} f(x) = 0 \qquad \forall x \in \mathfrak{g}$$
-			\end{propblock}
-			}
-		\end{column}	
-		%
-		\onslide<5->{\vrule{}}
-		%
-		\begin{column}{.50\linewidth}
-			\centering \it
-			\onslide<5->{			
-			\begin{propblock}[RWZ16 Theorem]
-				\small Fixed $H\in \Omega^{n-1}_{\text{Ham}}(M)$ ($\mathfrak{g}$-invariant),
-				$$\mathcal{L}_{v_H} f_k(p) \in B^k(M) \qquad \forall p \in Z_k(\mathfrak{g})$$			
-			\end{propblock}
-			}
-		\end{column}	
-	\end{columns}		
-\end{frame}
-\note{
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%------------------------------------------------------------------------------------------------
-\begin{frame}{Reminder: $L_\infty$ Algebras}
-
-		\emph{
-			$L_\infty$-algebra is the notion that one obtains from a Lie algebra when one requires the Jacobi identity to be satisfied only up to a higher coherent chain homotopy.
-		}
-		\\
-		\vspace{.5em}
-		\begin{defblock}[$L_\infty$-algebra ~\emph{(Lada, Markl)} ~\cite{Lada1995}]
-			\includestandalone{Pictures/Figure_Linfinitydef}
-		\end{defblock}	
-		%
-		%
-	\pause
-	\vfill
-	\begin{thmblock}[Rogers \cite{Rogers2010}]
-		The \emph{higher observable algebra} $L_{\infty}(M,\omega)$ 	forms an honest $L_\infty$ algebra.
-		\footnotetext{ Take $\mu_1 = \text{d}$, $\mu_k=\lbrace\dots\rbrace_k$, $L$ is a shifted truncation of the de Rham complex.}
-	\end{thmblock}
-\end{frame}
-\note[itemize]{
-	\item $L_\infty$-algebra is the notion obtained from a Lie algebra requiring that the Jacobi identity is satisfied only up to a higher coherent chain homotopy.
-	\item The Lie-n algebra mentioned before is a $L_\infty$ algebra with underlying graded vector space concentrated in degrees $0,1...n$.
-
-	\item Definition. We say that a permutation $\sigma \in S_n$ is a $(j,n-j)$-unshuffle, $0\leq j \le1 n$  if $\sigma(1)< \dots < \sigma(j)$ and $\sigma(j+1)<\dots<\sigma(n)$.
-	\\
-	You can also say that $\sigma$ is a $(j,n-j)$-unshuffle if $\sigma(i)< \sigma(i+1)$ when $i\neq j$.
-
-	\item 	Alternatively, the Jacobiators can be also denoted as $$\displaystyle J_m=\sum_{i+j=m+1} 	\mu_i \triangleleft \mu_j = 0$$
-	employing the so-called \emph{ Richardson-Nijenhuis product}
-		 $$\mu_i\circ \mu_j := (-)^{i(j+1)}\frac{1}{j!(i-1)!}\mu_i \triangleleft \mu_j\otimes \mathbb{1}_{i-1} \circ \mathcal{A}~,$$
-		 where $\mathcal{A}$ denotes the (graded) total skew-symmetrizator.
-
-	\item see frame extra-\ref{Frame:unwapping-Jacobi} for a slightly demystification of the higher Jacobi equations.
-
-	\item more precisely this statement is a proposition/definition
-
-}
-%------------------------------------------------------------------------------------------------
-
-	%\input{msconstraints-aknowledgements}
-%------------------------------------------------------------------------------------------------
+\begin{block}{Lemma: Relating the reductions}	
+There is a natural injection $R:\frac{\Ham(M,\omega)_N}{\Ham(M,\omega)_0}\hookrightarrow \Ham(M_r,\omega_r)$.
+\end{block}
+\pause 
+\begin{exampleblock}{Non-surjectivity in general}
+	\begin{itemize} 
+	\item 	$M=\mathbb R^5$, $\omega=dt\wedge (dx_1\wedge dy_1+dx_2\wedge dy_2)$\pause 
+	\item $\mathfrak g=\langle\xi\rangle, \underline{\xi}=\partial_{x_1}$, $\mu(\xi)=-y_1dt$\pause 
+	\item $S=\{y_1=0\}$, $M_r\cong \mathbb R^3$ with $t,x_2,y_2$ and $\omega_r=dt\wedge dx_2\wedge dy_2$\pause 
+	\item $(\alpha,v)=(x_2tdy_2,x_2\partial_t-t\partial_{x_2})$ is not in the image of $R$.\pause 
+	\end{itemize}
+\end{exampleblock}
+{\bf Reason for non-surjectivity:} From the perspective of $M_r$ it does not make sense to require $d\alpha=-\iota_v\omega$ on all of $M$.\pause \\
+{\bf Remark:} We can easily construct examples where $\omega_r$ degenerates.
+\end{frame}
+
+\subsection{Lessons learned}
+\begin{frame}{Lessons learned}
+	\begin{itemize} 
+\item Constraint triples permit to do differential geometry/ Cartan calculus on singular subquotients,\\ ... in particular constructing observable algebras on them.\pause
+\item Even if $\omega$ is non-degenerate, $\omega_r$ could degenerate, forcing us to pull along the Hamiltonian vector fields explicitly\pause
+\item Coomentum maps in the sense of the Leibniz structure seem better for reducing than $L_\infty$-comomenta \pause
+\item The algebraic approach can treat algebroid / singular foliation symmetries and remembers vanishing orders a the singularities. \pause
+\item The reduction seems to give something novel even in the symplectic case \pause
+\item A 'softer' notion of constraint $L_\infty$ algebra is necessary to obtain all observables of the reduced space.
+
+	\end{itemize}
+\end{frame}
 

### 2025-01-19 msconstraints-short-main.tex
Slides almost done.

@@
 	\newif\ifHandout
-	\Handouttrue  %uncomment for the printable version
+	%\Handouttrue  %uncomment for the printable version
 	%Handling of flags it is not preserved when passing to standalone-subfiles!
@@
 \newcommand{\Der}{\mathrm{Der}}
+\usepackage{enumitem}
+\setlist{topsep=0pt, leftmargin=*,label=$\bullet$}
 
@@
 %------------------------------------------------------------------------------------------------
-\section{Symplectic Reduction}
+\section{Motivation: Symplectic Reduction}
 \checkpoint	
@@
 %- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\begin{frame}{Reduction in Classical Mechanics}
-
-\end{frame}
-\note[itemize]{
-	\item  In classical mechanics symmetry reduction plays an important role.
-	\item Mathematically, this is usually phrased in terms of Marsden-Weinstein reduction
-}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\begin{frame}{Geometric Reduction} 
-	{Def. Symplectic manifold $(M,\omega)$} $M$ a smooth manifold, $\omega\in \Omega^{2}(M)$ closed and non-degenerate, i.e.:
-		\begin{itemize} 	
-			\item $d\omega=0$
-			\item $\omega^\flat:TM\to T^*M, v\mapsto \iota_v\omega$ is injective
-		\end{itemize}
-
-\end{frame}
-\note[itemize]{
-	\item   Examples:
-		\begin{itemize}
-			\item orientable 2-manifolds with volume, e.g. $S^2$, $T^2$, $\mathbb R^2$
-			\item cotangent bunlde $T^*Q$ of any manifold $Q$, with $\omega=d\theta$. $\theta_\eta(v)=\eta(T\pi_Q(v))$.
-			\item coadjoint orbits
-		\end{itemize}
-}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\begin{frame}{Poisson Reduction} 
-{Def. Poisson algebra of observables} Let $(M,\omega)$ be symplectic.
-		\begin{itemize}
-			\item $X_f:=-(\omega^\flat)^{-1}(df)$  \emph{Hamiltonian vector field} of $f\in C^\infty(M)$.
-			\item $\{f,g\}:=\omega(X_f,X_g)=L_{X_f}g$ \emph{Poisson bracket of observables}
-		\end{itemize}
-	Indeed $(C^{\infty}(M), \cdot, \{-,-\})$ Poisson algebra:
-			\begin{itemize}
-		\item $\cdot$ is a commutative, associative mutliplication
-		\item $\{-,-\}$ is a Lie bracket
-		\item $\{f,- \}$ is a derivation
-	\end{itemize}\pause
-	And $f\mapsto X_f$ is a Lie algebra map. 
-\end{frame}
-\note[itemize]{
-	\item  
-}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\subsection{Marsden-Weinstein-Meyer reduction}
-\begin{frame}[fragile]{Marsden-Weinstein-Meyer reduction}
-Let $(M,\omega)$ symplectic, $G\circlearrowright M$ be a Lie group action\pause and $\mu:M\to \mathfrak g^*$ such that:\pause
-\begin{itemize}
-\item  $\mu$ is a momentum, i.e. the infinitesimal action $\xi\mapsto \underline\xi:\mathfrak g\to \mathfrak X(M)$ of $G$ satisfies $X_{\langle\mu,\xi\rangle}=\underline \xi$. \pause
-\item $\mu$ is $G$-equivariant, i.e. $\mu(gm)=Ad^*_g\mu(m)$ \pause
-\item The action of $G$ on $\mu^{-1}(0)$ is free and proper.\\ (This implies $0$ is reg. val. of $\mu$) \pause
-\end{itemize}
-Then $\exists!$ symplectic form $\omega_r$ on $M_r=\frac{\mu^{-1}(0)}{G}$ such that $\pi^*\omega_r=i^*\omega$.
-
-% https://q.uiver.app/#q=WzAsMyxbMCwwLCJNIl0sWzMsMCwiXFxtdV57LTF9KDApIl0sWzYsMCwiTV9yIl0sWzEsMCwiaVxcXFwgXFxzdWJzdGFja3tpbmNsdXNpb25+b2Z+c3Vic3BhY2V9IiwyLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoiaG9vayIsInNpZGUiOiJib3R0b20ifX19XSxbMSwyLCJcXHBpXFxcXCBcXHN1YnN0YWNre3F1b3RpZW50fmJ5fnJlbGF0aW9ufSJdXQ==
-\[\begin{tikzcd}
-	M &&& {\mu^{-1}(0)} &&& {M_r}
-	\arrow["\begin{array}{c} i\\ \substack{inclusion~of~subspace} \end{array}"', hook', from=1-4, to=1-1]
-	\arrow["\begin{array}{c} \pi\\ \substack{quotient~by~relation} \end{array}", two heads, from=1-4, to=1-7]
-\end{tikzcd}\]
-
-\pause
-Examples: $\mathbb CP^n$ from $S^1$-action on $\mathbb C^{n+1}$.
-
-\end{frame}
-
-\subsection{Attempting algebraic reduction}
-
-\begin{frame}[fragile]
-When the action is not 'free and proper', we can try to mimic this directly using the function algebras:
-% https://q.uiver.app/#q=WzAsNixbMCwwLCJNIl0sWzEsMCwiXFxtdV57LTF9KDApPVMiXSxbMywwLCJNX3IiXSxbMCwxLCJDXlxcaW5mdHkoTSkiXSxbMSwxLCJDXntcXGluZnR5fShTKT1cXGZyYWN7Q157XFxpbmZ0eX0oTSl9e0lfe1N9fSJdLFszLDEsIkNee1xcaW5mdHl9KE1fcik9Q15cXGluZnR5KFMpXkciXSxbMSwyLCJcXHN1YnN0YWNre3F1b3RpZW50fSIsMCx7InN0eWxlIjp7ImhlYWQiOnsibmFtZSI6ImVwaSJ9fX1dLFszLDQsIlxcc3Vic3RhY2t7cXVvdGllbnR9IiwwLHsic3R5bGUiOnsiaGVhZCI6eyJuYW1lIjoiZXBpIn19fV0sWzAsMSwiXFxzdWJzdGFja3tyZXN0cmljdGlvbn0iLDAseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dLFs0LDUsIlxcc3Vic3RhY2t7cmVzdHJpY3Rpb259IiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoic3F1aWdnbHkifX19XV0=
-\[\begin{tikzcd}
-	M & {\mu^{-1}(0)=S} && {M_r} \\
-	{C^\infty(M)} & {C^{\infty}(S):=\frac{C^{\infty}(M)}{I_{S}}} && {C^{\infty}(M_r)=C^\infty(S)^G}
-	\arrow["{\substack{restriction}}", squiggly, from=1-1, to=1-2]
-	\arrow["{\substack{quotient}}", two heads, from=1-2, to=1-4]
-	\arrow["{\substack{quotient}}", two heads, from=2-1, to=2-2]
-	\arrow["{\substack{restriction}}", squiggly, from=2-2, to=2-4]
-\end{tikzcd}\]
-
-where $I_S=\{f\in C^{\infty}(M)~|~f|_S=0\}$.\pause Equivalently:
-
-% https://q.uiver.app/#q=WzAsMyxbMCwwLCJDXlxcaW5mdHkoTSkiXSxbMiwwLCJOX1M9XFx7Zn58fiBmXFxpbiBDXlxcaW5mdHkoTSl8X1N+fkdcXG1hdGhybXstaW52YXJpYW50fVxcfSJdLFs0LDAsIlxcZnJhY3tOX1N9e0lfU30iXSxbMCwxLCJcXHN1YnN0YWNre3Jlc3RyaWN0aW9ufSIsMCx7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6InNxdWlnZ2x5In19fV0sWzEsMiwiXFxzdWJzdGFja3txdW90aWVudH0iLDAseyJzdHlsZSI6eyJoZWFkIjp7Im5hbWUiOiJlcGkifX19XV0=
-\[\small\begin{tikzcd}
-	{C^\infty(M)} && {N_S=\{f~|~ f\in C^\infty(M)|_S~~G\mathrm{-invariant}\}} && {\frac{N_S}{I_S}}
-	\arrow["{\substack{restriction}}", squiggly, from=1-1, to=1-3]
-	\arrow["{\substack{quotient}}", two heads, from=1-3, to=1-5]
-\end{tikzcd}\]
-\pause
-
-\begin{alertblock}{Problem}
-	$C^\infty(S)^G=\frac{N_S}{I_S}$ is not a Poisson algebra in general.
-\end{alertblock}
-(when constraints not first class, cf. Dirac reduction)
-\end{frame}
-
- \begin{frame}{Other approaches to reduction}
-
-\begin{table}[]
-	\begin{tabular}{l|l|l||l}
-		algebra $\mathcal{A}_T$ & subalgebra $\mathcal{A}_N$ & ideal $\mathcal{A}_0$ & comment \\
-		\hline
-
-		$C^\infty(M)$&      $N_S$     &   $I_S$   &  $\substack{S=\mu^{-1}(0),~ I_S=\{f~|~f|_S=0\}}$ \\
-			&&&  $\substack{N_S= \{ f | gf-f\in I_S \forall g\in G\}}$ \\
-	& & & \color{red} not Poisson \\ 
-	\hline	\pause
-	$C^\infty(M)$&   $F_S$         &   $I_S$   &  $\substack{F_S=\{f~|~\{f,I_S\}\subset I_S\}}$ \\
-	& & & \color{red} if $I_S\subset F_S$\\
-	\hline \pause
-
-	$C^\infty(M)$&   $C^\infty(M)^G$         &   $(I_S)^G$   &  $\substack{C^\infty(M)^G=\{f~|~gf=f\forall g\in G\}}$ \\
-	\hline \pause
-		$C^\infty(M)$&   $C^\infty(M)^G$         &   $(I_\mu)^G$   & $\substack{I_\mu=\{\sum_{i=1}^k f_i\langle \mu,\xi_i\rangle|~f_i\in C^\infty(M), \xi_i\in \mathfrak g\}}$\\
-		\hline \pause
-	$C^\infty(M)$&      $N_\mu$     &   $I_\mu$   & $\substack{N_\mu= \{ f | gf-f\in I_\mu \forall g\in G\}}$\\
-	\hline
-
-	\end{tabular}\pause
-\end{table}
-{\bf Remarks }names in order: 'naive' , Dirac, Sniatycki, Arms-Cushman-Gotay, Sniatycki-Weinstein.\pause \\
-When $G$ connected $N_\mu=N(I_\mu):=\{f~|~\{f,I_\mu\}\subset I_\mu\}$. 
- \end{frame}
-
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\begin{frame}{Algebraic Reduction} 
- a
-
-\end{frame}
-\note[itemize]{
-	\item  
-}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\begin{frame}{Constraint Algebras} 
- a
-
-\end{frame}
-\note[itemize]{
-	\item  
-}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%------------------------------------------------------------------------------------------------
-\section{Multisymplectic Geometry}
-\checkpoint	
-%------------------------------------------------------------------------------------------------
-
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\begin{frame}{From symplectic to {multi}symplectic} 
-	%
-	\begin{center}
-		$-$ \emph{multisymplectic means \textbf{going higher} in the degree of $\omega$} $-$
-	\end{center}
-	\pause
-	\begin{defblock}[$n$-plectic manifold ~\emph{(Cantrijn, Ibort, De Le\'on)} \cite{Cantrun2017}]
-		\includestandalone[width=0.95\textwidth]{Pictures/Figure_multisym}	
-	\end{defblock}
-	%
-	\pause
-		\begin{table}
-			\begin{tabular}{c c c}
-				symplectic forms \small($n=1$) & $\leftrightsquigarrow$ & volume forms \small($n= \text{dim}(M)-1$)
-			\end{tabular}
-		\end{table}
-
-	\vfill
-	\pause
-	\begin{block}{Historical motivation}
-		Mechanics: geometrical foundations of \textit{(first-order)} field theories.
-	\end{block}
-	%
-	\begin{table}
-		\ifHandout
-		%
-		\else
-		\only<4>{
-		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
-            \hline
-            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
-            \hline
-            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold &  \\[.25em]
-            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra &  \\[.25em]
-            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map &  
-            \\
-            \hline
-  \multicolumn{1}{c}{}
-            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
-            &  \multicolumn{1}{@{}c@{}}{}              \\
-		\end{tabular}
-		}
-		\fi
-		\onslide<5->{
-		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
-            \hline
-            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
-            \hline
-            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold & multisymplectic manifold \\[.25em]
-            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra & $L_\infty$-algebra \\[.25em]
-            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map & group actions admitting (homotopy) comomentum map
-            \\
-            \hline
-  			\multicolumn{1}{c}{}
-            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
-            &
-            \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{field-theoretic systems}}$} 
-               \\
-		\end{tabular}
-		}
-	\end{table}
-
-\end{frame}
-\note[itemize]{
-	\item Historically, the interest in multisymplectic manifolds, has been motivated by the need for understanding the geometrical foundations of first-order classical field theories.
-	The key point is that, just as one can associate a symplectic manifold to an ordinary classical mechanical system (e.g. a single
-point-like particle constrained to some manifold), it is possible to associate a multisymplectic
-manifold to any classical field system (e.g. a continuous medium like a filament or a fluid). See frame Extra-\ref{Frame:Ms-Field-Mechanics}
-
-	\item General ideas basic parallelisms with caveats
-	\item caveat: points in multiphase spaces are not states
-	\item the table hides the duality between geometric and algebraic approaches to the problem.
-	\item	Mechanics: geometrical foundations of \textit{(first-order)} field theories.
-		\begin{itemize}
-		 \item[-] Kijowski, W. Tulczyjew \cite{Kijowski1979}; %(1979)
-		 \item[-] Cariñena, Crampin, Ibort \cite{Carinena1991b};% (1991)
-		 \item[-] Gotay, Isenberg, Marsden, Montgomery \cite{Gimmsy1};%(1998)
-		 \\ $\cdots$
-		\end{itemize}
-	\item {Def. Multisymplectic manifold $(M,\omega)$}
-	$M$ a smooth manifold, $\omega\in \Omega^{n+1}(M)$ closed and non-deg., i.e.:
-	\begin{itemize}
-		\item $d\omega=0$
-		\item $\omega^\flat:TM\to \Lambda^nT^*M, v\mapsto \iota_v\omega$ is injective
-	\end{itemize} 
-	\item Without the non-deg. condition we call it \emph{premultisymplectic}. 
-	\item Examples:
-		\begin{itemize} 
-			\item orientable $n{+}1$-manifolds with volume, e.g. $S^{n+1}$, $T^{n+1}$, $\mathbb R^{n+1}$ 
-			\item multicotangent bunlde $\Lambda^nT^*Q$ of any manifold $Q$, with $\omega=d\theta$. $\theta_\eta(v_1,...,v_n)=\eta(T\pi_Q(v_n),...,T\pi_Q(v_n))$. 
-			\item semisimple Lie groups, hyperKähler manifolds,...
-		\end{itemize}
-}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\begin{frame}{Geometric Multisymplectic Reduction} 
- a
-
-\end{frame}
-\note[itemize]{
-	\item  
-}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%------------------------------------------------------------------------------------------------
-\section{Multisymplectic observables reduction}
-\checkpoint	
-%------------------------------------------------------------------------------------------------
-
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\begin{frame}{Observables in $n$-plectic geometry}
-	%
-	\begin{defblock}[Hamiltonian $(n-1)$-forms]
-		\begin{displaymath}
-			\Omega^{n-1}_{ham}(M,\omega) 	:=
-			\biggr\{ \sigma \in  \Omega^{n-1}(M) \; \biggr\vert \; 
-				\exists \vHam_\sigma \in \mathfrak{X}(M) ~:~ 
-				\tikz[baseline,remember picture]{\node[rounded corners,
-                        fill=orange!5,draw=orange!30,anchor=base]            
-            			(target) {$d \sigma = -\iota_{\vHam_\sigma} \omega$ };
-            	}				
-				~\biggr\} 
-			\end{displaymath}
-	\end{defblock}
-
-	\pause
-		\tikz[overlay,remember picture]
-		{
-			\node[rounded corners,
-                 fill=orange!5,draw=orange!30,anchor=base]
-            	 (base) at ($(current page.north east)-(2,1)$) [rotate=-0,text width=3.5cm,align=center] {\footnotesize{\textcolor{red}{Hamilton-DeDonder-Weyl \\equation}}};
-		}	
-	\begin{tikzpicture}[overlay,remember picture]
-    	\path[->] (base.south) edge[bend right,red](target.north);
-    \end{tikzpicture}
-	%
-	\vfill
-	\begin{columns}[T]
-		\pause
-		\setlength{\belowdisplayskip}{5pt}
-		\begin{column}{.50\linewidth}
-			%
-			\vspace{-1em}
-			\begin{thmblock}[Observables $L_\infty$-algebra]
-				$\Omega^{n-1}_{ham}(M,\omega)$ endowed with
-				\vspace{-.5em}
-				\begin{displaymath}
-					\lbrace \sigma_1, \sigma_2 \rbrace =			
-					~ - \iota_{\vHam_1}\iota_{\vHam_2} \omega 
-				\end{displaymath}			
-				can be "completed" to a \\ $L_\infty-algebra$.
-			\end{thmblock}
-			%	
-		\end{column}	
-		%
-		\pause
-		\begin{column}{.50\linewidth}
-		%
-			\begin{itemize}
-				\item[\cmark] Skew-symmetric;
-				\item[\xmark] multiplication of observables;
-				\item[\xmark] Jacobi equation;
-				%\\ \hspace*{4.25em} full-fledged Jacobi equation;
-				\item[\smark] Jacobi equation \emph{up to homotopies}.
-			\end{itemize}			
-			%
-				\[
-					\small
-					\{\alpha,\{\beta,\gamma\}\} + \text{\it cyc. perm.}
-					= {\color{orange}\d \iota_{X_\alpha} \iota_{X_\beta} \iota_{X_\gamma}\omega}
-				\]
-		\end{column}	
-	\end{columns}
-	%
-	\vfill
-	\pause
-	Interesting alternatives:
-	\begin{itemize}
-		\item  descend to $\Omega^{k-1}_{ham}(M) / {\color{orange}\d\hspace{1pt}\Omega^{k-2}(M)}$, hence getting a Lie algebra;
-		\item Incorporate the {\color{orange}discrepancy} as part of the data of the space of observables $ 
-				L_\infty(M,\omega) = \Omega_{ham}^{k-1}(M)\oplus{\color{orange}\Omega^{\leq k-2}(M)}$
-			%a \textbf{homotopy Lie algebra} or \textbf{$L_\infty$-algebra}.
-	\end{itemize}
-
-\end{frame}
-\note[itemize]{
-	\item
-}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\subsection{$L_\infty$-algebra of Observables}
-\begin{frame}[fragile,t]{$L_\infty$-algebra of Observables (higher observables) }
-	Let be $(M,\omega)$ a $n$-plectic manifold.
-	\begin{defblock}[$L_\infty$-algebra of observables ~\emph{(Rogers)} ~\cite{Rogers2010}]
-
-		\hspace{.25em} $L\infty(M,\omega)$ is given by:
-
-		\begin{itemize}
-			\item[•] a cochain-complex $(L,\{\cdot\}_1)$ 
-		\end{itemize}
-		\begin{center}
-		\ifHandout
-			\includestandalone{Pictures/Figure_Observables}	
-		\else
-			\includestandalone{Pictures/Frame_Observables}
-		\fi				
-		\end{center}
-		\onslide<2->{
-			\begin{itemize}
-				\item[•] with $n$ (skew-symmetric) multibrackets $(2 \leq k \leq n+1)$
-			\end{itemize}
-			\begin{center}
-				\includestandalone{Pictures/Equation_Multibracket}	
-			\end{center}
-		}
-		%
-	\end{defblock}
-  \end{frame}
- \note[itemize]{
-	\item if symplectic manifolds are the symmetric take on mechanics, Poisson algebras are the algebraic counterpart.
- 	\item A Lie algebra is associated to an ordinary symplectic manifold (its Poisson algebra).
-	%(Underlying this is a Lie algebra, whose Lie bracket is the Poisson bracket.)
-	Similarly, one associates an Lie-$n$ algebra to any $n$-plectic manifold.
- 	% https://ncatlab.org/nlab/show/n-plectic+geometry 	 
- 	 %https://ncatlab.org/nlab/show/Poisson+bracket+Lie+n-algebra
-	 \item Basically, the higher observables algebra is a chunk of the de Rham complex of $M$ with inverted grading( convention employed here) and an extra structure called "multibrackets".
- 	\item ( In the 1-plectic case it reduces to the corresponding Poisson algebra of classical observables)
- 	\item Rogers associated to any n-plectic mfd a $L\-\infty$ algebra, Zambon generalized it to the pre-n-plectic case.
- 	\item Recognize in the definition of $\{\cdot,\ldots,\cdot\}_k$ the contraction with hamiltonian fields $v_\sigma$ w.r.t. $\sigma$.
-  	\item Note $	\iota_{v_{\sigma_1}}\cdots\iota_{v_{\sigma_k}} = (-)^{(k-1)+(k-2)+\dots+1}\iota_{v_{\sigma_k}}\cdots\iota_{v_{\sigma_1}} = (-)^{\frac{k(k-1)}{2}}\iota_{v_{\sigma_k}}\cdots\iota_{v_{\sigma_1}}$
- 	The definition usually find in literature of Rogers multibrackets involves the coefficient $ (-)^{\frac{k(k-1)}{2}} = -\varsigma(k-1) = (-)^{k+1} \varsigma(k)$.
-  \item higher observables is Special instance of a more general object  called $L\-\infty$ Algebra...
- }
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%------------------------------------------------------------------------------------------------
-% APPENDIX
-%------------------------------------------------------------------------------------------------
-\appendix
-%------------------------------------------------------------------------------------------------
-
-\section{Supplementary Material}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\begin{frame}
-	\begin{center}
-	\Huge\emph{Supplementary Material}
-	\end{center}
-\end{frame}
-\note[itemize]{
-	\item
-}
-\addtocounter{framenumber}{-1}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\begin{frame}[fragile]{MS geometry and classical field mechanics}\label{Frame:Ms-Field-Mechanics}
-		Consider a smooth manifold $Y$,
-		\begin{columns}
-			\hfill
-			\begin{column}{.5\linewidth}
-				\emph{Multicotangent bundle} $\bigwedge = \bigwedge^n T^\ast Y$\\
-				is naturally $n$-plectic
-			\end{column}
-			\begin{column}{.4\linewidth}
-				\[
-				\begin{tikzcd}
-					\Lambda \ar[d,"\pi"'] & T \Lambda \ar[d,"T \pi"] \ar[l] \\
-					Y								& T Y \ar[l]
-				\end{tikzcd}	
-				\]
-			\end{column}
-		\end{columns}
-	\pause
-	\begin{defblock}[Tautological $n$-form]
-		$\theta \in \Omega^n(\Lambda)$ such that:
-		\begin{displaymath}
-		\begin{split}
-			\left[ \iota_{u_1 \wedge \ldots \wedge u_n} \theta \right]_\eta 
-			&= \iota_{(T \pi)_\ast u_1 \wedge \ldots \wedge (T \pi)_\ast u_n} \eta \\
-			&= \iota_{u_1 \wedge \ldots \wedge u_n} \pi^\ast \eta 
-			\qquad \qquad \forall \eta \in \Lambda \, , \: \forall u_i \in T_\eta \Lambda 		
-		\end{split}
-		\end{displaymath}
-	\end{defblock}
-	\vfill
-	\begin{columns}
-		\begin{column}{.6\linewidth}
-			\begin{defblock}[Tautological (multisymplectic) (n+1)-form]
-				$$\omega := d \theta$$
-			\end{defblock}
-		\end{column}
-		\begin{column}{.4\linewidth}
-		 	\begin{claimblock}$\omega$ is not degenerate.\end{claimblock}	
-		\end{column}
-	\end{columns}	
-	\pause
-	\begin{keywordblock}
-		\begin{tabular}{|c|c|c|}
-			\hline 
-			point-particles mechanics & $\rightsquigarrow$ & classical fields mechanics \\
-			%(finite discrete DOF) & & (finite dimensional continuous DOF) \\
-			\hline 
-			symplectic & $\rightsquigarrow$ & multisymplectic \\ 
-			\hline 
-			Observables (Poisson) algebra & $\rightsquigarrow$ & Observables $L-\infty$ algebra
-			 \\ 
-			\hline 
-			Co-moment map & $\rightsquigarrow$ & Homotopy co-momentum map \\ 
-			\hline 
-		\end{tabular} 
-	\end{keywordblock}
-
-\end{frame}
-\note[itemize]{
-	\item This example is significant from the perspective of geometric classical field theory:
-		\begin{displaymath}
-			\frac{\text{classical mechanics}}{\text{symplectic geo.}} =
-			\frac{\text{classical field mechanics}}{\text{multisymplectic geo.}}
-		\end{displaymath}
-	\item Multicotangent bundle is the \emph{Higher analogue} of the cotangent bundle.
-	(but it is not yet the analogue of a \emph{phase space}.)
-\item The multiphase space is the sub-bundle of $n$-forms vanishing when contracted with 2 vertical fields.
-  	\item The reason why this sub-bundle has a particular role is that it can be proved to be isomorphic to a suitable dual of the first Jet bundle.
-  	\item For further details see Gotay et al.
-\href{https://arxiv.org/abs/physics/9801019}{arXiv:physics/9801019}.
-For a pictorial representation of all the structures involved in the geometric mechanics of I order classical field theories see appendix, pag: \ref{frame:Gimmsy}.
-}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\begin{frame}[t]{Symmetries in \textbf{multisymplectic geometry}}
-	Consider a Lie algebra action $v:\mathfrak{g} \to \mathfrak{X}(M)$  preserving the $n$-plectic form $\omega$,
-	\vfill
-
-	\vspace{-1em}
-	\begin{columns}[T]
-		\setlength{\belowdisplayskip}{5pt}
-		\begin{column}{.50\linewidth}
-			%
-			\centering \it
-			\onslide<2->{
-				$-$ symplectic case $-$
-				\begin{defblock}[Comoment map pertaining to $v$]
-					Lie algebra morphism
-					$$ f: \mathfrak{g} \to C^\infty(M) $$
-					such that
-					$$ d~f (x) = -\iota_{v_x} \omega \qquad \forall x \in \mathfrak{g}~.$$
-				\end{defblock}
-			}
-		\end{column}	
-		%
-		\onslide<2->{\vrule{}}
-		%
-		\begin{column}{.50\linewidth}
-			\centering \it
-			\onslide<3->{			
-				$-$ $n$-plectic case $-$
-				\begin{defblock}[Homotopy comoment map \tiny (HCMM)]
-					$L_\infty$-morphism 
-					$$ (f_k) : \mathfrak{g} \to L_\infty (M,\omega)$$
-					such that
-					$$ d~f_1(x) = -\iota_{v_x} \omega \qquad \forall x \in \mathfrak{g}~.$$
-				\end{defblock}	
-			}
-		\end{column}	
-	\end{columns}	
-	%
-	\pause
-	\vfill
-	\centering 
-	\onslide<4->{\textbf{-- Conserved quantities --}}
-	%
-	\vspace{-.5em}
-	\begin{columns}[T]
-		\setlength{\belowdisplayskip}{5pt}
-		\begin{column}{.50\linewidth}
-			%
-			\centering \it
-			\onslide<4->{
-			\begin{propblock}[Noether Theorem]
-				\small Fixed $H\in C^\infty_{\text{Ham}}(M)$ ($\mathfrak{g}$-invariant) ,
-				$$\mathcal{L}_{v_H} f(x) = 0 \qquad \forall x \in \mathfrak{g}$$
-			\end{propblock}
-			}
-		\end{column}	
-		%
-		\onslide<5->{\vrule{}}
-		%
-		\begin{column}{.50\linewidth}
-			\centering \it
-			\onslide<5->{			
-			\begin{propblock}[RWZ16 Theorem]
-				\small Fixed $H\in \Omega^{n-1}_{\text{Ham}}(M)$ ($\mathfrak{g}$-invariant),
-				$$\mathcal{L}_{v_H} f_k(p) \in B^k(M) \qquad \forall p \in Z_k(\mathfrak{g})$$			
-			\end{propblock}
-			}
-		\end{column}	
-	\end{columns}		
-\end{frame}
-\note{
-}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\begin{frame}{Reminder: $L_\infty$ Algebras}
-
-		\emph{
-			$L_\infty$-algebra is the notion that one obtains from a Lie algebra when one requires the Jacobi identity to be satisfied only up to a higher coherent chain homotopy.
-		}
-		\\
-		\vspace{.5em}
-		\begin{defblock}[$L_\infty$-algebra ~\emph{(Lada, Markl)} ~\cite{Lada1995}]
-			\includestandalone{Pictures/Figure_Linfinitydef}
-		\end{defblock}	
-		%
-		%
-	\pause
-	\vfill
-	\begin{thmblock}[Rogers \cite{Rogers2010}]
-		The \emph{higher observable algebra} $L_{\infty}(M,\omega)$ 	forms an honest $L_\infty$ algebra.
-		\footnotetext{ Take $\mu_1 = \text{d}$, $\mu_k=\lbrace\dots\rbrace_k$, $L$ is a shifted truncation of the de Rham complex.}
-	\end{thmblock}
-\end{frame}
-\note[itemize]{
-	\item $L_\infty$-algebra is the notion obtained from a Lie algebra requiring that the Jacobi identity is satisfied only up to a higher coherent chain homotopy.
-	\item The Lie-n algebra mentioned before is a $L_\infty$ algebra with underlying graded vector space concentrated in degrees $0,1...n$.
-
-	\item Definition. We say that a permutation $\sigma \in S_n$ is a $(j,n-j)$-unshuffle, $0\leq j \le1 n$  if $\sigma(1)< \dots < \sigma(j)$ and $\sigma(j+1)<\dots<\sigma(n)$.
-	\\
-	You can also say that $\sigma$ is a $(j,n-j)$-unshuffle if $\sigma(i)< \sigma(i+1)$ when $i\neq j$.
-
-	\item 	Alternatively, the Jacobiators can be also denoted as $$\displaystyle J_m=\sum_{i+j=m+1} 	\mu_i \triangleleft \mu_j = 0$$
-	employing the so-called \emph{ Richardson-Nijenhuis product}
-		 $$\mu_i\circ \mu_j := (-)^{i(j+1)}\frac{1}{j!(i-1)!}\mu_i \triangleleft \mu_j\otimes \mathbb{1}_{i-1} \circ \mathcal{A}~,$$
-		 where $\mathcal{A}$ denotes the (graded) total skew-symmetrizator.
-
-	\item see frame extra-\ref{Frame:unwapping-Jacobi} for a slightly demystification of the higher Jacobi equations.
-
-	\item more precisely this statement is a proposition/definition
-
-}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%------------------------------------------------------------------------------------------------
 \begin{frame}{Symplectic geometry (mechanics flavour)}
@@
 
-		\item take away message: geometric (based on "states") vs algebraic (based on "measurable quantities").7
-	}
-	%------------------------------------------------------------------------------------------------
-
-	%------------------------------------------------------------------------------------------------
+		\item take away message: geometric (based on "states") vs algebraic (based on "measurable quantities").
+		\item 	{Def. Symplectic manifold $(M,\omega)$} $M$ a smooth manifold, $\omega\in \Omega^{2}(M)$ closed and non-degenerate, i.e.:
+		\begin{itemize} 	
+			\item $d\omega=0$
+			\item $\omega^\flat:TM\to T^*M, v\mapsto \iota_v\omega$ is injective
+		\end{itemize}
+	\item   Examples:
+		\begin{itemize}
+			\item orientable 2-manifolds with volume, e.g. $S^2$, $T^2$, $\mathbb R^2$
+			\item cotangent bunlde $T^*Q$ of any manifold $Q$, with $\omega=d\theta$. $\theta_\eta(v)=\eta(T\pi_Q(v))$.
+			\item coadjoint orbits
+		\end{itemize}
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
 \begin{frame}{Reminder: momentum maps in symplectic geometry}\label{frame:symplecticmomaps}
@@
 }
-	%------------------------------------------------------------------------------------------------
-
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%	
 \subsection{Regular reduction} 
-	%------------------------------------------------------------------------------------------------
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%	
 \begin{frame}{Regular reduction in symplectic geometry}
@@
 	\vfill
-		\pause
-		\begin{thmblock}[Marsden-Weinstein reduction \cite{MarsdenWeinstein74}]
-			\vspace{-.4em}\hspace{-1em}
-			\begin{tabular}{l p{14cm}}
-				Given: & $(M,\omega)$ symplectic
-				\\
-				& $G\curvearrowright M$ symplectic with equivariant momap. $\mu:M\to \mathfrak{g}^*$
-				\\[.2em]
-				Assume: & $\phi \in \mathfrak{g}^*$ regular value of $\mu$ 
-				\qquad\quad \footnotesize \textcolor{gray}{($\Rightarrow$ $\mu^{-1}(\phi)\hookrightarrow M$ smooth embedding)}
-				\\
-				& $G_\phi\curvearrowright \mu^{-1}(\phi)$ free and proper
-				\quad \footnotesize \textcolor{gray}{($\Rightarrow$ $\mu^{-1}(\phi)/G_\phi$ smooth manifold)}
-				\\[.4em]
-				Then: & $\exists!$ symplectic structure $\omega_\phi$ in $M_\phi:= \mu^{-1}(\phi)/G_\phi$ \\
-				& s.t. $\pi^\ast \omega_\phi = j^\ast \omega$ 
-				\qquad {\footnotesize with $j:\mu^{-1}(\phi) \hookrightarrow M$ and $\pi:\mu^{-1}(\phi)\twoheadrightarrow M_\mu$}
-			\end{tabular}
-			\vspace{-.4em}
-		\end{thmblock}
-		%
-		\vfill
+
 	\pause
@@
 \note[itemize]{
+	\item  In classical mechanics symmetry reduction plays an important role. Mathematically, this is usually phrased in terms of Marsden-Weinstein reduction
 	\item {Symplectic Reduction} takes two inputs:
@@
 
+	\item Heuristic Approach to Reduction:
+	\\1. describe $G\curvearrowright M$ in terms of $\omega$ 	\hspace{1cm}
+	({\color{green}moment map $\mu$})
+	\\2. identify a distinguished reduced space \hspace{1cm}
+	({\color{green}reduction at $\mu=0$})
+	\\3. use the ambiguity in 1.\ to obtain a family of reduced spaces \hspace{1cm}
+	({\color{green}reduction at $\mu-\phi=0$, i.e.\ reduction at $\mu=\phi$}
+	\\
+	{\tiny Note: If $G_\phi\neq G$, then $\mu-\phi:M\to\g^*$ is not a moment map for either $G\curvearrowright M$ or $G_\phi\curvearrowright M$.}
+
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}[fragile]{Marsden-Weinstein-Meyer reduction}
+	\begin{thmblock}[Marsden-Weinstein reduction \cite{MarsdenWeinstein74}]
+		\vspace{-.4em}\hspace{-1em}
+		\begin{tabular}{l p{14cm}}
+			Given: & $(M,\omega)$ symplectic
+			\\
+			& $\color{orange}G\curvearrowright M$ symplectic with equivariant momap. $\mu:M\to \mathfrak{g}^*$
+			\\[.2em]
+			Assume: & ${\color{blue}\phi} \in \mathfrak{g}^*$ regular value of $\mu$ 
+			\qquad\quad \footnotesize \textcolor{gray}{($\Rightarrow$ $\mu^{-1}(\phi)\hookrightarrow M$ smooth embedding)}
+			\\
+			& $G_\phi\curvearrowright \mu^{-1}(\phi)$ free and proper
+			\quad \footnotesize \textcolor{gray}{($\Rightarrow$ $\mu^{-1}(\phi)/G_\phi$ smooth manifold)}
+			\\[.4em]
+			Then: & \textbf{$\exists!$ symplectic structure} $\omega_\phi$ in $M_\phi:={\color{blue}\mu^{-1}(\phi)}{\color{orange}/G_\phi}$ \\
+			& s.t. $\pi^\ast \omega_\phi = j^\ast \omega$ 
+			\qquad {\footnotesize with $j:\mu^{-1}(\phi) \hookrightarrow M$ and $\pi:\mu^{-1}(\phi)\twoheadrightarrow M_\mu$}
+		\end{tabular}
+		\vspace{-.4em}
+	\end{thmblock}
+	%
+	\vfill
 	\begin{center}
@@
 	\end{center}
-		\item Heuristic Approach to Reduction:
-		\\1. describe $G\curvearrowright M$ in terms of $\omega$ 	\hspace{1cm}
-		({\color{green}moment map $\mu$})
-		\\2. identify a distinguished reduced space \hspace{1cm}
-		({\color{green}reduction at $\mu=0$})
-		\\3. use the ambiguity in 1.\ to obtain a family of reduced spaces \hspace{1cm}
-		({\color{green}reduction at $\mu-\phi=0$, i.e.\ reduction at $\mu=\phi$}
-		\\
-		{\tiny Note: If $G_\phi\neq G$, then $\mu-\phi:M\to\g^*$ is not a moment map for either $G\curvearrowright M$ or $G_\phi\curvearrowright M$.}
-
-	}
-	%------------------------------------------------------------------------------------------------
-
-	%------------------------------------------------------------------------------------------------
+	\pause
+	\vfill
+	\centering
+	The action of $G$ on $\mu^{-1}(0)$ is free and proper $\Rightarrow$ $0$ is reg. val. of $\mu$
+
+\end{frame}
+\note[itemize]{
+ \item 
+	Let $(M,\omega)$ symplectic, $G\circlearrowright M$ be a Lie group action\pause and $\mu:M\to \mathfrak g^*$ such that: 
+	\item  $\mu$ is a momentum, i.e. the infinitesimal action $\xi\mapsto \underline\xi:\mathfrak g\to \mathfrak X(M)$ of $G$ satisfies $X_{\langle\mu,\xi\rangle}=\underline \xi$. 
+	\item $\mu$ is $G$-equivariant, i.e. $\mu(gm)=Ad^*_g\mu(m)$ 
+	\item Then $\exists!$ symplectic form $\omega_r$ on $M_r=\frac{\mu^{-1}(0)}{G}$ such that $\pi^*\omega_r=i^*\omega$.
+%% https://q.uiver.app/#q=WzAsMyxbMCwwLCJNIl0sWzMsMCwiXFxtdV57LTF9KDApIl0sWzYsMCwiTV9yIl0sWzEsMCwiaVxcXFwgXFxzdWJzdGFja3tpbmNsdXNpb25+b2Z+c3Vic3BhY2V9IiwyLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoiaG9vayIsInNpZGUiOiJib3R0b20ifX19XSxbMSwyLCJcXHBpXFxcXCBcXHN1YnN0YWNre3F1b3RpZW50fmJ5fnJlbGF0aW9ufSJdXQ==
+%\[\begin{tikzcd}
+%	M &&& {\mu^{-1}(0)} &&& {M_r}
+%	\arrow["\begin{array}{c} i\\ \substack{inclusion~of~subspace} \end{array}"', hook', from=1-4, to=1-1]
+%	\arrow["\begin{array}{c} \pi\\ \substack{quotient~by~relation} \end{array}", two heads, from=1-4, to=1-7]
+%\end{tikzcd}\]
+
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
 \subsection{Singular reduction}
@@
 	\end{thmblock}
-
  \end{frame}
@@
 }
-	%------------------------------------------------------------------------------------------------
-
-%------------------------------------------------------------------------------------------------
-\subsection{References \& Aknowledgments}
-%------------------------------------------------------------------------------------------------
-
-%TODO aknowledgiare Leonid (sue slides) e Marvin (sua Tesi su Arxiv
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\begin{frame}[t,allowframebreaks]{Aknowledgments}
-	\begin{itemize}
-		\item MW reduction as "restriction to level sets", C. Lessig,
-			\href{https://arxiv.org/abs/1206.3302}{arXiv:1206.3302}
-
-	\end{itemize}
-\end{frame}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%TODO Modificare il Readme ricordando che questo si compila con Biber
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-% https://en.wikibooks.org/wiki/LaTeX/Bibliographies_with_biblatex_and_biber
-\begin{frame}[t,allowframebreaks]{Bibliography}
-	%\nocite{*}
-	\printbibliography
-\end{frame}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-% TEMP! All credit to Leonid Ryvkin www.ryvkin.eu
-\section{Leos}
-
-\subsection{Motivating example of $L_\infty$-algebra}
-%TODO All credits to Leo 
-\begin{frame}{Back to the symplectic case, $M=\mathbb R^2$}
-	Let $\omega=dx\wedge dy$, $\mathfrak X(\mathbb R^2,\omega)=\{X|~L_X\omega=0\}$.\pause
-
-	\begin{itemize}
-		\item {\bf Symplectic gradient}\\  $sgrad:C^\infty(\mathbb R^2)\to \mathfrak X(\mathbb R^2,\omega)$ (surjecive, kernel $\mathbb R$):\\ 
-		$$f\mapsto sgrad(f)={-\partial^yf \choose \partial^xf}$$\pause 
-		\item {\bf Poisson bracket} on $C^\infty(\mathbb R^2)$: $$\{f,g\}:=\partial^xf\partial^yg-\partial^xg\partial^yf$$ \\pause
-
-		\item {\bf Preservation of the bracket} $$sgrad(\{f,g\})=[sgrad(f),sgrad(g)]$$
-	\end{itemize}\pause
-	{\color{teal} Conclusion: } One can use the nicer space $C^\infty(\mathbb R^2)$ instead of $\mathfrak X(\mathbb R^2,\omega)$!
-\end{frame}
-
-\begin{frame}{Let's try the same in $\mathbb R^3$}
-	\begin{itemize}
-		\item $\mathfrak X(\mathbb R^3)=\{(v_x,  v_y,  v_z)^T\}
-		$\\ 
-		\item {\bf Lie bracket :}
-		$$[(v_x,  v_y,  v_z)^T,(w_x,  w_y,  w_z)^T]= (\sum_i v_i\partial^i(w_x) - w_i\partial^i(v_x) ,  \ldots ,\ldots)^T  $$
-		\item {\bf volume form: }$\Omega=dx\wedge dy\wedge dz$ 
-		\item {\bf volume-preserving fields: }$$\mathfrak X(\mathbb R^3,\Omega)=\{(v_x,v_y,v_z)^T~| \sum_i\partial^iv_i=0\}$$
-	\end{itemize}\pause~\\
-	This time the surjection is given by the {\bf Rotational}:
-
-	$$rot:\mathfrak X (\mathbb R^3)\to \mathfrak X (\mathbb R^3,\Omega)$$
-	$$
-	rot((v_x,v_y,v_z)^T)= (\partial^yv_z-\partial^zv_y, \partial^z v_x-\partial^xv_z, \partial^x v_y-\partial^yv_x)^T
-	$$
-\end{frame}
-
-\begin{frame}
-
-	{\color{red} Problem: } $rot$ does not commute with the bracket: $[rot(X),rot(Y)]\neq rot([X,Y])$ in general\\
-	~\\
-	\pause
-	{\color{teal} Solution: } New bracket $\{X,Y\}:=rot(X)\times rot(Y)$,\\ where $\times$ is the vector cross product on $\mathbb R^3$.\\~\\
-	\pause
-	We have $rot(\{X,Y\})=[rot(X), rot(Y)]$ \pause but no Jacobi identity. However: $$\{X,\{Y,Z\}\}-\{\{X,Y\},Z\}-\{Y,\{X,Z\}\}$$
-	$$=- grad((rot(X)\times rot(Y))\cdot rot(Z))$$
-
-\end{frame}
-
-\begin{frame}
-	$C^\infty(\mathbb R^3)\oplus \mathfrak X(\mathbb R^3)=:L_{-1}\oplus L_0$ form a \underline{\bf $L_\infty$ algebra} with:
-	\begin{itemize} 	
-		\item $l_1:L_{-1}\to L_0$, $l_1(f)=grad(f)$
-		\item $l_2:L_{0}\times L_0\to L_0$, $l_2(X,Y)=\{X,Y\}$
-		\item $l_3:L_{0}\times L_0\times L_0\to L_{-1}$, $l_3(X,Y,Z)=-(rot(X)\times rot(Y))\cdot rot(Z)$ 
-	\end{itemize}~\\~\\ \pause
-	In our case it means the following identities are satisfied:
-	\begin{itemize} 	
-		\item $l_2(l_1(f),Y)=0$
-		\item $l_2(l_2(X,Y),Z) - cycl= l_1l_3(X,Y,Z)$
-		\item $l_3(l_2(X,Y),Z,W)-cycl=0$
-	\end{itemize}
-\end{frame}
-
-\subsection{The multisymplectic observable algebra}
-
-\begin{frame}[fragile]
-	\begin{block}{Def. Observable $L_\infty$ algebra [Rogers2012]}
-		Let $(M,\omega)$ pre-multisymplectic. Set:
-			\begin{itemize} 	
-			\item $\Ham^0(M,\omega)=\{(\alpha,v)\in \Omega^{n-1}(M)\times \mathfrak X(M)~|~d\alpha=-\iota_v\omega  \}$
-			\item $\Ham^{-i}(M,\omega)= \Omega^{n-1-i}(M)$, $1\leq i\leq n-1$.
-			\item  $l_1=d:\Ham^{-i}(M,\omega)\to \Ham^{-i+1}(M,\omega)$,\\ (resp. $(d,0)$ for $i=1$)
-			\item $l_k:\Lambda^k\Ham^0(M,\omega)\to \Ham^{2-k}(M,\omega),$
-			\begin{align*}
-			&l_k((\alpha_1,v_1),...,(\alpha_k,v_k))=-(-1)^{\frac{k(k+1)}{2}}\iota_{v_k}...\iota_{v_1}\omega & k\geq 3\\
-			&l_2((\alpha_1,v_1),(\alpha_2,v_2))=(\iota_{v_2}\iota_{v_1}\omega, [v_1,v_2])
-			\end{align*}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\subsection{Constraints Algebras}
+\begin{frame}[fragile]{Attempting algebraic reduction}
+When the action is not 'free and proper', we can try to mimic this directly using the function algebras:
+% https://q.uiver.app/#q=WzAsNixbMCwwLCJNIl0sWzEsMCwiXFxtdV57LTF9KDApPVMiXSxbMywwLCJNX3IiXSxbMCwxLCJDXlxcaW5mdHkoTSkiXSxbMSwxLCJDXntcXGluZnR5fShTKT1cXGZyYWN7Q157XFxpbmZ0eX0oTSl9e0lfe1N9fSJdLFszLDEsIkNee1xcaW5mdHl9KE1fcik9Q15cXGluZnR5KFMpXkciXSxbMSwyLCJcXHN1YnN0YWNre3F1b3RpZW50fSIsMCx7InN0eWxlIjp7ImhlYWQiOnsibmFtZSI6ImVwaSJ9fX1dLFszLDQsIlxcc3Vic3RhY2t7cXVvdGllbnR9IiwwLHsic3R5bGUiOnsiaGVhZCI6eyJuYW1lIjoiZXBpIn19fV0sWzAsMSwiXFxzdWJzdGFja3tyZXN0cmljdGlvbn0iLDAseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dLFs0LDUsIlxcc3Vic3RhY2t7cmVzdHJpY3Rpb259IiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoic3F1aWdnbHkifX19XV0=
+\[\begin{tikzcd}
+	M & {\mu^{-1}(0)=S} && {M_r} \\
+	{C^\infty(M)} & {C^{\infty}(S):=\frac{C^{\infty}(M)}{I_{S}}} && {C^{\infty}(M_r)=C^\infty(S)^G}
+	\arrow["{\substack{restriction}}", squiggly, from=1-1, to=1-2]
+	\arrow["{\substack{quotient}}", two heads, from=1-2, to=1-4]
+	\arrow["{\substack{quotient}}", two heads, from=2-1, to=2-2]
+	\arrow["{\substack{restriction}}", squiggly, from=2-2, to=2-4]
+\end{tikzcd}\]
+
+where $I_S=\{f\in C^{\infty}(M)~|~f|_S=0\}$.
+\pause 
+\vfill
+Equivalently:
+
+% https://q.uiver.app/#q=WzAsMyxbMCwwLCJDXlxcaW5mdHkoTSkiXSxbMiwwLCJOX1M9XFx7Zn58fiBmXFxpbiBDXlxcaW5mdHkoTSl8X1N+fkdcXG1hdGhybXstaW52YXJpYW50fVxcfSJdLFs0LDAsIlxcZnJhY3tOX1N9e0lfU30iXSxbMCwxLCJcXHN1YnN0YWNre3Jlc3RyaWN0aW9ufSIsMCx7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6InNxdWlnZ2x5In19fV0sWzEsMiwiXFxzdWJzdGFja3txdW90aWVudH0iLDAseyJzdHlsZSI6eyJoZWFkIjp7Im5hbWUiOiJlcGkifX19XV0=
+\[\small\begin{tikzcd}
+	{C^\infty(M)} && {N_S=\{f~|~ f\in C^\infty(M)|_S~~G\mathrm{-invariant}\}} && {\frac{N_S}{I_S}}
+	\arrow["{\substack{restriction}}", squiggly, from=1-1, to=1-3]
+	\arrow["{\substack{quotient}}", two heads, from=1-3, to=1-5]
+\end{tikzcd}\]
+\pause
+\vfill
+
+\begin{alertblock}{Problem}
+	$C^\infty(S)^G=\frac{N_S}{I_S}$ is not a Poisson algebra in general.
+\end{alertblock}
+(when constraints not first class, cf. Dirac reduction)
+\end{frame}
+\note[itemize]{
+	\item
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}{Constraint Algebras} 
+	\begin{block}{Idea:}
+	    \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
+			\item[-] Both regular/geometric and singular/algebraic reduction are 2-steps procedures (1. restrict 2. quotient).
+			\item[-] Let's work in a category where all data needed for the reduction are bundled together in suitable categorical objects. {\tiny (To avoid pathologies arising from these steps)}
 	    \end{itemize}
 	\end{block}
-	\vspace{-15mm}
-	\pause
-	% https://q.uiver.app/#q=WzAsNixbMCwwLCJDXlxcaW5mdHkoTSkiXSxbMSwwLCJcXE9tZWdhXjEoTSkiXSxbMiwwLCIuLi4iXSxbMywwLCJcXE9tZWdhXntuLTN9KE0pIl0sWzQsMCwiXFxPbWVnYV57bi0yfShNKSJdLFs1LDAsIlxcSGFtXjAoTSkiXSxbMCwxLCJkIl0sWzEsMiwiZCJdLFsyLDMsImQiXSxbMyw0LCJkIl0sWzQsNSwiKGQsMCkiXSxbNSw1LCJsXzIiLDAseyJsYWJlbF9wb3NpdGlvbiI6NDAsIm9mZnNldCI6MSwiYW5nbGUiOjQ1LCJsZXZlbCI6Mn1dLFs1LDQsImxfMyIsMCx7ImN1cnZlIjotMywibGV2ZWwiOjN9XSxbNSwzLCJsXzQiLDIseyJjdXJ2ZSI6MywibGV2ZWwiOjR9XV0=
-	\[\tiny\begin{tikzcd}
-		{C^\infty(M)} & {\Omega^1(M)} & {...} & {\Omega^{n-3}(M)} & {\Omega^{n-2}(M)} & {\Ham^0(M)}
-		\arrow["d", from=1-1, to=1-2]
-		\arrow["d", from=1-2, to=1-3]
-		\arrow["d", from=1-3, to=1-4]
-		\arrow["d", from=1-4, to=1-5]
-		\arrow["{(d,0)}", from=1-5, to=1-6]
-		\arrow["{l_4}"', curve={height=18pt}, Rightarrow, scaling nfold=4, from=1-6, to=1-4]
-		\arrow["{l_3}", curve={height=-18pt}, Rightarrow, scaling nfold=3, from=1-6, to=1-5]
-		\arrow["{l_2}"{pos=0.4}, shift right, Rightarrow, from=1-6, to=1-6, loop, in=10, out=80, distance=10mm]
-	\end{tikzcd}\]
-\end{frame}
-
-\begin{frame}
-\begin{block}{Thm. $Ham^\bullet(M,\omega)$ is an $L_\infty$-algebra [Rogers2012]}
-This means $
-\substack{
-l_1l_{m+1}(x_1,...,x_{m+1})=\sum_{i<j}(-1)^{i+j}l_m(l_2(x_{i},x_j),x_1,...,\widehat{x_i},...,\widehat{x_j},...,x_{m+1})}
-$ for all $m$ and all possible $x_i$, where $l_0:=0$ and $l_{m+2}:=0$.
-\end{block}\pause
-
-{\bf Remark:} We could instead turn $\Ham^0(M,\omega)$ into a Left-Leibniz algebra by $[(\alpha,v)(\beta, w)]:=(L_v\beta,[v,w])$. This satisfies (left-)Jacobi, but is not skew-symmetric.\pause
-
-\begin{block}{Remark}
- The above also works if we replace $(C^\infty(M),\mathfrak X(M))$ with any Lie-Rinehart algebra $(A, L)$ and $\omega$ with a cocycle in $(\Lambda^{n+1}_AL)^*$.
-\end{block}\pause
-A Lie Rinehart algebra is: 
-\begin{itemize} 
-	\item A commutative algebra $A$ and an A-module $L$
-	\item A Lie algebra structure on $L$
-	\item A Lie algebra and module homomorphism $\rho:L\to \Der(A)$
-\end{itemize}
-such that $[\ell, a\tilde \ell]=a[\ell,\tilde \ell]+\rho(\ell)(a) \cdot \tilde\ell$
-\end{frame}
-
-\subsection{Preview of our answer}
-\begin{frame}
-We will develop a multisymplectic reduction in this talk, symplectically it is:
-\begin{block}{Construction: Multisymplectic reduction in the symplectic case}
-Let $Q_S=\{f~|~ f|_S=0\rm{~and~} df|_S=0\}$ Then the $L_\infty$-reduction is:
-$$
-\frac{N(I_S)\cap N(I_\mu+Q)}{I_\mu+Q}
-$$
-\end{block}	\pause
-Such a formula can be more generally applied to a Poisson algebra $P$ with associative ideals $I\subset J$ such that $\{I,I\}\subset I$ and $\{I,J\}\subset J$:
-$$
-\frac{N(J)\cap N(I+Q)}{I+Q}
-$$
-with $Q=\{f\in J|~\{f,P\}\subset J\}$
-\end{frame}
-
-\section{Reduction using Constraint triples}
-
-\subsection{General idea}
-\begin{frame}
-\begin{exampleblock}{Idea of multisymplectic observable reduction:}
-	Mimic the above construction of $\Ham^\bullet$\\ with triples of the type (algebra , subalgebra, ideal).
-\end{exampleblock}\pause
-After [Dippel2023] we call such triples { \bf constraint triples} and their parts \emph{total space, normal space, zero space}.\\~
-
-Let $S$ be a closed set. We describe $C^\infty(S)$ by $\frac{C^\infty(M)}{I_S}$.\\ We think of it as the constraint triple:
+	\pause
+	\vfill
+	\begin{defblock}[Constraint algebra triples \cite{Dippell2023}]
+		A (strong embedded) constraint algebra $\mathcal A$ is given by a triple $(\mathcal A_T, \mathcal A_N, \mathcal A_0)$, where
+		\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
+			\item[•] $\mathcal A_T$ is an algebra \emph{("total space")}
+			\item[•] $\mathcal A_N\subset \mathcal A_T$ a subalgebra  \emph{("normal space")}
+			\item[•] $\mathcal A_0\subset \mathcal A_N$ a two-sided ideal in $\mathcal A_T$ \emph{("zero space")}
+		\end{itemize}
+	\end{defblock}
+	\vfill
+	\pause
+	\begin{exblock}
+		Let $S$ be a closed set. Algebraically, we describe $C^\infty(S)$ by $\frac{C^\infty(M)}{I_S}$.
+		\\ 
+		We can think of it as the constraint triple:
 		$$
@@
 		$$
-It is a (strong) constraint algebra,\\ i.e. $\mathcal A_0\subset \mathcal A_N\subset \mathcal A_T$ subalgebras and $\mathcal A_0\subset \mathcal A_T$ ideal.
-
-\end{frame}
-
-\subsection{A dictionary between algebra and geometry}
+	\end{exblock}
+
+\end{frame}
+\note[itemize]{
+	\item  triples of the type (algebra , subalgebra, ideal).
+	\item After \cite{Dippell2023} we call such triples { \bf constraint triples} and their parts \emph{total space, normal space, zero space}.
+	\item It is a (strong) constraint algebra if $\mathcal A_0\subset \mathcal A_N\subset \mathcal A_T$ subalgebras and $\mathcal A_0\subset \mathcal A_T$ ideal.
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}{Other approaches to reduction}
+
+\begin{table}[]
+	\begin{tabular}{l|l|l||l}
+		algebra $\mathcal{A}_T$ & subalgebra $\mathcal{A}_N$ & ideal $\mathcal{A}_0$ & comment \\
+		\hline
+
+		$C^\infty(M)$&      $N_S$     &   $I_S$   &  $\substack{S=\mu^{-1}(0),~ I_S=\{f~|~f|_S=0\}}$ \\
+			&&&  $\substack{N_S= \{ f | gf-f\in I_S \forall g\in G\}}$ \\
+	& & & \color{red} not Poisson \\ 
+	\hline	\pause
+	$C^\infty(M)$&   $F_S$         &   $I_S$   &  $\substack{F_S=\{f~|~\{f,I_S\}\subset I_S\}}$ \\
+	& & & \color{red} if $I_S\subset F_S$\\
+	\hline \pause
+
+	$C^\infty(M)$&   $C^\infty(M)^G$         &   $(I_S)^G$   &  $\substack{C^\infty(M)^G=\{f~|~gf=f\forall g\in G\}}$ \\
+	\hline \pause
+		$C^\infty(M)$&   $C^\infty(M)^G$         &   $(I_\mu)^G$   & $\substack{I_\mu=\{\sum_{i=1}^k f_i\langle \mu,\xi_i\rangle|~f_i\in C^\infty(M), \xi_i\in \mathfrak g\}}$\\
+		\hline \pause
+	$C^\infty(M)$&      $N_\mu$     &   $I_\mu$   & $\substack{N_\mu= \{ f | gf-f\in I_\mu \forall g\in G\}}$\\
+	\hline
+
+	\end{tabular}\pause
+\end{table}
+	\vfill
+{\bf Remarks }names in order: 'naive' , Dirac, Sniatycki, Arms-Cushman-Gotay, Sniatycki-Weinstein.\pause \\
+When $G$ connected $N_\mu=N(I_\mu):=\{f~|~\{f,I_\mu\}\subset I_\mu\}$. 
+\end{frame}
+\note[itemize]{
+	\item  
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%------------------------------------------------------------------------------------------------
+\section{Multisymplectic Geometry}
+\checkpoint	
+%------------------------------------------------------------------------------------------------
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\subsection{Multisymplectic manifolds}
+\begin{frame}{From symplectic to {multi}symplectic} 
+	%
+	\begin{center}
+		$-$ \emph{multisymplectic means \textbf{going higher} in the degree of $\omega$} $-$
+	\end{center}
+	\pause
+	\begin{defblock}[$n$-plectic manifold ~\emph{(Cantrijn, Ibort, De Le\'on)} \cite{Cantrun2017}]
+		\includestandalone[width=0.95\textwidth]{Pictures/Figure_multisym}	
+	\end{defblock}
+	%
+	\pause
+		\begin{table}
+			\begin{tabular}{c c c}
+				symplectic forms \small($n=1$) & $\leftrightsquigarrow$ & volume forms \small($n= \text{dim}(M)-1$)
+			\end{tabular}
+		\end{table}
+
+	\vfill
+	\pause
+	\begin{block}{Historical motivation}
+		Mechanics: geometrical foundations of \textit{(first-order)} field theories.
+	\end{block}
+	%
+	\begin{table}
+		\ifHandout
+		%
+		\else
+		\only<4>{
+		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
+            \hline
+            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
+            \hline
+            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold &  \\[.25em]
+            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra &  \\[.25em]
+            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map &  
+            \\
+            \hline
+  \multicolumn{1}{c}{}
+            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
+            &  \multicolumn{1}{@{}c@{}}{}              \\
+		\end{tabular}
+		}
+		\fi
+		\onslide<5->{
+		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
+            \hline
+            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
+            \hline
+            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold & multisymplectic manifold \\[.25em]
+            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra & $L_\infty$-algebra \\[.25em]
+            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map & group actions admitting (homotopy) comomentum map
+            \\
+            \hline
+  			\multicolumn{1}{c}{}
+            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
+            &
+            \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{field-theoretic systems}}$} 
+               \\
+		\end{tabular}
+		}
+	\end{table}
+
+\end{frame}
+\note[itemize]{
+	\item Historically, the interest in multisymplectic manifolds, has been motivated by the need for understanding the geometrical foundations of first-order classical field theories.
+	The key point is that, just as one can associate a symplectic manifold to an ordinary classical mechanical system (e.g. a single
+point-like particle constrained to some manifold), it is possible to associate a multisymplectic
+manifold to any classical field system (e.g. a continuous medium like a filament or a fluid). See frame Extra-\ref{Frame:Ms-Field-Mechanics}
+
+	\item General ideas basic parallelisms with caveats
+	\item caveat: points in multiphase spaces are not states
+	\item the table hides the duality between geometric and algebraic approaches to the problem.
+	\item	Mechanics: geometrical foundations of \textit{(first-order)} field theories.
+		\begin{itemize}
+		 \item[-] Kijowski, W. Tulczyjew \cite{Kijowski1979}; %(1979)
+		 \item[-] Cariñena, Crampin, Ibort \cite{Carinena1991b};% (1991)
+		 \item[-] Gotay, Isenberg, Marsden, Montgomery \cite{Gimmsy1};%(1998)
+		 \\ $\cdots$
+		\end{itemize}
+	\item {Def. Multisymplectic manifold $(M,\omega)$}
+	$M$ a smooth manifold, $\omega\in \Omega^{n+1}(M)$ closed and non-deg., i.e.:
+	\begin{itemize}
+		\item $d\omega=0$
+		\item $\omega^\flat:TM\to \Lambda^nT^*M, v\mapsto \iota_v\omega$ is injective
+	\end{itemize} 
+	\item Without the non-deg. condition we call it \emph{premultisymplectic}. 
+	\item Examples:
+		\begin{itemize} 
+			\item orientable $n{+}1$-manifolds with volume, e.g. $S^{n+1}$, $T^{n+1}$, $\mathbb R^{n+1}$ 
+			\item multicotangent bunlde $\Lambda^nT^*Q$ of any manifold $Q$, with $\omega=d\theta$. $\theta_\eta(v_1,...,v_n)=\eta(T\pi_Q(v_n),...,T\pi_Q(v_n))$. 
+			\item semisimple Lie groups, hyperKähler manifolds,...
+		\end{itemize}
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\subsection{Higher Observables}
+\begin{frame}{Observables in $n$-plectic geometry}
+	%
+	\begin{defblock}[Hamiltonian $(n-1)$-forms]
+		\begin{displaymath}
+			\Omega^{n-1}_{ham}(M,\omega) 	:=
+			\biggr\{ \sigma \in  \Omega^{n-1}(M) \; \biggr\vert \; 
+				\exists \vHam_\sigma \in \mathfrak{X}(M) ~:~ 
+				\tikz[baseline,remember picture]{\node[rounded corners,
+                        fill=orange!5,draw=orange!30,anchor=base]            
+            			(target) {$d \sigma = -\iota_{\vHam_\sigma} \omega$ };
+            	}				
+				~\biggr\} 
+			\end{displaymath}
+	\end{defblock}
+
+	\pause
+		\tikz[overlay,remember picture]
+		{
+			\node[rounded corners,
+                 fill=orange!5,draw=orange!30,anchor=base]
+            	 (base) at ($(current page.north east)-(2,1)$) [rotate=-0,text width=3.5cm,align=center] {\footnotesize{\textcolor{red}{Hamilton-DeDonder-Weyl \\equation}}};
+		}	
+	\begin{tikzpicture}[overlay,remember picture]
+    	\path[->] (base.south) edge[bend right,red](target.north);
+    \end{tikzpicture}
+	%
+	\vfill
+	\begin{columns}[T]
+		\pause
+		\setlength{\belowdisplayskip}{5pt}
+		\begin{column}{.50\linewidth}
+			%
+			\vspace{-1em}
+			\begin{thmblock}[Observables $L_\infty$-algebra]
+				$\Omega^{n-1}_{ham}(M,\omega)$ endowed with
+				\vspace{-.5em}
+				\begin{displaymath}
+					\lbrace \sigma_1, \sigma_2 \rbrace =			
+					~ - \iota_{\vHam_1}\iota_{\vHam_2} \omega 
+				\end{displaymath}			
+				can be "completed" to a \\ $L_\infty-algebra$.
+			\end{thmblock}
+			%	
+		\end{column}	
+		%
+		\pause
+		\begin{column}{.50\linewidth}
+		%
+			\begin{itemize}
+				\item[\cmark] Skew-symmetric;
+				\item[\xmark] multiplication of observables;
+				\item[\xmark] Jacobi equation;
+				%\\ \hspace*{4.25em} full-fledged Jacobi equation;
+				\item[\smark] Jacobi equation \emph{up to homotopies}.
+			\end{itemize}			
+			%
+				\[
+					\small
+					\{\alpha,\{\beta,\gamma\}\} + \text{\it cyc. perm.}
+					= {\color{orange}\d \iota_{X_\alpha} \iota_{X_\beta} \iota_{X_\gamma}\omega}
+				\]
+		\end{column}	
+	\end{columns}
+	%
+	\vfill
+	\pause
+	Interesting alternatives:
+	\begin{itemize}
+		\item  descend to $\Omega^{k-1}_{ham}(M) / {\color{orange}\d\hspace{1pt}\Omega^{k-2}(M)}$, hence getting a Lie algebra;
+		\item Incorporate the {\color{orange}discrepancy} as part of the data of the space of observables $ 
+				L_\infty(M,\omega) = \Omega_{ham}^{k-1}(M)\oplus{\color{orange}\Omega^{\leq k-2}(M)}$
+			%a \textbf{homotopy Lie algebra} or \textbf{$L_\infty$-algebra}.
+	\end{itemize}
+
+\end{frame}
+\note[itemize]{
+	\item
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}[fragile,t]{$L_\infty$-algebra of Observables (higher observables) }
+	Let be $(M,\omega)$ a $n$-plectic manifold.
+	\begin{defblock}[$L_\infty$-algebra of observables ~\emph{(Rogers)} ~\cite{Rogers2010}]
+
+		\hspace{.25em} $L\infty(M,\omega)$ is given by:
+
+		\begin{itemize}
+			\item[•] a cochain-complex $(L,\{\cdot\}_1)$ 
+		\end{itemize}
+		\begin{center}
+		\ifHandout
+			\includestandalone{Pictures/Figure_Observables}	
+		\else
+			\includestandalone{Pictures/Frame_Observables}
+		\fi				
+		\end{center}
+		\onslide<2->{
+			\begin{itemize}
+				\item[•] with $n$ (skew-symmetric) multibrackets $(2 \leq k \leq n+1)$
+			\end{itemize}
+			\begin{center}
+				\includestandalone{Pictures/Equation_Multibracket}	
+			\end{center}
+		}
+		%
+	\end{defblock}
+  \end{frame}
+ \note[itemize]{
+	\item if symplectic manifolds are the symmetric take on mechanics, Poisson algebras are the algebraic counterpart.
+ 	\item A Lie algebra is associated to an ordinary symplectic manifold (its Poisson algebra).
+	%(Underlying this is a Lie algebra, whose Lie bracket is the Poisson bracket.)
+	Similarly, one associates an Lie-$n$ algebra to any $n$-plectic manifold.
+ 	% https://ncatlab.org/nlab/show/n-plectic+geometry 	 
+ 	 %https://ncatlab.org/nlab/show/Poisson+bracket+Lie+n-algebra
+	 \item Basically, the higher observables algebra is a chunk of the de Rham complex of $M$ with inverted grading( convention employed here) and an extra structure called "multibrackets".
+ 	\item ( In the 1-plectic case it reduces to the corresponding Poisson algebra of classical observables)
+ 	\item Rogers associated to any n-plectic mfd a $L\-\infty$ algebra, Zambon generalized it to the pre-n-plectic case.
+ 	\item Recognize in the definition of $\{\cdot,\ldots,\cdot\}_k$ the contraction with hamiltonian fields $v_\sigma$ w.r.t. $\sigma$.
+  	\item Note $	\iota_{v_{\sigma_1}}\cdots\iota_{v_{\sigma_k}} = (-)^{(k-1)+(k-2)+\dots+1}\iota_{v_{\sigma_k}}\cdots\iota_{v_{\sigma_1}} = (-)^{\frac{k(k-1)}{2}}\iota_{v_{\sigma_k}}\cdots\iota_{v_{\sigma_1}}$
+ 	The definition usually find in literature of Rogers multibrackets involves the coefficient $ (-)^{\frac{k(k-1)}{2}} = -\varsigma(k-1) = (-)^{k+1} \varsigma(k)$.
+  \item higher observables is Special instance of a more general object  called $L\-\infty$ Algebra...
+ }
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%------------------------------------------------------------------------------------------------
+\section{Multisymplectic observables reduction}
+\checkpoint	
+%------------------------------------------------------------------------------------------------
+
+ %- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\subsection{General idea}
+\begin{frame}{Singular Reduction: Roadmap}
+	%
+	\begin{block}{Data:}
+			\begin{itemize}
+				\item $(M,\omega)$ multisymplectic,
+				\item $S\subset M$ closed $N$ (possibly singular),
+				\item $I_S$ the ideal of smooth functions vanishing on $S$,
+				\item $F\subset \mathfrak X(M)$ a Lie subalgebra s.th. $F(I_S)\subset I_S$.
+			\end{itemize}
+	\end{block}
+	%
+	\vfill
+	\pause
+	%
+	\begin{block}{Goal:}
+		\begin{itemize}
+			\item Identify a constraint triple of the type (algebra , subalgebra, ideal) pertaining to the $L_\infty$ algebra of observables.
+		\end{itemize}
+	\end{block}
+	%
+	\vfill
+	\pause
+	%
+	\begin{block}{Strategy:}
+		\begin{enumerate}
+			\item Define smooth fields/forms \emph{tangent to $N$},
+			\item define smooth fields/forms \emph{vanishing along $N$},
+			\item define \emph{reducible fields} requiring the preservation of the vanishing objects,
+			\item define \emph{reducible forms} requiring their conservation w.r.t. the infinitesimal action,
+			\item define \emph{reducible and vanishing observables},
+			\item \textbf{quotient}
+		\end{enumerate}
+	\end{block}
+
+\end{frame}
+\note[itemize]{
+	\item
+}
+ %- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+ %- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
 \begin{frame}{Translating geometry to algebra}
 
+	\vfill
 	\begin{table}[]
@@
 		 of connected group &$\underline{\cdot}:\mathfrak g\to \Der(\mathcal A_T)$ & of the action \\ \hline \pause
-	 $G$ action preserves $S$ & $\underline \xi(I_S)\subset I_S$ $\forall \xi\in\mathfrak g$& \color{red} Careful! Not equivalent! \\ \hline
+		 $G$ action preserves $S$ & $\underline \xi(I_S)\subset I_S$ $\forall \xi\in\mathfrak g$& \color{red} Careful! Not equivalent! 
+		 \\ \hline
 		\end{tabular}\pause
 	\end{table}
-	\begin{alertblock}{Warning}
+	\vfill
+
+\end{frame}
+\note[itemize]{
+	\item {Warning}
 	$\partial_x$ is algebraically preserving $S=[0,1]\subset \mathbb R=M$, even though the flow leads out of the set.
-\end{alertblock}
-\end{frame}
-
-\begin{frame}{Derivations of constraint algebras}
-	$\mathcal A=(\mathcal A_T,\mathcal A_N,\mathcal A_0)=(C^\infty(M),C^\infty(M), I_S)$\\~
-\begin{itemize} 
-	\item $\Der(\mathcal A)_T:=\Der(\mathcal A)_T$ corresponds to all vector fields\pause
-	\item  $\Der(\mathcal A)_N:=\{v\in \Der(\mathcal A)~|~v(\mathcal A_N)\subset \mathcal A_N, ~v(\mathcal A_0)\subset \mathcal A_0\}$\\
-	corresponds to vector fields ({\color{red}algebraically}) tangent to $S$.\\ \pause
-
-	\item  $\Der(\mathcal A)_0:=\{v\in \Der(\mathcal A)~|~v(\mathcal A_N)\subset \mathcal A_0\}$\\
-	are vector fields vanishing on $S$.\pause
-		\begin{block}{Lemma: Algebraic vanishing = geometric vanishing}
-		$\Der(\mathcal A)_0=\{v ~| ~v|_S=0\}=I_S\cdot \mathfrak X(M)$.
-	\end{block}\pause
-\end{itemize}	
-\end{frame}
-
-\begin{frame}
-	$\mathcal A=(C^\infty(M),C^\infty(M), I_S)$\\
-	$\Der(\mathcal A)=(\mathfrak X(M),~~\{v| v(I_S)\subset I_S\},~~ I_S\mathfrak X(M))$
-		\begin{block}{Lemma: $\mathfrak L:=\Der(\mathcal A)$ is a constraint Lie-Rinehart algebra over $\mathcal A$}
-			This means 
-	\begin{itemize} 
-		\item $\mathfrak L_T$ is a Lie Rinehart algebra over $\mathcal A_T$.
-		\item $\mathfrak L$ is a strong constraint module over $\mathcal A$, i.e.\\ $\mathcal A_N\mathfrak L_N\subset \mathfrak L_N$ and $\mathcal A_0\mathfrak L_T+\mathcal A_T\mathfrak L_0\subset \mathfrak L_0$.
-		\item $[\mathfrak L_N,\mathfrak L_N]\subset \mathfrak L_N$ and  $[\mathfrak L_N,\mathfrak L_0]\subset \mathfrak L_0$
-	\end{itemize}
-
-\end{block}\pause
-
-\begin{exampleblock}{Corollary: $(\Lambda \mathfrak L)^*$ has a constraint Cartan calculus $d, \iota, L$}
-	\begin{itemize} 
-	\item $(\Lambda^k \mathfrak L)^*_T=\Omega^k(M)$
-	\item $(\Lambda^k \mathfrak L)^*_N=\{\alpha~|~\alpha(v_1,...,v_k)\in \mathcal A_N~\forall v_i\in \mathfrak L_N , $ \\ ~~~~~~~~~~~~~~~~~~~~$ \alpha(v_1,...,v_{k-1},w)\in \mathcal A_0~\forall v_i\in \mathfrak L_N , w\in \mathfrak L_0 \}$
-	\item $(\Lambda^k \mathfrak L)^*_0=\{\alpha~|~\alpha(v_1,...,v_k)\in \mathcal A_0~\forall v_i\in \mathfrak L_N\}$
-	\end{itemize}
-
-\end{exampleblock}
-
-\end{frame}
-
-\subsection{Introducing symmetry}
-\begin{frame}
-Let $F\subset \Der(\mathcal A)_N$ a Lie subalgebra  (typically $F=\underline{\mathfrak g}$). Consider:
-\begin{itemize} 
-	\item the constraint algebra $\mathcal B= (C^\infty(M),~~~~ \{f~|~F(f)\subset I_S\},~~~ I_S)$\pause
-	\item the constraint Lie-Rinehart algebra $\mathcal L$  \[ (\mathfrak X(M),~~~~\{v ~|~ [v,F]\subset C^\infty(M)F+I_S\mathfrak X(M)\}, ~~~~ C^\infty(M)F+I_S\mathfrak X(M) )\]
-	\item \pause the constaint differential forms 
-	\[
-	\mathcal W=(\Omega(M),~~~, \{\alpha |\iota_\xi\alpha,L_\xi\alpha\in (\Lambda \mathfrak L)^*_0 ~~\forall \xi\in F \},~~~~(\Lambda \mathfrak L)^*_0  )
-	\]
-	where $(\Lambda^k \mathfrak L)^*_0=\{\alpha~|~\alpha(v_1,...,v_k)\in \mathcal A_0~\forall v_i\in \mathfrak L_N\}$
-\end{itemize}
-\begin{block}{'Lemma': $\mathcal L$ has a Cartan calculus on $\mathcal W$}
-	In particular, from the premultisymplectic form $\omega$ we obtain a constraint $L_{\infty}$-algebra.
-\end{block}
-\end{frame}
-
-\subsection{The reduced $L_\infty$-algebra}
-\begin{frame}[fragile]
-Let $(M,\omega)$ premultisymplectic, $S\subset M$ closed and \\ $F\subset \mathfrak X(M)$ a Lie subalgebra s.th. $F(I_S)\subset I_S$\\ ~\\
-The following subquotient $\frac{\Ham(M,\omega)_N}{\Ham(M,\omega)_0}$\\ of $\Ham(M,\omega)_T=\Ham(M,\omega)$ forms an $L_\infty$-algebra:
-
-	\[\small
-		\frac{
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\subsection{Higher Observables Constraint Algebra}
+\begin{frame}[fragile]{Higher Observables Constraint Algebra}
+	\begin{defpropblock}[$L_\infty$-observables constraint algebra]
+		The following $L_\infty$ algebras form a constraint triple
+		\begin{align*}
+			\Ham_T =&~ L_\infty(M,\omega) \\
+			\Ham_N =&~
+			{\small
 			\left\lbrace
@@
 			\right\rbrace 
-		}{
+			}
+			\\
+			\Ham_0 =&~
+		{\small
 			\left\lbrace
@@
 		}
+		\end{align*}
+		where $(\Lambda^k \mathfrak L)^*_0=\{\alpha~|~\alpha(v_1,...,v_k)\in \mathcal A_0~\forall v_i\in \mathfrak L_N\}$.
+	\end{defpropblock}
+	\vfill
+	\pause
+	Hence, The following subquotient $\frac{\Ham_N}{\Ham_0}$ of $\Ham_T$ forms an $L_\infty$-algebra.
+\end{frame}
+\note[itemize]{
+	\item 	\begin{defblock}[Reducible v.fields ]
+			\begin{displaymath}
+				\X(M)_{[N]} :=
+				\left\lbrace
+					v \in \X(M)
+				~\left\vert~
+					\begin{array}{l}
+						\L_v (I_N) \subseteq I_N	\\		
+						\L_v (\X_g) \subseteq \X_g + I_\X
+					\end{array}
+				\right\rbrace\right.
+			\end{displaymath}
+%			\blfootnote{
+%			 $\X_g$ = $C^\infty(M)$-module generated by the fundamental distribution.
+%			}
+
+	\end{defblock}	
+	%
+	\pause
+	%
+	\begin{defblock}[Reducible forms ]
+		\begin{displaymath}
+			\Omega(M)_{[N]} :=
+			\left\lbrace
+				\alpha \in \Omega(M)
+			~\left\vert~
+				\begin{array}{l r}
+					\L_\underline{\xi} \,\alpha \in I_{\Omega(N)}	\\		
+					\iota_\underline{\xi} \,\alpha \in I_{\Omega(N)}	& \forall \xi \in \g				\end{array}
+			\right\rbrace\right.
+		\end{displaymath}	
+	\end{defblock}	
+	%
+	\pause
+	%
+	\begin{defblock}[Reducible Hamiltonian forms]
+		\begin{displaymath}
+			(\Omega(M)_{ham}^{n-1})_{[N]} :=
+			\left\lbrace
+				\alpha \in \Omega(M)_{ham}^{n-1}
+			~\left\vert~
+				\begin{array}{l r}
+					\alpha \text{ is a reducible form} \\
+					\vHam_\alpha \text{ is a reducible v.field}
+				\end{array}
+			\right\rbrace\right.
+		\end{displaymath}	
+	\end{defblock}	
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\subsection{Conclusions}
+\begin{frame}{Lessons learned}
+	\begin{itemize} 
+\item Constraint triples permit to do differential geometry/ Cartan calculus on singular subquotients,\\ ... in particular constructing observable algebras on them.\pause
+\item Even if $\omega$ is non-degenerate, $\omega_r$ could degenerate, forcing us to pull along the Hamiltonian vector fields explicitly\pause
+\item Coomentum maps in the sense of the Leibniz structure seem better for reducing than $L_\infty$-comomenta \pause
+\item The algebraic approach can treat algebroid / singular foliation symmetries and remembers vanishing orders a the singularities. \pause
+\item The reduction seems to give something novel even in the symplectic case \pause
+\item A 'softer' notion of constraint $L_\infty$ algebra is necessary to obtain all observables of the reduced space.
+	\pause
+			\vfill
+		  \centering 
+		  {\Huge\color{red} 
+		  \emph{Thank you for your attention!}}
+			\vfill
+	\end{itemize}
+\end{frame}
+\note[itemize]{
+	\item 
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%------------------------------------------------------------------------------------------------
+% APPENDIX
+%------------------------------------------------------------------------------------------------
+\appendix
+%------------------------------------------------------------------------------------------------
+
+\section{Supplementary Material}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}
+	\begin{center}
+	\Huge\emph{Supplementary Material}
+	\end{center}
+\end{frame}
+\note[itemize]{
+	\item
+}
+\addtocounter{framenumber}{-1}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}[fragile]{MS geometry and classical field mechanics}\label{Frame:Ms-Field-Mechanics}
+		Consider a smooth manifold $Y$,
+		\begin{columns}
+			\hfill
+			\begin{column}{.5\linewidth}
+				\emph{Multicotangent bundle} $\bigwedge = \bigwedge^n T^\ast Y$\\
+				is naturally $n$-plectic
+			\end{column}
+			\begin{column}{.4\linewidth}
+				\[
+				\begin{tikzcd}
+					\Lambda \ar[d,"\pi"'] & T \Lambda \ar[d,"T \pi"] \ar[l] \\
+					Y								& T Y \ar[l]
+				\end{tikzcd}	
 				\]
-where $(\Lambda^k \mathfrak L)^*_0=\{\alpha~|~\alpha(v_1,...,v_k)\in \mathcal A_0~\forall v_i\in \mathfrak L_N\}$
+			\end{column}
+		\end{columns}
+	\pause
+	\begin{defblock}[Tautological $n$-form]
+		$\theta \in \Omega^n(\Lambda)$ such that:
+		\begin{displaymath}
+		\begin{split}
+			\left[ \iota_{u_1 \wedge \ldots \wedge u_n} \theta \right]_\eta 
+			&= \iota_{(T \pi)_\ast u_1 \wedge \ldots \wedge (T \pi)_\ast u_n} \eta \\
+			&= \iota_{u_1 \wedge \ldots \wedge u_n} \pi^\ast \eta 
+			\qquad \qquad \forall \eta \in \Lambda \, , \: \forall u_i \in T_\eta \Lambda 		
+		\end{split}
+		\end{displaymath}
+	\end{defblock}
+	\vfill
+	\begin{columns}
+		\begin{column}{.6\linewidth}
+			\begin{defblock}[Tautological (multisymplectic) (n+1)-form]
+				$$\omega := d \theta$$
+			\end{defblock}
+		\end{column}
+		\begin{column}{.4\linewidth}
+		 	\begin{claimblock}$\omega$ is not degenerate.\end{claimblock}	
+		\end{column}
+	\end{columns}	
+	\pause
+	\begin{keywordblock}
+		\begin{tabular}{|c|c|c|}
+			\hline 
+			point-particles mechanics & $\rightsquigarrow$ & classical fields mechanics \\
+			%(finite discrete DOF) & & (finite dimensional continuous DOF) \\
+			\hline 
+			symplectic & $\rightsquigarrow$ & multisymplectic \\ 
+			\hline 
+			Observables (Poisson) algebra & $\rightsquigarrow$ & Observables $L-\infty$ algebra
+			 \\ 
+			\hline 
+			Co-moment map & $\rightsquigarrow$ & Homotopy co-momentum map \\ 
+			\hline 
+		\end{tabular} 
+	\end{keywordblock}
+
+\end{frame}
+\note[itemize]{
+	\item This example is significant from the perspective of geometric classical field theory:
+		\begin{displaymath}
+			\frac{\text{classical mechanics}}{\text{symplectic geo.}} =
+			\frac{\text{classical field mechanics}}{\text{multisymplectic geo.}}
+		\end{displaymath}
+	\item Multicotangent bundle is the \emph{Higher analogue} of the cotangent bundle.
+	(but it is not yet the analogue of a \emph{phase space}.)
+\item The multiphase space is the sub-bundle of $n$-forms vanishing when contracted with 2 vertical fields.
+  	\item The reason why this sub-bundle has a particular role is that it can be proved to be isomorphic to a suitable dual of the first Jet bundle.
+  	\item For further details see Gotay et al.
+\href{https://arxiv.org/abs/physics/9801019}{arXiv:physics/9801019}.
+For a pictorial representation of all the structures involved in the geometric mechanics of I order classical field theories see appendix, pag: \ref{frame:Gimmsy}.
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}[t]{Symmetries in \textbf{multisymplectic geometry}}
+	Consider a Lie algebra action $v:\mathfrak{g} \to \mathfrak{X}(M)$  preserving the $n$-plectic form $\omega$,
+	\vfill
+
+	\vspace{-1em}
+	\begin{columns}[T]
+		\setlength{\belowdisplayskip}{5pt}
+		\begin{column}{.50\linewidth}
+			%
+			\centering \it
+			\onslide<2->{
+				$-$ symplectic case $-$
+				\begin{defblock}[Comoment map pertaining to $v$]
+					Lie algebra morphism
+					$$ f: \mathfrak{g} \to C^\infty(M) $$
+					such that
+					$$ d~f (x) = -\iota_{v_x} \omega \qquad \forall x \in \mathfrak{g}~.$$
+				\end{defblock}
+			}
+		\end{column}	
+		%
+		\onslide<2->{\vrule{}}
+		%
+		\begin{column}{.50\linewidth}
+			\centering \it
+			\onslide<3->{			
+				$-$ $n$-plectic case $-$
+				\begin{defblock}[Homotopy comoment map \tiny (HCMM)]
+					$L_\infty$-morphism 
+					$$ (f_k) : \mathfrak{g} \to L_\infty (M,\omega)$$
+					such that
+					$$ d~f_1(x) = -\iota_{v_x} \omega \qquad \forall x \in \mathfrak{g}~.$$
+				\end{defblock}	
+			}
+		\end{column}	
+	\end{columns}	
+	%
+	\pause
+	\vfill
+	\centering 
+	\onslide<4->{\textbf{-- Conserved quantities --}}
+	%
+	\vspace{-.5em}
+	\begin{columns}[T]
+		\setlength{\belowdisplayskip}{5pt}
+		\begin{column}{.50\linewidth}
+			%
+			\centering \it
+			\onslide<4->{
+			\begin{propblock}[Noether Theorem]
+				\small Fixed $H\in C^\infty_{\text{Ham}}(M)$ ($\mathfrak{g}$-invariant) ,
+				$$\mathcal{L}_{v_H} f(x) = 0 \qquad \forall x \in \mathfrak{g}$$
+			\end{propblock}
+			}
+		\end{column}	
+		%
+		\onslide<5->{\vrule{}}
+		%
+		\begin{column}{.50\linewidth}
+			\centering \it
+			\onslide<5->{			
+			\begin{propblock}[RWZ16 Theorem]
+				\small Fixed $H\in \Omega^{n-1}_{\text{Ham}}(M)$ ($\mathfrak{g}$-invariant),
+				$$\mathcal{L}_{v_H} f_k(p) \in B^k(M) \qquad \forall p \in Z_k(\mathfrak{g})$$			
+			\end{propblock}
+			}
+		\end{column}	
+	\end{columns}		
+\end{frame}
+\note{
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}{Reminder: $L_\infty$ Algebras}
+
+		\emph{
+			$L_\infty$-algebra is the notion that one obtains from a Lie algebra when one requires the Jacobi identity to be satisfied only up to a higher coherent chain homotopy.
+		}
+		\\
+		\vspace{.5em}
+		\begin{defblock}[$L_\infty$-algebra ~\emph{(Lada, Markl)} ~\cite{Lada1995}]
+			\includestandalone{Pictures/Figure_Linfinitydef}
+		\end{defblock}	
+		%
+		%
+	\pause
+	\vfill
+	\begin{thmblock}[Rogers \cite{Rogers2010}]
+		The \emph{higher observable algebra} $L_{\infty}(M,\omega)$ 	forms an honest $L_\infty$ algebra.
+		\footnotetext{ Take $\mu_1 = \text{d}$, $\mu_k=\lbrace\dots\rbrace_k$, $L$ is a shifted truncation of the de Rham complex.}
+	\end{thmblock}
+\end{frame}
+\note[itemize]{
+	\item $L_\infty$-algebra is the notion obtained from a Lie algebra requiring that the Jacobi identity is satisfied only up to a higher coherent chain homotopy.
+	\item The Lie-n algebra mentioned before is a $L_\infty$ algebra with underlying graded vector space concentrated in degrees $0,1...n$.
+
+	\item Definition. We say that a permutation $\sigma \in S_n$ is a $(j,n-j)$-unshuffle, $0\leq j \le1 n$  if $\sigma(1)< \dots < \sigma(j)$ and $\sigma(j+1)<\dots<\sigma(n)$.
+	\\
+	You can also say that $\sigma$ is a $(j,n-j)$-unshuffle if $\sigma(i)< \sigma(i+1)$ when $i\neq j$.
+
+	\item 	Alternatively, the Jacobiators can be also denoted as $$\displaystyle J_m=\sum_{i+j=m+1} 	\mu_i \triangleleft \mu_j = 0$$
+	employing the so-called \emph{ Richardson-Nijenhuis product}
+		 $$\mu_i\circ \mu_j := (-)^{i(j+1)}\frac{1}{j!(i-1)!}\mu_i \triangleleft \mu_j\otimes \mathbb{1}_{i-1} \circ \mathcal{A}~,$$
+		 where $\mathcal{A}$ denotes the (graded) total skew-symmetrizator.
+
+	\item see frame extra-\ref{Frame:unwapping-Jacobi} for a slightly demystification of the higher Jacobi equations.
+
+	\item more precisely this statement is a proposition/definition
+
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%------------------------------------------------------------------------------------------------
+\subsection{References \& Aknowledgments}
+%------------------------------------------------------------------------------------------------
+
+%TODO aknowledgiare Leonid (sue slides) e Marvin (sua Tesi su Arxiv
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}[t,allowframebreaks]{Aknowledgments}
+	\begin{itemize}
+		\item MW reduction as "restriction to level sets", C. Lessig,
+			\href{https://arxiv.org/abs/1206.3302}{arXiv:1206.3302}
+
+	\end{itemize}
+\end{frame}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%TODO Modificare il Readme ricordando che questo si compila con Biber
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+% https://en.wikibooks.org/wiki/LaTeX/Bibliographies_with_biblatex_and_biber
+\begin{frame}[t,allowframebreaks]{Bibliography}
+	%\nocite{*}
+	\printbibliography
+\end{frame}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+% TEMP! All credit to Leonid Ryvkin www.ryvkin.eu
+\section{Leos}
+
+\subsection{Motivating example of $L_\infty$-algebra}
+%TODO All credits to Leo 
+\begin{frame}{Back to the symplectic case, $M=\mathbb R^2$}
+	Let $\omega=dx\wedge dy$, $\mathfrak X(\mathbb R^2,\omega)=\{X|~L_X\omega=0\}$.\pause
+
+	\begin{itemize}
+		\item {\bf Symplectic gradient}\\  $sgrad:C^\infty(\mathbb R^2)\to \mathfrak X(\mathbb R^2,\omega)$ (surjecive, kernel $\mathbb R$):\\ 
+		$$f\mapsto sgrad(f)={-\partial^yf \choose \partial^xf}$$\pause 
+		\item {\bf Poisson bracket} on $C^\infty(\mathbb R^2)$: $$\{f,g\}:=\partial^xf\partial^yg-\partial^xg\partial^yf$$ \\pause
+
+		\item {\bf Preservation of the bracket} $$sgrad(\{f,g\})=[sgrad(f),sgrad(g)]$$
+	\end{itemize}\pause
+	{\color{teal} Conclusion: } One can use the nicer space $C^\infty(\mathbb R^2)$ instead of $\mathfrak X(\mathbb R^2,\omega)$!
+\end{frame}
+
+\begin{frame}{Let's try the same in $\mathbb R^3$}
+	\begin{itemize}
+		\item $\mathfrak X(\mathbb R^3)=\{(v_x,  v_y,  v_z)^T\}
+		$\\ 
+		\item {\bf Lie bracket :}
+		$$[(v_x,  v_y,  v_z)^T,(w_x,  w_y,  w_z)^T]= (\sum_i v_i\partial^i(w_x) - w_i\partial^i(v_x) ,  \ldots ,\ldots)^T  $$
+		\item {\bf volume form: }$\Omega=dx\wedge dy\wedge dz$ 
+		\item {\bf volume-preserving fields: }$$\mathfrak X(\mathbb R^3,\Omega)=\{(v_x,v_y,v_z)^T~| \sum_i\partial^iv_i=0\}$$
+	\end{itemize}\pause~\\
+	This time the surjection is given by the {\bf Rotational}:
+
+	$$rot:\mathfrak X (\mathbb R^3)\to \mathfrak X (\mathbb R^3,\Omega)$$
+	$$
+	rot((v_x,v_y,v_z)^T)= (\partial^yv_z-\partial^zv_y, \partial^z v_x-\partial^xv_z, \partial^x v_y-\partial^yv_x)^T
+	$$
+\end{frame}
+
+\begin{frame}
+
+	{\color{red} Problem: } $rot$ does not commute with the bracket: $[rot(X),rot(Y)]\neq rot([X,Y])$ in general\\
+	~\\
+	\pause
+	{\color{teal} Solution: } New bracket $\{X,Y\}:=rot(X)\times rot(Y)$,\\ where $\times$ is the vector cross product on $\mathbb R^3$.\\~\\
+	\pause
+	We have $rot(\{X,Y\})=[rot(X), rot(Y)]$ \pause but no Jacobi identity. However: $$\{X,\{Y,Z\}\}-\{\{X,Y\},Z\}-\{Y,\{X,Z\}\}$$
+	$$=- grad((rot(X)\times rot(Y))\cdot rot(Z))$$
+
+\end{frame}
+
+\begin{frame}
+	$C^\infty(\mathbb R^3)\oplus \mathfrak X(\mathbb R^3)=:L_{-1}\oplus L_0$ form a \underline{\bf $L_\infty$ algebra} with:
+	\begin{itemize} 	
+		\item $l_1:L_{-1}\to L_0$, $l_1(f)=grad(f)$
+		\item $l_2:L_{0}\times L_0\to L_0$, $l_2(X,Y)=\{X,Y\}$
+		\item $l_3:L_{0}\times L_0\times L_0\to L_{-1}$, $l_3(X,Y,Z)=-(rot(X)\times rot(Y))\cdot rot(Z)$ 
+	\end{itemize}~\\~\\ \pause
+	In our case it means the following identities are satisfied:
+	\begin{itemize} 	
+		\item $l_2(l_1(f),Y)=0$
+		\item $l_2(l_2(X,Y),Z) - cycl= l_1l_3(X,Y,Z)$
+		\item $l_3(l_2(X,Y),Z,W)-cycl=0$
+	\end{itemize}
+\end{frame}
+
+\subsection{The multisymplectic observable algebra}
+
+\begin{frame}[fragile]
+	\begin{block}{Def. Observable $L_\infty$ algebra [Rogers2012]}
+		Let $(M,\omega)$ pre-multisymplectic. Set:
+			\begin{itemize} 	
+			\item $\Ham^0(M,\omega)=\{(\alpha,v)\in \Omega^{n-1}(M)\times \mathfrak X(M)~|~d\alpha=-\iota_v\omega  \}$
+			\item $\Ham^{-i}(M,\omega)= \Omega^{n-1-i}(M)$, $1\leq i\leq n-1$.
+			\item  $l_1=d:\Ham^{-i}(M,\omega)\to \Ham^{-i+1}(M,\omega)$,\\ (resp. $(d,0)$ for $i=1$)
+			\item $l_k:\Lambda^k\Ham^0(M,\omega)\to \Ham^{2-k}(M,\omega),$
+			\begin{align*}
+			&l_k((\alpha_1,v_1),...,(\alpha_k,v_k))=-(-1)^{\frac{k(k+1)}{2}}\iota_{v_k}...\iota_{v_1}\omega & k\geq 3\\
+			&l_2((\alpha_1,v_1),(\alpha_2,v_2))=(\iota_{v_2}\iota_{v_1}\omega, [v_1,v_2])
+			\end{align*}
+		\end{itemize}
+	\end{block}
+	\vspace{-15mm}
+	\pause
+	% https://q.uiver.app/#q=WzAsNixbMCwwLCJDXlxcaW5mdHkoTSkiXSxbMSwwLCJcXE9tZWdhXjEoTSkiXSxbMiwwLCIuLi4iXSxbMywwLCJcXE9tZWdhXntuLTN9KE0pIl0sWzQsMCwiXFxPbWVnYV57bi0yfShNKSJdLFs1LDAsIlxcSGFtXjAoTSkiXSxbMCwxLCJkIl0sWzEsMiwiZCJdLFsyLDMsImQiXSxbMyw0LCJkIl0sWzQsNSwiKGQsMCkiXSxbNSw1LCJsXzIiLDAseyJsYWJlbF9wb3NpdGlvbiI6NDAsIm9mZnNldCI6MSwiYW5nbGUiOjQ1LCJsZXZlbCI6Mn1dLFs1LDQsImxfMyIsMCx7ImN1cnZlIjotMywibGV2ZWwiOjN9XSxbNSwzLCJsXzQiLDIseyJjdXJ2ZSI6MywibGV2ZWwiOjR9XV0=
+	\[\tiny\begin{tikzcd}
+		{C^\infty(M)} & {\Omega^1(M)} & {...} & {\Omega^{n-3}(M)} & {\Omega^{n-2}(M)} & {\Ham^0(M)}
+		\arrow["d", from=1-1, to=1-2]
+		\arrow["d", from=1-2, to=1-3]
+		\arrow["d", from=1-3, to=1-4]
+		\arrow["d", from=1-4, to=1-5]
+		\arrow["{(d,0)}", from=1-5, to=1-6]
+		\arrow["{l_4}"', curve={height=18pt}, Rightarrow, scaling nfold=4, from=1-6, to=1-4]
+		\arrow["{l_3}", curve={height=-18pt}, Rightarrow, scaling nfold=3, from=1-6, to=1-5]
+		\arrow["{l_2}"{pos=0.4}, shift right, Rightarrow, from=1-6, to=1-6, loop, in=10, out=80, distance=10mm]
+	\end{tikzcd}\]
+\end{frame}
+
+\begin{frame}
+\begin{block}{Thm. $Ham^\bullet(M,\omega)$ is an $L_\infty$-algebra [Rogers2012]}
+This means $
+\substack{
+l_1l_{m+1}(x_1,...,x_{m+1})=\sum_{i<j}(-1)^{i+j}l_m(l_2(x_{i},x_j),x_1,...,\widehat{x_i},...,\widehat{x_j},...,x_{m+1})}
+$ for all $m$ and all possible $x_i$, where $l_0:=0$ and $l_{m+2}:=0$.
+\end{block}\pause
+
+{\bf Remark:} We could instead turn $\Ham^0(M,\omega)$ into a Left-Leibniz algebra by $[(\alpha,v)(\beta, w)]:=(L_v\beta,[v,w])$. This satisfies (left-)Jacobi, but is not skew-symmetric.\pause
+
+\begin{block}{Remark}
+ The above also works if we replace $(C^\infty(M),\mathfrak X(M))$ with any Lie-Rinehart algebra $(A, L)$ and $\omega$ with a cocycle in $(\Lambda^{n+1}_AL)^*$.
+\end{block}\pause
+A Lie Rinehart algebra is: 
+\begin{itemize} 
+	\item A commutative algebra $A$ and an A-module $L$
+	\item A Lie algebra structure on $L$
+	\item A Lie algebra and module homomorphism $\rho:L\to \Der(A)$
+\end{itemize}
+such that $[\ell, a\tilde \ell]=a[\ell,\tilde \ell]+\rho(\ell)(a) \cdot \tilde\ell$
+\end{frame}
+
+\subsection{Preview of our answer}
+\begin{frame}
+We will develop a multisymplectic reduction in this talk, symplectically it is:
+\begin{block}{Construction: Multisymplectic reduction in the symplectic case}
+Let $Q_S=\{f~|~ f|_S=0\rm{~and~} df|_S=0\}$ Then the $L_\infty$-reduction is:
+$$
+\frac{N(I_S)\cap N(I_\mu+Q)}{I_\mu+Q}
+$$
+\end{block}	\pause
+Such a formula can be more generally applied to a Poisson algebra $P$ with associative ideals $I\subset J$ such that $\{I,I\}\subset I$ and $\{I,J\}\subset J$:
+$$
+\frac{N(J)\cap N(I+Q)}{I+Q}
+$$
+with $Q=\{f\in J|~\{f,P\}\subset J\}$
 \end{frame}
@@
 \subsection{Main application}
-\begin{frame}[fragile]
+\begin{frame}[fragile]{Geometric Multisymplectic reduction}
 Let $(M,\omega)$ premultisymplectic, $\underline{\cdot}:\mathfrak g\to \mathfrak X(M)$ an action and\\
@@
 
-\begin{frame}
+\begin{frame}{Relating Geometric and Algebraic reduction}
 \begin{block}{Lemma: Relating the reductions}	
@@
 
-\subsection{Lessons learned}
-\begin{frame}{Lessons learned}
-	\begin{itemize} 
-\item Constraint triples permit to do differential geometry/ Cartan calculus on singular subquotients,\\ ... in particular constructing observable algebras on them.\pause
-\item Even if $\omega$ is non-degenerate, $\omega_r$ could degenerate, forcing us to pull along the Hamiltonian vector fields explicitly\pause
-\item Coomentum maps in the sense of the Leibniz structure seem better for reducing than $L_\infty$-comomenta \pause
-\item The algebraic approach can treat algebroid / singular foliation symmetries and remembers vanishing orders a the singularities. \pause
-\item The reduction seems to give something novel even in the symplectic case \pause
-\item A 'softer' notion of constraint $L_\infty$ algebra is necessary to obtain all observables of the reduced space.
-
-	\end{itemize}
+\begin{frame}{Derivations of constraint algebras}
+	$\mathcal A=(\mathcal A_T,\mathcal A_N,\mathcal A_0)=(C^\infty(M),C^\infty(M), I_S)$\\~
+\begin{itemize} 
+	\item $\Der(\mathcal A)_T:=\Der(\mathcal A)_T$ corresponds to all vector fields\pause
+	\item  $\Der(\mathcal A)_N:=\{v\in \Der(\mathcal A)~|~v(\mathcal A_N)\subset \mathcal A_N, ~v(\mathcal A_0)\subset \mathcal A_0\}$\\
+	corresponds to vector fields ({\color{red}algebraically}) tangent to $S$.\\ \pause
+
+	\item  $\Der(\mathcal A)_0:=\{v\in \Der(\mathcal A)~|~v(\mathcal A_N)\subset \mathcal A_0\}$\\
+	are vector fields vanishing on $S$.\pause
+		\begin{block}{Lemma: Algebraic vanishing = geometric vanishing}
+		$\Der(\mathcal A)_0=\{v ~| ~v|_S=0\}=I_S\cdot \mathfrak X(M)$.
+	\end{block}\pause
+\end{itemize}	
+\end{frame}
+
+\begin{frame}
+	$\mathcal A=(C^\infty(M),C^\infty(M), I_S)$\\
+	$\Der(\mathcal A)=(\mathfrak X(M),~~\{v| v(I_S)\subset I_S\},~~ I_S\mathfrak X(M))$
+		\begin{block}{Lemma: $\mathfrak L:=\Der(\mathcal A)$ is a constraint Lie-Rinehart algebra over $\mathcal A$}
+			This means 
+	\begin{itemize} 
+		\item $\mathfrak L_T$ is a Lie Rinehart algebra over $\mathcal A_T$.
+		\item $\mathfrak L$ is a strong constraint module over $\mathcal A$, i.e.\\ $\mathcal A_N\mathfrak L_N\subset \mathfrak L_N$ and $\mathcal A_0\mathfrak L_T+\mathcal A_T\mathfrak L_0\subset \mathfrak L_0$.
+		\item $[\mathfrak L_N,\mathfrak L_N]\subset \mathfrak L_N$ and  $[\mathfrak L_N,\mathfrak L_0]\subset \mathfrak L_0$
+	\end{itemize}
+
+\end{block}\pause
+
+\begin{exampleblock}{Corollary: $(\Lambda \mathfrak L)^*$ has a constraint Cartan calculus $d, \iota, L$}
+	\begin{itemize} 
+	\item $(\Lambda^k \mathfrak L)^*_T=\Omega^k(M)$
+	\item $(\Lambda^k \mathfrak L)^*_N=\{\alpha~|~\alpha(v_1,...,v_k)\in \mathcal A_N~\forall v_i\in \mathfrak L_N , $ \\ ~~~~~~~~~~~~~~~~~~~~$ \alpha(v_1,...,v_{k-1},w)\in \mathcal A_0~\forall v_i\in \mathfrak L_N , w\in \mathfrak L_0 \}$
+	\item $(\Lambda^k \mathfrak L)^*_0=\{\alpha~|~\alpha(v_1,...,v_k)\in \mathcal A_0~\forall v_i\in \mathfrak L_N\}$
+	\end{itemize}
+
+\end{exampleblock}
+
+\end{frame}
+
+\subsection{Introducing symmetry}
+\begin{frame}
+Let $F\subset \Der(\mathcal A)_N$ a Lie subalgebra  (typically $F=\underline{\mathfrak g}$). Consider:
+\begin{itemize} 
+	\item the constraint algebra $\mathcal B= (C^\infty(M),~~~~ \{f~|~F(f)\subset I_S\},~~~ I_S)$\pause
+	\item the constraint Lie-Rinehart algebra $\mathcal L$  \[ (\mathfrak X(M),~~~~\{v ~|~ [v,F]\subset C^\infty(M)F+I_S\mathfrak X(M)\}, ~~~~ C^\infty(M)F+I_S\mathfrak X(M) )\]
+	\item \pause the constaint differential forms 
+	\[
+	\mathcal W=(\Omega(M),~~~, \{\alpha |\iota_\xi\alpha,L_\xi\alpha\in (\Lambda \mathfrak L)^*_0 ~~\forall \xi\in F \},~~~~(\Lambda \mathfrak L)^*_0  )
+	\]
+	where $(\Lambda^k \mathfrak L)^*_0=\{\alpha~|~\alpha(v_1,...,v_k)\in \mathcal A_0~\forall v_i\in \mathfrak L_N\}$
+\end{itemize}
+\begin{block}{'Lemma': $\mathcal L$ has a Cartan calculus on $\mathcal W$}
+	In particular, from the premultisymplectic form $\omega$ we obtain a constraint $L_{\infty}$-algebra.
+\end{block}
 \end{frame}

### 2025-01-20 msconstraints-short-main.tex
Conference version.

@@
 \begin{frame}{Regular reduction in symplectic geometry}
+
 	\textbf{\color{UniGreen}Symplectic reduction:}~~
@@
 	\pause
-	\begin{columns}
-		\begin{column}{0.40\textwidth}
-			\includegraphics[width=\textwidth]{Pictures/Reduction}
-		\end{column}
-
-		\begin{column}{0.6\textwidth}
+
+	\begin{center}
+		\includegraphics[width=.5\textwidth]{Pictures/Reduction}	
+	\end{center}
+
 	\textbf{\color{UniGreen}In mechanics:}~~
@@
 			\color{gray}\small( e.g. restricting to studying a point-like particle in a central potential by studying it in radial coordinates)
-		\end{column}	
-	\end{columns}	
+
 \end{frame}
@@
 	 \pause
+	 \vfill
 	 %
@@
 \subsection{Constraints Algebras}
-\begin{frame}[fragile]{Attempting algebraic reduction}
+\begin{frame}[fragile]{Attempting algebraic reduction naively}
 When the action is not 'free and proper', we can try to mimic this directly using the function algebras:
@@
 			\item[-] Both regular/geometric and singular/algebraic reduction are 2-steps procedures (1. restrict 2. quotient).
-			\item[-] Let's work in a category where all data needed for the reduction are bundled together in suitable categorical objects. {\tiny (To avoid pathologies arising from these steps)}
+			\item[-] Let's work in a category where all data needed for the reduction are bundled together in a suitable categorical objects. {\tiny (To avoid pathologies arising from these steps)}
 	    \end{itemize}
@@
 \begin{frame}{Other approaches to reduction}
-
+ 	Many singular reduction schemes adhere to this pattern!
+ 	\vfill
+ 	\pause
 \begin{table}[]
@@
 		\hline \pause
-	$C^\infty(M)$&      $N_\mu$     &   $I_\mu$   & $\substack{N_\mu= \{ f | gf-f\in I_\mu \forall g\in G\}}$\\
+	$C^\infty(M)$&      $N_\mu$     &   $I_\mu$   & $\substack{N_\mu= \{ f | gf-f\in I_\mu \forall g\in G\}}$ \footnote{When $G$ connected $N_\mu=N(I_\mu):=\{f~|~\{f,I_\mu\}\subset I_\mu\}$.}\\
 	\hline
@@
 	\vfill
-{\bf Remarks }names in order: 'naive' , Dirac, Sniatycki, Arms-Cushman-Gotay, Sniatycki-Weinstein.\pause \\
-When $G$ connected $N_\mu=N(I_\mu):=\{f~|~\{f,I_\mu\}\subset I_\mu\}$. 
+	{\bf Remarks }names in order: 'naive' , Dirac, Sniatycki, Arms-Cushman-Gotay, Sniatycki-Weinstein.
+
 \end{frame}
@@
 		 \\ \hline
-		\end{tabular}\pause
+		\end{tabular}
 	\end{table}
@@
 \subsection{Higher Observables Constraint Algebra}
-\begin{frame}[fragile]{Higher Observables Constraint Algebra}
+\begin{frame}[shrink]{Higher Observables Constraint Algebra}
 	\begin{defpropblock}[$L_\infty$-observables constraint algebra]
@@
 		\begin{align*}
-			\Ham_T =&~ L_\infty(M,\omega) \\
+			\Ham_T =&~ L_\infty(M,\omega) \\[1em]
 			\Ham_N =&~
@@
 			\begin{array}{l l}
-				\iota_\xi \alpha \in (\Lambda \mathfrak L)^*_0 &\\
-				L_\xi\alpha \in (\Lambda \mathfrak L)^*_0&~\forall \xi \in F\\
+				\iota_\xi \alpha \in \Omega_0 &\\
+				\L_\xi\alpha \in \Omega_0&~\forall \xi \in F\\
 				\hline
@@
 				X(I_S)\subset I_S &\\
-				L_\xi X \in C^{\infty}(M) F + I_S\mathfrak X(M)
+				\L_\xi X \in C^{\infty}(M) F + I_S\mathfrak X(M)
 				&~\forall \xi \in F\\
@@
 			}
-			\\
+			\\[1em]
 			\Ham_0 =&~
@@
 			\begin{array}{l}
-				\alpha \in (\Lambda \mathfrak L)^*_0\\
+				\alpha \in \Omega_0\\
 				\hline
@@
 		\end{align*}
-		where $(\Lambda^k \mathfrak L)^*_0=\{\alpha~|~\alpha(v_1,...,v_k)\in \mathcal A_0~\forall v_i\in \mathfrak L_N\}$.
+		where: 
+			\begin{align*}
+				\small\Omega_0^k &:=~\{\alpha \in \Omega^k(M)~|~\alpha(v_1,...,v_k)\in  I_S~\forall v_i\in \X_N\} 
+				\\
+				\mathfrak{X}_N &:=~ 
+				\left\lbrace
+					v \in \X(M)
+				~\left\vert~
+					\begin{array}{l}
+						\L_v (I_N) \subseteq I_N	\\		
+						\L_v (C^{\infty}(M) F) \subseteq C^{\infty}(M) F + I_S\mathfrak X(M)
+					\end{array}
+				\right\rbrace\right.
+			\end{align*} 
 	\end{defpropblock}
@@
 	\pause
-	Hence, The following subquotient $\frac{\Ham_N}{\Ham_0}$ of $\Ham_T$ forms an $L_\infty$-algebra.
+	Hence, the subquotient $\frac{\Ham_N}{\Ham_0}$ of $\Ham_T$ forms an $L_\infty$-algebra.
 \end{frame}
@@
 			\end{displaymath}
-%			\blfootnote{
-%			 $\X_g$ = $C^\infty(M)$-module generated by the fundamental distribution.
-%			}
-
+			$\X_g$ = $C^\infty(M)$-module generated by the fundamental distribution.
 	\end{defblock}	
@@
 \subsection{Conclusions}
-\begin{frame}{Lessons learned}
+\begin{frame}{Conclusions}
 	\begin{itemize} 
@@
 \item Coomentum maps in the sense of the Leibniz structure seem better for reducing than $L_\infty$-comomenta \pause
-\item The algebraic approach can treat algebroid / singular foliation symmetries and remembers vanishing orders a the singularities. \pause
-\item The reduction seems to give something novel even in the symplectic case \pause
-\item A 'softer' notion of constraint $L_\infty$ algebra is necessary to obtain all observables of the reduced space.
+%\item The algebraic approach can treat algebroid / singular foliation symmetries and remembers vanishing orders a the singularities. \pause
+\item The reduction seems to give something novel even in the symplectic case 
+\begin{block}{Construction: Multisymplectic reduction in the symplectic case}
+Let $Q=\{f~|~ f|_S=0\rm{~and~} df|_S=0\}$ Then the $L_\infty$-reduction is:
+$$
+\frac{N(I_S)\cap N(I_\mu+Q)}{I_\mu+Q}
+$$
+\end{block}
+
 	\pause
@@
 \note[itemize]{
-	\item 
+	\item We will develop a multisymplectic reduction in this talk, symplectically is (see slide).
+	\item Such a formula can be more generally applied to a Poisson algebra $P$ with associative ideals $I\subset J$ such that $\{I,I\}\subset I$ and $\{I,J\}\subset J$:
+$$
+\frac{N(J)\cap N(I+Q)}{I+Q}
+$$
+with $Q=\{f\in J|~\{f,P\}\subset J\}$
+
 }
@@
 such that $[\ell, a\tilde \ell]=a[\ell,\tilde \ell]+\rho(\ell)(a) \cdot \tilde\ell$
-\end{frame}
-
-\subsection{Preview of our answer}
-\begin{frame}
-We will develop a multisymplectic reduction in this talk, symplectically it is:
-\begin{block}{Construction: Multisymplectic reduction in the symplectic case}
-Let $Q_S=\{f~|~ f|_S=0\rm{~and~} df|_S=0\}$ Then the $L_\infty$-reduction is:
-$$
-\frac{N(I_S)\cap N(I_\mu+Q)}{I_\mu+Q}
-$$
-\end{block}	\pause
-Such a formula can be more generally applied to a Poisson algebra $P$ with associative ideals $I\subset J$ such that $\{I,I\}\subset I$ and $\{I,J\}\subset J$:
-$$
-\frac{N(J)\cap N(I+Q)}{I+Q}
-$$
-with $Q=\{f\in J|~\{f,P\}\subset J\}$
 \end{frame}

### 2025-01-21 msconstraints-short-main.tex
Slides final version.

@@
 	\\
-%
-This talk explores key algebraic structures in multisymplectic geometry, a generalization of symplectic geometry where higher-degree $k$-forms replace 2-forms.
-A central theme is the interplay between symmetries (group actions preserving the differential form) and reduction, which constructs a lower-dimensional space inheriting the geometric structure of the original manifold.
-
-The Marsden--Weinstein--Meyer theorem in symplectic geometry connects this reduction process to regular-level sets of momentum maps, with extensions to singular cases by Śniatycki and Weinstein.
-Marvin Dippel, Chiara Esposito, and Stephan Waldmann (\href{https://arxiv.org/abs/2310.05613}{\texttt{arXiv:2310.05613}}) developed a framework for constraint algebras of observables in the context of coisotropic reduction in Poisson geometry.
-
-Our research builds on previous work by adapting and implementing algebraic reduction schemes within multisymplectic geometry, providing a higher-dimensional perspective on the relationship between symmetries and reduction.
-
-This talk reviews higher versions of observable algebras and moment maps in multisymplectic geometry and examines how regular and singular reduction schemes extend to this framework.
-The presentation is based on ongoing joint work with Leonid Ryvkin.
+    % Multisymplectic manifolds are a straightforward generalization of symplectic manifolds where closed non-degenerate $n$-forms are considered in place of $2$-forms.
+    % Investigating the relationship between symmetries (group action preserving the fixed differential form) and reduction is a natural theme when dealing with (multi) symplectic structures.
+	%
+    In the context of (multi)-symplectic, a reduction scheme can be taught to construct a second space of reduced dimension out of a given (multi)-symplectic manifold with symmetries.
+The reduced space thus obtained enjoys the convenient property of embodying the relevant geometric structure of the starting unreduced object.
+
+    A well-known result in symplectic geometry, the Marsden–Weinstein–Meyer theorem, states that the relevant geometric structure of a symplectic manifold can be studied on the orbits contained in a regular level set of a so-called "momentum map."
+    Following the seminal work by Śniatycki and Weinstein, many extensions to singular momentum maps have been discussed in the literature.
+
+    Recently, Marvin Dippel, Chiara Esposito, and Stephan Waldmann (see, e.g.
+\href{https://arxiv.org/abs/2310.05613}{arXiv:2310.05613}) developed a framework, known as constraints or isotropic algebras, that conveniently helps to make order in this plethora of constructions taking advanced of their similar structural patterns.
+
+    This talk, based on ongoing joint work with Casey Blacker and Leonid Ryvkin, reviews the relevant algebraic structures related to multisymplectic manifolds and discusses how the framework of constraint algebras can be adapted to algebraic reduction schemes in this setting.
 
@@
 	\begin{block}{Based on:}
-%		 \emph{ \small
-%			 Blacker, M, Ryvkin;
-%			\textbf{Reduction of $L_\infty$-algebra of observables on multisymplectic manifolds}; 
-%			\href{https://arxiv.org/abs/2206.03137}{arXiv:2206.03137}.
-%		}
-%		\\
+		 \emph{ \small
+			 Blacker, M., Ryvkin;
+			\textbf{Reduction of $L_\infty$-algebra of observables on multisymplectic manifolds}; 
+			\href{https://arxiv.org/abs/2206.03137}{arXiv:2206.03137}.
+		}
+		\\
 		 \emph{ \small
@@
 \note[itemize]{
-	\item Provide a vague idea of the words that make up the title.
-	\item \cite{Dippell2023}
 	\item Conventions:
@@
 		\footnotesize 
-
 		\item We work in the framework of multisymplectic geometry which is one of the possible generalizations of the well-established field of symplectic geometry.
-
 		\item To recall what symplectic geometry is let me assume a particular point of view: mechanics.
@@
 		Symplectic geometry is a branch of differential geometry studying symplectic manifolds; it originated as a formalization of the mathematical apparatus of classical mechanics and geometric optics."{\href{https://ncatlab.org/nlab/show/symplectic+geometry}{nlab}}
-
-		Namely, a sym. mfd. is the geometric structure encoding the phase space of conservative, ordinary, classical, mechanical systems.
-
+		\\
+		Namely, a sym. mfd. is the geometric structure encoding the phase space of conservative, autonomous, ordinary, classical, mechanical systems.
+		\item 	{Geometrically: a Symplectic manifold $(M,\omega)$} $M$ a smooth manifold, $\omega\in \Omega^{2}(M)$ closed and non-degenerate, i.e.
+$d\omega=0$ and  $\omega^\flat:TM\to T^*M, v\mapsto \iota_v\omega$ is injective.
+		\item
+		Examples: orientable 2-manifolds with volume (e.g.
+$S^2$, $T^2$, $\mathbb R^2$), cotangent bunlde $T^*Q$ of any manifold $Q$ (with $\omega=d\theta$, $\theta_\eta(v)=\eta(T\pi_Q(v))$), coadjoint orbits.
 		\item $\theta$ = \emph{tautological 1-form}.
 			$\theta$ evaluated at $p\in T^*Q$ in the fibre of $q\in Q$ and contracted with $v$ coincides with the form $p$ evaluated at $q$ and contracted with the push forward of $v$.
-
 		\item We identify a special class of vector fields.
 			Out of them one can define a Lie bracket.
-
 		\item Poisson is a Lie algebra with the extra property of compatibility with the associative product (Leibniz rule)
-
 		\item take away message: geometric (based on "states") vs algebraic (based on "measurable quantities").
-		\item 	{Def. Symplectic manifold $(M,\omega)$} $M$ a smooth manifold, $\omega\in \Omega^{2}(M)$ closed and non-degenerate, i.e.:
-		\begin{itemize} 	
-			\item $d\omega=0$
-			\item $\omega^\flat:TM\to T^*M, v\mapsto \iota_v\omega$ is injective
-		\end{itemize}
-	\item   Examples:
-		\begin{itemize}
-			\item orientable 2-manifolds with volume, e.g. $S^2$, $T^2$, $\mathbb R^2$
-			\item cotangent bunlde $T^*Q$ of any manifold $Q$, with $\omega=d\theta$. $\theta_\eta(v)=\eta(T\pi_Q(v))$.
-			\item coadjoint orbits
-		\end{itemize}
+
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%	
+\subsection{Regular reduction} 
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%	
+\begin{frame}{Regular reduction in symplectic geometry}
+
+	\textbf{\color{UniGreen}Symplectic reduction:}~~
+	\\ 
+	{\it \small
+	Procedure associating to any (suitably regular) pair of symplectic manifold and Hamiltonian action another symplectic manifold of smaller dimension.}
+	\vfill
+
+	\pause
+
+	\begin{center}
+		\includegraphics[width=.5\textwidth]{Pictures/Reduction}	
+	\end{center}
+
+	\textbf{\color{UniGreen}In mechanics:}~~
+				\\
+			{\it \small
+				it embodies the process of restricting the dynamics of the system to the level sets of the conserved quantities pertaining to the symmetry group.		
+			}
+			\\[.2em]
+			\color{gray}\small( e.g. restricting to studying a point-like particle in a central potential by studying it in radial coordinates)
+
+\end{frame}
+\note[itemize]{
+	\item  \emph{(Credits to \href{https://math.gmu.edu/~cblacke/}{Casey Blacker} for the notes and to \href{https://arxiv.org/abs/1206.3302}{Christian Lessig} for the picture. See acknowledgements.}
+	\item  In classical mechanics symmetry reduction plays an important role. Mathematically, this is usually phrased in terms of Marsden-Weinstein reduction
+	\item {Symplectic Reduction} takes two inputs:
+	\\ 1. Hamiltonian $G$-space $(M,\omega,{\color{orange}G},{\color{blue}\mu})$
+	\\ 2. parameter ${\color{blue}\phi}\in\g^*$
+	\item The \emph{reduced space} is $M_\phi:={\color{blue}\mu^{-1}(\phi)}{\color{orange}/G_\phi}$.
+	\item (Marsden--Weinstein '74, Meyer '73) THM:\\
+		If $\mu^{-1}(\phi)\subset M$ is smooth and $G_\phi\curvearrowright \mu^{-1}(\phi)$ is free and proper, then there is a \textbf{unique symplectic form} $\omega_\phi\in\Omega^2(M_\phi)$ such that $\pi^*\omega_\phi = i^*\omega$.
+
+	\item Heuristic Approach to Reduction:
+	\\1. describe $G\curvearrowright M$ in terms of $\omega$ 	\hspace{1cm}
+	({\color{green}moment map $\mu$})
+	\\2. identify a distinguished reduced space \hspace{1cm}
+	({\color{green}reduction at $\mu=0$})
+	\\3. use the ambiguity in 1.\ to obtain a family of reduced spaces \hspace{1cm}
+	({\color{green}reduction at $\mu-\phi=0$, i.e.\ reduction at $\mu=\phi$}
+	\\
+	{\tiny Note: If $G_\phi\neq G$, then $\mu-\phi:M\to\g^*$ is not a moment map for either $G\curvearrowright M$ or $G_\phi\curvearrowright M$.}
+
 }
@@
 \note[itemize]{
+		\item Moment maps are instrumental to the proper formalization of reduction in symplectic geometry.
 		\item consider an action preserving the symplectic form.
@@
 %- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\subsection{Regular reduction} 
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%	
-\begin{frame}{Regular reduction in symplectic geometry}
-
-	\textbf{\color{UniGreen}Symplectic reduction:}~~
-	\\ 
-	{\it \small
-	Procedure associating to any (suitably regular) pair of symplectic manifold and Hamiltonian action another symplectic manifold of smaller dimension.}
-	\vfill
-
-	\pause
-
-	\begin{center}
-		\includegraphics[width=.5\textwidth]{Pictures/Reduction}	
-	\end{center}
-
-	\textbf{\color{UniGreen}In mechanics:}~~
-				\\
-			{\it \small
-				it embodies the process of restricting the dynamics of the system to the level sets of the conserved quantities pertaining to the symmetry group.		
-			}
-			\\[.2em]
-			\color{gray}\small( e.g. restricting to studying a point-like particle in a central potential by studying it in radial coordinates)
-
-\end{frame}
-\note[itemize]{
-	\item  In classical mechanics symmetry reduction plays an important role. Mathematically, this is usually phrased in terms of Marsden-Weinstein reduction
-	\item {Symplectic Reduction} takes two inputs:
-	\\ 1. Hamiltonian $G$-space $(M,\omega,{\color{orange}G},{\color{blue}\mu})$
-	\\ 2. parameter ${\color{blue}\phi}\in\g^*$
-	\item The \emph{reduced space} is $M_\phi:={\color{blue}\mu^{-1}(\phi)}{\color{orange}/G_\phi}$.
-	\item (Marsden--Weinstein '74, Meyer '73) THM:\\
-		If $\mu^{-1}(\phi)\subset M$ is smooth and $G_\phi\curvearrowright \mu^{-1}(\phi)$ is free and proper, then there is a \textbf{unique symplectic form} $\omega_\phi\in\Omega^2(M_\phi)$ such that $\pi^*\omega_\phi = i^*\omega$.
-
-	\item Heuristic Approach to Reduction:
-	\\1. describe $G\curvearrowright M$ in terms of $\omega$ 	\hspace{1cm}
-	({\color{green}moment map $\mu$})
-	\\2. identify a distinguished reduced space \hspace{1cm}
-	({\color{green}reduction at $\mu=0$})
-	\\3. use the ambiguity in 1.\ to obtain a family of reduced spaces \hspace{1cm}
-	({\color{green}reduction at $\mu-\phi=0$, i.e.\ reduction at $\mu=\phi$}
-	\\
-	{\tiny Note: If $G_\phi\neq G$, then $\mu-\phi:M\to\g^*$ is not a moment map for either $G\curvearrowright M$ or $G_\phi\curvearrowright M$.}
-
-}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
 \begin{frame}[fragile]{Marsden-Weinstein-Meyer reduction}
@@
 \note[itemize]{
-	\item
+	\item \emph{(Credits to \href{https://www.ryvkin.eu/}{Leonid Ryvkin} for the tex code of this slide.)}
 }
@@
 %- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\begin{frame}{Other approaches to reduction}
+\begin{frame}{Other approaches to singular reduction}
  	Many singular reduction schemes adhere to this pattern!
@@
 \note[itemize]{
-	\item  
+	\item \emph{(Credits to \href{https://www.ryvkin.eu/}{Leonid Ryvkin} for the tex code of this slide.)}
 }
@@
 	\item {Def. Multisymplectic manifold $(M,\omega)$}
-	$M$ a smooth manifold, $\omega\in \Omega^{n+1}(M)$ closed and non-deg., i.e.:
-	\begin{itemize}
-		\item $d\omega=0$
-		\item $\omega^\flat:TM\to \Lambda^nT^*M, v\mapsto \iota_v\omega$ is injective
-	\end{itemize} 
+	$M$ a smooth manifold, $\omega\in \Omega^{n+1}(M)$ closed and non-deg., i.e.: $d\omega=0$ and $\omega^\flat:TM\to \Lambda^nT^*M, v\mapsto \iota_v\omega$ is injective.
+	\item Examples: orientable $n{+}1$-manifolds with volume (e.g.
+$S^{n+1}$, $T^{n+1}$, $\mathbb R^{n+1}$ ), multicotangent bunlde $\Lambda^nT^*Q$ of any manifold $Q$ (with $\omega=d\theta$.
+$\theta_\eta(v_1,...,v_n)=\eta(T\pi_Q(v_n),...,T\pi_Q(v_n))$),  semisimple Lie groups, hyperKähler manifolds,...
  	\item Without the non-deg. condition we call it \emph{premultisymplectic}.
-	\item Examples:
-		\begin{itemize} 
-			\item orientable $n{+}1$-manifolds with volume, e.g. $S^{n+1}$, $T^{n+1}$, $\mathbb R^{n+1}$ 
-			\item multicotangent bunlde $\Lambda^nT^*Q$ of any manifold $Q$, with $\omega=d\theta$. $\theta_\eta(v_1,...,v_n)=\eta(T\pi_Q(v_n),...,T\pi_Q(v_n))$. 
-			\item semisimple Lie groups, hyperKähler manifolds,...
-		\end{itemize}
+
 }
@@
 	\end{defblock}
-
-	\pause
-		\tikz[overlay,remember picture]
-		{
-			\node[rounded corners,
-                 fill=orange!5,draw=orange!30,anchor=base]
-            	 (base) at ($(current page.north east)-(2,1)$) [rotate=-0,text width=3.5cm,align=center] {\footnotesize{\textcolor{red}{Hamilton-DeDonder-Weyl \\equation}}};
-		}	
-	\begin{tikzpicture}[overlay,remember picture]
-    	\path[->] (base.south) edge[bend right,red](target.north);
-    \end{tikzpicture}
+%
+%	\pause
+%		\tikz[overlay,remember picture]
+%		{
+%			\node[rounded corners,
+%                 fill=orange!5,draw=orange!30,anchor=base]
+%            	 (base) at ($(current page.north east)-(2,1)$) [rotate=-0,text width=3.5cm,align=center] {\footnotesize{\textcolor{red}{Hamilton-DeDonder-Weyl \\equation}}};
+%		}	
+%	\begin{tikzpicture}[overlay,remember picture]
+%    	\path[->] (base.south) edge[bend right,red](target.north);
+%    \end{tikzpicture}
 	%
@@
 	\begin{itemize}
-		\item  descend to $\Omega^{k-1}_{ham}(M) / {\color{orange}\d\hspace{1pt}\Omega^{k-2}(M)}$, hence getting a Lie algebra;
+		\item  descend to $\Omega^{n-1}_{ham}(M) / {\color{orange}\d\hspace{1pt}\Omega^{n-2}(M)}$, hence getting a Lie algebra;
 		\item Incorporate the {\color{orange}discrepancy} as part of the data of the space of observables $ 
-				L_\infty(M,\omega) = \Omega_{ham}^{k-1}(M)\oplus{\color{orange}\Omega^{\leq k-2}(M)}$
+				L_\infty(M,\omega) = \Omega_{ham}^{n-1}(M)\oplus{\color{orange}\Omega^{\leq n-2}(M)}$.
 			%a \textbf{homotopy Lie algebra} or \textbf{$L_\infty$-algebra}.
@@
 \note[itemize]{
-	\item
+	\item In the paper 
+ \href{https://www.sciencedirect.com/science/article/pii/S0393044018301189}{Invitation to Multisymplectic Geometry} \cite{RYVKIN20199}\	, the equation highlighted in orange, which defines Hamiltonian forms, is referred to as the Hamilton--DeDonder--Weyl equation---a somewhat imaginative extension compared to its traditional formulation in \href{https://en.wikipedia.org/wiki/De_Donder\%E2\%80\%93Weyl_theory}{De Donder--Weyl theory}.
 }
@@
 				\item $(M,\omega)$ multisymplectic,
-				\item $S\subset M$ closed $N$ (possibly singular),
+				\item $S\subset M$ closed subset (possibly singular),
 				\item $I_S$ the ideal of smooth functions vanishing on $S$,
@@
 \note[itemize]{
-	\item
+	\item Remark: the following singular reduction scheme is slightly different from what we proposed in our paper \cite{Blacker2022}.
 }
@@
 \note[itemize]{
+	\item \emph{(Credits to \href{https://www.ryvkin.eu/}{Leonid Ryvkin} for the tex code of this slide.)}
 	\item {Warning}
@@
 	\begin{defpropblock}[$L_\infty$-observables constraint algebra]
-		The following $L_\infty$ algebras form a constraint triple
+		The following $L_\infty$ algebra\footnote{ 
+			\vspace{-1.75em}
 			\begin{align*}
-			\Ham_T =&~ L_\infty(M,\omega) \\[1em]
-			\Ham_N =&~
-			{\small
-			\left\lbrace
-			\begin{array}{l}
-				\alpha\in \Omega^{\leq n-2}(M) ~\mathrm{, respectively}\\	
-				(\alpha,X) \in \Omega^{n{-}1}(M) \oplus\mathfrak X(M)
-			\end{array}
-			~\left\vert~
-			\begin{array}{l l}
-				\iota_\xi \alpha \in \Omega_0 &\\
-				\L_\xi\alpha \in \Omega_0&~\forall \xi \in F\\
-				\hline
-				\iota_X \omega = -d \alpha &\\
-				X(I_S)\subset I_S &\\
-				\L_\xi X \in C^{\infty}(M) F + I_S\mathfrak X(M)
-				&~\forall \xi \in F\\
-			\end{array}
-			\right.
-			\right\rbrace 
-			}
-			\\[1em]
-			\Ham_0 =&~
-		{\small
-			\left\lbrace
-			\begin{array}{l}
-				\alpha\in \Omega^{\leq n-2}(M) ~\mathrm{, respectively}\\	
-				(\alpha,X) \in \Omega^{n{-}1}(M) \oplus \mathfrak X(M)
-			\end{array}
-			~\left\vert~
-			\begin{array}{l}
-				\alpha \in \Omega_0\\
-				\hline
-				\iota_X \omega = -d \alpha\\
-				X \in C^{\infty}(M) F + I_S\mathfrak X(M)
-			\end{array}
-			\right.
-			\right\rbrace
-		}
-		\end{align*}
-		where: 
-			\begin{align*}
-				\small\Omega_0^k &:=~\{\alpha \in \Omega^k(M)~|~\alpha(v_1,...,v_k)\in  I_S~\forall v_i\in \X_N\} 
-				\\
-				\mathfrak{X}_N &:=~ 
+				\small \text{where:\quad} &\Omega_0^k ~:=&\{\alpha \in \Omega^k(M)~|~\alpha(v_1,...,v_k)\in  I_S~\forall v_i\in \X_N\} 
+				\\
+				& \mathfrak{X}_N ~:=& 
 				\left\lbrace
@@
 			\end{align*} 
+		} form a constraint triple
+		\begin{align*}
+			\Ham_T =&~ L_\infty(M,\omega) \\[1em]
+			\Ham_N =&~
+			{\small
+			\left\lbrace
+			\begin{array}{l}
+				\alpha\in \Omega^{\leq n-2}(M) \\\mathrm{\small, respectively}\\	
+				(\alpha,X) \in \Omega^{n{-}1}(M) \oplus\mathfrak X(M)
+			\end{array}
+			~\left\vert~
+			\begin{array}{l l}
+				\iota_\xi \alpha \in \Omega_0 &\\
+				\L_\xi\alpha \in \Omega_0&~\forall \xi \in F\\
+				\hline
+				\iota_X \omega = -d \alpha &\\
+				X(I_S)\subset I_S &\\
+				\L_\xi X \in C^{\infty}(M) F + I_S\mathfrak X(M)
+				&~\forall \xi \in F\\
+			\end{array}
+			\right.
+			\right\rbrace 
+			}
+			\\[1em]
+			\Ham_0 =&~
+		{\small
+			\left\lbrace
+			\begin{array}{l}
+				\alpha\in \Omega^{\leq n-2}(M) \\\mathrm{\small, respectively}\\	
+				(\alpha,X) \in \Omega^{n{-}1}(M) \oplus\mathfrak X(M)
+			\end{array}
+			~\left\vert~
+			\begin{array}{l}
+				\alpha \in \Omega_0\\
+				\hline
+				\iota_X \omega = -d \alpha\\
+				X \in C^{\infty}(M) F + I_S\mathfrak X(M)
+			\end{array}
+			\right.
+			\right\rbrace
+		}
+		\end{align*}
 	\end{defpropblock}
@@
 	\pause
-	Hence, the subquotient $\frac{\Ham_N}{\Ham_0}$ of $\Ham_T$ forms an $L_\infty$-algebra.
-\end{frame}
-\note[itemize]{
-	\item 	\begin{defblock}[Reducible v.fields ]
+	{\centering \color{red} $\Rightarrow$  the subquotient ${\Ham_N} / {\Ham_0}$ forms an $L_\infty$-algebra!}
+\end{frame}
+\note[itemize]{
+	\item 	
+	\begin{defblock}[Reducible v.fields ]
 			\begin{displaymath}
-				\X(M)_{[N]} :=
+				\mathfrak{X}_N ~:=
 				\left\lbrace
@@
 						\L_v (I_N) \subseteq I_N	\\		
-						\L_v (\X_g) \subseteq \X_g + I_\X
+						\L_v (C^{\infty}(M) F) \subseteq C^{\infty}(M) F + I_S\mathfrak X(M)
 					\end{array}
@@
 			\end{displaymath}
-			$\X_g$ = $C^\infty(M)$-module generated by the fundamental distribution.
-	\end{defblock}	
-	%
-	\pause
+			e.g. $F=\X_g$ is the $C^\infty(M)$-module generated by the fundamental distribution of an acting group.
+	\end{defblock}	
 	%
@@
 		\begin{displaymath}
-			\Omega(M)_{[N]} :=
+			\Omega_{N} :=
 			\left\lbrace
@@
 				\begin{array}{l r}
-					\L_\underline{\xi} \,\alpha \in I_{\Omega(N)}	\\		
-					\iota_\underline{\xi} \,\alpha \in I_{\Omega(N)}	& \forall \xi \in \g				\end{array}
+					\L_\underline{\xi} \,\alpha \in \Omega_0	\\		
+					\iota_\underline{\xi} \,\alpha \in \Omega_0	& \forall \xi \in \g				\end{array}
 			\right\rbrace\right.
@@
 	%
-	\pause
 	%
@@
 \subsection{Conclusions}
+%TODO questa slide non è leggibile!
 \begin{frame}{Conclusions}
@@
 \item The reduction seems to give something novel even in the symplectic case 
-\begin{block}{Construction: Multisymplectic reduction in the symplectic case}
+\begin{thmblock}[Multisymplectic reduction in the symplectic case \cite{Blacker2022}]
 Let $Q=\{f~|~ f|_S=0\rm{~and~} df|_S=0\}$ Then the $L_\infty$-reduction is:
@@
 $$
-\end{block}
+\end{thmblock}
 
@@
 \note[itemize]{
-	\item We will develop a multisymplectic reduction in this talk, symplectically is (see slide).
-	\item Such a formula can be more generally applied to a Poisson algebra $P$ with associative ideals $I\subset J$ such that $\{I,I\}\subset I$ and $\{I,J\}\subset J$:
-$$
-\frac{N(J)\cap N(I+Q)}{I+Q}
-$$
-with $Q=\{f\in J|~\{f,P\}\subset J\}$
-
+	\item
 }
@@
 
-%TODO aknowledgiare Leonid (sue slides) e Marvin (sua Tesi su Arxiv
 %- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
@@
 			\href{https://arxiv.org/abs/1206.3302}{arXiv:1206.3302}
+		\item Several tex code snippets and slides in appendix are due to \href{https://www.ryvkin.eu/}{Leonid Ryvkin}.
+		\item Some tex code snippets are due to \href{https://math.gmu.edu/~cblacke/}{Casey Blacker}.
 
@@
 
-% TEMP! All credit to Leonid Ryvkin www.ryvkin.eu
-\section{Leos}
-
-\subsection{Motivating example of $L_\infty$-algebra}
-%TODO All credits to Leo 
-\begin{frame}{Back to the symplectic case, $M=\mathbb R^2$}
-	Let $\omega=dx\wedge dy$, $\mathfrak X(\mathbb R^2,\omega)=\{X|~L_X\omega=0\}$.\pause
-
-	\begin{itemize}
-		\item {\bf Symplectic gradient}\\  $sgrad:C^\infty(\mathbb R^2)\to \mathfrak X(\mathbb R^2,\omega)$ (surjecive, kernel $\mathbb R$):\\ 
-		$$f\mapsto sgrad(f)={-\partial^yf \choose \partial^xf}$$\pause 
-		\item {\bf Poisson bracket} on $C^\infty(\mathbb R^2)$: $$\{f,g\}:=\partial^xf\partial^yg-\partial^xg\partial^yf$$ \\pause
-
-		\item {\bf Preservation of the bracket} $$sgrad(\{f,g\})=[sgrad(f),sgrad(g)]$$
-	\end{itemize}\pause
-	{\color{teal} Conclusion: } One can use the nicer space $C^\infty(\mathbb R^2)$ instead of $\mathfrak X(\mathbb R^2,\omega)$!
-\end{frame}
-
-\begin{frame}{Let's try the same in $\mathbb R^3$}
-	\begin{itemize}
-		\item $\mathfrak X(\mathbb R^3)=\{(v_x,  v_y,  v_z)^T\}
-		$\\ 
-		\item {\bf Lie bracket :}
-		$$[(v_x,  v_y,  v_z)^T,(w_x,  w_y,  w_z)^T]= (\sum_i v_i\partial^i(w_x) - w_i\partial^i(v_x) ,  \ldots ,\ldots)^T  $$
-		\item {\bf volume form: }$\Omega=dx\wedge dy\wedge dz$ 
-		\item {\bf volume-preserving fields: }$$\mathfrak X(\mathbb R^3,\Omega)=\{(v_x,v_y,v_z)^T~| \sum_i\partial^iv_i=0\}$$
-	\end{itemize}\pause~\\
-	This time the surjection is given by the {\bf Rotational}:
-
-	$$rot:\mathfrak X (\mathbb R^3)\to \mathfrak X (\mathbb R^3,\Omega)$$
-	$$
-	rot((v_x,v_y,v_z)^T)= (\partial^yv_z-\partial^zv_y, \partial^z v_x-\partial^xv_z, \partial^x v_y-\partial^yv_x)^T
-	$$
-\end{frame}
-
-\begin{frame}
-
-	{\color{red} Problem: } $rot$ does not commute with the bracket: $[rot(X),rot(Y)]\neq rot([X,Y])$ in general\\
-	~\\
-	\pause
-	{\color{teal} Solution: } New bracket $\{X,Y\}:=rot(X)\times rot(Y)$,\\ where $\times$ is the vector cross product on $\mathbb R^3$.\\~\\
-	\pause
-	We have $rot(\{X,Y\})=[rot(X), rot(Y)]$ \pause but no Jacobi identity. However: $$\{X,\{Y,Z\}\}-\{\{X,Y\},Z\}-\{Y,\{X,Z\}\}$$
-	$$=- grad((rot(X)\times rot(Y))\cdot rot(Z))$$
-
-\end{frame}
-
-\begin{frame}
-	$C^\infty(\mathbb R^3)\oplus \mathfrak X(\mathbb R^3)=:L_{-1}\oplus L_0$ form a \underline{\bf $L_\infty$ algebra} with:
-	\begin{itemize} 	
-		\item $l_1:L_{-1}\to L_0$, $l_1(f)=grad(f)$
-		\item $l_2:L_{0}\times L_0\to L_0$, $l_2(X,Y)=\{X,Y\}$
-		\item $l_3:L_{0}\times L_0\times L_0\to L_{-1}$, $l_3(X,Y,Z)=-(rot(X)\times rot(Y))\cdot rot(Z)$ 
-	\end{itemize}~\\~\\ \pause
-	In our case it means the following identities are satisfied:
-	\begin{itemize} 	
-		\item $l_2(l_1(f),Y)=0$
-		\item $l_2(l_2(X,Y),Z) - cycl= l_1l_3(X,Y,Z)$
-		\item $l_3(l_2(X,Y),Z,W)-cycl=0$
-	\end{itemize}
-\end{frame}
-
-\subsection{The multisymplectic observable algebra}
-
-\begin{frame}[fragile]
-	\begin{block}{Def. Observable $L_\infty$ algebra [Rogers2012]}
-		Let $(M,\omega)$ pre-multisymplectic. Set:
-			\begin{itemize} 	
-			\item $\Ham^0(M,\omega)=\{(\alpha,v)\in \Omega^{n-1}(M)\times \mathfrak X(M)~|~d\alpha=-\iota_v\omega  \}$
-			\item $\Ham^{-i}(M,\omega)= \Omega^{n-1-i}(M)$, $1\leq i\leq n-1$.
-			\item  $l_1=d:\Ham^{-i}(M,\omega)\to \Ham^{-i+1}(M,\omega)$,\\ (resp. $(d,0)$ for $i=1$)
-			\item $l_k:\Lambda^k\Ham^0(M,\omega)\to \Ham^{2-k}(M,\omega),$
-			\begin{align*}
-			&l_k((\alpha_1,v_1),...,(\alpha_k,v_k))=-(-1)^{\frac{k(k+1)}{2}}\iota_{v_k}...\iota_{v_1}\omega & k\geq 3\\
-			&l_2((\alpha_1,v_1),(\alpha_2,v_2))=(\iota_{v_2}\iota_{v_1}\omega, [v_1,v_2])
-			\end{align*}
-		\end{itemize}
-	\end{block}
-	\vspace{-15mm}
-	\pause
-	% https://q.uiver.app/#q=WzAsNixbMCwwLCJDXlxcaW5mdHkoTSkiXSxbMSwwLCJcXE9tZWdhXjEoTSkiXSxbMiwwLCIuLi4iXSxbMywwLCJcXE9tZWdhXntuLTN9KE0pIl0sWzQsMCwiXFxPbWVnYV57bi0yfShNKSJdLFs1LDAsIlxcSGFtXjAoTSkiXSxbMCwxLCJkIl0sWzEsMiwiZCJdLFsyLDMsImQiXSxbMyw0LCJkIl0sWzQsNSwiKGQsMCkiXSxbNSw1LCJsXzIiLDAseyJsYWJlbF9wb3NpdGlvbiI6NDAsIm9mZnNldCI6MSwiYW5nbGUiOjQ1LCJsZXZlbCI6Mn1dLFs1LDQsImxfMyIsMCx7ImN1cnZlIjotMywibGV2ZWwiOjN9XSxbNSwzLCJsXzQiLDIseyJjdXJ2ZSI6MywibGV2ZWwiOjR9XV0=
-	\[\tiny\begin{tikzcd}
-		{C^\infty(M)} & {\Omega^1(M)} & {...} & {\Omega^{n-3}(M)} & {\Omega^{n-2}(M)} & {\Ham^0(M)}
-		\arrow["d", from=1-1, to=1-2]
-		\arrow["d", from=1-2, to=1-3]
-		\arrow["d", from=1-3, to=1-4]
-		\arrow["d", from=1-4, to=1-5]
-		\arrow["{(d,0)}", from=1-5, to=1-6]
-		\arrow["{l_4}"', curve={height=18pt}, Rightarrow, scaling nfold=4, from=1-6, to=1-4]
-		\arrow["{l_3}", curve={height=-18pt}, Rightarrow, scaling nfold=3, from=1-6, to=1-5]
-		\arrow["{l_2}"{pos=0.4}, shift right, Rightarrow, from=1-6, to=1-6, loop, in=10, out=80, distance=10mm]
-	\end{tikzcd}\]
-\end{frame}
-
-\begin{frame}
-\begin{block}{Thm. $Ham^\bullet(M,\omega)$ is an $L_\infty$-algebra [Rogers2012]}
-This means $
-\substack{
-l_1l_{m+1}(x_1,...,x_{m+1})=\sum_{i<j}(-1)^{i+j}l_m(l_2(x_{i},x_j),x_1,...,\widehat{x_i},...,\widehat{x_j},...,x_{m+1})}
-$ for all $m$ and all possible $x_i$, where $l_0:=0$ and $l_{m+2}:=0$.
-\end{block}\pause
-
-{\bf Remark:} We could instead turn $\Ham^0(M,\omega)$ into a Left-Leibniz algebra by $[(\alpha,v)(\beta, w)]:=(L_v\beta,[v,w])$. This satisfies (left-)Jacobi, but is not skew-symmetric.\pause
-
-\begin{block}{Remark}
- The above also works if we replace $(C^\infty(M),\mathfrak X(M))$ with any Lie-Rinehart algebra $(A, L)$ and $\omega$ with a cocycle in $(\Lambda^{n+1}_AL)^*$.
-\end{block}\pause
-A Lie Rinehart algebra is: 
-\begin{itemize} 
-	\item A commutative algebra $A$ and an A-module $L$
-	\item A Lie algebra structure on $L$
-	\item A Lie algebra and module homomorphism $\rho:L\to \Der(A)$
-\end{itemize}
-such that $[\ell, a\tilde \ell]=a[\ell,\tilde \ell]+\rho(\ell)(a) \cdot \tilde\ell$
-\end{frame}
-
-\subsection{Main application}
-\begin{frame}[fragile]{Geometric Multisymplectic reduction}
-Let $(M,\omega)$ premultisymplectic, $\underline{\cdot}:\mathfrak g\to \mathfrak X(M)$ an action and\\
- $\mu:\mathfrak g\to \Omega^{n-1}(M)$ a Leibniz momentum, i.e.
-\[
-X_{\mu(\xi)}=\underline \xi ~~\forall \xi ~~~~~~~\mu([\xi,\zeta])=L_{\underline \xi}\mu(\zeta)~\forall \xi,\zeta
-\]
-Then $F=\underline {\mathfrak g}$ and $S=\{p\in M~|~\mu(\xi)_p=0\forall \xi\in\mathfrak g\}$ satisfy the necessary condition. \pause  Moreover:
-\begin{block}{Thm: The geometric case [Blacker21]}
-If in the above $S$ is smooth and the foliation spannd by $\underline{\mathfrak g}|_S$ is simple, then $M_{r}=\frac{S}{\underline{\mathfrak g}|_S}$ is premultisymplectic with $\omega_r$ unique, satisfying $\pi^*\omega_r=i^*\omega$.
-\[\begin{tikzcd}
-	M &&& S &&& {M_r}
-	\arrow["\begin{array}{c} i \end{array}"', hook', from=1-4, to=1-1]
-	\arrow["\begin{array}{c} \pi \end{array}", two heads, from=1-4, to=1-7]
-\end{tikzcd}\]
-\end{block}
-\end{frame}
-
-\begin{frame}{Relating Geometric and Algebraic reduction}
-\begin{block}{Lemma: Relating the reductions}	
-There is a natural injection $R:\frac{\Ham(M,\omega)_N}{\Ham(M,\omega)_0}\hookrightarrow \Ham(M_r,\omega_r)$.
-\end{block}
-\pause 
-\begin{exampleblock}{Non-surjectivity in general}
-	\begin{itemize} 
-	\item 	$M=\mathbb R^5$, $\omega=dt\wedge (dx_1\wedge dy_1+dx_2\wedge dy_2)$\pause 
-	\item $\mathfrak g=\langle\xi\rangle, \underline{\xi}=\partial_{x_1}$, $\mu(\xi)=-y_1dt$\pause 
-	\item $S=\{y_1=0\}$, $M_r\cong \mathbb R^3$ with $t,x_2,y_2$ and $\omega_r=dt\wedge dx_2\wedge dy_2$\pause 
-	\item $(\alpha,v)=(x_2tdy_2,x_2\partial_t-t\partial_{x_2})$ is not in the image of $R$.\pause 
-	\end{itemize}
-\end{exampleblock}
-{\bf Reason for non-surjectivity:} From the perspective of $M_r$ it does not make sense to require $d\alpha=-\iota_v\omega$ on all of $M$.\pause \\
-{\bf Remark:} We can easily construct examples where $\omega_r$ degenerates.
-\end{frame}
-
-\begin{frame}{Derivations of constraint algebras}
-	$\mathcal A=(\mathcal A_T,\mathcal A_N,\mathcal A_0)=(C^\infty(M),C^\infty(M), I_S)$\\~
-\begin{itemize} 
-	\item $\Der(\mathcal A)_T:=\Der(\mathcal A)_T$ corresponds to all vector fields\pause
-	\item  $\Der(\mathcal A)_N:=\{v\in \Der(\mathcal A)~|~v(\mathcal A_N)\subset \mathcal A_N, ~v(\mathcal A_0)\subset \mathcal A_0\}$\\
-	corresponds to vector fields ({\color{red}algebraically}) tangent to $S$.\\ \pause
-
-	\item  $\Der(\mathcal A)_0:=\{v\in \Der(\mathcal A)~|~v(\mathcal A_N)\subset \mathcal A_0\}$\\
-	are vector fields vanishing on $S$.\pause
-		\begin{block}{Lemma: Algebraic vanishing = geometric vanishing}
-		$\Der(\mathcal A)_0=\{v ~| ~v|_S=0\}=I_S\cdot \mathfrak X(M)$.
-	\end{block}\pause
-\end{itemize}	
-\end{frame}
-
-\begin{frame}
-	$\mathcal A=(C^\infty(M),C^\infty(M), I_S)$\\
-	$\Der(\mathcal A)=(\mathfrak X(M),~~\{v| v(I_S)\subset I_S\},~~ I_S\mathfrak X(M))$
-		\begin{block}{Lemma: $\mathfrak L:=\Der(\mathcal A)$ is a constraint Lie-Rinehart algebra over $\mathcal A$}
-			This means 
-	\begin{itemize} 
-		\item $\mathfrak L_T$ is a Lie Rinehart algebra over $\mathcal A_T$.
-		\item $\mathfrak L$ is a strong constraint module over $\mathcal A$, i.e.\\ $\mathcal A_N\mathfrak L_N\subset \mathfrak L_N$ and $\mathcal A_0\mathfrak L_T+\mathcal A_T\mathfrak L_0\subset \mathfrak L_0$.
-		\item $[\mathfrak L_N,\mathfrak L_N]\subset \mathfrak L_N$ and  $[\mathfrak L_N,\mathfrak L_0]\subset \mathfrak L_0$
-	\end{itemize}
-
-\end{block}\pause
-
-\begin{exampleblock}{Corollary: $(\Lambda \mathfrak L)^*$ has a constraint Cartan calculus $d, \iota, L$}
-	\begin{itemize} 
-	\item $(\Lambda^k \mathfrak L)^*_T=\Omega^k(M)$
-	\item $(\Lambda^k \mathfrak L)^*_N=\{\alpha~|~\alpha(v_1,...,v_k)\in \mathcal A_N~\forall v_i\in \mathfrak L_N , $ \\ ~~~~~~~~~~~~~~~~~~~~$ \alpha(v_1,...,v_{k-1},w)\in \mathcal A_0~\forall v_i\in \mathfrak L_N , w\in \mathfrak L_0 \}$
-	\item $(\Lambda^k \mathfrak L)^*_0=\{\alpha~|~\alpha(v_1,...,v_k)\in \mathcal A_0~\forall v_i\in \mathfrak L_N\}$
-	\end{itemize}
-
-\end{exampleblock}
-
-\end{frame}
-
-\subsection{Introducing symmetry}
-\begin{frame}
-Let $F\subset \Der(\mathcal A)_N$ a Lie subalgebra  (typically $F=\underline{\mathfrak g}$). Consider:
-\begin{itemize} 
-	\item the constraint algebra $\mathcal B= (C^\infty(M),~~~~ \{f~|~F(f)\subset I_S\},~~~ I_S)$\pause
-	\item the constraint Lie-Rinehart algebra $\mathcal L$  \[ (\mathfrak X(M),~~~~\{v ~|~ [v,F]\subset C^\infty(M)F+I_S\mathfrak X(M)\}, ~~~~ C^\infty(M)F+I_S\mathfrak X(M) )\]
-	\item \pause the constaint differential forms 
-	\[
-	\mathcal W=(\Omega(M),~~~, \{\alpha |\iota_\xi\alpha,L_\xi\alpha\in (\Lambda \mathfrak L)^*_0 ~~\forall \xi\in F \},~~~~(\Lambda \mathfrak L)^*_0  )
-	\]
-	where $(\Lambda^k \mathfrak L)^*_0=\{\alpha~|~\alpha(v_1,...,v_k)\in \mathcal A_0~\forall v_i\in \mathfrak L_N\}$
-\end{itemize}
-\begin{block}{'Lemma': $\mathcal L$ has a Cartan calculus on $\mathcal W$}
-	In particular, from the premultisymplectic form $\omega$ we obtain a constraint $L_{\infty}$-algebra.
-\end{block}
-\end{frame}
-
 %------------------------------------------------------------------------------------------------

### 2025-10-21 bv-triples-main.tex
Slides Tor Vergata - First Draft

%+----------------------------------------------------------+
%| SLIDES: Construction and Reduction of the L-infinity Algebra of Observables
%|         Associated with a BV-Module
%| Contents: - 60 minutes (estimated duration ~2.5 minutes per slide, ~24 slides)
%|
%| Author: Antonio Miti
%| Event: ARTS — Algebra and Representation Theory Seminar
%| Place: Università di Roma  "Tor Vergata "
%| Date: 21/10/2025
%| Link: https://www.mat.uniroma2.it/~ricerca/algebr/page-AREA_files/page-AREA-2_files/talks.html
%+----------------------------------------------------------+

%- HandOut Flag -----------------------------------------------------------------------------------------
	\newif\ifHandout
	\Handouttrue  %uncomment for the printable version
	%Handling of flags it is not preserved when passing to standalone-subfiles!

%- D0cum3nt ----------------------------------------------------------------------------------------------
\ifHandout
	\documentclass[handout,10pt]{beamer}   
	\setbeameroption{show notes} %print notes   
\else
	\documentclass[10pt]{beamer}
\fi

%- Packages ----------------------------------------------------------------------------------------------
\usepackage{custom-style}
\usepackage{math}

%- Bibliography (Biber) ----------------------------------------------------------------------------------
\usepackage[backend=biber,style=alphabetic,maxnames=2]{biblatex}
\bibliography{bibfile.bib}

%- L30's ----------------------------------------------------------------------------------------------
\usepackage{quiver} %https://q.uiver.app/ % Not in Miktex!
\usetikzlibrary{nfold}
\usetikzlibrary{decorations.pathmorphing} 
\renewcommand{\Ham}{\mathrm{Ham}}
\newcommand{\Der}{\mathrm{Der}}
\usepackage{enumitem}
\setlist{topsep=0pt, leftmargin=*,label=$\bullet$}

%--Beamer Style-----------------------------------------------------------------------------------------------
\usetheme{toninus}

\usetikzlibrary{backgrounds}
  \tikzset{
    invisible/.style={opacity=0},
    visible on/.style={alt=#1{}{invisible}},
    alt/.code args={<#1>#2#3}{%
      \alt<#1>{\pgfkeysalso{#2}}{\pgfkeysalso{#3}} % \pgfkeysalso doesn't change the path
    },
  }

%- T1tle P4g3 -------------------------------------------------------------------------------------------
\title{Construction and Reduction of the $L_\infty$ Algebra of Observables Associated with a BV-Module} 
\subtitle{\href{https://www.mat.uniroma2.it/~ricerca/algebr/page-AREA_files/page-AREA-2_files/talks.html}{- ARTS - Algebra and Representation Theory Seminar in Roma "Tor Vergata"}}
\author[AMM]{
	\href{https://www.antoniomiti.it/}{Antonio Michele Miti}
	{\small joint work w/ Leonid Ryvkin}
}
\institute[SUR]{
	Sapienza Università di Roma \\
	Rome, Italy 	\\
	\vspace{.5em}
  \begin{tabular}[h]{ccc}
      \href{https://www.mat.uniroma1.it/en}{\includegraphics[width=6cm]{./Logos/Sur_logo}} & & 
      \href{https://civis3i.univ-amu.fr/en/civis3i-alliance-programme}{\includegraphics[width=3cm]{Logos/Civis_logo}}
  \end{tabular}    
}
\date[TorV25] % (optional, should be abbreviation of conference name)
{	
	{\vskip 1ex}
	Universit\'a di Roma - Tor Vergata, October 2025
}

%+----------------------------------------------------------+
%- D0cum3nt ------------------------------------------------+
%+----------------------------------------------------------+
\begin{document}
%+----------------------------------------------------------+

\begin{frame}
  \titlepage
\end{frame}

%+----------------------------------------------------------+
% S3cti0n: Intr0ducti0n ------------------------------------+
\section{Introduction}
%+----------------------------------------------------------+
%

\begin{frame}{Symplectic Geometry}
\begin{itemize}
  \item Symplectic manifold: $(M,\omega)$ with $\omega$ closed, nondegenerate 2-form.
  \item Observables: $C^\infty(M)$ with Poisson bracket $\{f,g\} = \omega(X_f, X_g)$.
  \item $X_f$ is the Hamiltonian vector field: $\iota_{X_f} \omega = df$.
\end{itemize}
\end{frame}
\note{Symplectic vs. Multisymplectic Geometry: In symplectic geometry, a closed nondegenerate 2-form $\omega$ on a manifold $M$ gives rise to a Poisson algebra of observables (smooth functions with the Poisson bracket) . In contrast, multisymplectic manifolds carry a closed nondegenerate form of degree $>2$ (often called an $n$-plectic form if its degree is $n+1$). These higher-degree forms naturally lead not to a Poisson Lie algebra, but to a higher (homotopy) Lie algebra structure on observables. In fact, as shown by Rogers, an $n$-plectic manifold yields an $n$-term $L_\infty$-algebra of observables (sometimes called a higher Poisson algebra) .org. This generalizes the Poisson bracket: for example, a 3-plectic form (degree 3) gives a Lie 2-algebra of observables, etc., with higher multi-brackets capturing the failure of the Jacobi identity up to homotopy.

Symplectic Case: If $(M,\omega)$ is a symplectic manifold (closed nondegenerate 2-form), every smooth function $f\in C^\infty(M)$ has an associated Hamiltonian vector field $X_f$ defined by $i_{X_f}\omega = d f$. The space of observables $C^\infty(M)$ forms a Poisson algebra with the Poisson bracket ${f,g} = \omega(X_f, X_g)$. This is just a Lie algebra (indeed a Lie derivation algebra on $C^\infty(M)$) satisfying the Jacobi identity strictly.

}

\begin{frame}{From Symplectic to Multisymplectic}
\begin{itemize}
  \item $k$-plectic manifold: $(M,\omega)$ with closed, nondegenerate $(k+1)$-form.
  \item Hamiltonian $(k-1)$-form $\alpha$: $\iota_X \omega = d\alpha$.
  \item Rogers (2010): observables form an $L_\infty$-algebra.
\end{itemize}
\end{frame}
\note{- **Multisymplectic (Higher-Degree) Forms:** Now let $(M,\omega)$ be a **$k$-plectic manifold**, i.e. $\omega$ is a closed, nondegenerate $(k+1)$-form (for example, a 3-form if $k=2$). The notion of *Hamiltonian observables* generalizes: a **Hamiltonian $(k-1)$-form** $\alpha \in \Omega^{k-1}(M)$ is one that admits a vector field $X$ (a *Hamiltonian field*) satisfying $i_X\omega = d\alpha$. We call the pair $(X,\alpha)$ a *Hamiltonian pair*. Just as in the symplectic case $(k=1)$ where $\alpha$ is a 0-form (function) and $X$ its Hamiltonian vector field, here $\alpha$ plays the role of the observable (often called an $(k-1)$-form observable). The collection of all such Hamiltonian forms (for various degrees) can be organized into a graded object, and Rogers showed that it carries a canonical **$L_\infty$-algebra structure** .
    - **Example:** For a 3-plectic manifold (degree 3 form $\omega$), one has Hamiltonian 1-forms: each 1-form $\alpha$ for which there exists $X$ with $i_X\omega = d\alpha$. These Hamiltonian pairs $(X,\alpha)$ form the degree-0 part of the observables. In addition, ordinary functions (0-forms) can be viewed as Hamiltonian 0-forms (with $X$ such that $i_X\omega = d(0) = 0$), and perhaps higher-degree observables appear up to degree 1 in this case. The resulting $L_\infty$ has non-trivial brackets of arity up to 2 (making it a *Lie 2-algebra* of observables, a kind of higher Poisson algebra). The 2-bracket extends the Poisson bracket, and a 3-bracket arises measuring the failure of the Jacobi identity (something that vanishes in the symplectic case but not in general). For a 4-plectic form, one would get a Lie 3-algebra, etc.}

\begin{frame}{$L_\infty$ Algebra of Observables}
\begin{itemize}
  \item Observables organized as graded vector space: Hamiltonian forms + multi-brackets.
  \item Higher brackets from Cartan calculus: $d$, $\iota_X$, $L_X$.
  \item No manifold needed if we have the algebraic structure.
\end{itemize}
\end{frame}
\note{Rogers’ Construction (2010/2012): The remarkable insight of Rogers  was that the construction of this observables $L_\infty$-algebra is essentially algebraic, relying only on the standard Cartan calculus identities for differential forms and vector fields. In other words, Rogers’ $L_\infty$ brackets can be derived from the algebraic relations between the exterior derivative $d$, the interior product $i_X$, and the Lie derivative $L_X$ on forms . This suggests we can abstract and generalize the construction beyond the category of manifolds. The goal is to build an $L_\infty$-algebra of observables in a purely algebraic setting, provided we have an analog of  "forms " and  "vector fields " satisfying the Cartan relations .}

\begin{frame}{Reminder: What’s an $L_\infty$ Algebra?}
\begin{itemize}
  \item Graded vector space $V = \bigoplus V^i$.
  \item Maps $\ell_k: V^{\otimes k} \to V$ of degree $2 - k$.
  \item Satisfying higher Jacobi identities (homotopy Lie algebra).
\end{itemize}
\end{frame}
\note{- **Higher Brackets via Cartan Calculus:** The construction of the $L_\infty$ brackets can be understood conceptually in terms of the **Cartan calculus identities**. Recall that on a manifold, we have for any vector fields $X,Y$ and differential forms $\alpha$:
    - $L_X = [d, i_X]$ (Cartan’s identity relating Lie derivative and interior contraction), and
    - $[L_X, i_Y] = i_{[X,Y]}$ (compatibility of Lie derivative with contraction),
    - $[L_X,L_Y] = L_{[X,Y]}$, etc.

        These identities ensure that the operations $d, i_X, L_X$ behave in a coordinated way (the essence of *Gerstenhaber algebra and BV-module* structure, as we formalize below). Rogers’ $L_\infty$ brackets are built using these ingredients: e.g., the binary bracket of two Hamiltonian forms $(X,\alpha)$ and $(Y,\beta)$ can be defined as $( [X,Y],; L_X\beta)$ (or plus cyclic terms), and higher brackets involve expressions with $i_{X_i} i_{X_j}\omega$ contracted with another argument, etc., ensuring the homotopy Jacobi identities hold . The key point is that all such formulas **only use the algebraic operations $d,i,L,[\cdot,\cdot]$ and the form $\omega$**. This algebraic nature allows generalization to any context where similar operators exist.

- **Limitations of Classical Reduction:** Before moving to the algebraic setup, note that reducing multisymplectic systems geometrically (analogue of Marsden-Weinstein reduction) can be challenging. Classical symplectic reduction requires a Lie group action that is free and proper and a regular value of the moment map; these conditions often fail (especially in field theory or higher form cases). Recent work has approached reduction **algebraically** by focusing on the algebra of observables (functions/forms) with constraints, rather than the quotient of manifolds. This algebraic approach, implemented for multisymplectic manifolds in Blacker-Miti-Ryvkin 2024, allows handling singular cases (non-free actions, etc.) by *encoding constraints and symmetries at the algebraic level.
Our work builds on this idea using *constraint triples*.}

\begin{frame}{Scope/Idea of the Talk}
\begin{itemize}
  \item Generalize Rogers' construction to a purely algebraic setting.
  \item Use Gerstenhaber algebras and BV-modules.
  \item Handle reduction via constraint triples.
  \item Apply to recover and extend results on multisymplectic reduction.
\end{itemize}
\end{frame}
\note{Our Aim: In this talk, we present such a fully algebraic formalism for constructing and reducing $L_\infty$-algebras of observables, inspired by multisymplectic geometryarxiv.org. We work in the framework of Gerstenhaber algebras and Batalin-Vilkovisky modules (BV-modules), which encapsulate the algebraic structure of Cartan calculus (including both commutative and non-commutative cases). Given any Gerstenhaber algebra $G$ together with a BV-module $M$ and a chosen closed element (a  "cocycle ") $c$ in $M$, we will show how to construct an associated $L_\infty$-algebra of observables without reference to any underlying manifold . This is our Theorem A. Moreover, we will address how to perform reduction of these observables $L_\infty$-algebras in the presence of constraints or symmetries. For this, we employ the notion of constraint triples (introduced by Dippel-Esposito-Waldmann 2019marvindippell.de) as an algebraic framework for coisotropic reduction. Adapting this to our BV-module setting, we obtain a general procedure to reduce an $L_\infty$ of observables, even in singular scenarios where classical quotient constructions fail  . This corresponds to Theorem C in our work. In particular, our approach reproduces the multisymplectic reduction results of Blacker-Miti-Ryvkin (SIGMA 2024) in a more conceptual way and clarifies the role of the so-called  "residue defect " that appears in the reduction process .}

%+----------------------------------------------------------+
%Overview: Roughly the first half of the talk will be introductory. We will recall the necessary background on multisymplectic observables and momentum maps, then introduce the algebraic structures (Gerstenhaber algebras and BV-modules) that replicate Cartan calculus. In the second half, we outline the construction of the observables $L_\infty$-algebra in the algebraic setting (Theorem A), and then discuss how to incorporate constraints via constraint triples, leading to a reduced $L_\infty$-algebra of observables (Theorem C).

%+----------------------------------------------------------+
%Section: BV-Modules ----------------------------------+
\section{BV-Modules: Algebraic Cartan Calculus}
%+----------------------------------------------------------+
%

\begin{frame}{Lie-Rinehart Algebras}
\begin{itemize}
  \item Pair $(A,E)$: $A$ a commutative algebra, $E$ an $A$-module and Lie algebra.
  \item Anchor map: $\rho: E \to \mathrm{Der}(A)$.
  \item Encodes derivations + Lie algebra structure.
\end{itemize}
\end{frame}
\note{To generalize the above geometric structures, we introduce the algebraic counterparts of  "multivector fields " and  "differential forms with Cartan calculus. " All vector spaces are over a field of characteristic 0 (e.g. $\mathbb{R}$). We work in graded settings since forms and multivectors are naturally graded.

- **Lie-Rinehart Algebras:** A *Lie-Rinehart algebra* $(A,E)$ consists of a commutative associative algebra $A$ (think of $A=C^\infty(M)$) and an $A$-module $E$ (think of $E=\mathfrak X(M)$, the vector fields) which is also a Lie algebra, together with an *anchor* map $\rho: E \to \mathop{\mathrm{Der}}(A)$ (derivations of $A$) satisfying a Leibniz rule: $[X, aY] = a[X,Y] + (\rho(X)a),Y$. This abstractly encodes the notion of derivations of $A$ with an $A$-linear Lie bracket. **Example:** If $A=C^\infty(M)$, then $E=\Gamma(TM)$ (the module of vector fields) with the identity anchor $\rho(X)=X$ is a Lie-Rinehart algebra. In fact, Lie-Rinehart algebras are algebraic analogues of Lie algebroids (and every Lie algebroid gives a Lie-Rinehart algebra).}

\begin{frame}{Gerstenhaber Algebras}
\begin{itemize}
  \item Graded commutative algebra $(\mathcal{G}, \wedge)$.
  \item Lie bracket $[\cdot,\cdot]$ of degree $-1$.
  \item Compatibility (Leibniz rule): $[x, y\wedge z] = [x,y]\wedge z + (-1)^{(\deg x -1)\deg y} y\wedge [x,z]$.
\end{itemize}
\end{frame}
\note{- **Gerstenhaber Algebras:** A *Gerstenhaber algebra* is a graded algebra that captures the structure of *exterior algebra of multivector fields*. Formally, it is a triple $(\mathcal{G}, \wedge, [\cdot,\cdot])$ where:
    - $\mathcal{G} = \bigoplus_{i\in\mathbb{Z}} \mathcal{G}^i$ is a $\mathbb{Z}$-graded vector space.
    - $\wedge: \mathcal{G}^p \times \mathcal{G}^q \to \mathcal{G}^{p+q}$ is a graded-commutative, associative product (degree $0$ operation).
    - $[\cdot,\cdot]: \mathcal{G}^p \times \mathcal{G}^q \to \mathcal{G}^{p+q-1}$ is a bracket of degree $-1$, making $\mathcal{G}$ into a graded Lie algebra.
    - **Compatibility (Leibniz rule):** The bracket is a derivation of the product: $[x, y\wedge z] = [x,y]\wedge z + (-1)^{(deg,x -1),deg,y} ,y\wedge [x,z]$ for homogeneous $x,y,z$. This is the defining Gerstenhaber identity, generalizing the fact that the Lie bracket of vector fields satisfies a Leibniz rule with respect to wedge of forms or functions.

    **Example:** If $(A,E)$ is a Lie-Rinehart algebra, the **exterior algebra** of $E$ (with a degree shift) carries a natural Gerstenhaber structure. In particular, take $\mathcal{G} = \Lambda^\bullet E$ (the exterior *wedge* algebra of $E$ treated as a graded space of multivectors). The wedge product is the usual wedge of multivectors, and the bracket is the **Schouten-Nijenhuis bracket** extending the Lie bracket on $E$ to all multivectors. This $(\Lambda E,\wedge,[\cdot,\cdot]_{SN})$ is a Gerstenhaber algebra, prototypical in geometry (for $E=\mathfrak X(M)$ one recovers the standard Gerstenhaber algebra of multivector fields on $M$).}

\begin{frame}{Gerstenhaber Modules}
\begin{itemize}
  \item $G$-module $M$ with contraction $\iota_X$ of degree $-\deg X$.
  \item Induced Lie derivative $L_X = [d,\iota_X]$ when $d$ is defined.
\end{itemize}
\end{frame}
\note{Gerstenhaber Module: Given a Gerstenhaber algebra $G$, a Gerstenhaber $G$-module is a graded module $M = \bigoplus M^i$ equipped with an action of $G$ that extends the idea of a multivector acting on forms by contraction. Concretely, for each element $X\in G^p$, we have a degree $-p$ operator $i_X: M^\ast \to M^{\ast-p}$ (interpreted as interior product by $X$) satisfying a compatible set of identities (graded derivations, etc.)ar5iv.labs.arxiv.org. We also typically get an induced Lie derivative action $L_X$ of degree 0 defined by $L_X := [D,;i_X]$ once a differential $D$ is present (see below). We won’t detail the full set of axioms here, but essentially a Gerstenhaber module gives an algebraic version of the pair of operations $(i_X, L_X)$ acting on a  "forms " module, with $i$ being antiderivations and $L$ Lie derivations. (The literature sometimes refers to this structure as a  "TTN (Tsygan-Tamarkin-Nest) calculus " .)}

\begin{frame}{BV-Modules}
\begin{itemize}
  \item A Gerstenhaber module $M$ with differential $d$.
  \item Cartan identity: $L_X = [d,\iota_X]$.
  \item Encodes full algebraic Cartan calculus.
\end{itemize}
\end{frame}
\note{Batalin-Vilkovisky Modules (BV-Modules): A BV-module is a Gerstenhaber module that is also equipped with a differential of degree $+1$ (like an exterior derivative) satisfying Cartan’s formula. Formally, let $G$ be a Gerstenhaber algebra and $(M,d)$ a cochain complex (so $d: M^i \to M^{i+1}$ with $d^2=0$). We say $M$ is a BV-module over $G$ if $M$ is a Gerstenhaber $G$-module and, for all $X\in G$, we have the Cartan identity $L_X = [d,; i_X]$ (and automatically $[L_X, i_Y] = i_{[X,Y]}$, etc.)  . In other words, $M$ carries an action of $G$ by contraction $i_X$ and Lie derivative $L_X$ such that together with the differential $d$ they satisfy the standard graded commutation relations of Cartan calculus. We often call $d$ the BV differential.}

\begin{frame}{Abstract Cartan Calculus}
\begin{itemize}
  \item $(G,M,d)$ with $G$ Gerstenhaber, $M$ BV-module, $d^2=0$.
  \item Examples: $(\mathfrak{X}^\bullet(M),\Omega^\bullet(M), d)$.
  \item Extends to noncommutative and algebraic settings.
\end{itemize}
\end{frame}
\note{Example (Classical Cartan Calculus): Take $G = \Lambda^\bullet \mathfrak X(M)$ (Gerstenhaber algebra of multivector fields on a manifold) and $M=\Omega^\bullet(M)$ (the de Rham complex of differential forms). This is a canonical example of a BV-module  : the differential $d$ is the exterior derivative, the contraction $i_X$ is the usual insertion of a multivector $X$ into a form, and the Lie derivative $L_X$ is the usual one acting on forms. These satisfy $L_X = d \circ i_X + i_X \circ d$ (Cartan formula) and all other Cartan identities. In fact, this example exactly recovers the classical Cartan calculus on $M$ as a BV-module structure on $\Omega^\bullet(M)$, with $G$ playing the role of  "polyvector fields " . This justifies the abstractions: any Gerstenhaber algebra + BV-module pair can be seen as a generalized  "space of multivectors and forms " with a full Cartan calculus available . We emphasize that such structures exist in much more general settings, including noncommutative geometry (where $A$ is a noncommutative algebra and one considers analogues of forms and multivectors  ), but for our purposes we stick to the algebraic axioms.}

%+----------------------------------------------------------+
%Section: L-infinity Algebra Associated with a BV-Module ---+
%
\section{$L_\infty$ Algebra Associated with a BV-Module}
%+----------------------------------------------------------+
%

\begin{frame}{Hamiltonian Pairs}
\begin{itemize}
  \item Data: $G$, $M$ BV-module, $c \in M$ closed.
  \item Pair $(X,m)$ with $\iota_X c = d m$.
  \item Generalizes $(X_f, f)$ in symplectic geometry.
\end{itemize}
\end{frame}
\note{Given an algebraic Cartan calculus as above, we can now construct the $L_\infty$-algebra of observables in complete generality. The construction mirrors the one Rogers gave on manifolds, but now in purely algebraic terms.

- **Data:** Let $G$ be a Gerstenhaber algebra, $M$ a BV-module over $G$ with differential $d$, and let $c \in M^k$ be a fixed *cocycle*, meaning $d c = 0$. 
Think of $c$ as the algebraic analog of a closed multisymplectic form (indeed in geometry $c$ could be $\omega$, which is closed by assumption). We also assume $c$ is *nondegenerate* in the sense that it induces the relevant pairings (this is automatic in the geometric case and can be treated as a cocycle condition in the algebraic case; for simplicity, we proceed assuming $c$ behaves like a  "volume form " or  "top form " to contract with).
- **Hamiltonian Pairs:** We define a **Hamiltonian pair** as a pair $(X, m)$ with $X \in G$ (a multivector) and $m \in M$ (an element of the module) such that $X$ and $m$ are related by the cocycle $c$ via:

    $i_X(c) = d m$.

    In other words, $m$ is an element whose BV-differential equals the contraction of $c$ with $X$. This is directly analogous to the condition $i_{X_f}\omega = d f$ in the geometric case (here $X$ plays the role of $X_f$ and $m$ plays the role of the observable like $f$ or $\alpha$). We denote by $\mathsf{Ham}(G,M;c)$ the set of all Hamiltonian pairs. In graded terms, one typically considers homogeneous $X$ and $m$ of complementary degrees summing to $k-1$ (so that $i_X c$ has the same degree as $d m$).

    **Intuition:** A Hamiltonian pair $(X,m)$ means that $m$ is an *observable* whose  "derived bracket " with the cocycle $c$ yields $X$. If $c$ is nondegenerate, $X$ is uniquely determined by $m$ (just as a symplectic form gives a unique $X_f$ for each $f$), so we can think of $m$ as the *observable element* and $X$ as its *Hamiltonian generator*. However, in singular or degenerate cases, there could be multiple $X$ for a given $m$ or vice versa, hence it is safer to keep the pair. (In the construction we actually consider an appropriate quotient to identify pairs that give the same physical observable; more formally $\mathsf{Ham}(G,M;c)$ can be constructed as a fiber product $G \times_{M} M$ via the maps $X \mapsto i_X c$ and $m \mapsto d m$ .)}

\begin{frame}{The Space and the Multibrackets}
\begin{itemize}
  \item Graded space $\mathcal{O}(G,M;c)$.
  \item Brackets $\ell_k$ built from $d$, $\iota_X$, $L_X$, $[\cdot,\cdot]$.
  \item $\ell_1 = d$, $\ell_2 = $ Lie + derived terms, $\ell_3 = i_{X_1}i_{X_2}i_{X_3}(c)$.
\end{itemize}
\end{frame}
\note{- \textbf{Graded observables space:} We assemble the observables into a graded vector space as follows.

\[
\mathcal{O}(G,M;c)\;=\;\bigoplus_{j\ge 0}\mathcal{O}^j,
\]

where:

- $\mathcal{O}^0$ (degree~0 part) is the space of Hamiltonian pairs $(X,m)$ as above (with $i_X c = d m$).
- For higher degrees $j>0$, roughly speaking $\mathcal{O}^j$ consists of elements of $M$ of degree $(k-1+j)$ (or related shifts) corresponding to forms of lower degree than $c$. In fact, in Rogers' original construction for an $n$-plectic manifold, the $L_\infty$-algebra of observables was an $n$-term complex concentrated in degrees $0,1,\dots,n-1$. Here $k=n+1$ (degree of $c$), so one can show $\mathcal{O}(G,M;c)$ is concentrated in degrees $0$ up to $n-1$ (i.e. $0$ up to $k-2$). Degree~0 are Hamiltonian $(n-1)$-forms (with vector fields), degree~1 would be Hamiltonian $(n-2)$-forms, ..., up to degree $n-1$ corresponding to Hamiltonian $0$-forms (basic observables). We will not need the explicit formula for each degree in this talk; the key is that this graded space includes all would-be observables and their "Hamiltonian partners."}

\begin{frame}{Examples}
\begin{itemize}
  \item Classical: $G=\mathfrak{X}^\bullet(M)$, $M=\Omega^\bullet(M)$, $c=\omega$.
  \item Recovers Rogers’ multisymplectic $L_\infty$.
  \item Other contexts: algebraic, noncommutative, etc.
\end{itemize}
\end{frame}
\note{- **$L_{\infty}$-Algebra Structure:** **Theorem A** (Miti-Ryvkin 2025) states that under the above setup, $\mathcal{O}(G,M;c)$ carries a natural structure of an $L_\infty$-algebra (homotopy Lie algebra) whose brackets are defined using the data of the Gerstenhaber algebra $G$, the BV-module operations, and the cocycle $c$ . Concretely, the multilinear $L_\infty$ operations $\ell_r: \mathcal{O}^{\otimes r} \to \mathcal{O}$ (of degree $2-r$) are given by formulas analogous to those in the multisymplectic manifold case :
    - The unary bracket $\ell_1$ (degree $+1$ map) is essentially induced by the BV differential $d$ on the observable part (it maps a degree~1 element to degree~0 by $\ell_1(m) = (X,d m)$ or something similar, and is zero on degree~0 pairs in the fully nondegenerate case).
    - The binary bracket $\ell_2((X_1,m_1), (X_2,m_2))$ has a result in degree~0 and is given by

        \[
        \ell_2((X_1,m_1),(X_2,m_2)) \;=\; \big([X_1,X_2],\; L_{X_1}m_2 * (-1)^{|X_1|\cdot|X_2|}L_{X_2}m_1\big),
        \]

        which in the simplest case recovers the Poisson bracket structure (when $m$’s are functions, $L_{X_1}m_2 = X_1(m_2)$). The precise formula involves appropriate Koszul signs for graded elements .

    - A tertiary bracket $\ell_3((X_1,m_1),(X_2,m_2),(X_3,m_3))$ can be defined using the cocycle $c$: essentially one can take $i_{X_1}i_{X_2}i_{X_3}(c)$ (which is an element of $M$) as part of the output (this corresponds to evaluating the 3-form on three vector fields to get a number or top-form), ensuring that the Jacobi identity holds up to homotopy.
    - Higher brackets $\ell_r$ for $r>3$ may be zero or determined similarly by $c$ if its degree is larger. In fact, for an $(n+1)$-form $c$, all brackets $\ell_r$ with $r> n$ will vanish (so the $L_\infty$ is  "finite " or $n$-term) .

    The upshot is that **all these brackets are built out of the operations $[\cdot,\cdot]$ in $G$, $i_X$, $L_X$, $d$, and contraction with $c$**, mimicking the standard formulas in coordinates. It is nontrivial but true that these operations satisfy the required homotopy Jacobi identities. The verification is essentially a translation of Rogers’ original proof to this abstract setting - since Rogers’ proof was  "purely algebraic in nature, " it adapts directly here . We have thus constructed an **$L_\infty$-algebra of observables** $\mathcal{O}(G,M;c)$ associated to any BV-module with a cocycle. This is the main result of the first part of the talk.

    Example (Geometric Case): If we take $G = \Lambda^\bullet \mathfrak X(M)$, $M = \Omega^\bullet(M)$ (so classical Cartan calculus on a manifold), and $c = \omega$ an $n$-plectic form, then $\mathcal{O}(G,M;c)$ precisely recovers Rogers’ $L_\infty$-algebra of observables on $(M,\omega)$  . In degree 0, $\mathcal{O}^0$ consists of Hamiltonian $(n!-!1)$-forms (with their Hamiltonian vector fields), which are exactly Rogers’ observables. The brackets $\ell_r$ coincide with those defined by Rogers (up to sign conventions), and one can check the $L_\infty$ identities by the same calculations in Cartan calculus . This generality shows the power of the BV-module approach: any example of a Gerstenhaber algebra + cocycle yields such an $L_\infty$. For instance, one could even take noncommutative analogues (with a suitable cyclic cocycle playing the role of $c$) to get  "$L_\infty$-observables " in noncommutative geometry  , although we won’t explore that in this talk.}

%+----------------------------------------------------------+
%S3cti0n: An Applicati0n: Multisymplectic Reducti0n -------+
%
\section{An Application: Multisymplectic Reduction}
%+----------------------------------------------------------+
%

\begin{frame}{Constraint Triples}
\begin{itemize}
  \item Triple $(A, A_C, \overline{A})$ with inclusion/projection.
  \item $A_C$ encodes constraints, $\overline{A} = A/I$ reduced algebra.
  \item Adapted to Gerstenhaber and BV-module settings.
\end{itemize}
\end{frame}

\begin{frame}{Constraint BV-Modules}
\begin{itemize}
  \item Triples $(G, G_C, \overline{G})$, $(M, M_C, \overline{M})$.
  \item Structures compatible with Cartan calculus.
  \item Closed cocycle triple $c = (c, c_C, \overline{c})$.
\end{itemize}
\end{frame}

\begin{frame}{Constraint $L_\infty$ Algebra Associated with…}
\begin{itemize}
  \item Construct observables $\mathcal{O} = (\mathcal{O}, \mathcal{O}_C, \overline{\mathcal{O}})$.
  \item Each component carries an $L_\infty$ structure.
  \item Brackets compatible with inclusions/projections.
\end{itemize}
\end{frame}

\begin{frame}{Reduction Functor}
\begin{itemize}
  \item Quotient part $\overline{\mathcal{O}}$ inherits $L_\infty$ structure.
  \item Encodes reduced observables algebra.
  \item No need for regular quotient at geometric level.
\end{itemize}
\end{frame}

\begin{frame}{Recovering Old Results}
\begin{itemize}
  \item Applies to multisymplectic reduction (Blacker-Miti-Ryvkin 2024).
  \item Explains residue defect in homotopy Jacobi identity.
  \item Matches geometric reduction under regularity.
\end{itemize}
\end{frame}

\begin{frame}{Conclusion / Summary}
\begin{itemize}
  \item Algebraic formalism for $L_\infty$ observables via BV-modules.
  \item Generalizes Rogers' result.
  \item Enables reduction via constraint triples.
\end{itemize}
\end{frame}

\begin{frame}{Outlook}
\begin{itemize}
  \item Homotopy momentum maps.
  \item Operadic reformulation.
  \item Applications to field theory.
\end{itemize}
\end{frame}

%+----------------------------------------------------------+
\end{document}
%+----------------------------------------------------------+

We now turn to the second main part: **reduction** of the $L_\infty$-algebra of observables in the presence of constraints or symmetries. In symplectic geometry, reduction is accomplished by the Marsden-Weinstein quotient: one restricts to the zero level set of a momentum map and then quotients by the symmetry group. Algebraically, this corresponds to first imposing ideal relations (for the constraints) and then modding out by gauge symmetries. The **constraint triple** formalism packages these two steps (subobject and quotient) in a single algebraic structure .

- **Constraint Triples:** A **constraint triple** (or **coisotropic triple**) in general consists of:
    1. An algebra (or other structure) $A$ representing the full system’s observables.
    2. A subalgebra $C \subset A$ representing the *constraints* (for example, functions vanishing on a certain submanifold, or first-class constraint algebra in Dirac’s theory).
    3. A quotient (factor) algebra $\overline{A} = A/ I$ for some ideal $I$ related to $C$, representing the *reduced* algebra of observables after constraints are imposed and quotiented.

    These are equipped with structure maps (inclusions and projections) satisfying compatibility conditions (e.g. $I$ is the ideal of relations defining $C$) . Intuitively, one has $C$ as the "constraint algebra" (functions that vanish on the constraint surface) and $\overline{A}$ as the algebra of functions on the quotient of that constraint surface by symmetries. Dippel, Esposito & Waldmann formalized this in the context of Poisson algebras and deformation quantization , showing that many reduction procedures can be understood as functors on such triples.

    We adopt this idea in our setting: we will consider **constraint Gerstenhaber algebras** and **constraint BV-modules**, which are triples $(G, G_C, \overline{G})$ and $(M, M_C, \overline{M})$ capturing the full, constraint, and reduced parts of our algebraic Cartan calculus . All the structure (brackets, differentials, etc.) is assumed to exist on each part and to be compatible. For instance, a *constraint Gerstenhaber algebra* means $G$ is a Gerstenhaber algebra, $G_C \subset G$ a subalgebra (constraints), and $\overline{G} = G/G_C$ (some quotient) such that the wedge and bracket operations map triples to triples (roughly $[![G, G]!]$ sends $G_C$ to $G_C$ and induces well-defined operations on the quotient) . Similarly, a *constraint BV-module* $(M, M_C, \overline{M})$ has $M_C$ a submodule (the  "constraints on forms ") and $\overline{M}=M/M_C$ the quotient module, with differential $d$ and contractions $i_X$ etc. respecting the triples (so that, e.g., $d(M_C)\subseteq M_C$ and induces a differential on $\overline{M}$) . This is a bit of structure to keep track of, but conceptually it means we have *Cartan calculus not just on one algebra, but simultaneously on a sub- and a quotient algebra*.

    - **Origin in Geometry:** If one has a manifold $M$ with a coisotropic submanifold $C\subset M$ (the constraint surface) and a group $G$ acting with gauge orbits, one can form a *constraint manifold* in the sense of Dippel-Kern 2025 . The algebra of smooth functions on a constraint manifold is exactly a constraint triple $(A, C, \overline{A})$ in which $C$ are the functions vanishing on the constraint surface and $\overline{A}$ functions on the quotient (when nice). Likewise, vector fields tangent to $C$ etc. form a constraint Lie-Rinehart algebra, and so on. Indeed, it has been shown that a **constraint Lie-Rinehart algebra** naturally induces a constraint Gerstenhaber algebra and constraint BV-module structures . So this framework is not lacking examples - it generalizes classical constrained Hamiltonian systems.
- **Constraint $L_\infty$ of Observables:** Once we have constraint versions of $G$ and $M$ **and** a *constraint cocycle* $c = (c, c_C, \overline{c})$ (meaning $c$ lies in $M$, $c_C$ in $M_C$ and $\overline{c}$ is its class in $\overline{M}$, with each closed under their respective differentials), we can perform the same construction as before *in the category of constraint complexes*. That is, we define the **constraint Hamiltonian pairs** as triples $((X, X_C, \overline{X}), (m, m_C, \overline{m}))$ such that $i_X(c) = d m$, $i_{X_C}(c_C) = d m_C$ and these are compatible/projection of the first (so $\overline{X}$ and $\overline{m}$ are the images of $X,m$, etc.) . All such triples form a constraint graded space of observables. **Theorem C** asserts that this constraint observables space carries a **constraint $L_\infty$-algebra** structure . By  "constraint $L_\infty$-algebra, " we mean an $L_\infty$ whose underlying structure is also a triple $(L, L_C, \overline{L})$: there are brackets $\ell_r$ on each of $L, L_C, \overline{L}$, and the inclusion/projection maps intertwine these (so that $L_C$ is an $L_\infty$-subalgebra and $\overline{L}$ the quotient $L_\infty$) . The brackets are defined using the same formulas as in the unconstrained case, applied levelwise to $(G, M, c)$, $(G_C, M_C, c_C)$ and inducing $(\overline{G}, \overline{M}, \overline{c})$ . The $L_\infty$ identities hold simultaneously on each level by the same reasoning as before, thanks to the compatibility of the constraint data.
- **Reduction Functor:** Once we have a constraint $L_\infty$-algebra of observables, *reducing it* means passing to the **quotient part** of the constraint triple. In categorical terms, there is a forgetful functor sending a constraint object $(X, X_C, \overline{X})$ to the quotient $\overline{X}$. When we apply this to the constraint $L_\infty$ of observables, we obtain an $L_\infty$-algebra on $\overline{L}$, which we interpret as the **reduced $L_\infty$-algebra of observables** of the constrained system. Intuitively, this $\overline{L}$ encodes observables that are invariant under the symmetry and defined on the constraint surface (since we mod out those that vanish or differ by constraint terms) . By construction, all the $L_\infty$ brackets descend to $\overline{L}$, so the homotopy Lie structure is well-defined on the quotient. This algebra $\overline{L}$ is the algebraic analog of the Poisson algebra of the reduced phase space in classical reduction, but here it can handle the homotopy brackets arising from a multisymplectic form and even if no nice manifold quotient exists (e.g. in singular cases).
- **Recovery of Known Results:** Our general reduction scheme, when applied to the **geometric case** of a multisymplectic manifold with a group action, reproduces the results of our earlier work (Blacker-Miti-Ryvkin, SIGMA 2024) . In that work, we constructed a reduced $L_\infty$ of observables by more ad-hoc means; now we see it fits into the constraint triple framework. Specifically, given a Lie group $G$ acting on an $n$-plectic manifold $(M,\omega)$ with a covariant momentum map $\mu$ , one can form the constraint triple:
    - $A = $ observables $L_\infty$ on $(M,\omega)$,
    - $A_C = $ those observables that vanish on the constraint (e.g. forms pulled back by $\mu$ setting to zero, etc.),
    - $\overline{A} = $ observables on the reduced space (when $0$ level set mod $G$ is nice, these correspond to forms on the quotient).

    Our formalism shows that $\overline{A}$ inherits an $L_\infty$-algebra structure automatically . No assumptions of regularity or freeness are needed in the algebraic approach - even if the quotient is singular, $\overline{A}$ is well-defined as a homotopy algebra. This extends the multisymplectic reduction of Blacker 2021 (which assumed regularity) to a far more general context . Moreover, within our algebraic setting we identify an object called the **residue defect**, which measures the slight difference between naive and actual reduction in the homotopy context. In the earlier work, this residue term appeared somewhat mysteriously to satisfy the homotopy Jacobi identities; here we can interpret it cleanly as arising from the constraint differential and the failure of a certain exactness on the constraint submodule. Our framework **clarifies the role of the  "residue defect "**: it is an intrinsic part of the constraint $L_\infty$ structure that vanishes under appropriate conditions (like when the momentum map level is regular) .

- **Summary of Main Results:** We can summarize the main technical results (theorems) as follows:
    - **Theorem A:** *Given any Gerstenhaber algebra $G$ with a BV-module $M$ and a closed element $c\in M$, the graded space of Hamiltonian pairs $\mathcal{O}(G,M;c)$ admits an $L_\infty$-algebra structure (observables algebra), defined by the multilinear maps derived from Cartan calculus.* 
    - **Theorem B:** *If $(A,E)$ is a **constraint** Lie-Rinehart algebra (constraint version of derivations over a constraint algebra $A$), then one naturally obtains a constraint Gerstenhaber algebra and a constraint BV-module $(G, M)$ out of it. (In short, classical constraint manifolds yield constraint Cartan calculus algebraically.)
    - **Theorem C:** *Given a constraint Gerstenhaber algebra and BV-module with a constraint cocycle $c$, one can construct a **constraint** $L_\infty$-algebra of observables. Moreover, its **reduced part** $\overline{\mathcal{O}}$ (the quotient level) is an $L_\infty$-algebra that describes the observables of the reduced system.*

    As an application, Theorem C applied to multisymplectic manifolds with symmetries recovers the reduced $L_\infty$ in  and explains the extra terms (residue defect) in a categorical way .

## **Conclusion and Outlook**

We have developed a **purely algebraic toolkit** for constructing and reducing $L_\infty$-algebras of observables, extending concepts from symplectic geometry to multisymplectic and even noncommutative settings . This framework shows the power of combining homotopy algebra (for observables) with constraint category theory (for reduction). It provides a unified perspective where classical geometric reduction is just one instance of an algebraic functor acting on $L_\infty$-algebras .

Some directions for further research include:

- **Homotopy Momentum Maps:** Relating our constraint $L_\infty$-reduction to the notion of *homotopy momentum maps* (which appear in alternative higher reduction approaches, e.g. the work of Callies-Frégier-Rogers-Zambon on $L_\infty$-moment maps . It would be interesting to connect the **Leibniz-algebra-valued momentum maps** used here  with homotopy moment maps in an $L_\infty$-context.
- **Operadic Formulation:** The constraint triple constructions hint at an operadic or higher-categorical organization. One could aim to describe the entire process (Cartan calculus + constraints + $L_\infty$) in terms of operads or properads encoding these algebraic relations . This might streamline proofs and allow further generalizations (e.g. to quantum or $A_\infty$ settings).
- **Applications to Field Theory:** Ultimately, multisymplectic forms arise in classical field theory (e.g. the 2-form in mechanics vs. a 3-form in 2-dimensional field theory). Our algebraic observables $L_\infty$ could serve as a foundation for understanding *higher Poisson brackets* on the phase space of fields and their reduction under symmetries. Recent works on polysymplectic and polycontact reduction provide complementary geometric approaches; linking those with our algebraic method is a promising avenue.

**References:** *(Selected key references in context)* Rogers (2012) for the original multisymplectic $L_\infty$-algebra construction; Dippel-Esposito-Waldmann (2019) for constraint (coisotropic) triples in Poisson algebra setting; Blacker-Miti-Ryvkin (2024) for algebraic multisymplectic reduction; and our work Miti-Ryvkin (2025) (Differential Geom. Appl.) which this talk is based on, for full details and proofs. The methods presented exemplify how **pure algebraic techniques can not only recover but also enlighten classical geometric results** in higher symplectic geometry, broadening the scope to singular and noncommutative realms.

### 2025-10-21 bv-triples-Rogers-generalized.tex
Compiler error- too tired :(

--- 2025-10-21 bv-triples-main.tex
@@
-%+----------------------------------------------------------+
-%| SLIDES: Construction and Reduction of the L-infinity Algebra of Observables
-%|         Associated with a BV-Module
-%| Contents: - 60 minutes (estimated duration ~2.5 minutes per slide, ~24 slides)
-%|
-%| Author: Antonio Miti
-%| Event: ARTS — Algebra and Representation Theory Seminar
-%| Place: Università di Roma  "Tor Vergata "
-%| Date: 21/10/2025
-%| Link: https://www.mat.uniroma2.it/~ricerca/algebr/page-AREA_files/page-AREA-2_files/talks.html
-%+----------------------------------------------------------+
-
 %- HandOut Flag -----------------------------------------------------------------------------------------
-	\newif\ifHandout
-	\Handouttrue  %uncomment for the printable version
-	%Handling of flags it is not preserved when passing to standalone-subfiles!
+\makeatletter
+\@ifundefined{ifHandout}{%
+  \expandafter\newif\csname ifHandout\endcsname
+}{}
+\makeatother
 
 %- D0cum3nt ----------------------------------------------------------------------------------------------
+%\documentclass[beamer,10pt]{standalone}   
+\documentclass[beamer,10pt,handout]{standalone}  \Handouttrue
+
 \ifHandout
-	\documentclass[handout,10pt]{beamer}   
 	\setbeameroption{show notes} %print notes   
-\else
-	\documentclass[10pt]{beamer}
 \fi
@@
 
-%- Bibliography (Biber) ----------------------------------------------------------------------------------
-\usepackage[backend=biber,style=alphabetic,maxnames=2]{biblatex}
-\bibliography{bibfile.bib}
-
-%- L30's ----------------------------------------------------------------------------------------------
-\usepackage{quiver} %https://q.uiver.app/ % Not in Miktex!
-\usetikzlibrary{nfold}
-\usetikzlibrary{decorations.pathmorphing} 
-\renewcommand{\Ham}{\mathrm{Ham}}
-\newcommand{\Der}{\mathrm{Der}}
-\usepackage{enumitem}
-\setlist{topsep=0pt, leftmargin=*,label=$\bullet$}
-
 %--Beamer Style-----------------------------------------------------------------------------------------------
 \usetheme{toninus}
+\usepackage{animate}
+\usetikzlibrary{positioning, arrows}
+\usetikzlibrary{shapes}
 
-\usetikzlibrary{backgrounds}
-  \tikzset{
-    invisible/.style={opacity=0},
-    visible on/.style={alt=#1{}{invisible}},
-    alt/.code args={<#1>#2#3}{%
-      \alt<#1>{\pgfkeysalso{#2}}{\pgfkeysalso{#3}} % \pgfkeysalso doesn't change the path
-    },
-  }
-
-%- T1tle P4g3 -------------------------------------------------------------------------------------------
-\title{Construction and Reduction of the $L_\infty$ Algebra of Observables Associated with a BV-Module} 
-\subtitle{\href{https://www.mat.uniroma2.it/~ricerca/algebr/page-AREA_files/page-AREA-2_files/talks.html}{- ARTS - Algebra and Representation Theory Seminar in Roma "Tor Vergata"}}
-\author[AMM]{
-	\href{https://www.antoniomiti.it/}{Antonio Michele Miti}
-	{\small joint work w/ Leonid Ryvkin}
-}
-\institute[SUR]{
-	Sapienza Università di Roma \\
-	Rome, Italy 	\\
-	\vspace{.5em}
-  \begin{tabular}[h]{ccc}
-      \href{https://www.mat.uniroma1.it/en}{\includegraphics[width=6cm]{./Logos/Sur_logo}} & & 
-      \href{https://civis3i.univ-amu.fr/en/civis3i-alliance-programme}{\includegraphics[width=3cm]{Logos/Civis_logo}}
-  \end{tabular}    
-}
-\date[TorV25] % (optional, should be abbreviation of conference name)
-{	
-	{\vskip 1ex}
-	Universit\'a di Roma - Tor Vergata, October 2025
-}
-
-%+----------------------------------------------------------+
-%- D0cum3nt ------------------------------------------------+
-%+----------------------------------------------------------+
+%===========================================================%
 \begin{document}
-%+----------------------------------------------------------+
-
-\begin{frame}
-  \titlepage
-\end{frame}
-
-%+----------------------------------------------------------+
-% S3cti0n: Intr0ducti0n ------------------------------------+
-\section{Introduction}
-%+----------------------------------------------------------+
-%
-
-\begin{frame}{Symplectic Geometry}
-\begin{itemize}
-  \item Symplectic manifold: $(M,\omega)$ with $\omega$ closed, nondegenerate 2-form.
-  \item Observables: $C^\infty(M)$ with Poisson bracket $\{f,g\} = \omega(X_f, X_g)$.
-  \item $X_f$ is the Hamiltonian vector field: $\iota_{X_f} \omega = df$.
-\end{itemize}
-\end{frame}
-\note{Symplectic vs.
-Multisymplectic Geometry: In symplectic geometry, a closed nondegenerate 2-form $\omega$ on a manifold $M$ gives rise to a Poisson algebra of observables (smooth functions with the Poisson bracket) .
-In contrast, multisymplectic manifolds carry a closed nondegenerate form of degree $>2$ (often called an $n$-plectic form if its degree is $n+1$).
-These higher-degree forms naturally lead not to a Poisson Lie algebra, but to a higher (homotopy) Lie algebra structure on observables.
-In fact, as shown by Rogers, an $n$-plectic manifold yields an $n$-term $L_\infty$-algebra of observables (sometimes called a higher Poisson algebra) .org.
-This generalizes the Poisson bracket: for example, a 3-plectic form (degree 3) gives a Lie 2-algebra of observables, etc., with higher multi-brackets capturing the failure of the Jacobi identity up to homotopy.
-
-Symplectic Case: If $(M,\omega)$ is a symplectic manifold (closed nondegenerate 2-form), every smooth function $f\in C^\infty(M)$ has an associated Hamiltonian vector field $X_f$ defined by $i_{X_f}\omega = d f$.
-The space of observables $C^\infty(M)$ forms a Poisson algebra with the Poisson bracket ${f,g} = \omega(X_f, X_g)$.
-This is just a Lie algebra (indeed a Lie derivation algebra on $C^\infty(M)$) satisfying the Jacobi identity strictly.
-
-}
-
-\begin{frame}{From Symplectic to Multisymplectic}
-\begin{itemize}
-  \item $k$-plectic manifold: $(M,\omega)$ with closed, nondegenerate $(k+1)$-form.
-  \item Hamiltonian $(k-1)$-form $\alpha$: $\iota_X \omega = d\alpha$.
-  \item Rogers (2010): observables form an $L_\infty$-algebra.
-\end{itemize}
-\end{frame}
-\note{- **Multisymplectic (Higher-Degree) Forms:** Now let $(M,\omega)$ be a **$k$-plectic manifold**, i.e.
-$\omega$ is a closed, nondegenerate $(k+1)$-form (for example, a 3-form if $k=2$).
-The notion of *Hamiltonian observables* generalizes: a **Hamiltonian $(k-1)$-form** $\alpha \in \Omega^{k-1}(M)$ is one that admits a vector field $X$ (a *Hamiltonian field*) satisfying $i_X\omega = d\alpha$.
-We call the pair $(X,\alpha)$ a *Hamiltonian pair*.
-Just as in the symplectic case $(k=1)$ where $\alpha$ is a 0-form (function) and $X$ its Hamiltonian vector field, here $\alpha$ plays the role of the observable (often called an $(k-1)$-form observable).
-The collection of all such Hamiltonian forms (for various degrees) can be organized into a graded object, and Rogers showed that it carries a canonical **$L_\infty$-algebra structure** .
-    - **Example:** For a 3-plectic manifold (degree 3 form $\omega$), one has Hamiltonian 1-forms: each 1-form $\alpha$ for which there exists $X$ with $i_X\omega = d\alpha$.
-These Hamiltonian pairs $(X,\alpha)$ form the degree-0 part of the observables.
-In addition, ordinary functions (0-forms) can be viewed as Hamiltonian 0-forms (with $X$ such that $i_X\omega = d(0) = 0$), and perhaps higher-degree observables appear up to degree 1 in this case.
-The resulting $L_\infty$ has non-trivial brackets of arity up to 2 (making it a *Lie 2-algebra* of observables, a kind of higher Poisson algebra).
-The 2-bracket extends the Poisson bracket, and a 3-bracket arises measuring the failure of the Jacobi identity (something that vanishes in the symplectic case but not in general).
-For a 4-plectic form, one would get a Lie 3-algebra, etc.}
-
-\begin{frame}{$L_\infty$ Algebra of Observables}
-\begin{itemize}
-  \item Observables organized as graded vector space: Hamiltonian forms + multi-brackets.
-  \item Higher brackets from Cartan calculus: $d$, $\iota_X$, $L_X$.
-  \item No manifold needed if we have the algebraic structure.
-\end{itemize}
-\end{frame}
-\note{Rogers’ Construction (2010/2012): The remarkable insight of Rogers  was that the construction of this observables $L_\infty$-algebra is essentially algebraic, relying only on the standard Cartan calculus identities for differential forms and vector fields.
-In other words, Rogers’ $L_\infty$ brackets can be derived from the algebraic relations between the exterior derivative $d$, the interior product $i_X$, and the Lie derivative $L_X$ on forms .
-This suggests we can abstract and generalize the construction beyond the category of manifolds.
-The goal is to build an $L_\infty$-algebra of observables in a purely algebraic setting, provided we have an analog of  "forms " and  "vector fields " satisfying the Cartan relations .}
-
-\begin{frame}{Reminder: What’s an $L_\infty$ Algebra?}
-\begin{itemize}
-  \item Graded vector space $V = \bigoplus V^i$.
-  \item Maps $\ell_k: V^{\otimes k} \to V$ of degree $2 - k$.
-  \item Satisfying higher Jacobi identities (homotopy Lie algebra).
-\end{itemize}
-\end{frame}
-\note{- **Higher Brackets via Cartan Calculus:** The construction of the $L_\infty$ brackets can be understood conceptually in terms of the **Cartan calculus identities**.
-Recall that on a manifold, we have for any vector fields $X,Y$ and differential forms $\alpha$:
-    - $L_X = [d, i_X]$ (Cartan’s identity relating Lie derivative and interior contraction), and
-    - $[L_X, i_Y] = i_{[X,Y]}$ (compatibility of Lie derivative with contraction),
-    - $[L_X,L_Y] = L_{[X,Y]}$, etc.
-
-        These identities ensure that the operations $d, i_X, L_X$ behave in a coordinated way (the essence of *Gerstenhaber algebra and BV-module* structure, as we formalize below).
-Rogers’ $L_\infty$ brackets are built using these ingredients: e.g., the binary bracket of two Hamiltonian forms $(X,\alpha)$ and $(Y,\beta)$ can be defined as $( [X,Y],; L_X\beta)$ (or plus cyclic terms), and higher brackets involve expressions with $i_{X_i} i_{X_j}\omega$ contracted with another argument, etc., ensuring the homotopy Jacobi identities hold .
-The key point is that all such formulas **only use the algebraic operations $d,i,L,[\cdot,\cdot]$ and the form $\omega$**.
-This algebraic nature allows generalization to any context where similar operators exist.
-
-- **Limitations of Classical Reduction:** Before moving to the algebraic setup, note that reducing multisymplectic systems geometrically (analogue of Marsden-Weinstein reduction) can be challenging.
-Classical symplectic reduction requires a Lie group action that is free and proper and a regular value of the moment map; these conditions often fail (especially in field theory or higher form cases).
-Recent work has approached reduction **algebraically** by focusing on the algebra of observables (functions/forms) with constraints, rather than the quotient of manifolds.
-This algebraic approach, implemented for multisymplectic manifolds in Blacker-Miti-Ryvkin 2024, allows handling singular cases (non-free actions, etc.) by *encoding constraints and symmetries at the algebraic level.
-Our work builds on this idea using *constraint triples*.}
-
-\begin{frame}{Scope/Idea of the Talk}
-\begin{itemize}
-  \item Generalize Rogers' construction to a purely algebraic setting.
-  \item Use Gerstenhaber algebras and BV-modules.
-  \item Handle reduction via constraint triples.
-  \item Apply to recover and extend results on multisymplectic reduction.
-\end{itemize}
-\end{frame}
-\note{Our Aim: In this talk, we present such a fully algebraic formalism for constructing and reducing $L_\infty$-algebras of observables, inspired by multisymplectic geometryarxiv.org.
-We work in the framework of Gerstenhaber algebras and Batalin-Vilkovisky modules (BV-modules), which encapsulate the algebraic structure of Cartan calculus (including both commutative and non-commutative cases).
-Given any Gerstenhaber algebra $G$ together with a BV-module $M$ and a chosen closed element (a  "cocycle ") $c$ in $M$, we will show how to construct an associated $L_\infty$-algebra of observables without reference to any underlying manifold .
-This is our Theorem A.
-Moreover, we will address how to perform reduction of these observables $L_\infty$-algebras in the presence of constraints or symmetries.
-For this, we employ the notion of constraint triples (introduced by Dippel-Esposito-Waldmann 2019marvindippell.de) as an algebraic framework for coisotropic reduction.
-Adapting this to our BV-module setting, we obtain a general procedure to reduce an $L_\infty$ of observables, even in singular scenarios where classical quotient constructions fail  .
-This corresponds to Theorem C in our work.
-In particular, our approach reproduces the multisymplectic reduction results of Blacker-Miti-Ryvkin (SIGMA 2024) in a more conceptual way and clarifies the role of the so-called  "residue defect " that appears in the reduction process .}
-
-%+----------------------------------------------------------+
-%Overview: Roughly the first half of the talk will be introductory.
-We will recall the necessary background on multisymplectic observables and momentum maps, then introduce the algebraic structures (Gerstenhaber algebras and BV-modules) that replicate Cartan calculus.
-In the second half, we outline the construction of the observables $L_\infty$-algebra in the algebraic setting (Theorem A), and then discuss how to incorporate constraints via constraint triples, leading to a reduced $L_\infty$-algebra of observables (Theorem C).
-
-%+----------------------------------------------------------+
-%Section: BV-Modules ----------------------------------+
-\section{BV-Modules: Algebraic Cartan Calculus}
-%+----------------------------------------------------------+
-%
-
-\begin{frame}{Lie-Rinehart Algebras}
-\begin{itemize}
-  \item Pair $(A,E)$: $A$ a commutative algebra, $E$ an $A$-module and Lie algebra.
-  \item Anchor map: $\rho: E \to \mathrm{Der}(A)$.
-  \item Encodes derivations + Lie algebra structure.
-\end{itemize}
-\end{frame}
-\note{To generalize the above geometric structures, we introduce the algebraic counterparts of  "multivector fields " and  "differential forms with Cartan calculus.
-" All vector spaces are over a field of characteristic 0 (e.g.
-$\mathbb{R}$).
-We work in graded settings since forms and multivectors are naturally graded.
-
-- **Lie-Rinehart Algebras:** A *Lie-Rinehart algebra* $(A,E)$ consists of a commutative associative algebra $A$ (think of $A=C^\infty(M)$) and an $A$-module $E$ (think of $E=\mathfrak X(M)$, the vector fields) which is also a Lie algebra, together with an *anchor* map $\rho: E \to \mathop{\mathrm{Der}}(A)$ (derivations of $A$) satisfying a Leibniz rule: $[X, aY] = a[X,Y] + (\rho(X)a),Y$.
-This abstractly encodes the notion of derivations of $A$ with an $A$-linear Lie bracket.
-**Example:** If $A=C^\infty(M)$, then $E=\Gamma(TM)$ (the module of vector fields) with the identity anchor $\rho(X)=X$ is a Lie-Rinehart algebra.
-In fact, Lie-Rinehart algebras are algebraic analogues of Lie algebroids (and every Lie algebroid gives a Lie-Rinehart algebra).}
-
-\begin{frame}{Gerstenhaber Algebras}
-\begin{itemize}
-  \item Graded commutative algebra $(\mathcal{G}, \wedge)$.
-  \item Lie bracket $[\cdot,\cdot]$ of degree $-1$.
-  \item Compatibility (Leibniz rule): $[x, y\wedge z] = [x,y]\wedge z + (-1)^{(\deg x -1)\deg y} y\wedge [x,z]$.
-\end{itemize}
-\end{frame}
-\note{- **Gerstenhaber Algebras:** A *Gerstenhaber algebra* is a graded algebra that captures the structure of *exterior algebra of multivector fields*.
-Formally, it is a triple $(\mathcal{G}, \wedge, [\cdot,\cdot])$ where:
-    - $\mathcal{G} = \bigoplus_{i\in\mathbb{Z}} \mathcal{G}^i$ is a $\mathbb{Z}$-graded vector space.
-    - $\wedge: \mathcal{G}^p \times \mathcal{G}^q \to \mathcal{G}^{p+q}$ is a graded-commutative, associative product (degree $0$ operation).
-    - $[\cdot,\cdot]: \mathcal{G}^p \times \mathcal{G}^q \to \mathcal{G}^{p+q-1}$ is a bracket of degree $-1$, making $\mathcal{G}$ into a graded Lie algebra.
-    - **Compatibility (Leibniz rule):** The bracket is a derivation of the product: $[x, y\wedge z] = [x,y]\wedge z + (-1)^{(deg,x -1),deg,y} ,y\wedge [x,z]$ for homogeneous $x,y,z$.
-This is the defining Gerstenhaber identity, generalizing the fact that the Lie bracket of vector fields satisfies a Leibniz rule with respect to wedge of forms or functions.
-
-    **Example:** If $(A,E)$ is a Lie-Rinehart algebra, the **exterior algebra** of $E$ (with a degree shift) carries a natural Gerstenhaber structure.
-In particular, take $\mathcal{G} = \Lambda^\bullet E$ (the exterior *wedge* algebra of $E$ treated as a graded space of multivectors).
-The wedge product is the usual wedge of multivectors, and the bracket is the **Schouten-Nijenhuis bracket** extending the Lie bracket on $E$ to all multivectors.
-This $(\Lambda E,\wedge,[\cdot,\cdot]_{SN})$ is a Gerstenhaber algebra, prototypical in geometry (for $E=\mathfrak X(M)$ one recovers the standard Gerstenhaber algebra of multivector fields on $M$).}
-
-\begin{frame}{Gerstenhaber Modules}
-\begin{itemize}
-  \item $G$-module $M$ with contraction $\iota_X$ of degree $-\deg X$.
-  \item Induced Lie derivative $L_X = [d,\iota_X]$ when $d$ is defined.
-\end{itemize}
-\end{frame}
-\note{Gerstenhaber Module: Given a Gerstenhaber algebra $G$, a Gerstenhaber $G$-module is a graded module $M = \bigoplus M^i$ equipped with an action of $G$ that extends the idea of a multivector acting on forms by contraction.
-Concretely, for each element $X\in G^p$, we have a degree $-p$ operator $i_X: M^\ast \to M^{\ast-p}$ (interpreted as interior product by $X$) satisfying a compatible set of identities (graded derivations, etc.)ar5iv.labs.arxiv.org.
-We also typically get an induced Lie derivative action $L_X$ of degree 0 defined by $L_X := [D,;i_X]$ once a differential $D$ is present (see below).
-We won’t detail the full set of axioms here, but essentially a Gerstenhaber module gives an algebraic version of the pair of operations $(i_X, L_X)$ acting on a  "forms " module, with $i$ being antiderivations and $L$ Lie derivations.
-(The literature sometimes refers to this structure as a  "TTN (Tsygan-Tamarkin-Nest) calculus " .)}
-
-\begin{frame}{BV-Modules}
-\begin{itemize}
-  \item A Gerstenhaber module $M$ with differential $d$.
-  \item Cartan identity: $L_X = [d,\iota_X]$.
-  \item Encodes full algebraic Cartan calculus.
-\end{itemize}
-\end{frame}
-\note{Batalin-Vilkovisky Modules (BV-Modules): A BV-module is a Gerstenhaber module that is also equipped with a differential of degree $+1$ (like an exterior derivative) satisfying Cartan’s formula.
-Formally, let $G$ be a Gerstenhaber algebra and $(M,d)$ a cochain complex (so $d: M^i \to M^{i+1}$ with $d^2=0$).
-We say $M$ is a BV-module over $G$ if $M$ is a Gerstenhaber $G$-module and, for all $X\in G$, we have the Cartan identity $L_X = [d,; i_X]$ (and automatically $[L_X, i_Y] = i_{[X,Y]}$, etc.)  .
-In other words, $M$ carries an action of $G$ by contraction $i_X$ and Lie derivative $L_X$ such that together with the differential $d$ they satisfy the standard graded commutation relations of Cartan calculus.
-We often call $d$ the BV differential.}
-
-\begin{frame}{Abstract Cartan Calculus}
-\begin{itemize}
-  \item $(G,M,d)$ with $G$ Gerstenhaber, $M$ BV-module, $d^2=0$.
-  \item Examples: $(\mathfrak{X}^\bullet(M),\Omega^\bullet(M), d)$.
-  \item Extends to noncommutative and algebraic settings.
-\end{itemize}
-\end{frame}
-\note{Example (Classical Cartan Calculus): Take $G = \Lambda^\bullet \mathfrak X(M)$ (Gerstenhaber algebra of multivector fields on a manifold) and $M=\Omega^\bullet(M)$ (the de Rham complex of differential forms).
-This is a canonical example of a BV-module  : the differential $d$ is the exterior derivative, the contraction $i_X$ is the usual insertion of a multivector $X$ into a form, and the Lie derivative $L_X$ is the usual one acting on forms.
-These satisfy $L_X = d \circ i_X + i_X \circ d$ (Cartan formula) and all other Cartan identities.
-In fact, this example exactly recovers the classical Cartan calculus on $M$ as a BV-module structure on $\Omega^\bullet(M)$, with $G$ playing the role of  "polyvector fields " .
-This justifies the abstractions: any Gerstenhaber algebra + BV-module pair can be seen as a generalized  "space of multivectors and forms " with a full Cartan calculus available .
-We emphasize that such structures exist in much more general settings, including noncommutative geometry (where $A$ is a noncommutative algebra and one considers analogues of forms and multivectors  ), but for our purposes we stick to the algebraic axioms.}
-
-%+----------------------------------------------------------+
-%Section: L-infinity Algebra Associated with a BV-Module ---+
-%
-\section{$L_\infty$ Algebra Associated with a BV-Module}
-%+----------------------------------------------------------+
-%
+%===========================================================%
+\checkpoint
 
@@
 
-%+----------------------------------------------------------+
-%S3cti0n: An Applicati0n: Multisymplectic Reducti0n -------+
-%
-\section{An Application: Multisymplectic Reduction}
-%+----------------------------------------------------------+
-%
+%-----------------------------------------------------------%
+\ifstandalone
+% https://en.wikibooks.org/wiki/LaTeX/Bibliographies_with_biblatex_and_biber
+\begin{frame}[t,allowframebreaks]{Bibliography}
+	%\nocite{*}
+	\printbibliography
+\end{frame}
+\fi
+%-----------------------------------------------------------%
 
-\begin{frame}{Constraint Triples}
-\begin{itemize}
-  \item Triple $(A, A_C, \overline{A})$ with inclusion/projection.
-  \item $A_C$ encodes constraints, $\overline{A} = A/I$ reduced algebra.
-  \item Adapted to Gerstenhaber and BV-module settings.
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Constraint BV-Modules}
-\begin{itemize}
-  \item Triples $(G, G_C, \overline{G})$, $(M, M_C, \overline{M})$.
-  \item Structures compatible with Cartan calculus.
-  \item Closed cocycle triple $c = (c, c_C, \overline{c})$.
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Constraint $L_\infty$ Algebra Associated with…}
-\begin{itemize}
-  \item Construct observables $\mathcal{O} = (\mathcal{O}, \mathcal{O}_C, \overline{\mathcal{O}})$.
-  \item Each component carries an $L_\infty$ structure.
-  \item Brackets compatible with inclusions/projections.
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Reduction Functor}
-\begin{itemize}
-  \item Quotient part $\overline{\mathcal{O}}$ inherits $L_\infty$ structure.
-  \item Encodes reduced observables algebra.
-  \item No need for regular quotient at geometric level.
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Recovering Old Results}
-\begin{itemize}
-  \item Applies to multisymplectic reduction (Blacker-Miti-Ryvkin 2024).
-  \item Explains residue defect in homotopy Jacobi identity.
-  \item Matches geometric reduction under regularity.
-\end{itemize}
-\end{frame}
+%-----------------------------------------------------------+
+\end{document}
+%-----------------------------------------------------------+
 
@@
 \end{frame}
-
-%+----------------------------------------------------------+
-\end{document}
-%+----------------------------------------------------------+
 

### 2025-10-21 bv-triples-background.tex
Compiler error- too tired :(

%- HandOut Flag ----------------------
\makeatletter
\@ifundefined{ifHandout}{%
  \expandafter\newif\csname ifHandout\endcsname
}{}
\makeatother

%- D0cum3nt ----------------------------------------------------------------------------------------------
%\documentclass[beamer,10pt]{standalone}   
\documentclass[beamer,10pt,handout]{standalone}  \Handouttrue

\ifHandout
	\setbeameroption{show notes} %print notes   
\fi

%- Packages ----------------------------------------------------------------------------------------------
\usepackage{custom-style}
\usepackage{math}

%--Beamer Style-----------------------------------------------------------------------------------------------
\usetheme{toninus}
\usepackage{animate}
\usetikzlibrary{positioning, arrows}
\usetikzlibrary{shapes}

%- Bibliography (Biber) ----------------------------------------------------------------------------------
\usepackage[backend=biber,style=alphabetic,maxnames=2]{biblatex}
\bibliography{bibfile.bib}

%===========================================================%
\begin{document}
%===========================================================%
\checkpoint

%-----------------------------------------------------------+
\begin{frame}{Lie-Rinehart Algebras}

  \begin{defblock}[Lie-Rinehart Algebra]
    A pair $(A,E)$ where
    \begin{itemize}
      \item $A$ is a commutative, associative algebra,
      \item $E$ is an $A$-module and a Lie algebra,
      \item there is an anchor map $\rho: E \to \mathrm{Der}(A)$ satisfying the Leibniz rule:
        \[
          [X, aY] = a[X,Y] + (\rho(X)a)Y, \quad \forall X,Y \in E, a \in A.
        \]
    \end{itemize}
  \end{defblock}

\begin{itemize}
  \item Encodes derivations + Lie algebra structure.
\end{itemize}

  \begin{exblock}
    If $A=C^\infty(M)$, then $E=\Gamma(TM)$ with $\rho=\mathrm{id}$ is a Lie-Rinehart algebra.

    Lie-Rinehart algebras are algebraic analogues of Lie algebroids (and every Lie algebroid gives a Lie-Rinehart algebra)
  \end{exblock}

\end{frame}
\note[itemize]{
  \item To generalize the above geometric structures, we introduce the algebraic counterparts of  "multivector fields " and  "differential forms with Cartan calculus. " 
  \item  A  Lie-Rinehart algebra  $(A,E)$ consists of a commutative associative algebra $A$ (think of $A=C^\infty(M)$) and an $A$-module $E$ (think of $E=\mathfrak X(M)$, the vector fields) which is also a Lie algebra, together with an *anchor* map $\rho: E \to \mathop{\mathrm{Der}}(A)$ (derivations of $A$) satisfying a Leibniz rule: $[X, aY] = a[X,Y] + (\rho(X)a),Y$. This abstractly encodes the notion of derivations of $A$ with an $A$-linear Lie bracket. 
  \item Example: If $A=C^\infty(M)$, then $E=\Gamma(TM)$ (the module of vector fields) with the identity anchor $\rho(X)=X$ is a Lie-Rinehart algebra. 
  \item   In fact, Lie-Rinehart algebras are algebraic analogues of Lie algebroids (and every Lie algebroid gives a Lie-Rinehart algebra).}
%-----------------------------------------------------------+

%-----------------------------------------------------------+
\begin{frame}{Gerstenhaber Algebras}
  \emph{A graded algebra that captures the structure of exterior algebra of multivector fields.}
  %
  \begin{defblock}[Gerstenhaber Algebra]
    A triple $(\mathcal{G}, \wedge, [\cdot,\cdot])$ where
    \begin{itemize}
      \item $\mathcal{G} = \bigoplus_{i\in\mathbb{Z}} \mathcal{G}^i$ is a $\mathbb{Z}$-graded vector space,
      \item $\wedge: \mathcal{G}^p \times \mathcal{G}^q \to \mathcal{G}^{p+q}$ is a graded-commutative, associative product (degree $0$ operation),
      \item $[\cdot,\cdot]: \mathcal{G}^p \times \mathcal{G}^q \to \mathcal{G}^{p+q-1}$ is a bracket of degree $-1$, making $\mathcal{G}$ into a graded Lie algebra,
      \item Compatibility (Leibniz rule): The bracket is a derivation of the product:
        \[
          [x, y\wedge z] = [x,y]\wedge z + (-1)^{(\deg x -1)\deg y} y\wedge [x,z]
        \]
        for homogeneous $x,y,z$.
    \end{itemize}

    \begin{exblock}%{Example}
      If $(A,E)$ is a Lie-Rinehart algebra, the exterior algebra of $E$ (with a degree shift) carries a natural Gerstenhaber structure.
    \end{exblock}

    \begin{exblock}%{Example}
      Take $\mathcal{G} = \Lambda^\bullet E$ (the exterior wedge algebra of $E$ treated as a graded space of multivectors). The wedge product is the usual wedge of multivectors, and the bracket is the Schouten-Nijenhuis bracket extending the Lie bracket on $E$ to all multivectors. This $(\Lambda E,\wedge,[\cdot,\cdot]_{SN})$ is a Gerstenhaber algebra, prototypical in geometry (for $E=\mathfrak X(M)$ one recovers the standard Gerstenhaber algebra of multivector fields on $M$).
    \end{exblock}

\end{frame}
\note[itemize]{
  \item  A Gerstenhaber algebra is a graded algebra that captures the structure of exterior algebra of multivector fields. 
  \item Compatibility (Leibniz rule): The bracket is a derivation of the product: $[x, y\wedge z] = [x,y]\wedge z + (-1)^{(\deg x -1)\deg y} y\wedge [x,z]$ for homogeneous $x,y,z$. This is the defining Gerstenhaber identity, generalizing the fact that the Lie bracket of vector fields satisfies a Leibniz rule with respect to wedge of forms or functions.
}
%-----------------------------------------------------------+

%-----------------------------------------------------------+
\begin{frame}{Gerstenhaber Modules}
  %
  \begin{defblock}[Gerstenhaber Module]
    A Gerstenhaber module over a Gerstenhaber algebra $(\mathcal{G}, \wedge, [\cdot,\cdot])$ is a graded module $\mathcal{M} = \bigoplus_{i\in\mathbb{Z}} \mathcal{M}^i$ together with an action
    \[
      \iota: \mathcal{G}^p \times \mathcal{M}^q \to \mathcal{M}^{q - p}
    \]
    satisfying:
    \begin{itemize}
      \item $\iota$ is $A$-linear in the second argument,
      \item **Compatibility:** For homogeneous $x,y\in \mathcal{G}$ and $m\in \mathcal{M}$,
        \[
          \iota_{[x,y]} m = \iota_x (\iota_y m) - (-1)^{(\deg x -1)(\deg y -1)} \iota_y (\iota_x m).
        \]
    \end{itemize}

\begin{itemize}
  \item $G$-module $M$ with contraction $\iota_X$ of degree $-\deg X$.
  \item Induced Lie derivative $L_X = [d,\iota_X]$ when $d$ is defined.
\end{itemize}
\end{frame}
\note[itemize]{
  \item Gerstenhaber Module extends the idea of a multivector acting on forms by contraction. 
  \item Concretely, for each element $X\in G^p$, we have a degree $-p$ operator $i_X: M^\ast \to M^{\ast-p}$ (interpreted as interior product by $X$) satisfying a compatible set of identities (graded derivations, etc.). 
  \item We also typically get an induced Lie derivative action $L_X$ of degree 0 defined by $L_X := [D,;i_X]$ once a differential $D$ is present (see below). We won’t detail the full set of axioms here, but essentially a Gerstenhaber module gives an algebraic version of the pair of operations $(i_X, L_X)$ acting on a  "forms " module, with $i$ being antiderivations and $L$ Lie derivations.
  \item (The literature sometimes refers to this structure as a  "TTN (Tsygan-Tamarkin-Nest) calculus " .)}
%-----------------------------------------------------------+

%-----------------------------------------------------------+
\begin{frame}{BV-Modules}
  %
  \begin{defblock}[Batalin-Vilkovisky Module]
    A Batalin-Vilkovisky module (BV-module) over a Gerstenhaber algebra $(\mathcal{G}, \wedge, [\cdot,\cdot])$ is a Gerstenhaber module $(\mathcal{M}, \iota)$ together with a differential $d: \mathcal{M}^i \to \mathcal{M}^{i+1}$ (i.e. $d^2=0$) satisfying the Cartan identity:
    \[
      L_x := [d, \iota_x] = d \circ \iota_x + (-1)^{\deg x -1} \iota_x \circ d
    \]
    for all homogeneous $x\in \mathcal{G}$, where $L_x$ is the Lie derivative induced by the Gerstenhaber module structure.
  \end{defblock}

\end{frame}
\note[itemize]{
  \item Batalin-Vilkovisky Modules (BV-Modules): A BV-module is a Gerstenhaber module that is also equipped with a differential of degree $+1$ (like an exterior derivative) satisfying Cartan’s formula. 
  \item Formally, let $G$ be a Gerstenhaber algebra and $(M,d)$ a cochain complex (so $d: M^i \to M^{i+1}$ with $d^2=0$). We say $M$ is a BV-module over $G$ if $M$ is a Gerstenhaber $G$-module and, for all $X\in G$, we have the Cartan identity $L_X = [d,; i_X]$ (and automatically $[L_X, i_Y] = i_{[X,Y]}$, etc.)  . 
  \item In other words, $M$ carries an action of $G$ by contraction $i_X$ and Lie derivative $L_X$ such that together with the differential $d$ they satisfy the standard graded commutation relations of Cartan calculus. \item We often call $d$ the BV differential.}
%-----------------------------------------------------------+

%-----------------------------------------------------------+
\begin{frame}{Abstract Cartan Calculus}
\begin{itemize}
  \item A Gerstenhaber module $M$ with differential $d$.
  \item Cartan identity: $L_X = [d,\iota_X]$.
  \item Encodes full algebraic Cartan calculus.
\end{itemize}

  \begin{itemize}
  \item $(G,M,d)$ with $G$ Gerstenhaber, $M$ BV-module, $d^2=0$.
  \item Examples: $(\mathfrak{X}^\bullet(M),\Omega^\bullet(M), d)$.
  \item Extends to noncommutative and algebraic settings.
\end{itemize}
\end{frame}
\note{Example (Classical Cartan Calculus): Take $G = \Lambda^\bullet \mathfrak X(M)$ (Gerstenhaber algebra of multivector fields on a manifold) and $M=\Omega^\bullet(M)$ (the de Rham complex of differential forms). This is a canonical example of a BV-module  : the differential $d$ is the exterior derivative, the contraction $i_X$ is the usual insertion of a multivector $X$ into a form, and the Lie derivative $L_X$ is the usual one acting on forms. These satisfy $L_X = d \circ i_X + i_X \circ d$ (Cartan formula) and all other Cartan identities. In fact, this example exactly recovers the classical Cartan calculus on $M$ as a BV-module structure on $\Omega^\bullet(M)$, with $G$ playing the role of  "polyvector fields " . This justifies the abstractions: any Gerstenhaber algebra + BV-module pair can be seen as a generalized  "space of multivectors and forms " with a full Cartan calculus available . We emphasize that such structures exist in much more general settings, including noncommutative geometry (where $A$ is a noncommutative algebra and one considers analogues of forms and multivectors  ), but for our purposes we stick to the algebraic axioms.}
%-----------------------------------------------------------+

%-----------------------------------------------------------%
\ifstandalone
% https://en.wikibooks.org/wiki/LaTeX/Bibliographies_with_biblatex_and_biber
\begin{frame}[t,allowframebreaks]{Bibliography}
	%\nocite{*}
	\printbibliography
\end{frame}
\fi
%-----------------------------------------------------------%

%-----------------------------------------------------------+
\end{document}
%-----------------------------------------------------------+

### 2025-10-21 bv-triples-intro.tex
Compiler error- too tired :(

--- 2025-01-21 msconstraints-short-main.tex
@@
-%+----------------------------------------------------------------------------+
-%| SLIDES: Constraint Algebras of multisymplectic Observables (Follow-up talk)
-%| Contents:	- 25 minutes (extimated duration ~2 minutes per slide, ~12 slides )
-%|
-%| Author: Antonio miti
-%| Event: 19th International Young Researchers Workshop on Geometry, Dynamics and Field Theory
-%| Place: Verona
-%| Date: 20/01/25
-%+----------------------------------------------------------------------------+
-
 %- HandOut Flag -----------------------------------------------------------------------------------------
-	\newif\ifHandout
-	\Handouttrue  %uncomment for the printable version
-	%Handling of flags it is not preserved when passing to standalone-subfiles!
+\makeatletter
+\@ifundefined{ifHandout}{%
+  \expandafter\newif\csname ifHandout\endcsname
+}{}
+\makeatother
 
 %- D0cum3nt ----------------------------------------------------------------------------------------------
+\documentclass[beamer,10pt]{standalone}   
+%\documentclass[beamer,10pt,handout]{standalone}  \Handouttrue
+
 \ifHandout
-	\documentclass[handout,10pt]{beamer}   
 	\setbeameroption{show notes} %print notes   
-\else
-	\documentclass[10pt]{beamer}
 \fi
@@
 
+%--Beamer Style-----------------------------------------------------------------------------------------------
+\usetheme{toninus}
+\usepackage{animate}
+\usetikzlibrary{positioning, arrows}
+\usetikzlibrary{shapes}
+
 %- Bibliography (Biber) ----------------------------------------------------------------------------------
@@
 
-%- L30's ----------------------------------------------------------------------------------------------
-\usepackage{quiver} %https://q.uiver.app/ % Not in Miktex!
-\usetikzlibrary{nfold}
-\usetikzlibrary{decorations.pathmorphing} 
-\renewcommand{\Ham}{\mathrm{Ham}}
-\newcommand{\Der}{\mathrm{Der}}
-\usepackage{enumitem}
-\setlist{topsep=0pt, leftmargin=*,label=$\bullet$}
+%===========================================================%
+\begin{document}
+%===========================================================%
 
-%--Beamer Style-----------------------------------------------------------------------------------------------
-\usetheme{toninus}
-
-\usetikzlibrary{backgrounds}
-  \tikzset{
-    invisible/.style={opacity=0},
-    visible on/.style={alt=#1{}{invisible}},
-    alt/.code args={<#1>#2#3}{%
-      \alt<#1>{\pgfkeysalso{#2}}{\pgfkeysalso{#3}} % \pgfkeysalso doesn't change the path
-    },
-  }
-
-%- T1tle P4g3 -------------------------------------------------------------------------------------------
-\title{ Constraint Algebras \\ of Multisymplectic Observables } 
-\subtitle{\href{https://sites.google.com/view/xix-yrw-verona/home?authuser=0}{19th International Young Researchers Workshop on Geometry, Dynamics and Field Theory}}
-\author[AMM]{
-	\href{https://www.antoniomiti.it/}{Antonio Michele Miti}
-	{\small joint work w/ Leonid Ryvkin}
-}
-\institute[SUR]{
-	Sapienza Università di Roma \\
-	Rome, Italy 	\\
-	\vspace{.5em}
-  \begin{tabular}[h]{ccc}
-      \href{https://www.mat.uniroma1.it/en}{\includegraphics[width=6cm]{./Logos/Sur_logo}} & & 
-      \href{https://civis3i.univ-amu.fr/en/civis3i-alliance-programme}{\includegraphics[width=3cm]{Logos/Civis_logo}}
-  \end{tabular}    
-}
-\date[YGMC] % (optional, should be abbreviation of conference name)
-{	
-	{\vskip 1ex}
-	University of Verona, Italy, January 2025
-}
-
-%--------------------------------------------------------------------------------------------------
-%- D0cum3nt ----------------------------------------------------------------------------------------------------------------------------------
-\begin{document}
-%------------------------------------------------------------------------------------------------
-\begin{frame}  % Alternative: \maketitle outside of frame
-	\titlepage
-	\ifHandout
-		\tikz[overlay,remember picture]
-		{
-	    	%	\node at ($(current page.west)+(1.5,0)$) [rotate=90] {\Huge\textcolor{gray}{\today}};
-	    	\node[        
-	    		draw,
-	    		shape border rotate=90,
-			isosceles triangle,
-			isosceles triangle apex angle=90,
-			fill=yellow]
-	        		at ($(current page.north east)-(1,1)$) [rotate=-45] {\textcolor{red}{Handout version}};
-		}
-	\fi
-\end{frame}
-\addtocounter{framenumber}{-1}
-\note{
-	%\textbf{\underline{OUTLINE}}:
-	%\tableofcontents
-	\textbf{Abstract:}
-	\\
-    % Multisymplectic manifolds are a straightforward generalization of symplectic manifolds where closed non-degenerate $n$-forms are considered in place of $2$-forms.
-    % Investigating the relationship between symmetries (group action preserving the fixed differential form) and reduction is a natural theme when dealing with (multi) symplectic structures.
-	%
-    In the context of (multi)-symplectic, a reduction scheme can be taught to construct a second space of reduced dimension out of a given (multi)-symplectic manifold with symmetries.
-The reduced space thus obtained enjoys the convenient property of embodying the relevant geometric structure of the starting unreduced object.
-
-    A well-known result in symplectic geometry, the Marsden–Weinstein–Meyer theorem, states that the relevant geometric structure of a symplectic manifold can be studied on the orbits contained in a regular level set of a so-called "momentum map."
-    Following the seminal work by Śniatycki and Weinstein, many extensions to singular momentum maps have been discussed in the literature.
-
-    Recently, Marvin Dippel, Chiara Esposito, and Stephan Waldmann (see, e.g.
-\href{https://arxiv.org/abs/2310.05613}{arXiv:2310.05613}) developed a framework, known as constraints or isotropic algebras, that conveniently helps to make order in this plethora of constructions taking advanced of their similar structural patterns.
-
-    This talk, based on ongoing joint work with Casey Blacker and Leonid Ryvkin, reviews the relevant algebraic structures related to multisymplectic manifolds and discusses how the framework of constraint algebras can be adapted to algebraic reduction schemes in this setting.
-
-}
-%--------------------------------------------------------------------------------------------------
-
-%------------------------------------------------------------------------------------------------
+%----------------------------------------------------+
 \begin{frame}[fragile]{Keywords}
@@
     	\begin{column}{.45\textwidth}
-    		\onslide<4->{
+    		\onslide<5->{
 			\tikz[baseline]{
 		            \node[draw=orange!40,anchor=base,text width=5cm] (s1)
-		            {Algebraic structure encoding informations necessary for defining coisotropic reduction in Poisson geometry.};
+		            {...};
 			}
@@
     	\begin{column}{.45\textwidth}
-    		\onslide<5->{
+    		\onslide<4->{
 			 \tikz[baseline]{
 		            \node[draw=blue!40,anchor=base, text width=5cm] (s2)
-		            {Mathematical formalization of classical measurable quantities.};
+		            {...};
 			}
@@
 		\large
+		Construction and 
 		\tikz[baseline]{
 		            \node[fill=orange!20,anchor=base] (t1)
-		            {Constraint Algebra};
+		            {Reduction};
 			}
-		\\
-		of 
-		\\
+		of the 
+		\tikz[baseline]{
+	            \node[fill=blue!20,anchor=base] (t2)
+	            {$L_\infty$-Algebra};
+		} 
+		\\ of \\
 		\tikz[baseline]{
 	            \node[fill=green!20,anchor=base] (t3)
-	            {Multi};
+	            {Observables};
 		}
-		\kern-3pt - \kern-3pt
+		associated with a
 		\tikz[baseline]{
 		            \node[fill=red!20,anchor=base] (t4)
-	            {Symplectic};
+		            {BV-module};
 		}		
-		  \tikz[baseline]{
-		            \node[fill=blue!20,anchor=base] (t2)
-		            {Observables};
-		        }
-
 	\end{center}
@@
 	            \node[draw=green!40,anchor=base,text width=5cm] (s3)
-	            {A certain higher version \\(involving differential forms in degree $\geq 2$)};
+	            {...};
 	         }
@@
 	            \node[draw=red!40,anchor=base,text width=5cm] (s4)
-	            {Closed $2$-form on a smooth manifold, providing a geometric framework for classical mechanics};
+	            {...};
 	           }	
@@
 	\begin{tikzpicture}[overlay]
-        \path[->,draw=orange!40]<4-> (s1) edge [bend right] (t1);
-        \path[->,draw=blue!40]<5-> (s2) edge [bend left] (t2);
+        \path[->,draw=orange!40]<5-> (s1) edge [bend left] (t1);
+        \path[->,draw=blue!40]<4-> (s2) edge [bend left] (t2);
         \path[->,draw=green!40]<3-> (s3) edge [bend left] (t3);
-        \path[->,draw=red!40]<2-> (s4) edge [bend left] (t4);
+        \path[->,draw=red!40]<2-> (s4) edge [bend right] (t4);
 	\end{tikzpicture}
@@
 	\vfill
-	\onslide<1->{
+	\onslide<6->{
 	\begin{block}{Based on:}
 		 \emph{ \small
-			 Blacker, M., Ryvkin;
-			\textbf{Reduction of $L_\infty$-algebra of observables on multisymplectic manifolds}; 
-			\href{https://arxiv.org/abs/2206.03137}{arXiv:2206.03137}.
-		}
-		\\
-		 \emph{ \small
 			 M. , Ryvkin;
-			\textbf{Constraint algebras of multisyplectic observables}; 
-			\href{https://www.antoniomiti.it/teaching/Obs-Constraint-2024/}{In preparation}.
-		}		
+			\textbf{Multisymplectic observable reduction using constraint triples}; 
+			\href{https://arxiv.org/abs/2506.00234}{arXiv:2506.00234}.
+		 }.
+
 	\end{block}
@@
 			for the ``$\xi$th component'' of $\mu$.
+	\item All vector spaces are over a field of characteristic 0 (e.g. $\mathbb{R}$). 
+	\item We work in graded settings since forms and multivectors are naturally graded.
+
 }
-%------------------------------------------------------------------------------------------------
+%----------------------------------------------------+
 
-%------------------------------------------------------------------------------------------------
-\section{Motivation: Symplectic Reduction}
+%-----------------------------------------------------------%
+\subsection{Symplectic geometry}
 \checkpoint
-%------------------------------------------------------------------------------------------------
 
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+%- . - . - . - . - . - . - . - . - . - . - . - . - . +
 \begin{frame}{Symplectic geometry (mechanics flavour)}
@@
 }
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+%- . - . - . - . - . - . - . - . - . - . - . - . - . +
+
+%-----------------------------------------------------------%
+\subsection{Multisymplectic geometry}
+%-----------------------------------------------------------%
 
 %- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\subsection{Regular reduction} 
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%	
-\begin{frame}{Regular reduction in symplectic geometry}
-
-	\textbf{\color{UniGreen}Symplectic reduction:}~~
-	\\ 
-	{\it \small
-	Procedure associating to any (suitably regular) pair of symplectic manifold and Hamiltonian action another symplectic manifold of smaller dimension.}
-	\vfill
-
-	\pause
-
-	\begin{center}
-		\includegraphics[width=.5\textwidth]{Pictures/Reduction}	
-	\end{center}
-
-	\textbf{\color{UniGreen}In mechanics:}~~
-				\\
-			{\it \small
-				it embodies the process of restricting the dynamics of the system to the level sets of the conserved quantities pertaining to the symmetry group.		
-			}
-			\\[.2em]
-			\color{gray}\small( e.g. restricting to studying a point-like particle in a central potential by studying it in radial coordinates)
-
-\end{frame}
-\note[itemize]{
-	\item  \emph{(Credits to \href{https://math.gmu.edu/~cblacke/}{Casey Blacker} for the notes and to \href{https://arxiv.org/abs/1206.3302}{Christian Lessig} for the picture. See acknowledgements.}
-	\item  In classical mechanics symmetry reduction plays an important role. Mathematically, this is usually phrased in terms of Marsden-Weinstein reduction
-	\item {Symplectic Reduction} takes two inputs:
-	\\ 1. Hamiltonian $G$-space $(M,\omega,{\color{orange}G},{\color{blue}\mu})$
-	\\ 2. parameter ${\color{blue}\phi}\in\g^*$
-	\item The \emph{reduced space} is $M_\phi:={\color{blue}\mu^{-1}(\phi)}{\color{orange}/G_\phi}$.
-	\item (Marsden--Weinstein '74, Meyer '73) THM:\\
-		If $\mu^{-1}(\phi)\subset M$ is smooth and $G_\phi\curvearrowright \mu^{-1}(\phi)$ is free and proper, then there is a \textbf{unique symplectic form} $\omega_\phi\in\Omega^2(M_\phi)$ such that $\pi^*\omega_\phi = i^*\omega$.
-
-	\item Heuristic Approach to Reduction:
-	\\1. describe $G\curvearrowright M$ in terms of $\omega$ 	\hspace{1cm}
-	({\color{green}moment map $\mu$})
-	\\2. identify a distinguished reduced space \hspace{1cm}
-	({\color{green}reduction at $\mu=0$})
-	\\3. use the ambiguity in 1.\ to obtain a family of reduced spaces \hspace{1cm}
-	({\color{green}reduction at $\mu-\phi=0$, i.e.\ reduction at $\mu=\phi$}
-	\\
-	{\tiny Note: If $G_\phi\neq G$, then $\mu-\phi:M\to\g^*$ is not a moment map for either $G\curvearrowright M$ or $G_\phi\curvearrowright M$.}
-
-}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\begin{frame}{Reminder: momentum maps in symplectic geometry}\label{frame:symplecticmomaps}
-	Consider $\theta:G\curvearrowright M$ symplectic,~~ $\underline{\cdot}:\mathfrak{g}\to \mathfrak{X}(M)$ infinitesimal action.
-	\vfill
-
-	\begin{columns}[T]
-		\setlength{\belowdisplayskip}{5pt}
-		\begin{column}{.50\linewidth}
-			%
-			\centering \it
-			\onslide<2->{
-				\begin{defblock}[Equivariant moment map]
-					Smooth map $$\mu:M\to \mathfrak{g}^\ast$$
-					such that:
-					\begin{itemize}
-						\item[i.] $d\langle \mu,\xi\rangle = -\iota_{\underline{\xi}}\omega$ 
-						~\qquad, $\forall \xi \in \mathfrak{g}$
-						\item[ii.] $\mu \circ \theta_g = Ad_g^\ast \circ \mu$
-						 \qquad\small, $\forall g \in G$
-					\end{itemize}
-				\end{defblock}
-			}
-		\end{column}	
-		%
-		\onslide<2->{\vrule{}}
-		%
-		\begin{column}{.50\linewidth}
-			\onslide<3->{			
-				\begin{defblock}[Comoment map]
-					Linear map $$\widetilde{\mu}: \mathfrak{g}\to C^\infty(M,\omega)$$
-					such that:
-					\begin{itemize}
-						\item[i.] $d\widetilde{\mu}(\xi) = -\iota_{\underline{\xi}}\omega$ 
-						\qquad~\small, $\forall \xi \in \mathfrak{g}$
-						\item[ii.] $\widetilde{\mu}([\xi,\eta]) = \lbrace\widetilde{\mu}(\xi),\widetilde{\mu}(\eta)\rbrace$ \small, $\forall \xi,\eta \in \mathfrak{g}$
-					\end{itemize}
-				\end{defblock}
-			}
-		\end{column}	
-	\end{columns}	
-	%
-	\pause
-	\vspace{1em}
-	%
-	\begin{columns}[]
-		\setlength{\belowdisplayskip}{5pt}
-		\begin{column}{.40\linewidth}
-			%
-			\centering \it
-			\onslide<5->{
-				\begin{upshotblocktitle}[Duality]
-					\begin{displaymath}
-						\mu(x) : \mathfrak{\xi} \mapsto \widetilde{\mu}(\xi)\big\vert_x
-					\end{displaymath}
-					%
-					\emph{
-					\small
-					"duality wrt. the currying operation"					
-					}
-				\end{upshotblocktitle}
-			}
-		\end{column}	
-		%
-		%
-		\begin{column}{.60\linewidth}
-			\onslide<4->{			
-				\begin{upshotblocktitle}[$\widetilde{\mu}$ as a lift]
-					\begin{displaymath}
-						\begin{tikzcd}[ampersand replacement = \&]
-						 \& C^\infty(M,\omega) \ar[d,"\vHam"]
-						 \\
-						 \mathfrak{g} \ar[ur,dashed,sloped,"\widetilde{\mu}"]\ar[r,"\underline{\cdot}"'] \& \mathfrak{X}(M)
-						\end{tikzcd}
-					\end{displaymath}
-					%
-					\emph{
-					\small
-					"it is a lift (in the Lie category) of the infinitesimal action by the assigment of hamiltonian v.fields."					
-					}
-				\end{upshotblocktitle}
-			}
-		\end{column}	
-	\end{columns}		
-\end{frame}
-\note[itemize]{
-		\item Moment maps are instrumental to the proper formalization of reduction in symplectic geometry.
-		\item consider an action preserving the symplectic form.
-		\item[-] $\langle \cdot, \cdot \rangle$ is the natural pairing of $\mathfrak{g}$ and $\mathfrak{g}^\ast$.
-			\item[-] $\theta_g$ is the diffeomorphism associated to $g\in G$ via $\theta:G\curvearrowright M$
-			\item[-] $Ad^\ast_g$ is the coadjoint action $G\curvearrowright \mathfrak{g}^\ast$
-		\item The moment map can be reexpressed as a comomentum map.
-		\item Observe that ii. on the left always implies ii. on the right. The converse is trure only if $G$ is connected.
-		\item $G\curvearrowright M$ is said "Hamiltonian" (see slide \ref{frame:gisthamaction} in appendix) iff $\exists$ comoment map $\widetilde{\mu}$.
-		\item \emph{moment map: Describe ${\color{orange}G\curvearrowright M}$ in terms of $\color{blue}C^\infty(M)\to\X(M)$.}
-		\begin{center}
-		\begin{tikzpicture}[scale=1.5]
-			\node[orange] (A) at (0,0) {$\g$};
-			\node[gray] (A1) at (0,-.3) {$\xi$};
-			\node[blue] (B) at (1,1) {$C^\infty(M)$};
-			\node[gray] (B2) at (1.55,1) {$f$};
-			\node[orange] (C) at (1,0) {$\X(M)$};
-			\node[gray] (C1) at (1,-.3) {$\underline\xi$};
-			\node[gray] (C2) at (1.55,0) {$X_f$};
-
-			\path[->,blue,dashed] (A) edge node[above left] {$\langle\mu,\cdot\,\rangle$} (B);
-			\path[->,orange] (A) edge (C);
-			\path[->] (B) edge (C);
-			\path[|->,gray] (A1) edge (C1);
-			\path[|->,gray] (B2) edge (C2);
-
-			\begin{scope}[xshift=3cm]
-				\node at (-.32,.8) {as Lie algebras};
-				\node at (-.13,.2) {i.e., {\color{blue}$\mu_\xi$} generates {\color{orange}$\underline\xi$}};
-			\end{scope}
-		\end{tikzpicture}
-
-			\footnotesize		(\emph{moment map:} ${\color{blue}\mu:M\to\g^*}$, 
-		 \emph{Hamiltonian $G$-space:} 	$(M,\omega,G,\mu)$)
-		\end{center}
-		\item
-		 $\alpha\mapsto X_\alpha$ is a homomorphism of Leibniz algebras:
-		$$\d\{\alpha,\beta\} = \d\L_{X_\alpha}\beta = \L_{X_\alpha}\iota_{X_\beta}\omega = \iota_{[X_\alpha,X_\beta]}\omega ~{\color{black!80} \implies}~
-		X_{\{\alpha,\beta\}} = [X_\alpha,X_\beta]$$
-}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\begin{frame}[fragile]{Marsden-Weinstein-Meyer reduction}
-	\begin{thmblock}[Marsden-Weinstein reduction \cite{MarsdenWeinstein74}]
-		\vspace{-.4em}\hspace{-1em}
-		\begin{tabular}{l p{14cm}}
-			Given: & $(M,\omega)$ symplectic
-			\\
-			& $\color{orange}G\curvearrowright M$ symplectic with equivariant momap. $\mu:M\to \mathfrak{g}^*$
-			\\[.2em]
-			Assume: & ${\color{blue}\phi} \in \mathfrak{g}^*$ regular value of $\mu$ 
-			\qquad\quad \footnotesize \textcolor{gray}{($\Rightarrow$ $\mu^{-1}(\phi)\hookrightarrow M$ smooth embedding)}
-			\\
-			& $G_\phi\curvearrowright \mu^{-1}(\phi)$ free and proper
-			\quad \footnotesize \textcolor{gray}{($\Rightarrow$ $\mu^{-1}(\phi)/G_\phi$ smooth manifold)}
-			\\[.4em]
-			Then: & \textbf{$\exists!$ symplectic structure} $\omega_\phi$ in $M_\phi:={\color{blue}\mu^{-1}(\phi)}{\color{orange}/G_\phi}$ \\
-			& s.t. $\pi^\ast \omega_\phi = j^\ast \omega$ 
-			\qquad {\footnotesize with $j:\mu^{-1}(\phi) \hookrightarrow M$ and $\pi:\mu^{-1}(\phi)\twoheadrightarrow M_\mu$}
-		\end{tabular}
-		\vspace{-.4em}
-	\end{thmblock}
-	%
-	\vfill
-	\begin{center}
-	\begin{tikzpicture}[scale=2]
-		\node[blue] (A) at (0,0) {$\mu^{-1}(\phi)$};
-		\node[gray] (A1) at (0,.3) {$i^*\omega$};
-		\node[gray] (A2) at (-.6,0) {$\pi^*\omega_\phi$};
-		\node[blue] (B) at (1,0) {$M$};
-		\node[gray] (B1) at (1,.3) {$\omega$};
-		\node[orange] (C) at (0,-.8) {$M_\phi$};
-		\node[gray] (C2) at (-.6,-.8) {$\omega_\phi$};
-
-		\path[right hook->,blue] (A) edge node[above] {$i$} (B);
-		\path[orange,->] (A) edge node[left] {$\pi$} (C);
-		\begin{scope}[xshift=-1.8cm]
-			\node[blue] at (0,0) {\small restrict to $\{\mu=\phi\}$};
-			\node[orange] at (.15,-.4) {\small quotient by $G_\phi$};
-		\end{scope}
-	\end{tikzpicture}
-	\end{center}
-	\pause
-	\vfill
-	\centering
-	The action of $G$ on $\mu^{-1}(0)$ is free and proper $\Rightarrow$ $0$ is reg. val. of $\mu$
-
-\end{frame}
-\note[itemize]{
- \item 
-	Let $(M,\omega)$ symplectic, $G\circlearrowright M$ be a Lie group action\pause and $\mu:M\to \mathfrak g^*$ such that: 
-	\item  $\mu$ is a momentum, i.e. the infinitesimal action $\xi\mapsto \underline\xi:\mathfrak g\to \mathfrak X(M)$ of $G$ satisfies $X_{\langle\mu,\xi\rangle}=\underline \xi$. 
-	\item $\mu$ is $G$-equivariant, i.e. $\mu(gm)=Ad^*_g\mu(m)$ 
-	\item Then $\exists!$ symplectic form $\omega_r$ on $M_r=\frac{\mu^{-1}(0)}{G}$ such that $\pi^*\omega_r=i^*\omega$.
-%% https://q.uiver.app/#q=WzAsMyxbMCwwLCJNIl0sWzMsMCwiXFxtdV57LTF9KDApIl0sWzYsMCwiTV9yIl0sWzEsMCwiaVxcXFwgXFxzdWJzdGFja3tpbmNsdXNpb25+b2Z+c3Vic3BhY2V9IiwyLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoiaG9vayIsInNpZGUiOiJib3R0b20ifX19XSxbMSwyLCJcXHBpXFxcXCBcXHN1YnN0YWNre3F1b3RpZW50fmJ5fnJlbGF0aW9ufSJdXQ==
-%\[\begin{tikzcd}
-%	M &&& {\mu^{-1}(0)} &&& {M_r}
-%	\arrow["\begin{array}{c} i\\ \substack{inclusion~of~subspace} \end{array}"', hook', from=1-4, to=1-1]
-%	\arrow["\begin{array}{c} \pi\\ \substack{quotient~by~relation} \end{array}", two heads, from=1-4, to=1-7]
-%\end{tikzcd}\]
-
-}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\subsection{Singular reduction}
-\begin{frame}{Symplectic singular reduction schemes}
-	\begin{block}{The gist of singular reduction}
-		 \begin{itemize}
-			 \item[-] when $\mu$ is singular (i.e. $\mu^{-1}(0)$ is not a mfd.), the (geometrically) reduced space may not exist.
-			 \item[-] a \emph{singular reduction scheme} is a procedure to construct a "reduced" algebra of observable out of the given data
-			 \item[-] such that it corresponds to the algebra of observable of the reduced manifold in the regular case.
-		 \end{itemize}
-	\end{block}
-	 %
-	 \pause
-	 \vfill
-	 %
-	\begin{thmblock}[Sniatycki-Weinstein reduction \cite{SniatyckiWeinstein83}]
-		\vspace{-.4em}\hspace{-1em}
-		\begin{tabular}{l p{14cm}}
-			Given: & $(M,\omega)$ symplectic
-			\\
-			& $G\curvearrowright M$ symplectic with equivariant momap. $\mu:M\to \mathfrak{g}^*$
-			\\[.4em]
-			Then: & 
-			$\displaystyle \left[\sfrac{C^\infty(M)}{I_\mu}\right]^G$
-			admits a Poisson algebra structure 
-			\footnote{$I_\mu$ = associative ideal generated by $\widetilde{\mu}(\g)$}			
-			\\
-			& it agrees with the M--W reduction in the regular case.		
-		\end{tabular}
-		\vspace{-.4em}
-	\end{thmblock}
- \end{frame}
-\note[itemize]{
- \item Let $(M,\omega,G,\mu)$ be a symplectic Hamiltonian $G$-space.
- \item The \emph{momentum ideal} is the associative ideal $I_\mu\subset C^\infty(M)$ generated by the momenta $\mu_{\xi}$ for any $\xi\in \mathfrak{g}$.
-		Namely
-		\[
-			I_\mu 
-			= 
-			\Big\langle \mu_\xi \Big\rangle_{\xi \in \mathfrak{g}}^{\text{\tiny asso.}} 
-			=
-			\left\{
-				\left.
-					\sum_{i=1}^n f_i ~ \mu_{\xi_i}
-				\right|~
-					f_i \in C^\infty(M),~ \xi_i\in \mathfrak{g},~  1 \leq i \leq n
-			\right\}
-		\]
-
- \item The \emph{\'Sniatycki--Weinstein reduction} is the Poisson algebra
-		\[
-			\left(C^\infty(M)/I_\mu\right)^G.
-		\]
-
-}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\subsection{Constraints Algebras}
-\begin{frame}[fragile]{Attempting algebraic reduction naively}
-When the action is not 'free and proper', we can try to mimic this directly using the function algebras:
-% https://q.uiver.app/#q=WzAsNixbMCwwLCJNIl0sWzEsMCwiXFxtdV57LTF9KDApPVMiXSxbMywwLCJNX3IiXSxbMCwxLCJDXlxcaW5mdHkoTSkiXSxbMSwxLCJDXntcXGluZnR5fShTKT1cXGZyYWN7Q157XFxpbmZ0eX0oTSl9e0lfe1N9fSJdLFszLDEsIkNee1xcaW5mdHl9KE1fcik9Q15cXGluZnR5KFMpXkciXSxbMSwyLCJcXHN1YnN0YWNre3F1b3RpZW50fSIsMCx7InN0eWxlIjp7ImhlYWQiOnsibmFtZSI6ImVwaSJ9fX1dLFszLDQsIlxcc3Vic3RhY2t7cXVvdGllbnR9IiwwLHsic3R5bGUiOnsiaGVhZCI6eyJuYW1lIjoiZXBpIn19fV0sWzAsMSwiXFxzdWJzdGFja3tyZXN0cmljdGlvbn0iLDAseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dLFs0LDUsIlxcc3Vic3RhY2t7cmVzdHJpY3Rpb259IiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoic3F1aWdnbHkifX19XV0=
-\[\begin{tikzcd}
-	M & {\mu^{-1}(0)=S} && {M_r} \\
-	{C^\infty(M)} & {C^{\infty}(S):=\frac{C^{\infty}(M)}{I_{S}}} && {C^{\infty}(M_r)=C^\infty(S)^G}
-	\arrow["{\substack{restriction}}", squiggly, from=1-1, to=1-2]
-	\arrow["{\substack{quotient}}", two heads, from=1-2, to=1-4]
-	\arrow["{\substack{quotient}}", two heads, from=2-1, to=2-2]
-	\arrow["{\substack{restriction}}", squiggly, from=2-2, to=2-4]
-\end{tikzcd}\]
-
-where $I_S=\{f\in C^{\infty}(M)~|~f|_S=0\}$.
-\pause 
-\vfill
-Equivalently:
-
-% https://q.uiver.app/#q=WzAsMyxbMCwwLCJDXlxcaW5mdHkoTSkiXSxbMiwwLCJOX1M9XFx7Zn58fiBmXFxpbiBDXlxcaW5mdHkoTSl8X1N+fkdcXG1hdGhybXstaW52YXJpYW50fVxcfSJdLFs0LDAsIlxcZnJhY3tOX1N9e0lfU30iXSxbMCwxLCJcXHN1YnN0YWNre3Jlc3RyaWN0aW9ufSIsMCx7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6InNxdWlnZ2x5In19fV0sWzEsMiwiXFxzdWJzdGFja3txdW90aWVudH0iLDAseyJzdHlsZSI6eyJoZWFkIjp7Im5hbWUiOiJlcGkifX19XV0=
-\[\small\begin{tikzcd}
-	{C^\infty(M)} && {N_S=\{f~|~ f\in C^\infty(M)|_S~~G\mathrm{-invariant}\}} && {\frac{N_S}{I_S}}
-	\arrow["{\substack{restriction}}", squiggly, from=1-1, to=1-3]
-	\arrow["{\substack{quotient}}", two heads, from=1-3, to=1-5]
-\end{tikzcd}\]
-\pause
-\vfill
-
-\begin{alertblock}{Problem}
-	$C^\infty(S)^G=\frac{N_S}{I_S}$ is not a Poisson algebra in general.
-\end{alertblock}
-(when constraints not first class, cf. Dirac reduction)
-\end{frame}
-\note[itemize]{
-	\item \emph{(Credits to \href{https://www.ryvkin.eu/}{Leonid Ryvkin} for the tex code of this slide.)}
-}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\begin{frame}{Constraint Algebras} 
-	\begin{block}{Idea:}
-	    \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
-			\item[-] Both regular/geometric and singular/algebraic reduction are 2-steps procedures (1. restrict 2. quotient).
-			\item[-] Let's work in a category where all data needed for the reduction are bundled together in a suitable categorical objects. {\tiny (To avoid pathologies arising from these steps)}
-	    \end{itemize}
-	\end{block}
-	\pause
-	\vfill
-	\begin{defblock}[Constraint algebra triples \cite{Dippell2023}]
-		A (strong embedded) constraint algebra $\mathcal A$ is given by a triple $(\mathcal A_T, \mathcal A_N, \mathcal A_0)$, where
-		\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
-			\item[•] $\mathcal A_T$ is an algebra \emph{("total space")}
-			\item[•] $\mathcal A_N\subset \mathcal A_T$ a subalgebra  \emph{("normal space")}
-			\item[•] $\mathcal A_0\subset \mathcal A_N$ a two-sided ideal in $\mathcal A_T$ \emph{("zero space")}
-		\end{itemize}
-	\end{defblock}
-	\vfill
-	\pause
-	\begin{exblock}
-		Let $S$ be a closed set. Algebraically, we describe $C^\infty(S)$ by $\frac{C^\infty(M)}{I_S}$.
-		\\ 
-		We can think of it as the constraint triple:
-		$$
-			\mathcal A=(\mathcal A_T,\mathcal A_N,\mathcal A_0)=(C^\infty(M),C^\infty(M), I_S)
-		$$
-	\end{exblock}
-
-\end{frame}
-\note[itemize]{
-	\item  triples of the type (algebra , subalgebra, ideal).
-	\item After \cite{Dippell2023} we call such triples { \bf constraint triples} and their parts \emph{total space, normal space, zero space}.
-	\item It is a (strong) constraint algebra if $\mathcal A_0\subset \mathcal A_N\subset \mathcal A_T$ subalgebras and $\mathcal A_0\subset \mathcal A_T$ ideal.
-}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\begin{frame}{Other approaches to singular reduction}
- 	Many singular reduction schemes adhere to this pattern!
- 	\vfill
- 	\pause
-\begin{table}[]
-	\begin{tabular}{l|l|l||l}
-		algebra $\mathcal{A}_T$ & subalgebra $\mathcal{A}_N$ & ideal $\mathcal{A}_0$ & comment \\
-		\hline
-
-		$C^\infty(M)$&      $N_S$     &   $I_S$   &  $\substack{S=\mu^{-1}(0),~ I_S=\{f~|~f|_S=0\}}$ \\
-			&&&  $\substack{N_S= \{ f | gf-f\in I_S \forall g\in G\}}$ \\
-	& & & \color{red} not Poisson \\ 
-	\hline	\pause
-	$C^\infty(M)$&   $F_S$         &   $I_S$   &  $\substack{F_S=\{f~|~\{f,I_S\}\subset I_S\}}$ \\
-	& & & \color{red} if $I_S\subset F_S$\\
-	\hline \pause
-
-	$C^\infty(M)$&   $C^\infty(M)^G$         &   $(I_S)^G$   &  $\substack{C^\infty(M)^G=\{f~|~gf=f\forall g\in G\}}$ \\
-	\hline \pause
-		$C^\infty(M)$&   $C^\infty(M)^G$         &   $(I_\mu)^G$   & $\substack{I_\mu=\{\sum_{i=1}^k f_i\langle \mu,\xi_i\rangle|~f_i\in C^\infty(M), \xi_i\in \mathfrak g\}}$\\
-		\hline \pause
-	$C^\infty(M)$&      $N_\mu$     &   $I_\mu$   & $\substack{N_\mu= \{ f | gf-f\in I_\mu \forall g\in G\}}$ \footnote{When $G$ connected $N_\mu=N(I_\mu):=\{f~|~\{f,I_\mu\}\subset I_\mu\}$.}\\
-	\hline
-
-	\end{tabular}\pause
-\end{table}
-	\vfill
-	{\bf Remarks }names in order: 'naive' , Dirac, Sniatycki, Arms-Cushman-Gotay, Sniatycki-Weinstein.
-
-\end{frame}
-\note[itemize]{
-	\item \emph{(Credits to \href{https://www.ryvkin.eu/}{Leonid Ryvkin} for the tex code of this slide.)}
-}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%------------------------------------------------------------------------------------------------
-\section{Multisymplectic Geometry}
-\checkpoint	
-%------------------------------------------------------------------------------------------------
-
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\subsection{Multisymplectic manifolds}
 \begin{frame}{From symplectic to {multi}symplectic} 
@@
 
+%-----------------------------------------------------------%
+\subsection{Higher Observables}
+%-----------------------------------------------------------%
+
 %- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\subsection{Higher Observables}
 \begin{frame}{Observables in $n$-plectic geometry}
@@
 				\end{displaymath}			
-				can be "completed" to a \\ $L_\infty-algebra$.
+				can be "completed" to a \\ $L_\infty$-algebra.
 			\end{thmblock}
@@
 		\item  descend to $\Omega^{n-1}_{ham}(M) / {\color{orange}\d\hspace{1pt}\Omega^{n-2}(M)}$, hence getting a Lie algebra;
-		\item Incorporate the {\color{orange}discrepancy} as part of the data of the space of observables $ 
-				L_\infty(M,\omega) = \Omega_{ham}^{n-1}(M)\oplus{\color{orange}\Omega^{\leq n-2}(M)}$.
+		\item Incorporate the {\color{orange}discrepancy} as part of the data of the space of observables 
+				$L_\infty(M,\omega) = \Omega_{ham}^{n-1}(M)\oplus{\color{orange}\Omega^{\leq n-2}(M)}$.
 			%a \textbf{homotopy Lie algebra} or \textbf{$L_\infty$-algebra}.
@@
  \href{https://www.sciencedirect.com/science/article/pii/S0393044018301189}{Invitation to Multisymplectic Geometry} \cite{RYVKIN20199}\	, the equation highlighted in orange, which defines Hamiltonian forms, is referred to as the Hamilton--DeDonder--Weyl equation---a somewhat imaginative extension compared to its traditional formulation in \href{https://en.wikipedia.org/wiki/De_Donder\%E2\%80\%93Weyl_theory}{De Donder--Weyl theory}.
+	\item a **Hamiltonian $(k-1)$-form** $\alpha \in \Omega^{k-1}(M)$ is one that admits a vector field $X$ (a *Hamiltonian field*) satisfying $i_X\omega = d\alpha$.
+We call the pair $(X,\alpha)$ a *Hamiltonian pair*.
+	\item Just as in the symplectic case $(k=1)$ where $\alpha$ is a 0-form (function) and $X$ its Hamiltonian vector field, here $\alpha$ plays the role of the observable (often called an $(k-1)$-form observable).
+	\item The collection of all such Hamiltonian forms (for various degrees) can be organized into a graded object, and Rogers showed that it carries a canonical **$L_\infty$-algebra structure** .
+    \item  **Example:** For a 3-plectic manifold (degree 3 form $\omega$), one has Hamiltonian 1-forms: each 1-form $\alpha$ for which there exists $X$ with $i_X\omega = d\alpha$.
+These Hamiltonian pairs $(X,\alpha)$ form the degree-0 part of the observables.
+In addition, ordinary functions (0-forms) can be viewed as Hamiltonian 0-forms (with $X$ such that $i_X\omega = d(0) = 0$), and perhaps higher-degree observables appear up to degree 1 in this case.
+The resulting $L_\infty$ has non-trivial brackets of arity up to 2 (making it a *Lie 2-algebra* of observables, a kind of higher Poisson algebra).
+The 2-bracket extends the Poisson bracket, and a 3-bracket arises measuring the failure of the Jacobi identity (something that vanishes in the symplectic case but not in general).
+For a 4-plectic form, one would get a Lie 3-algebra, etc.
 }
@@
 
+%-----------------------------------------------------------%
 %------------------------------------------------------------------------------------------------
-\section{Multisymplectic observables reduction}
-\checkpoint	
-%------------------------------------------------------------------------------------------------
-
- %- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\subsection{General idea}
-\begin{frame}{Singular Reduction: Roadmap}
-	%
-	\begin{block}{Data:}
-			\begin{itemize}
-				\item $(M,\omega)$ multisymplectic,
-				\item $S\subset M$ closed subset (possibly singular),
-				\item $I_S$ the ideal of smooth functions vanishing on $S$,
-				\item $F\subset \mathfrak X(M)$ a Lie subalgebra s.th. $F(I_S)\subset I_S$.
-			\end{itemize}
-	\end{block}
-	%
-	\vfill
-	\pause
-	%
-	\begin{block}{Goal:}
-		\begin{itemize}
-			\item Identify a constraint triple of the type (algebra , subalgebra, ideal) pertaining to the $L_\infty$ algebra of observables.
-		\end{itemize}
-	\end{block}
-	%
-	\vfill
-	\pause
-	%
-	\begin{block}{Strategy:}
-		\begin{enumerate}
-			\item Define smooth fields/forms \emph{tangent to $N$},
-			\item define smooth fields/forms \emph{vanishing along $N$},
-			\item define \emph{reducible fields} requiring the preservation of the vanishing objects,
-			\item define \emph{reducible forms} requiring their conservation w.r.t. the infinitesimal action,
-			\item define \emph{reducible and vanishing observables},
-			\item \textbf{quotient}
-		\end{enumerate}
-	\end{block}
-
-\end{frame}
-\note[itemize]{
-	\item Remark: the following singular reduction scheme is slightly different from what we proposed in our paper \cite{Blacker2022}.
-}
- %- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
- %- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\begin{frame}{Translating geometry to algebra}
-
-	\vfill
-	\begin{table}[]
-		\begin{tabular}{l|l|l}
-		 geometry & algebra & translation \\
-			\hline	
-		smooth manifold $M$ & comm. algebra $\mathcal A_T$  	& $\mathcal A_T=C^{\infty}(M)$\\ \hline\pause
-		vector fields $\mathfrak X(M)$ & derivations $\Der(\mathcal A_T)$ &  $\Der(C^\infty(M))=\mathfrak X(M)$\\ \hline\pause
-		closed subset $S\subset M$ & ideals $\mathcal A_0\subset \mathcal A_T$ & $\mathcal A_0=I_S=\{f~|~f|_S=0\}$ \\ \hline\pause
-		action $G\circlearrowleft M$ & Lie algebra map & infinitesimal generators\\
-		 of connected group &$\underline{\cdot}:\mathfrak g\to \Der(\mathcal A_T)$ & of the action \\ \hline \pause
-		 $G$ action preserves $S$ & $\underline \xi(I_S)\subset I_S$ $\forall \xi\in\mathfrak g$& \color{red} Careful! Not equivalent! 
-		 \\ \hline
-		\end{tabular}
-	\end{table}
-	\vfill
-
-\end{frame}
-\note[itemize]{
-	\item \emph{(Credits to \href{https://www.ryvkin.eu/}{Leonid Ryvkin} for the tex code of this slide.)}
-	\item {Warning}
-	$\partial_x$ is algebraically preserving $S=[0,1]\subset \mathbb R=M$, even though the flow leads out of the set.
-}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\subsection{Higher Observables Constraint Algebra}
-\begin{frame}[shrink]{Higher Observables Constraint Algebra}
-	\begin{defpropblock}[$L_\infty$-observables constraint algebra]
-		The following $L_\infty$ algebra\footnote{ 
-			\vspace{-1.75em}
-			\begin{align*}
-				\small \text{where:\quad} &\Omega_0^k ~:=&\{\alpha \in \Omega^k(M)~|~\alpha(v_1,...,v_k)\in  I_S~\forall v_i\in \X_N\} 
-				\\
-				& \mathfrak{X}_N ~:=& 
-				\left\lbrace
-					v \in \X(M)
-				~\left\vert~
-					\begin{array}{l}
-						\L_v (I_N) \subseteq I_N	\\		
-						\L_v (C^{\infty}(M) F) \subseteq C^{\infty}(M) F + I_S\mathfrak X(M)
-					\end{array}
-				\right\rbrace\right.
-			\end{align*} 
-		} form a constraint triple
-		\begin{align*}
-			\Ham_T =&~ L_\infty(M,\omega) \\[1em]
-			\Ham_N =&~
-			{\small
-			\left\lbrace
-			\begin{array}{l}
-				\alpha\in \Omega^{\leq n-2}(M) \\\mathrm{\small, respectively}\\	
-				(\alpha,X) \in \Omega^{n{-}1}(M) \oplus\mathfrak X(M)
-			\end{array}
-			~\left\vert~
-			\begin{array}{l l}
-				\iota_\xi \alpha \in \Omega_0 &\\
-				\L_\xi\alpha \in \Omega_0&~\forall \xi \in F\\
-				\hline
-				\iota_X \omega = -d \alpha &\\
-				X(I_S)\subset I_S &\\
-				\L_\xi X \in C^{\infty}(M) F + I_S\mathfrak X(M)
-				&~\forall \xi \in F\\
-			\end{array}
-			\right.
-			\right\rbrace 
-			}
-			\\[1em]
-			\Ham_0 =&~
-		{\small
-			\left\lbrace
-			\begin{array}{l}
-				\alpha\in \Omega^{\leq n-2}(M) \\\mathrm{\small, respectively}\\	
-				(\alpha,X) \in \Omega^{n{-}1}(M) \oplus\mathfrak X(M)
-			\end{array}
-			~\left\vert~
-			\begin{array}{l}
-				\alpha \in \Omega_0\\
-				\hline
-				\iota_X \omega = -d \alpha\\
-				X \in C^{\infty}(M) F + I_S\mathfrak X(M)
-			\end{array}
-			\right.
-			\right\rbrace
-		}
-		\end{align*}
-	\end{defpropblock}
-	\vfill
-	\pause
-	{\centering \color{red} $\Rightarrow$  the subquotient ${\Ham_N} / {\Ham_0}$ forms an $L_\infty$-algebra!}
-\end{frame}
-\note[itemize]{
-	\item 	
-	\begin{defblock}[Reducible v.fields ]
-			\begin{displaymath}
-				\mathfrak{X}_N ~:=
-				\left\lbrace
-					v \in \X(M)
-				~\left\vert~
-					\begin{array}{l}
-						\L_v (I_N) \subseteq I_N	\\		
-						\L_v (C^{\infty}(M) F) \subseteq C^{\infty}(M) F + I_S\mathfrak X(M)
-					\end{array}
-				\right\rbrace\right.
-			\end{displaymath}
-			e.g. $F=\X_g$ is the $C^\infty(M)$-module generated by the fundamental distribution of an acting group.
-	\end{defblock}	
-	%
-	\begin{defblock}[Reducible forms ]
-		\begin{displaymath}
-			\Omega_{N} :=
-			\left\lbrace
-				\alpha \in \Omega(M)
-			~\left\vert~
-				\begin{array}{l r}
-					\L_\underline{\xi} \,\alpha \in \Omega_0	\\		
-					\iota_\underline{\xi} \,\alpha \in \Omega_0	& \forall \xi \in \g				\end{array}
-			\right\rbrace\right.
-		\end{displaymath}	
-	\end{defblock}	
-	%
-	%
-	\begin{defblock}[Reducible Hamiltonian forms]
-		\begin{displaymath}
-			(\Omega(M)_{ham}^{n-1})_{[N]} :=
-			\left\lbrace
-				\alpha \in \Omega(M)_{ham}^{n-1}
-			~\left\vert~
-				\begin{array}{l r}
-					\alpha \text{ is a reducible form} \\
-					\vHam_\alpha \text{ is a reducible v.field}
-				\end{array}
-			\right\rbrace\right.
-		\end{displaymath}	
-	\end{defblock}	
-}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\subsection{Conclusions}
-%TODO questa slide non è leggibile!
-\begin{frame}{Conclusions}
-	\begin{itemize} 
-\item Constraint triples permit to do differential geometry/ Cartan calculus on singular subquotients,\\ ... in particular constructing observable algebras on them.\pause
-\item Even if $\omega$ is non-degenerate, $\omega_r$ could degenerate, forcing us to pull along the Hamiltonian vector fields explicitly\pause
-\item Coomentum maps in the sense of the Leibniz structure seem better for reducing than $L_\infty$-comomenta \pause
-%\item The algebraic approach can treat algebroid / singular foliation symmetries and remembers vanishing orders a the singularities. \pause
-\item The reduction seems to give something novel even in the symplectic case 
-\begin{thmblock}[Multisymplectic reduction in the symplectic case \cite{Blacker2022}]
-Let $Q=\{f~|~ f|_S=0\rm{~and~} df|_S=0\}$ Then the $L_\infty$-reduction is:
-$$
-\frac{N(I_S)\cap N(I_\mu+Q)}{I_\mu+Q}
-$$
-\end{thmblock}
-
-	\pause
-			\vfill
-		  \centering 
-		  {\Huge\color{red} 
-		  \emph{Thank you for your attention!}}
-			\vfill
-	\end{itemize}
-\end{frame}
-\note[itemize]{
-	\item
-}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%------------------------------------------------------------------------------------------------
-% APPENDIX
-%------------------------------------------------------------------------------------------------
-\appendix
-%------------------------------------------------------------------------------------------------
-
-\section{Supplementary Material}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\begin{frame}
-	\begin{center}
-	\Huge\emph{Supplementary Material}
-	\end{center}
-\end{frame}
-\note[itemize]{
-	\item
-}
-\addtocounter{framenumber}{-1}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\begin{frame}[fragile]{MS geometry and classical field mechanics}\label{Frame:Ms-Field-Mechanics}
-		Consider a smooth manifold $Y$,
-		\begin{columns}
-			\hfill
-			\begin{column}{.5\linewidth}
-				\emph{Multicotangent bundle} $\bigwedge = \bigwedge^n T^\ast Y$\\
-				is naturally $n$-plectic
-			\end{column}
-			\begin{column}{.4\linewidth}
-				\[
-				\begin{tikzcd}
-					\Lambda \ar[d,"\pi"'] & T \Lambda \ar[d,"T \pi"] \ar[l] \\
-					Y								& T Y \ar[l]
-				\end{tikzcd}	
-				\]
-			\end{column}
-		\end{columns}
-	\pause
-	\begin{defblock}[Tautological $n$-form]
-		$\theta \in \Omega^n(\Lambda)$ such that:
-		\begin{displaymath}
-		\begin{split}
-			\left[ \iota_{u_1 \wedge \ldots \wedge u_n} \theta \right]_\eta 
-			&= \iota_{(T \pi)_\ast u_1 \wedge \ldots \wedge (T \pi)_\ast u_n} \eta \\
-			&= \iota_{u_1 \wedge \ldots \wedge u_n} \pi^\ast \eta 
-			\qquad \qquad \forall \eta \in \Lambda \, , \: \forall u_i \in T_\eta \Lambda 		
-		\end{split}
-		\end{displaymath}
-	\end{defblock}
-	\vfill
-	\begin{columns}
-		\begin{column}{.6\linewidth}
-			\begin{defblock}[Tautological (multisymplectic) (n+1)-form]
-				$$\omega := d \theta$$
-			\end{defblock}
-		\end{column}
-		\begin{column}{.4\linewidth}
-		 	\begin{claimblock}$\omega$ is not degenerate.\end{claimblock}	
-		\end{column}
-	\end{columns}	
-	\pause
-	\begin{keywordblock}
-		\begin{tabular}{|c|c|c|}
-			\hline 
-			point-particles mechanics & $\rightsquigarrow$ & classical fields mechanics \\
-			%(finite discrete DOF) & & (finite dimensional continuous DOF) \\
-			\hline 
-			symplectic & $\rightsquigarrow$ & multisymplectic \\ 
-			\hline 
-			Observables (Poisson) algebra & $\rightsquigarrow$ & Observables $L-\infty$ algebra
-			 \\ 
-			\hline 
-			Co-moment map & $\rightsquigarrow$ & Homotopy co-momentum map \\ 
-			\hline 
-		\end{tabular} 
-	\end{keywordblock}
-
-\end{frame}
-\note[itemize]{
-	\item This example is significant from the perspective of geometric classical field theory:
-		\begin{displaymath}
-			\frac{\text{classical mechanics}}{\text{symplectic geo.}} =
-			\frac{\text{classical field mechanics}}{\text{multisymplectic geo.}}
-		\end{displaymath}
-	\item Multicotangent bundle is the \emph{Higher analogue} of the cotangent bundle.
-	(but it is not yet the analogue of a \emph{phase space}.)
-\item The multiphase space is the sub-bundle of $n$-forms vanishing when contracted with 2 vertical fields.
-  	\item The reason why this sub-bundle has a particular role is that it can be proved to be isomorphic to a suitable dual of the first Jet bundle.
-  	\item For further details see Gotay et al.
-\href{https://arxiv.org/abs/physics/9801019}{arXiv:physics/9801019}.
-For a pictorial representation of all the structures involved in the geometric mechanics of I order classical field theories see appendix, pag: \ref{frame:Gimmsy}.
-}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\begin{frame}[t]{Symmetries in \textbf{multisymplectic geometry}}
-	Consider a Lie algebra action $v:\mathfrak{g} \to \mathfrak{X}(M)$  preserving the $n$-plectic form $\omega$,
-	\vfill
-
-	\vspace{-1em}
-	\begin{columns}[T]
-		\setlength{\belowdisplayskip}{5pt}
-		\begin{column}{.50\linewidth}
-			%
-			\centering \it
-			\onslide<2->{
-				$-$ symplectic case $-$
-				\begin{defblock}[Comoment map pertaining to $v$]
-					Lie algebra morphism
-					$$ f: \mathfrak{g} \to C^\infty(M) $$
-					such that
-					$$ d~f (x) = -\iota_{v_x} \omega \qquad \forall x \in \mathfrak{g}~.$$
-				\end{defblock}
-			}
-		\end{column}	
-		%
-		\onslide<2->{\vrule{}}
-		%
-		\begin{column}{.50\linewidth}
-			\centering \it
-			\onslide<3->{			
-				$-$ $n$-plectic case $-$
-				\begin{defblock}[Homotopy comoment map \tiny (HCMM)]
-					$L_\infty$-morphism 
-					$$ (f_k) : \mathfrak{g} \to L_\infty (M,\omega)$$
-					such that
-					$$ d~f_1(x) = -\iota_{v_x} \omega \qquad \forall x \in \mathfrak{g}~.$$
-				\end{defblock}	
-			}
-		\end{column}	
-	\end{columns}	
-	%
-	\pause
-	\vfill
-	\centering 
-	\onslide<4->{\textbf{-- Conserved quantities --}}
-	%
-	\vspace{-.5em}
-	\begin{columns}[T]
-		\setlength{\belowdisplayskip}{5pt}
-		\begin{column}{.50\linewidth}
-			%
-			\centering \it
-			\onslide<4->{
-			\begin{propblock}[Noether Theorem]
-				\small Fixed $H\in C^\infty_{\text{Ham}}(M)$ ($\mathfrak{g}$-invariant) ,
-				$$\mathcal{L}_{v_H} f(x) = 0 \qquad \forall x \in \mathfrak{g}$$
-			\end{propblock}
-			}
-		\end{column}	
-		%
-		\onslide<5->{\vrule{}}
-		%
-		\begin{column}{.50\linewidth}
-			\centering \it
-			\onslide<5->{			
-			\begin{propblock}[RWZ16 Theorem]
-				\small Fixed $H\in \Omega^{n-1}_{\text{Ham}}(M)$ ($\mathfrak{g}$-invariant),
-				$$\mathcal{L}_{v_H} f_k(p) \in B^k(M) \qquad \forall p \in Z_k(\mathfrak{g})$$			
-			\end{propblock}
-			}
-		\end{column}	
-	\end{columns}		
-\end{frame}
-\note{
-}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
 \begin{frame}{Reminder: $L_\infty$ Algebras}
@@
 		\vspace{.5em}
-		\begin{defblock}[$L_\infty$-algebra ~\emph{(Lada, Markl)} ~\cite{Lada1995}]
+		\begin{defblock}[$L_\infty$-algebra ~\emph{(Lada, Markl, Stasheff)} ~\cite{Lada1993}\cite{Lada1995}]
 			\includestandalone{Pictures/Figure_Linfinitydef}
@@
 	\pause
-	\vfill
-	\begin{thmblock}[Rogers \cite{Rogers2010}]
-		The \emph{higher observable algebra} $L_{\infty}(M,\omega)$ 	forms an honest $L_\infty$ algebra.
-		\footnotetext{ Take $\mu_1 = \text{d}$, $\mu_k=\lbrace\dots\rbrace_k$, $L$ is a shifted truncation of the de Rham complex.}
-	\end{thmblock}
+
+	\begin{itemize}
+		\item<2-> You can construct a coalgebra out of $L$ \\
+			{\small \color{UniGreen} (the reduced cofree coalgebra $S^{\geq 1}(L[1]),\Delta)$)}.
+		\item<3-> You can assemble all $\mu_k$ to get a coderivation $Q_\mu$\\
+				{\small \color{UniGreen} (the unique lift to a coderivation of the decalage of $ \mu=	\mu_1+\mu_2 + \dots$) }.
+		\item<4-> Higher Jacobi is tantamount to having $Q_\mu ^2 = 0$.
+	\end{itemize}
 \end{frame}
@@
 }
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%------------------------------------------------------------------------------------------------
-\subsection{References \& Aknowledgments}
 %------------------------------------------------------------------------------------------------
 
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\begin{frame}[t,allowframebreaks]{Aknowledgments}
+%%-----------------------------------------------------------%
+%-----------------------------------------------------------%
+\subsection{Goals}
+%-----------------------------------------------------------%
+
+%-----------------------------------------------------------%
+\begin{frame}[fragile]{Scope / Goals}
+	\begin{block}{Upshots:}
 		\begin{itemize}
-		\item MW reduction as "restriction to level sets", C. Lessig,
-			\href{https://arxiv.org/abs/1206.3302}{arXiv:1206.3302}
-		\item Several tex code snippets and slides in appendix are due to \href{https://www.ryvkin.eu/}{Leonid Ryvkin}.
-		\item Some tex code snippets are due to \href{https://math.gmu.edu/~cblacke/}{Casey Blacker}.
+			\item[$\bullet$] Observables $L_\infty$-algebra construction is purely algebraic!
+			\begin{itemize}
+				\item[$\cdot$] \emph{(It relies only on the \underline{standard Cartan calculus identities} for differential forms and vector fields.)}
+			\end{itemize}\pause
+			\item[$\bullet$] Possible generalization to \underline{BV-modules over a Gerstenhaber algebra!}
+			\begin{itemize}
+				\item[$\cdot$] \emph{(A suitably general framework to formalize Cartan calculus.)}
+			\end{itemize}
+		\end{itemize}
+	\end{block}
+	\pause \vfill
 
+	\begin{block}{Claim:}
+		To any given BV-module over a Gerstenhaber algebra together with a chosen closed element (a "cocycle") in the module, we can define:
+		\begin{itemize}
+			\item[$\cdot$] Hamiltonian pairs,
+			\item[$\cdot$] together with an associated $L_\infty$-algebra structure.
 		\end{itemize}
+	\end{block}
+	\pause \vfill
+
+	\begin{block}{Applications:}
+		\begin{itemize}
+			\item[$\bullet$] A more conceptual picture for the algebraic reduction of the observables $L_\infty$-algebra in presence of constraints / symmetries.
+		\end{itemize}
+	\end{block}
+	\vfill
+
 \end{frame}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\note[itemize]{
+	\item   Cartan's identities ensure that the operations $d, i_X, L_X$ behave in a coordinated way (the essence of *Gerstenhaber algebra and BV-module* structure, as we formalize below). 
+	\item Rogers’ $L_\infty$ brackets are built using these ingredients: e.g., the binary bracket of two Hamiltonian forms $(X,\alpha)$ and $(Y,\beta)$ can be defined as $( [X,Y],; L_X\beta)$ (or plus cyclic terms), and higher brackets involve expressions with $i_{X_i} i_{X_j}\omega$ contracted with another argument, etc., ensuring the homotopy Jacobi identities hold .
+	\item The key point is that all such formulas **only use the algebraic operations $d,i,L,[\cdot,\cdot]$ and the form $\omega$**.
+This algebraic nature allows generalization to any context where similar operators exist.
+	\item *Limitations of Classical Reduction:** Before moving to the algebraic setup, note that reducing multisymplectic systems geometrically (analogue of Marsden-Weinstein reduction) can be challenging.
+Classical symplectic reduction requires a Lie group action that is free and proper and a regular value of the moment map; these conditions often fail (especially in field theory or higher form cases).
+Recent work has approached reduction **algebraically** by focusing on the algebra of observables (functions/forms) with constraints, rather than the quotient of manifolds.
+This algebraic approach, implemented for multisymplectic manifolds in Blacker-Miti-Ryvkin 2024, allows handling singular cases (non-free actions, etc.) by *encoding constraints and symmetries at the algebraic level.
+Our work builds on this idea using *constraint triples*.
+\item Given any Gerstenhaber algebra $G$ together with a BV-module $M$ and a chosen closed element (a  "cocycle ") $c$ in $M$, we will show how to construct an associated $L_\infty$-algebra of observables without reference to any underlying manifold .
+\item Moreover, we will address how to perform reduction of these observables $L_\infty$-algebras in the presence of constraints or symmetries.
+For this, we employ the notion of constraint triples as an algebraic framework for coisotropic reduction.
+Adapting this to our BV-module setting, we obtain a general procedure to reduce an $L_\infty$ of observables, even in singular scenarios where classical quotient constructions fail
+}
+%-----------------------------------------------------------%
 
-%TODO Modificare il Readme ricordando che questo si compila con Biber
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+%-----------------------------------------------------------%
+\ifstandalone
 % https://en.wikibooks.org/wiki/LaTeX/Bibliographies_with_biblatex_and_biber
@@
 \end{frame}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\fi
+%-----------------------------------------------------------%
 
-%------------------------------------------------------------------------------------------------
+%-----------------------------------------------------------+
 \end{document}
+%-----------------------------------------------------------+

### 2025-10-21 bv-triples-main.tex
Compiler error- too tired :(

@@
 
-\begin{frame}
+%----------------------------------------------------------------------------------+
+\begin{frame}  % Alternative: \maketitle outside of frame
 	\titlepage
+	\ifHandout
+		\tikz[overlay,remember picture]
+		{
+	    	%	\node at ($(current page.west)+(1.5,0)$) [rotate=90] {\Huge\textcolor{gray}{\today}};
+	    	\node[        
+	    		draw,
+	    		shape border rotate=90,
+			isosceles triangle,
+			isosceles triangle apex angle=90,
+			fill=yellow]
+	        		at ($(current page.north east)-(1,1)$) [rotate=-45] {\textcolor{red}{Handout version}};
+		}
+	\fi
 \end{frame}
+\addtocounter{framenumber}{-1}
+\note{
+	%\textbf{\underline{OUTLINE}}:
+	%\tableofcontents
+	\textbf{Abstract:}
+	\\
+	\footnotesize
+Multisymplectic manifolds generalize symplectic manifolds by carrying a closed, nondegenerate differential form of degree higher than 2.
+Such structures naturally arise in the geometric formulation of classical field theories.
+Rogers (2010) showed that, just as a symplectic manifold yields a Poisson algebra of functions, an n-plectic manifold gives rise to an n-term Lie infinity algebra of observables.
+Remarkably, his construction is purely algebraic and based only on Cartan calculus, suggesting that this higher “Poisson algebra” can be generalized beyond manifolds.
+In this talk, we present such a generalization within the setting of Gerstenhaber algebras and Batalin–Vilkovisky (BV) modules, which provide an algebraic formulation of Cartan calculus relevant to noncommutative geometry.
+This framework allows us to define Lie infinity algebras of observables in a fully algebraic way, without referring to an underlying manifold.
+As an application, we address the reduction of multisymplectic observables in the presence of constraints or symmetries.
+Building on the work of Dippel, Esposito, and Waldmann on “constraint triples” for coisotropic reduction, we adapt this formalism to BV-modules and their Lie infinity algebras.
+This yields a conceptual setting for the algebraic reduction of multisymplectic observables, as developed in our joint work with Casey Blacker (SIGMA 2024).
+The results are part of a collaboration with Leonid Ryvkin, published in *Differential Geometry and its Applications* (2025).
+
+}
+%--------------------------------------------------------------------------------------------------
 
 %+----------------------------------------------------------+
-% S3cti0n: Intr0ducti0n ------------------------------------+
 \section{Introduction}
 %+----------------------------------------------------------+
+	\input{bv-triples-intro}
+%+----------------------------------------------------------+
+
+%+----------------------------------------------------------+
+\section{BV-Modules: Algebraic Cartan Calculus}
+%+----------------------------------------------------------+
+	\checkpoint	
+	\input{bv-triples-background}
+%-----------------------------------------------------------%
+
+%+----------------------------------------------------------+
+\section{$L_\infty$ Algebra Associated with a BV-Module}
+%+----------------------------------------------------------+
+	\checkpoint	
+	%\input{bv-triples-Rogers-generalized}
+%-----------------------------------------------------------%
+
+%+----------------------------------------------------------+
+\section{An Application: Multisymplectic Reduction}
+%+----------------------------------------------------------+
+	\checkpoint	
+	%\input{bv-triples-reduction}
+%-----------------------------------------------------------%
+
+%--------------------------------------------------------------------------------------------------%
+	\addtocounter{framenumber}{-1}
+		\begin{frame}{Conclusion:}
+			\vfill
+		  \centering 
+		  \onslide<2->{\Huge\color{red} 
+		  \emph{Thank you for your attention!}\normalsize \color{black}}
+			\vfill
 			%
 
-\begin{frame}{Symplectic Geometry}
-\begin{itemize}
-  \item Symplectic manifold: $(M,\omega)$ with $\omega$ closed, nondegenerate 2-form.
-  \item Observables: $C^\infty(M)$ with Poisson bracket $\{f,g\} = \omega(X_f, X_g)$.
-  \item $X_f$ is the Hamiltonian vector field: $\iota_{X_f} \omega = df$.
-\end{itemize}
 		\end{frame}
-\note{Symplectic vs.
-Multisymplectic Geometry: In symplectic geometry, a closed nondegenerate 2-form $\omega$ on a manifold $M$ gives rise to a Poisson algebra of observables (smooth functions with the Poisson bracket) .
-In contrast, multisymplectic manifolds carry a closed nondegenerate form of degree $>2$ (often called an $n$-plectic form if its degree is $n+1$).
-These higher-degree forms naturally lead not to a Poisson Lie algebra, but to a higher (homotopy) Lie algebra structure on observables.
-In fact, as shown by Rogers, an $n$-plectic manifold yields an $n$-term $L_\infty$-algebra of observables (sometimes called a higher Poisson algebra) .org.
-This generalizes the Poisson bracket: for example, a 3-plectic form (degree 3) gives a Lie 2-algebra of observables, etc., with higher multi-brackets capturing the failure of the Jacobi identity up to homotopy.
+		\note[itemize]{
+			\item
+		}
+%------------------------------------------------------------------------------------------------
 
-Symplectic Case: If $(M,\omega)$ is a symplectic manifold (closed nondegenerate 2-form), every smooth function $f\in C^\infty(M)$ has an associated Hamiltonian vector field $X_f$ defined by $i_{X_f}\omega = d f$.
-The space of observables $C^\infty(M)$ forms a Poisson algebra with the Poisson bracket ${f,g} = \omega(X_f, X_g)$.
-This is just a Lie algebra (indeed a Lie derivation algebra on $C^\infty(M)$) satisfying the Jacobi identity strictly.
-
-}
-
-\begin{frame}{From Symplectic to Multisymplectic}
-\begin{itemize}
-  \item $k$-plectic manifold: $(M,\omega)$ with closed, nondegenerate $(k+1)$-form.
-  \item Hamiltonian $(k-1)$-form $\alpha$: $\iota_X \omega = d\alpha$.
-  \item Rogers (2010): observables form an $L_\infty$-algebra.
-\end{itemize}
-\end{frame}
-\note{- **Multisymplectic (Higher-Degree) Forms:** Now let $(M,\omega)$ be a **$k$-plectic manifold**, i.e.
-$\omega$ is a closed, nondegenerate $(k+1)$-form (for example, a 3-form if $k=2$).
-The notion of *Hamiltonian observables* generalizes: a **Hamiltonian $(k-1)$-form** $\alpha \in \Omega^{k-1}(M)$ is one that admits a vector field $X$ (a *Hamiltonian field*) satisfying $i_X\omega = d\alpha$.
-We call the pair $(X,\alpha)$ a *Hamiltonian pair*.
-Just as in the symplectic case $(k=1)$ where $\alpha$ is a 0-form (function) and $X$ its Hamiltonian vector field, here $\alpha$ plays the role of the observable (often called an $(k-1)$-form observable).
-The collection of all such Hamiltonian forms (for various degrees) can be organized into a graded object, and Rogers showed that it carries a canonical **$L_\infty$-algebra structure** .
-    - **Example:** For a 3-plectic manifold (degree 3 form $\omega$), one has Hamiltonian 1-forms: each 1-form $\alpha$ for which there exists $X$ with $i_X\omega = d\alpha$.
-These Hamiltonian pairs $(X,\alpha)$ form the degree-0 part of the observables.
-In addition, ordinary functions (0-forms) can be viewed as Hamiltonian 0-forms (with $X$ such that $i_X\omega = d(0) = 0$), and perhaps higher-degree observables appear up to degree 1 in this case.
-The resulting $L_\infty$ has non-trivial brackets of arity up to 2 (making it a *Lie 2-algebra* of observables, a kind of higher Poisson algebra).
-The 2-bracket extends the Poisson bracket, and a 3-bracket arises measuring the failure of the Jacobi identity (something that vanishes in the symplectic case but not in general).
-For a 4-plectic form, one would get a Lie 3-algebra, etc.}
-
-\begin{frame}{$L_\infty$ Algebra of Observables}
-\begin{itemize}
-  \item Observables organized as graded vector space: Hamiltonian forms + multi-brackets.
-  \item Higher brackets from Cartan calculus: $d$, $\iota_X$, $L_X$.
-  \item No manifold needed if we have the algebraic structure.
-\end{itemize}
-\end{frame}
-\note{Rogers’ Construction (2010/2012): The remarkable insight of Rogers  was that the construction of this observables $L_\infty$-algebra is essentially algebraic, relying only on the standard Cartan calculus identities for differential forms and vector fields.
-In other words, Rogers’ $L_\infty$ brackets can be derived from the algebraic relations between the exterior derivative $d$, the interior product $i_X$, and the Lie derivative $L_X$ on forms .
-This suggests we can abstract and generalize the construction beyond the category of manifolds.
-The goal is to build an $L_\infty$-algebra of observables in a purely algebraic setting, provided we have an analog of  "forms " and  "vector fields " satisfying the Cartan relations .}
-
-\begin{frame}{Reminder: What’s an $L_\infty$ Algebra?}
-\begin{itemize}
-  \item Graded vector space $V = \bigoplus V^i$.
-  \item Maps $\ell_k: V^{\otimes k} \to V$ of degree $2 - k$.
-  \item Satisfying higher Jacobi identities (homotopy Lie algebra).
-\end{itemize}
-\end{frame}
-\note{- **Higher Brackets via Cartan Calculus:** The construction of the $L_\infty$ brackets can be understood conceptually in terms of the **Cartan calculus identities**.
-Recall that on a manifold, we have for any vector fields $X,Y$ and differential forms $\alpha$:
-    - $L_X = [d, i_X]$ (Cartan’s identity relating Lie derivative and interior contraction), and
-    - $[L_X, i_Y] = i_{[X,Y]}$ (compatibility of Lie derivative with contraction),
-    - $[L_X,L_Y] = L_{[X,Y]}$, etc.
-
-        These identities ensure that the operations $d, i_X, L_X$ behave in a coordinated way (the essence of *Gerstenhaber algebra and BV-module* structure, as we formalize below).
-Rogers’ $L_\infty$ brackets are built using these ingredients: e.g., the binary bracket of two Hamiltonian forms $(X,\alpha)$ and $(Y,\beta)$ can be defined as $( [X,Y],; L_X\beta)$ (or plus cyclic terms), and higher brackets involve expressions with $i_{X_i} i_{X_j}\omega$ contracted with another argument, etc., ensuring the homotopy Jacobi identities hold .
-The key point is that all such formulas **only use the algebraic operations $d,i,L,[\cdot,\cdot]$ and the form $\omega$**.
-This algebraic nature allows generalization to any context where similar operators exist.
-
-- **Limitations of Classical Reduction:** Before moving to the algebraic setup, note that reducing multisymplectic systems geometrically (analogue of Marsden-Weinstein reduction) can be challenging.
-Classical symplectic reduction requires a Lie group action that is free and proper and a regular value of the moment map; these conditions often fail (especially in field theory or higher form cases).
-Recent work has approached reduction **algebraically** by focusing on the algebra of observables (functions/forms) with constraints, rather than the quotient of manifolds.
-This algebraic approach, implemented for multisymplectic manifolds in Blacker-Miti-Ryvkin 2024, allows handling singular cases (non-free actions, etc.) by *encoding constraints and symmetries at the algebraic level.
-Our work builds on this idea using *constraint triples*.}
-
-\begin{frame}{Scope/Idea of the Talk}
-\begin{itemize}
-  \item Generalize Rogers' construction to a purely algebraic setting.
-  \item Use Gerstenhaber algebras and BV-modules.
-  \item Handle reduction via constraint triples.
-  \item Apply to recover and extend results on multisymplectic reduction.
-\end{itemize}
-\end{frame}
-\note{Our Aim: In this talk, we present such a fully algebraic formalism for constructing and reducing $L_\infty$-algebras of observables, inspired by multisymplectic geometryarxiv.org.
-We work in the framework of Gerstenhaber algebras and Batalin-Vilkovisky modules (BV-modules), which encapsulate the algebraic structure of Cartan calculus (including both commutative and non-commutative cases).
-Given any Gerstenhaber algebra $G$ together with a BV-module $M$ and a chosen closed element (a  "cocycle ") $c$ in $M$, we will show how to construct an associated $L_\infty$-algebra of observables without reference to any underlying manifold .
-This is our Theorem A.
-Moreover, we will address how to perform reduction of these observables $L_\infty$-algebras in the presence of constraints or symmetries.
-For this, we employ the notion of constraint triples (introduced by Dippel-Esposito-Waldmann 2019marvindippell.de) as an algebraic framework for coisotropic reduction.
-Adapting this to our BV-module setting, we obtain a general procedure to reduce an $L_\infty$ of observables, even in singular scenarios where classical quotient constructions fail  .
-This corresponds to Theorem C in our work.
-In particular, our approach reproduces the multisymplectic reduction results of Blacker-Miti-Ryvkin (SIGMA 2024) in a more conceptual way and clarifies the role of the so-called  "residue defect " that appears in the reduction process .}
-
-%+----------------------------------------------------------+
-%Overview: Roughly the first half of the talk will be introductory.
-We will recall the necessary background on multisymplectic observables and momentum maps, then introduce the algebraic structures (Gerstenhaber algebras and BV-modules) that replicate Cartan calculus.
-In the second half, we outline the construction of the observables $L_\infty$-algebra in the algebraic setting (Theorem A), and then discuss how to incorporate constraints via constraint triples, leading to a reduced $L_\infty$-algebra of observables (Theorem C).
-
-%+----------------------------------------------------------+
-%Section: BV-Modules ----------------------------------+
-\section{BV-Modules: Algebraic Cartan Calculus}
-%+----------------------------------------------------------+
-%
-
-\begin{frame}{Lie-Rinehart Algebras}
-\begin{itemize}
-  \item Pair $(A,E)$: $A$ a commutative algebra, $E$ an $A$-module and Lie algebra.
-  \item Anchor map: $\rho: E \to \mathrm{Der}(A)$.
-  \item Encodes derivations + Lie algebra structure.
-\end{itemize}
-\end{frame}
-\note{To generalize the above geometric structures, we introduce the algebraic counterparts of  "multivector fields " and  "differential forms with Cartan calculus.
-" All vector spaces are over a field of characteristic 0 (e.g.
-$\mathbb{R}$).
-We work in graded settings since forms and multivectors are naturally graded.
-
-- **Lie-Rinehart Algebras:** A *Lie-Rinehart algebra* $(A,E)$ consists of a commutative associative algebra $A$ (think of $A=C^\infty(M)$) and an $A$-module $E$ (think of $E=\mathfrak X(M)$, the vector fields) which is also a Lie algebra, together with an *anchor* map $\rho: E \to \mathop{\mathrm{Der}}(A)$ (derivations of $A$) satisfying a Leibniz rule: $[X, aY] = a[X,Y] + (\rho(X)a),Y$.
-This abstractly encodes the notion of derivations of $A$ with an $A$-linear Lie bracket.
-**Example:** If $A=C^\infty(M)$, then $E=\Gamma(TM)$ (the module of vector fields) with the identity anchor $\rho(X)=X$ is a Lie-Rinehart algebra.
-In fact, Lie-Rinehart algebras are algebraic analogues of Lie algebroids (and every Lie algebroid gives a Lie-Rinehart algebra).}
-
-\begin{frame}{Gerstenhaber Algebras}
-\begin{itemize}
-  \item Graded commutative algebra $(\mathcal{G}, \wedge)$.
-  \item Lie bracket $[\cdot,\cdot]$ of degree $-1$.
-  \item Compatibility (Leibniz rule): $[x, y\wedge z] = [x,y]\wedge z + (-1)^{(\deg x -1)\deg y} y\wedge [x,z]$.
-\end{itemize}
-\end{frame}
-\note{- **Gerstenhaber Algebras:** A *Gerstenhaber algebra* is a graded algebra that captures the structure of *exterior algebra of multivector fields*.
-Formally, it is a triple $(\mathcal{G}, \wedge, [\cdot,\cdot])$ where:
-    - $\mathcal{G} = \bigoplus_{i\in\mathbb{Z}} \mathcal{G}^i$ is a $\mathbb{Z}$-graded vector space.
-    - $\wedge: \mathcal{G}^p \times \mathcal{G}^q \to \mathcal{G}^{p+q}$ is a graded-commutative, associative product (degree $0$ operation).
-    - $[\cdot,\cdot]: \mathcal{G}^p \times \mathcal{G}^q \to \mathcal{G}^{p+q-1}$ is a bracket of degree $-1$, making $\mathcal{G}$ into a graded Lie algebra.
-    - **Compatibility (Leibniz rule):** The bracket is a derivation of the product: $[x, y\wedge z] = [x,y]\wedge z + (-1)^{(deg,x -1),deg,y} ,y\wedge [x,z]$ for homogeneous $x,y,z$.
-This is the defining Gerstenhaber identity, generalizing the fact that the Lie bracket of vector fields satisfies a Leibniz rule with respect to wedge of forms or functions.
-
-    **Example:** If $(A,E)$ is a Lie-Rinehart algebra, the **exterior algebra** of $E$ (with a degree shift) carries a natural Gerstenhaber structure.
-In particular, take $\mathcal{G} = \Lambda^\bullet E$ (the exterior *wedge* algebra of $E$ treated as a graded space of multivectors).
-The wedge product is the usual wedge of multivectors, and the bracket is the **Schouten-Nijenhuis bracket** extending the Lie bracket on $E$ to all multivectors.
-This $(\Lambda E,\wedge,[\cdot,\cdot]_{SN})$ is a Gerstenhaber algebra, prototypical in geometry (for $E=\mathfrak X(M)$ one recovers the standard Gerstenhaber algebra of multivector fields on $M$).}
-
-\begin{frame}{Gerstenhaber Modules}
-\begin{itemize}
-  \item $G$-module $M$ with contraction $\iota_X$ of degree $-\deg X$.
-  \item Induced Lie derivative $L_X = [d,\iota_X]$ when $d$ is defined.
-\end{itemize}
-\end{frame}
-\note{Gerstenhaber Module: Given a Gerstenhaber algebra $G$, a Gerstenhaber $G$-module is a graded module $M = \bigoplus M^i$ equipped with an action of $G$ that extends the idea of a multivector acting on forms by contraction.
-Concretely, for each element $X\in G^p$, we have a degree $-p$ operator $i_X: M^\ast \to M^{\ast-p}$ (interpreted as interior product by $X$) satisfying a compatible set of identities (graded derivations, etc.)ar5iv.labs.arxiv.org.
-We also typically get an induced Lie derivative action $L_X$ of degree 0 defined by $L_X := [D,;i_X]$ once a differential $D$ is present (see below).
-We won’t detail the full set of axioms here, but essentially a Gerstenhaber module gives an algebraic version of the pair of operations $(i_X, L_X)$ acting on a  "forms " module, with $i$ being antiderivations and $L$ Lie derivations.
-(The literature sometimes refers to this structure as a  "TTN (Tsygan-Tamarkin-Nest) calculus " .)}
-
-\begin{frame}{BV-Modules}
-\begin{itemize}
-  \item A Gerstenhaber module $M$ with differential $d$.
-  \item Cartan identity: $L_X = [d,\iota_X]$.
-  \item Encodes full algebraic Cartan calculus.
-\end{itemize}
-\end{frame}
-\note{Batalin-Vilkovisky Modules (BV-Modules): A BV-module is a Gerstenhaber module that is also equipped with a differential of degree $+1$ (like an exterior derivative) satisfying Cartan’s formula.
-Formally, let $G$ be a Gerstenhaber algebra and $(M,d)$ a cochain complex (so $d: M^i \to M^{i+1}$ with $d^2=0$).
-We say $M$ is a BV-module over $G$ if $M$ is a Gerstenhaber $G$-module and, for all $X\in G$, we have the Cartan identity $L_X = [d,; i_X]$ (and automatically $[L_X, i_Y] = i_{[X,Y]}$, etc.)  .
-In other words, $M$ carries an action of $G$ by contraction $i_X$ and Lie derivative $L_X$ such that together with the differential $d$ they satisfy the standard graded commutation relations of Cartan calculus.
-We often call $d$ the BV differential.}
-
-\begin{frame}{Abstract Cartan Calculus}
-\begin{itemize}
-  \item $(G,M,d)$ with $G$ Gerstenhaber, $M$ BV-module, $d^2=0$.
-  \item Examples: $(\mathfrak{X}^\bullet(M),\Omega^\bullet(M), d)$.
-  \item Extends to noncommutative and algebraic settings.
-\end{itemize}
-\end{frame}
-\note{Example (Classical Cartan Calculus): Take $G = \Lambda^\bullet \mathfrak X(M)$ (Gerstenhaber algebra of multivector fields on a manifold) and $M=\Omega^\bullet(M)$ (the de Rham complex of differential forms).
-This is a canonical example of a BV-module  : the differential $d$ is the exterior derivative, the contraction $i_X$ is the usual insertion of a multivector $X$ into a form, and the Lie derivative $L_X$ is the usual one acting on forms.
-These satisfy $L_X = d \circ i_X + i_X \circ d$ (Cartan formula) and all other Cartan identities.
-In fact, this example exactly recovers the classical Cartan calculus on $M$ as a BV-module structure on $\Omega^\bullet(M)$, with $G$ playing the role of  "polyvector fields " .
-This justifies the abstractions: any Gerstenhaber algebra + BV-module pair can be seen as a generalized  "space of multivectors and forms " with a full Cartan calculus available .
-We emphasize that such structures exist in much more general settings, including noncommutative geometry (where $A$ is a noncommutative algebra and one considers analogues of forms and multivectors  ), but for our purposes we stick to the algebraic axioms.}
-
-%+----------------------------------------------------------+
-%Section: L-infinity Algebra Associated with a BV-Module ---+
-%
-\section{$L_\infty$ Algebra Associated with a BV-Module}
-%+----------------------------------------------------------+
-%
-
-\begin{frame}{Hamiltonian Pairs}
-\begin{itemize}
-  \item Data: $G$, $M$ BV-module, $c \in M$ closed.
-  \item Pair $(X,m)$ with $\iota_X c = d m$.
-  \item Generalizes $(X_f, f)$ in symplectic geometry.
-\end{itemize}
-\end{frame}
-\note{Given an algebraic Cartan calculus as above, we can now construct the $L_\infty$-algebra of observables in complete generality.
-The construction mirrors the one Rogers gave on manifolds, but now in purely algebraic terms.
-
-- **Data:** Let $G$ be a Gerstenhaber algebra, $M$ a BV-module over $G$ with differential $d$, and let $c \in M^k$ be a fixed *cocycle*, meaning $d c = 0$. 
-Think of $c$ as the algebraic analog of a closed multisymplectic form (indeed in geometry $c$ could be $\omega$, which is closed by assumption).
-We also assume $c$ is *nondegenerate* in the sense that it induces the relevant pairings (this is automatic in the geometric case and can be treated as a cocycle condition in the algebraic case; for simplicity, we proceed assuming $c$ behaves like a  "volume form " or  "top form " to contract with).
-- **Hamiltonian Pairs:** We define a **Hamiltonian pair** as a pair $(X, m)$ with $X \in G$ (a multivector) and $m \in M$ (an element of the module) such that $X$ and $m$ are related by the cocycle $c$ via:
-
-    $i_X(c) = d m$.
-
-    In other words, $m$ is an element whose BV-differential equals the contraction of $c$ with $X$.
-This is directly analogous to the condition $i_{X_f}\omega = d f$ in the geometric case (here $X$ plays the role of $X_f$ and $m$ plays the role of the observable like $f$ or $\alpha$).
-We denote by $\mathsf{Ham}(G,M;c)$ the set of all Hamiltonian pairs.
-In graded terms, one typically considers homogeneous $X$ and $m$ of complementary degrees summing to $k-1$ (so that $i_X c$ has the same degree as $d m$).
-
-    **Intuition:** A Hamiltonian pair $(X,m)$ means that $m$ is an *observable* whose  "derived bracket " with the cocycle $c$ yields $X$.
-If $c$ is nondegenerate, $X$ is uniquely determined by $m$ (just as a symplectic form gives a unique $X_f$ for each $f$), so we can think of $m$ as the *observable element* and $X$ as its *Hamiltonian generator*.
-However, in singular or degenerate cases, there could be multiple $X$ for a given $m$ or vice versa, hence it is safer to keep the pair.
-(In the construction we actually consider an appropriate quotient to identify pairs that give the same physical observable; more formally $\mathsf{Ham}(G,M;c)$ can be constructed as a fiber product $G \times_{M} M$ via the maps $X \mapsto i_X c$ and $m \mapsto d m$ .)}
-
-\begin{frame}{The Space and the Multibrackets}
-\begin{itemize}
-  \item Graded space $\mathcal{O}(G,M;c)$.
-  \item Brackets $\ell_k$ built from $d$, $\iota_X$, $L_X$, $[\cdot,\cdot]$.
-  \item $\ell_1 = d$, $\ell_2 = $ Lie + derived terms, $\ell_3 = i_{X_1}i_{X_2}i_{X_3}(c)$.
-\end{itemize}
-\end{frame}
-\note{- \textbf{Graded observables space:} We assemble the observables into a graded vector space as follows.
-
-\[
-\mathcal{O}(G,M;c)\;=\;\bigoplus_{j\ge 0}\mathcal{O}^j,
-\]
-
-where:
-
-- $\mathcal{O}^0$ (degree~0 part) is the space of Hamiltonian pairs $(X,m)$ as above (with $i_X c = d m$).
-- For higher degrees $j>0$, roughly speaking $\mathcal{O}^j$ consists of elements of $M$ of degree $(k-1+j)$ (or related shifts) corresponding to forms of lower degree than $c$.
-In fact, in Rogers' original construction for an $n$-plectic manifold, the $L_\infty$-algebra of observables was an $n$-term complex concentrated in degrees $0,1,\dots,n-1$.
-Here $k=n+1$ (degree of $c$), so one can show $\mathcal{O}(G,M;c)$ is concentrated in degrees $0$ up to $n-1$ (i.e.
-$0$ up to $k-2$).
-Degree~0 are Hamiltonian $(n-1)$-forms (with vector fields), degree~1 would be Hamiltonian $(n-2)$-forms, ..., up to degree $n-1$ corresponding to Hamiltonian $0$-forms (basic observables).
-We will not need the explicit formula for each degree in this talk; the key is that this graded space includes all would-be observables and their "Hamiltonian partners."}
-
-\begin{frame}{Examples}
-\begin{itemize}
-  \item Classical: $G=\mathfrak{X}^\bullet(M)$, $M=\Omega^\bullet(M)$, $c=\omega$.
-  \item Recovers Rogers’ multisymplectic $L_\infty$.
-  \item Other contexts: algebraic, noncommutative, etc.
-\end{itemize}
-\end{frame}
-\note{- **$L_{\infty}$-Algebra Structure:** **Theorem A** (Miti-Ryvkin 2025) states that under the above setup, $\mathcal{O}(G,M;c)$ carries a natural structure of an $L_\infty$-algebra (homotopy Lie algebra) whose brackets are defined using the data of the Gerstenhaber algebra $G$, the BV-module operations, and the cocycle $c$ .
-Concretely, the multilinear $L_\infty$ operations $\ell_r: \mathcal{O}^{\otimes r} \to \mathcal{O}$ (of degree $2-r$) are given by formulas analogous to those in the multisymplectic manifold case :
-    - The unary bracket $\ell_1$ (degree $+1$ map) is essentially induced by the BV differential $d$ on the observable part (it maps a degree~1 element to degree~0 by $\ell_1(m) = (X,d m)$ or something similar, and is zero on degree~0 pairs in the fully nondegenerate case).
-    - The binary bracket $\ell_2((X_1,m_1), (X_2,m_2))$ has a result in degree~0 and is given by
-
-        \[
-        \ell_2((X_1,m_1),(X_2,m_2)) \;=\; \big([X_1,X_2],\; L_{X_1}m_2 * (-1)^{|X_1|\cdot|X_2|}L_{X_2}m_1\big),
-        \]
-
-        which in the simplest case recovers the Poisson bracket structure (when $m$’s are functions, $L_{X_1}m_2 = X_1(m_2)$).
-The precise formula involves appropriate Koszul signs for graded elements .
-
-    - A tertiary bracket $\ell_3((X_1,m_1),(X_2,m_2),(X_3,m_3))$ can be defined using the cocycle $c$: essentially one can take $i_{X_1}i_{X_2}i_{X_3}(c)$ (which is an element of $M$) as part of the output (this corresponds to evaluating the 3-form on three vector fields to get a number or top-form), ensuring that the Jacobi identity holds up to homotopy.
-    - Higher brackets $\ell_r$ for $r>3$ may be zero or determined similarly by $c$ if its degree is larger.
-In fact, for an $(n+1)$-form $c$, all brackets $\ell_r$ with $r> n$ will vanish (so the $L_\infty$ is  "finite " or $n$-term) .
-
-    The upshot is that **all these brackets are built out of the operations $[\cdot,\cdot]$ in $G$, $i_X$, $L_X$, $d$, and contraction with $c$**, mimicking the standard formulas in coordinates.
-It is nontrivial but true that these operations satisfy the required homotopy Jacobi identities.
-The verification is essentially a translation of Rogers’ original proof to this abstract setting - since Rogers’ proof was  "purely algebraic in nature, " it adapts directly here .
-We have thus constructed an **$L_\infty$-algebra of observables** $\mathcal{O}(G,M;c)$ associated to any BV-module with a cocycle.
-This is the main result of the first part of the talk.
-
-    Example (Geometric Case): If we take $G = \Lambda^\bullet \mathfrak X(M)$, $M = \Omega^\bullet(M)$ (so classical Cartan calculus on a manifold), and $c = \omega$ an $n$-plectic form, then $\mathcal{O}(G,M;c)$ precisely recovers Rogers’ $L_\infty$-algebra of observables on $(M,\omega)$  .
-In degree 0, $\mathcal{O}^0$ consists of Hamiltonian $(n!-!1)$-forms (with their Hamiltonian vector fields), which are exactly Rogers’ observables.
-The brackets $\ell_r$ coincide with those defined by Rogers (up to sign conventions), and one can check the $L_\infty$ identities by the same calculations in Cartan calculus .
-This generality shows the power of the BV-module approach: any example of a Gerstenhaber algebra + cocycle yields such an $L_\infty$.
-For instance, one could even take noncommutative analogues (with a suitable cyclic cocycle playing the role of $c$) to get  "$L_\infty$-observables " in noncommutative geometry  , although we won’t explore that in this talk.}
-
-%+----------------------------------------------------------+
-%S3cti0n: An Applicati0n: Multisymplectic Reducti0n -------+
-%
-\section{An Application: Multisymplectic Reduction}
-%+----------------------------------------------------------+
-%
-
-\begin{frame}{Constraint Triples}
-\begin{itemize}
-  \item Triple $(A, A_C, \overline{A})$ with inclusion/projection.
-  \item $A_C$ encodes constraints, $\overline{A} = A/I$ reduced algebra.
-  \item Adapted to Gerstenhaber and BV-module settings.
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Constraint BV-Modules}
-\begin{itemize}
-  \item Triples $(G, G_C, \overline{G})$, $(M, M_C, \overline{M})$.
-  \item Structures compatible with Cartan calculus.
-  \item Closed cocycle triple $c = (c, c_C, \overline{c})$.
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Constraint $L_\infty$ Algebra Associated with…}
-\begin{itemize}
-  \item Construct observables $\mathcal{O} = (\mathcal{O}, \mathcal{O}_C, \overline{\mathcal{O}})$.
-  \item Each component carries an $L_\infty$ structure.
-  \item Brackets compatible with inclusions/projections.
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Reduction Functor}
-\begin{itemize}
-  \item Quotient part $\overline{\mathcal{O}}$ inherits $L_\infty$ structure.
-  \item Encodes reduced observables algebra.
-  \item No need for regular quotient at geometric level.
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Recovering Old Results}
-\begin{itemize}
-  \item Applies to multisymplectic reduction (Blacker-Miti-Ryvkin 2024).
-  \item Explains residue defect in homotopy Jacobi identity.
-  \item Matches geometric reduction under regularity.
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Conclusion / Summary}
-\begin{itemize}
-  \item Algebraic formalism for $L_\infty$ observables via BV-modules.
-  \item Generalizes Rogers' result.
-  \item Enables reduction via constraint triples.
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Outlook}
-\begin{itemize}
-  \item Homotopy momentum maps.
-  \item Operadic reformulation.
-  \item Applications to field theory.
-\end{itemize}
-\end{frame}
+%------------------------------------------------------------------------------------------------
+% APPENDIX
+%------------------------------------------------------------------------------------------------
+\appendix
+%------------------------------------------------------------------------------------------------
+\section{Complementary Material}
+	%\input{bv-triples-complementary-material}
+	%\input{bv-triples-aknowledgements}
+%------------------------------------------------------------------------------------------------
 
@@
 %+----------------------------------------------------------+
-
-We now turn to the second main part: **reduction** of the $L_\infty$-algebra of observables in the presence of constraints or symmetries.
-In symplectic geometry, reduction is accomplished by the Marsden-Weinstein quotient: one restricts to the zero level set of a momentum map and then quotients by the symmetry group.
-Algebraically, this corresponds to first imposing ideal relations (for the constraints) and then modding out by gauge symmetries.
-The **constraint triple** formalism packages these two steps (subobject and quotient) in a single algebraic structure .
-
-- **Constraint Triples:** A **constraint triple** (or **coisotropic triple**) in general consists of:
-    1. An algebra (or other structure) $A$ representing the full system’s observables.
-    2. A subalgebra $C \subset A$ representing the *constraints* (for example, functions vanishing on a certain submanifold, or first-class constraint algebra in Dirac’s theory).
-    3. A quotient (factor) algebra $\overline{A} = A/ I$ for some ideal $I$ related to $C$, representing the *reduced* algebra of observables after constraints are imposed and quotiented.
-
-    These are equipped with structure maps (inclusions and projections) satisfying compatibility conditions (e.g.
-$I$ is the ideal of relations defining $C$) .
-Intuitively, one has $C$ as the "constraint algebra" (functions that vanish on the constraint surface) and $\overline{A}$ as the algebra of functions on the quotient of that constraint surface by symmetries.
-Dippel, Esposito & Waldmann formalized this in the context of Poisson algebras and deformation quantization , showing that many reduction procedures can be understood as functors on such triples.
-
-    We adopt this idea in our setting: we will consider **constraint Gerstenhaber algebras** and **constraint BV-modules**, which are triples $(G, G_C, \overline{G})$ and $(M, M_C, \overline{M})$ capturing the full, constraint, and reduced parts of our algebraic Cartan calculus .
-All the structure (brackets, differentials, etc.) is assumed to exist on each part and to be compatible.
-For instance, a *constraint Gerstenhaber algebra* means $G$ is a Gerstenhaber algebra, $G_C \subset G$ a subalgebra (constraints), and $\overline{G} = G/G_C$ (some quotient) such that the wedge and bracket operations map triples to triples (roughly $[![G, G]!]$ sends $G_C$ to $G_C$ and induces well-defined operations on the quotient) .
-Similarly, a *constraint BV-module* $(M, M_C, \overline{M})$ has $M_C$ a submodule (the  "constraints on forms ") and $\overline{M}=M/M_C$ the quotient module, with differential $d$ and contractions $i_X$ etc.
-respecting the triples (so that, e.g., $d(M_C)\subseteq M_C$ and induces a differential on $\overline{M}$) .
-This is a bit of structure to keep track of, but conceptually it means we have *Cartan calculus not just on one algebra, but simultaneously on a sub- and a quotient algebra*.
-
-    - **Origin in Geometry:** If one has a manifold $M$ with a coisotropic submanifold $C\subset M$ (the constraint surface) and a group $G$ acting with gauge orbits, one can form a *constraint manifold* in the sense of Dippel-Kern 2025 .
-The algebra of smooth functions on a constraint manifold is exactly a constraint triple $(A, C, \overline{A})$ in which $C$ are the functions vanishing on the constraint surface and $\overline{A}$ functions on the quotient (when nice).
-Likewise, vector fields tangent to $C$ etc.
-form a constraint Lie-Rinehart algebra, and so on.
-Indeed, it has been shown that a **constraint Lie-Rinehart algebra** naturally induces a constraint Gerstenhaber algebra and constraint BV-module structures .
-So this framework is not lacking examples - it generalizes classical constrained Hamiltonian systems.
-- **Constraint $L_\infty$ of Observables:** Once we have constraint versions of $G$ and $M$ **and** a *constraint cocycle* $c = (c, c_C, \overline{c})$ (meaning $c$ lies in $M$, $c_C$ in $M_C$ and $\overline{c}$ is its class in $\overline{M}$, with each closed under their respective differentials), we can perform the same construction as before *in the category of constraint complexes*.
-That is, we define the **constraint Hamiltonian pairs** as triples $((X, X_C, \overline{X}), (m, m_C, \overline{m}))$ such that $i_X(c) = d m$, $i_{X_C}(c_C) = d m_C$ and these are compatible/projection of the first (so $\overline{X}$ and $\overline{m}$ are the images of $X,m$, etc.) .
-All such triples form a constraint graded space of observables.
-**Theorem C** asserts that this constraint observables space carries a **constraint $L_\infty$-algebra** structure .
-By  "constraint $L_\infty$-algebra, " we mean an $L_\infty$ whose underlying structure is also a triple $(L, L_C, \overline{L})$: there are brackets $\ell_r$ on each of $L, L_C, \overline{L}$, and the inclusion/projection maps intertwine these (so that $L_C$ is an $L_\infty$-subalgebra and $\overline{L}$ the quotient $L_\infty$) .
-The brackets are defined using the same formulas as in the unconstrained case, applied levelwise to $(G, M, c)$, $(G_C, M_C, c_C)$ and inducing $(\overline{G}, \overline{M}, \overline{c})$ .
-The $L_\infty$ identities hold simultaneously on each level by the same reasoning as before, thanks to the compatibility of the constraint data.
-- **Reduction Functor:** Once we have a constraint $L_\infty$-algebra of observables, *reducing it* means passing to the **quotient part** of the constraint triple.
-In categorical terms, there is a forgetful functor sending a constraint object $(X, X_C, \overline{X})$ to the quotient $\overline{X}$.
-When we apply this to the constraint $L_\infty$ of observables, we obtain an $L_\infty$-algebra on $\overline{L}$, which we interpret as the **reduced $L_\infty$-algebra of observables** of the constrained system.
-Intuitively, this $\overline{L}$ encodes observables that are invariant under the symmetry and defined on the constraint surface (since we mod out those that vanish or differ by constraint terms) .
-By construction, all the $L_\infty$ brackets descend to $\overline{L}$, so the homotopy Lie structure is well-defined on the quotient.
-This algebra $\overline{L}$ is the algebraic analog of the Poisson algebra of the reduced phase space in classical reduction, but here it can handle the homotopy brackets arising from a multisymplectic form and even if no nice manifold quotient exists (e.g.
-in singular cases).
-- **Recovery of Known Results:** Our general reduction scheme, when applied to the **geometric case** of a multisymplectic manifold with a group action, reproduces the results of our earlier work (Blacker-Miti-Ryvkin, SIGMA 2024) .
-In that work, we constructed a reduced $L_\infty$ of observables by more ad-hoc means; now we see it fits into the constraint triple framework.
-Specifically, given a Lie group $G$ acting on an $n$-plectic manifold $(M,\omega)$ with a covariant momentum map $\mu$ , one can form the constraint triple:
-    - $A = $ observables $L_\infty$ on $(M,\omega)$,
-    - $A_C = $ those observables that vanish on the constraint (e.g. forms pulled back by $\mu$ setting to zero, etc.),
-    - $\overline{A} = $ observables on the reduced space (when $0$ level set mod $G$ is nice, these correspond to forms on the quotient).
-
-    Our formalism shows that $\overline{A}$ inherits an $L_\infty$-algebra structure automatically .
-No assumptions of regularity or freeness are needed in the algebraic approach - even if the quotient is singular, $\overline{A}$ is well-defined as a homotopy algebra.
-This extends the multisymplectic reduction of Blacker 2021 (which assumed regularity) to a far more general context .
-Moreover, within our algebraic setting we identify an object called the **residue defect**, which measures the slight difference between naive and actual reduction in the homotopy context.
-In the earlier work, this residue term appeared somewhat mysteriously to satisfy the homotopy Jacobi identities; here we can interpret it cleanly as arising from the constraint differential and the failure of a certain exactness on the constraint submodule.
-Our framework **clarifies the role of the  "residue defect "**: it is an intrinsic part of the constraint $L_\infty$ structure that vanishes under appropriate conditions (like when the momentum map level is regular) .
-
-- **Summary of Main Results:** We can summarize the main technical results (theorems) as follows:
-    - **Theorem A:** *Given any Gerstenhaber algebra $G$ with a BV-module $M$ and a closed element $c\in M$, the graded space of Hamiltonian pairs $\mathcal{O}(G,M;c)$ admits an $L_\infty$-algebra structure (observables algebra), defined by the multilinear maps derived from Cartan calculus.*
-    - **Theorem B:** *If $(A,E)$ is a **constraint** Lie-Rinehart algebra (constraint version of derivations over a constraint algebra $A$), then one naturally obtains a constraint Gerstenhaber algebra and a constraint BV-module $(G, M)$ out of it.
-(In short, classical constraint manifolds yield constraint Cartan calculus algebraically.)
-    - **Theorem C:** *Given a constraint Gerstenhaber algebra and BV-module with a constraint cocycle $c$, one can construct a **constraint** $L_\infty$-algebra of observables.
-Moreover, its **reduced part** $\overline{\mathcal{O}}$ (the quotient level) is an $L_\infty$-algebra that describes the observables of the reduced system.*
-
-    As an application, Theorem C applied to multisymplectic manifolds with symmetries recovers the reduced $L_\infty$ in  and explains the extra terms (residue defect) in a categorical way .
-
-## **Conclusion and Outlook**
-
-We have developed a **purely algebraic toolkit** for constructing and reducing $L_\infty$-algebras of observables, extending concepts from symplectic geometry to multisymplectic and even noncommutative settings .
-This framework shows the power of combining homotopy algebra (for observables) with constraint category theory (for reduction).
-It provides a unified perspective where classical geometric reduction is just one instance of an algebraic functor acting on $L_\infty$-algebras .
-
-Some directions for further research include:
-
-- **Homotopy Momentum Maps:** Relating our constraint $L_\infty$-reduction to the notion of *homotopy momentum maps* (which appear in alternative higher reduction approaches, e.g.
-the work of Callies-Frégier-Rogers-Zambon on $L_\infty$-moment maps .
-It would be interesting to connect the **Leibniz-algebra-valued momentum maps** used here  with homotopy moment maps in an $L_\infty$-context.
-- **Operadic Formulation:** The constraint triple constructions hint at an operadic or higher-categorical organization.
-One could aim to describe the entire process (Cartan calculus + constraints + $L_\infty$) in terms of operads or properads encoding these algebraic relations .
-This might streamline proofs and allow further generalizations (e.g.
-to quantum or $A_\infty$ settings).
-- **Applications to Field Theory:** Ultimately, multisymplectic forms arise in classical field theory (e.g.
-the 2-form in mechanics vs.
-a 3-form in 2-dimensional field theory).
-Our algebraic observables $L_\infty$ could serve as a foundation for understanding *higher Poisson brackets* on the phase space of fields and their reduction under symmetries.
-Recent works on polysymplectic and polycontact reduction provide complementary geometric approaches; linking those with our algebraic method is a promising avenue.
-
-**References:** *(Selected key references in context)* Rogers (2012) for the original multisymplectic $L_\infty$-algebra construction; Dippel-Esposito-Waldmann (2019) for constraint (coisotropic) triples in Poisson algebra setting; Blacker-Miti-Ryvkin (2024) for algebraic multisymplectic reduction; and our work Miti-Ryvkin (2025) (Differential Geom.
-Appl.) which this talk is based on, for full details and proofs.
-The methods presented exemplify how **pure algebraic techniques can not only recover but also enlighten classical geometric results** in higher symplectic geometry, broadening the scope to singular and noncommutative realms.

### 2025-10-21 bv-triples-reduction.tex
Compiler error- too tired :(

--- 2025-10-21 bv-triples-Rogers-generalized.tex
@@
 
-\begin{frame}{Hamiltonian Pairs}
+\begin{frame}{Constraint Triples}
 \begin{itemize}
-  \item Data: $G$, $M$ BV-module, $c \in M$ closed.
-  \item Pair $(X,m)$ with $\iota_X c = d m$.
-  \item Generalizes $(X_f, f)$ in symplectic geometry.
+  \item Triple $(A, A_C, \overline{A})$ with inclusion/projection.
+  \item $A_C$ encodes constraints, $\overline{A} = A/I$ reduced algebra.
+  \item Adapted to Gerstenhaber and BV-module settings.
 \end{itemize}
 \end{frame}
-\note{Given an algebraic Cartan calculus as above, we can now construct the $L_\infty$-algebra of observables in complete generality.
-The construction mirrors the one Rogers gave on manifolds, but now in purely algebraic terms.
 
-- **Data:** Let $G$ be a Gerstenhaber algebra, $M$ a BV-module over $G$ with differential $d$, and let $c \in M^k$ be a fixed *cocycle*, meaning $d c = 0$. 
-Think of $c$ as the algebraic analog of a closed multisymplectic form (indeed in geometry $c$ could be $\omega$, which is closed by assumption).
-We also assume $c$ is *nondegenerate* in the sense that it induces the relevant pairings (this is automatic in the geometric case and can be treated as a cocycle condition in the algebraic case; for simplicity, we proceed assuming $c$ behaves like a  "volume form " or  "top form " to contract with).
-- **Hamiltonian Pairs:** We define a **Hamiltonian pair** as a pair $(X, m)$ with $X \in G$ (a multivector) and $m \in M$ (an element of the module) such that $X$ and $m$ are related by the cocycle $c$ via:
-
-    $i_X(c) = d m$.
-
-    In other words, $m$ is an element whose BV-differential equals the contraction of $c$ with $X$.
-This is directly analogous to the condition $i_{X_f}\omega = d f$ in the geometric case (here $X$ plays the role of $X_f$ and $m$ plays the role of the observable like $f$ or $\alpha$).
-We denote by $\mathsf{Ham}(G,M;c)$ the set of all Hamiltonian pairs.
-In graded terms, one typically considers homogeneous $X$ and $m$ of complementary degrees summing to $k-1$ (so that $i_X c$ has the same degree as $d m$).
-
-    **Intuition:** A Hamiltonian pair $(X,m)$ means that $m$ is an *observable* whose  "derived bracket " with the cocycle $c$ yields $X$.
-If $c$ is nondegenerate, $X$ is uniquely determined by $m$ (just as a symplectic form gives a unique $X_f$ for each $f$), so we can think of $m$ as the *observable element* and $X$ as its *Hamiltonian generator*.
-However, in singular or degenerate cases, there could be multiple $X$ for a given $m$ or vice versa, hence it is safer to keep the pair.
-(In the construction we actually consider an appropriate quotient to identify pairs that give the same physical observable; more formally $\mathsf{Ham}(G,M;c)$ can be constructed as a fiber product $G \times_{M} M$ via the maps $X \mapsto i_X c$ and $m \mapsto d m$ .)}
-
-\begin{frame}{The Space and the Multibrackets}
+\begin{frame}{Constraint BV-Modules}
 \begin{itemize}
-  \item Graded space $\mathcal{O}(G,M;c)$.
-  \item Brackets $\ell_k$ built from $d$, $\iota_X$, $L_X$, $[\cdot,\cdot]$.
-  \item $\ell_1 = d$, $\ell_2 = $ Lie + derived terms, $\ell_3 = i_{X_1}i_{X_2}i_{X_3}(c)$.
+  \item Triples $(G, G_C, \overline{G})$, $(M, M_C, \overline{M})$.
+  \item Structures compatible with Cartan calculus.
+  \item Closed cocycle triple $c = (c, c_C, \overline{c})$.
 \end{itemize}
 \end{frame}
-\note{- \textbf{Graded observables space:} We assemble the observables into a graded vector space as follows.
 
-\[
-\mathcal{O}(G,M;c)\;=\;\bigoplus_{j\ge 0}\mathcal{O}^j,
-\]
-
-where:
-
-- $\mathcal{O}^0$ (degree~0 part) is the space of Hamiltonian pairs $(X,m)$ as above (with $i_X c = d m$).
-- For higher degrees $j>0$, roughly speaking $\mathcal{O}^j$ consists of elements of $M$ of degree $(k-1+j)$ (or related shifts) corresponding to forms of lower degree than $c$.
-In fact, in Rogers' original construction for an $n$-plectic manifold, the $L_\infty$-algebra of observables was an $n$-term complex concentrated in degrees $0,1,\dots,n-1$.
-Here $k=n+1$ (degree of $c$), so one can show $\mathcal{O}(G,M;c)$ is concentrated in degrees $0$ up to $n-1$ (i.e.
-$0$ up to $k-2$).
-Degree~0 are Hamiltonian $(n-1)$-forms (with vector fields), degree~1 would be Hamiltonian $(n-2)$-forms, ..., up to degree $n-1$ corresponding to Hamiltonian $0$-forms (basic observables).
-We will not need the explicit formula for each degree in this talk; the key is that this graded space includes all would-be observables and their "Hamiltonian partners."}
-
-\begin{frame}{Examples}
+\begin{frame}{Constraint $L_\infty$ Algebra Associated with…}
 \begin{itemize}
-  \item Classical: $G=\mathfrak{X}^\bullet(M)$, $M=\Omega^\bullet(M)$, $c=\omega$.
-  \item Recovers Rogers’ multisymplectic $L_\infty$.
-  \item Other contexts: algebraic, noncommutative, etc.
+  \item Construct observables $\mathcal{O} = (\mathcal{O}, \mathcal{O}_C, \overline{\mathcal{O}})$.
+  \item Each component carries an $L_\infty$ structure.
+  \item Brackets compatible with inclusions/projections.
 \end{itemize}
 \end{frame}
-\note{- **$L_{\infty}$-Algebra Structure:** **Theorem A** (Miti-Ryvkin 2025) states that under the above setup, $\mathcal{O}(G,M;c)$ carries a natural structure of an $L_\infty$-algebra (homotopy Lie algebra) whose brackets are defined using the data of the Gerstenhaber algebra $G$, the BV-module operations, and the cocycle $c$ .
-Concretely, the multilinear $L_\infty$ operations $\ell_r: \mathcal{O}^{\otimes r} \to \mathcal{O}$ (of degree $2-r$) are given by formulas analogous to those in the multisymplectic manifold case :
-    - The unary bracket $\ell_1$ (degree $+1$ map) is essentially induced by the BV differential $d$ on the observable part (it maps a degree~1 element to degree~0 by $\ell_1(m) = (X,d m)$ or something similar, and is zero on degree~0 pairs in the fully nondegenerate case).
-    - The binary bracket $\ell_2((X_1,m_1), (X_2,m_2))$ has a result in degree~0 and is given by
 
-        \[
-        \ell_2((X_1,m_1),(X_2,m_2)) \;=\; \big([X_1,X_2],\; L_{X_1}m_2 * (-1)^{|X_1|\cdot|X_2|}L_{X_2}m_1\big),
-        \]
+\begin{frame}{Reduction Functor}
+\begin{itemize}
+  \item Quotient part $\overline{\mathcal{O}}$ inherits $L_\infty$ structure.
+  \item Encodes reduced observables algebra.
+  \item No need for regular quotient at geometric level.
+\end{itemize}
+\end{frame}
 
-        which in the simplest case recovers the Poisson bracket structure (when $m$’s are functions, $L_{X_1}m_2 = X_1(m_2)$).
-The precise formula involves appropriate Koszul signs for graded elements .
-
-    - A tertiary bracket $\ell_3((X_1,m_1),(X_2,m_2),(X_3,m_3))$ can be defined using the cocycle $c$: essentially one can take $i_{X_1}i_{X_2}i_{X_3}(c)$ (which is an element of $M$) as part of the output (this corresponds to evaluating the 3-form on three vector fields to get a number or top-form), ensuring that the Jacobi identity holds up to homotopy.
-    - Higher brackets $\ell_r$ for $r>3$ may be zero or determined similarly by $c$ if its degree is larger.
-In fact, for an $(n+1)$-form $c$, all brackets $\ell_r$ with $r> n$ will vanish (so the $L_\infty$ is  "finite " or $n$-term) .
-
-    The upshot is that **all these brackets are built out of the operations $[\cdot,\cdot]$ in $G$, $i_X$, $L_X$, $d$, and contraction with $c$**, mimicking the standard formulas in coordinates.
-It is nontrivial but true that these operations satisfy the required homotopy Jacobi identities.
-The verification is essentially a translation of Rogers’ original proof to this abstract setting - since Rogers’ proof was  "purely algebraic in nature, " it adapts directly here .
-We have thus constructed an **$L_\infty$-algebra of observables** $\mathcal{O}(G,M;c)$ associated to any BV-module with a cocycle.
-This is the main result of the first part of the talk.
-
-    Example (Geometric Case): If we take $G = \Lambda^\bullet \mathfrak X(M)$, $M = \Omega^\bullet(M)$ (so classical Cartan calculus on a manifold), and $c = \omega$ an $n$-plectic form, then $\mathcal{O}(G,M;c)$ precisely recovers Rogers’ $L_\infty$-algebra of observables on $(M,\omega)$  .
-In degree 0, $\mathcal{O}^0$ consists of Hamiltonian $(n!-!1)$-forms (with their Hamiltonian vector fields), which are exactly Rogers’ observables.
-The brackets $\ell_r$ coincide with those defined by Rogers (up to sign conventions), and one can check the $L_\infty$ identities by the same calculations in Cartan calculus .
-This generality shows the power of the BV-module approach: any example of a Gerstenhaber algebra + cocycle yields such an $L_\infty$.
-For instance, one could even take noncommutative analogues (with a suitable cyclic cocycle playing the role of $c$) to get  "$L_\infty$-observables " in noncommutative geometry  , although we won’t explore that in this talk.}
+\begin{frame}{Recovering Old Results}
+\begin{itemize}
+  \item Applies to multisymplectic reduction (Blacker-Miti-Ryvkin 2024).
+  \item Explains residue defect in homotopy Jacobi identity.
+  \item Matches geometric reduction under regularity.
+\end{itemize}
+\end{frame}
 
@@
 %-----------------------------------------------------------+
-
-\begin{frame}{Conclusion / Summary}
-\begin{itemize}
-  \item Algebraic formalism for $L_\infty$ observables via BV-modules.
-  \item Generalizes Rogers' result.
-  \item Enables reduction via constraint triples.
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Outlook}
-\begin{itemize}
-  \item Homotopy momentum maps.
-  \item Operadic reformulation.
-  \item Applications to field theory.
-\end{itemize}
-\end{frame}
-
-We now turn to the second main part: **reduction** of the $L_\infty$-algebra of observables in the presence of constraints or symmetries.
-In symplectic geometry, reduction is accomplished by the Marsden-Weinstein quotient: one restricts to the zero level set of a momentum map and then quotients by the symmetry group.
-Algebraically, this corresponds to first imposing ideal relations (for the constraints) and then modding out by gauge symmetries.
-The **constraint triple** formalism packages these two steps (subobject and quotient) in a single algebraic structure .
-
-- **Constraint Triples:** A **constraint triple** (or **coisotropic triple**) in general consists of:
-    1. An algebra (or other structure) $A$ representing the full system’s observables.
-    2. A subalgebra $C \subset A$ representing the *constraints* (for example, functions vanishing on a certain submanifold, or first-class constraint algebra in Dirac’s theory).
-    3. A quotient (factor) algebra $\overline{A} = A/ I$ for some ideal $I$ related to $C$, representing the *reduced* algebra of observables after constraints are imposed and quotiented.
-
-    These are equipped with structure maps (inclusions and projections) satisfying compatibility conditions (e.g.
-$I$ is the ideal of relations defining $C$) .
-Intuitively, one has $C$ as the "constraint algebra" (functions that vanish on the constraint surface) and $\overline{A}$ as the algebra of functions on the quotient of that constraint surface by symmetries.
-Dippel, Esposito & Waldmann formalized this in the context of Poisson algebras and deformation quantization , showing that many reduction procedures can be understood as functors on such triples.
-
-    We adopt this idea in our setting: we will consider **constraint Gerstenhaber algebras** and **constraint BV-modules**, which are triples $(G, G_C, \overline{G})$ and $(M, M_C, \overline{M})$ capturing the full, constraint, and reduced parts of our algebraic Cartan calculus .
-All the structure (brackets, differentials, etc.) is assumed to exist on each part and to be compatible.
-For instance, a *constraint Gerstenhaber algebra* means $G$ is a Gerstenhaber algebra, $G_C \subset G$ a subalgebra (constraints), and $\overline{G} = G/G_C$ (some quotient) such that the wedge and bracket operations map triples to triples (roughly $[![G, G]!]$ sends $G_C$ to $G_C$ and induces well-defined operations on the quotient) .
-Similarly, a *constraint BV-module* $(M, M_C, \overline{M})$ has $M_C$ a submodule (the  "constraints on forms ") and $\overline{M}=M/M_C$ the quotient module, with differential $d$ and contractions $i_X$ etc.
-respecting the triples (so that, e.g., $d(M_C)\subseteq M_C$ and induces a differential on $\overline{M}$) .
-This is a bit of structure to keep track of, but conceptually it means we have *Cartan calculus not just on one algebra, but simultaneously on a sub- and a quotient algebra*.
-
-    - **Origin in Geometry:** If one has a manifold $M$ with a coisotropic submanifold $C\subset M$ (the constraint surface) and a group $G$ acting with gauge orbits, one can form a *constraint manifold* in the sense of Dippel-Kern 2025 .
-The algebra of smooth functions on a constraint manifold is exactly a constraint triple $(A, C, \overline{A})$ in which $C$ are the functions vanishing on the constraint surface and $\overline{A}$ functions on the quotient (when nice).
-Likewise, vector fields tangent to $C$ etc.
-form a constraint Lie-Rinehart algebra, and so on.
-Indeed, it has been shown that a **constraint Lie-Rinehart algebra** naturally induces a constraint Gerstenhaber algebra and constraint BV-module structures .
-So this framework is not lacking examples - it generalizes classical constrained Hamiltonian systems.
-- **Constraint $L_\infty$ of Observables:** Once we have constraint versions of $G$ and $M$ **and** a *constraint cocycle* $c = (c, c_C, \overline{c})$ (meaning $c$ lies in $M$, $c_C$ in $M_C$ and $\overline{c}$ is its class in $\overline{M}$, with each closed under their respective differentials), we can perform the same construction as before *in the category of constraint complexes*.
-That is, we define the **constraint Hamiltonian pairs** as triples $((X, X_C, \overline{X}), (m, m_C, \overline{m}))$ such that $i_X(c) = d m$, $i_{X_C}(c_C) = d m_C$ and these are compatible/projection of the first (so $\overline{X}$ and $\overline{m}$ are the images of $X,m$, etc.) .
-All such triples form a constraint graded space of observables.
-**Theorem C** asserts that this constraint observables space carries a **constraint $L_\infty$-algebra** structure .
-By  "constraint $L_\infty$-algebra, " we mean an $L_\infty$ whose underlying structure is also a triple $(L, L_C, \overline{L})$: there are brackets $\ell_r$ on each of $L, L_C, \overline{L}$, and the inclusion/projection maps intertwine these (so that $L_C$ is an $L_\infty$-subalgebra and $\overline{L}$ the quotient $L_\infty$) .
-The brackets are defined using the same formulas as in the unconstrained case, applied levelwise to $(G, M, c)$, $(G_C, M_C, c_C)$ and inducing $(\overline{G}, \overline{M}, \overline{c})$ .
-The $L_\infty$ identities hold simultaneously on each level by the same reasoning as before, thanks to the compatibility of the constraint data.
-- **Reduction Functor:** Once we have a constraint $L_\infty$-algebra of observables, *reducing it* means passing to the **quotient part** of the constraint triple.
-In categorical terms, there is a forgetful functor sending a constraint object $(X, X_C, \overline{X})$ to the quotient $\overline{X}$.
-When we apply this to the constraint $L_\infty$ of observables, we obtain an $L_\infty$-algebra on $\overline{L}$, which we interpret as the **reduced $L_\infty$-algebra of observables** of the constrained system.
-Intuitively, this $\overline{L}$ encodes observables that are invariant under the symmetry and defined on the constraint surface (since we mod out those that vanish or differ by constraint terms) .
-By construction, all the $L_\infty$ brackets descend to $\overline{L}$, so the homotopy Lie structure is well-defined on the quotient.
-This algebra $\overline{L}$ is the algebraic analog of the Poisson algebra of the reduced phase space in classical reduction, but here it can handle the homotopy brackets arising from a multisymplectic form and even if no nice manifold quotient exists (e.g.
-in singular cases).
-- **Recovery of Known Results:** Our general reduction scheme, when applied to the **geometric case** of a multisymplectic manifold with a group action, reproduces the results of our earlier work (Blacker-Miti-Ryvkin, SIGMA 2024) .
-In that work, we constructed a reduced $L_\infty$ of observables by more ad-hoc means; now we see it fits into the constraint triple framework.
-Specifically, given a Lie group $G$ acting on an $n$-plectic manifold $(M,\omega)$ with a covariant momentum map $\mu$ , one can form the constraint triple:
-    - $A = $ observables $L_\infty$ on $(M,\omega)$,
-    - $A_C = $ those observables that vanish on the constraint (e.g. forms pulled back by $\mu$ setting to zero, etc.),
-    - $\overline{A} = $ observables on the reduced space (when $0$ level set mod $G$ is nice, these correspond to forms on the quotient).
-
-    Our formalism shows that $\overline{A}$ inherits an $L_\infty$-algebra structure automatically .
-No assumptions of regularity or freeness are needed in the algebraic approach - even if the quotient is singular, $\overline{A}$ is well-defined as a homotopy algebra.
-This extends the multisymplectic reduction of Blacker 2021 (which assumed regularity) to a far more general context .
-Moreover, within our algebraic setting we identify an object called the **residue defect**, which measures the slight difference between naive and actual reduction in the homotopy context.
-In the earlier work, this residue term appeared somewhat mysteriously to satisfy the homotopy Jacobi identities; here we can interpret it cleanly as arising from the constraint differential and the failure of a certain exactness on the constraint submodule.
-Our framework **clarifies the role of the  "residue defect "**: it is an intrinsic part of the constraint $L_\infty$ structure that vanishes under appropriate conditions (like when the momentum map level is regular) .
-
-- **Summary of Main Results:** We can summarize the main technical results (theorems) as follows:
-    - **Theorem A:** *Given any Gerstenhaber algebra $G$ with a BV-module $M$ and a closed element $c\in M$, the graded space of Hamiltonian pairs $\mathcal{O}(G,M;c)$ admits an $L_\infty$-algebra structure (observables algebra), defined by the multilinear maps derived from Cartan calculus.*
-    - **Theorem B:** *If $(A,E)$ is a **constraint** Lie-Rinehart algebra (constraint version of derivations over a constraint algebra $A$), then one naturally obtains a constraint Gerstenhaber algebra and a constraint BV-module $(G, M)$ out of it.
-(In short, classical constraint manifolds yield constraint Cartan calculus algebraically.)
-    - **Theorem C:** *Given a constraint Gerstenhaber algebra and BV-module with a constraint cocycle $c$, one can construct a **constraint** $L_\infty$-algebra of observables.
-Moreover, its **reduced part** $\overline{\mathcal{O}}$ (the quotient level) is an $L_\infty$-algebra that describes the observables of the reduced system.*
-
-    As an application, Theorem C applied to multisymplectic manifolds with symmetries recovers the reduced $L_\infty$ in  and explains the extra terms (residue defect) in a categorical way .
-
-## **Conclusion and Outlook**
-
-We have developed a **purely algebraic toolkit** for constructing and reducing $L_\infty$-algebras of observables, extending concepts from symplectic geometry to multisymplectic and even noncommutative settings .
-This framework shows the power of combining homotopy algebra (for observables) with constraint category theory (for reduction).
-It provides a unified perspective where classical geometric reduction is just one instance of an algebraic functor acting on $L_\infty$-algebras .
-
-Some directions for further research include:
-
-- **Homotopy Momentum Maps:** Relating our constraint $L_\infty$-reduction to the notion of *homotopy momentum maps* (which appear in alternative higher reduction approaches, e.g.
-the work of Callies-Frégier-Rogers-Zambon on $L_\infty$-moment maps .
-It would be interesting to connect the **Leibniz-algebra-valued momentum maps** used here  with homotopy moment maps in an $L_\infty$-context.
-- **Operadic Formulation:** The constraint triple constructions hint at an operadic or higher-categorical organization.
-One could aim to describe the entire process (Cartan calculus + constraints + $L_\infty$) in terms of operads or properads encoding these algebraic relations .
-This might streamline proofs and allow further generalizations (e.g.
-to quantum or $A_\infty$ settings).
-- **Applications to Field Theory:** Ultimately, multisymplectic forms arise in classical field theory (e.g.
-the 2-form in mechanics vs.
-a 3-form in 2-dimensional field theory).
-Our algebraic observables $L_\infty$ could serve as a foundation for understanding *higher Poisson brackets* on the phase space of fields and their reduction under symmetries.
-Recent works on polysymplectic and polycontact reduction provide complementary geometric approaches; linking those with our algebraic method is a promising avenue.
-
-**References:** *(Selected key references in context)* Rogers (2012) for the original multisymplectic $L_\infty$-algebra construction; Dippel-Esposito-Waldmann (2019) for constraint (coisotropic) triples in Poisson algebra setting; Blacker-Miti-Ryvkin (2024) for algebraic multisymplectic reduction; and our work Miti-Ryvkin (2025) (Differential Geom.
-Appl.) which this talk is based on, for full details and proofs.
-The methods presented exemplify how **pure algebraic techniques can not only recover but also enlighten classical geometric results** in higher symplectic geometry, broadening the scope to singular and noncommutative realms.

### 2025-10-22 bv-triples-background.tex
Background complete. ToninusThem updated.

@@
 
+  \begin{quote}
+    \centering
+    \emph{... generalize the structure of vector fields acting as derivations ...}
+  \end{quote}
+
   \begin{defblock}[Lie-Rinehart Algebra]
-    A pair $(A,E)$ where
-    \begin{itemize}
+    A \underline{triple} $(A,\mathfrak{L},\rho)$ where
+    \begin{itemize}[label=$\triangleright$]
       \item $A$ is a commutative, associative algebra,
-      \item $E$ is an $A$-module and a Lie algebra,
-      \item there is an anchor map $\rho: E \to \mathrm{Der}(A)$ satisfying the Leibniz rule:
-        \[
-          [X, aY] = a[X,Y] + (\rho(X)a)Y, \quad \forall X,Y \in E, a \in A.
-        \]
-    \end{itemize}
-  \end{defblock}
+      \item $\mathfrak{L}$ is an $A$-module and a Lie algebra,
+      \item there is an anchor map $\rho: \mathfrak{L} \to \mathrm{Der}(A)$ satisfying the Leibniz rule:
 
-\begin{itemize}
-  \item Encodes derivations + Lie algebra structure.
+      \vspace{-.5em}
+        $$
+          [X, aY] = a[X,Y] + (\rho(X)a)Y, \quad \forall X,Y \in \mathfrak{L}, a \in A.
+        $$
     \end{itemize}
 
-  \begin{exblock}
-    If $A=C^\infty(M)$, then $E=\Gamma(TM)$ with $\rho=\mathrm{id}$ is a Lie-Rinehart algebra.
+  \end{defblock}  
+  \pause\vfill
 
-    Lie-Rinehart algebras are algebraic analogues of Lie algebroids (and every Lie algebroid gives a Lie-Rinehart algebra)
+  \begin{exblock}[Derivations]
+    $$
+      A=\text{any commutative algebra}~, \qquad \mathfrak{L}=\mathrm{Der}(A)~,\qquad \rho=\mathrm{id}
+    $$ 
+  \end{exblock}
+  \pause\vfill
+
+  \begin{exblock}[Vector fields]
+    $$
+      A=C^\infty(M)~,  \qquad \mathfrak{L}=\Gamma(TM)~,\qquad \rho=\mathrm{id}
+    $$ 
+    \begin{quotation}
+      \centering
+      Lie-Rinehart algebras are algebraic analogues of Lie algebroids
+      \\
+      (and every Lie algebroid gives a Lie-Rinehart algebra)
+    \end{quotation} 
+  \end{exblock}
+  \vfill
+
+\end{frame}
+\note[itemize]{
+    \item Let ${A}$ be a commutative  algebra over a field $\mathbb{k}$.
+  Denote by $\X(A)=\Der_{\mathbb{k}}(A)$ its Lie algebra of derivations, which naturally forms an $A$-submodule of $\End(A)$ with the action $A\action \End(A)$ given by postmultiplying with the element of $A$.
+  \item In the context of differential geometry, a primary example is when $A = C^\infty(M)$, the algebra of smooth functions on a smooth manifold $M$.
+In this case, $\mathfrak{X}(A)$ is isomorphic to the standard $C^\infty(M)$-module of smooth vector fields on $M$, often denoted by $\mathfrak{X}(M)$.
+  \item To generalize the above geometric structures, we introduce the algebraic counterparts of  "multivector fields " and  "differential forms with Cartan calculus. " 
+  \item The anchor map $\rho: E \to \mathop{\mathrm{Der}}(A)$ abstractly encodes the notion of derivations of $A$ with an $A$-linear Lie bracket. 
+  \item   In fact, Lie-Rinehart algebras are algebraic analogues of Lie algebroids (and every Lie algebroid gives a Lie-Rinehart algebra).
+  \item singular foliations in the sense of Androulidakis and Skandalis can be viewed as Lie--Rinehart algebras
+  \item a Lie--Rinehart algebra over $C^{\infty}(M)$ that is projective as a module is equivalent to a Lie algebroid,  
+}
+%-----------------------------------------------------------+
+
+%-----------------------------------------------------------+
+\begin{frame}{Gerstenhaber Algebras}
+
+  \begin{quote}
+    \centering
+    \emph{... generalize the structure of the exterior algebra of multivector fields ...}
+  \end{quote}
+  %
+  \begin{defblock}[Gerstenhaber Algebra]
+    A \underline{triple} $(G, \wedge, \lbrace\cdot,\cdot\rbrace)$ where
+    \begin{itemize}[label=$\triangleright$]
+		\item $G$ is a $\mathbb{Z}$-graded vector space;
+		\item $\wedge : G \otimes G \to G$ is a graded commutative, associative product;
+		\item $\{\blank,\blank\} :G[1]\otimes G[1]\to G[1]$ is a graded Lie bracket,
+  \end{itemize}
+Compatibility: The bracket is a derivation of $\wedge$:
+	\begin{align*}\label{eq:Gerstenhaber-derivationProperty}
+		\{a, b \wedge c\} = \{a, b\} \wedge c + (-1)^{(|a|-1)|b|} b \wedge \{a, c\}
+		&& \forall~ a, b, c \in G.
+	\end{align*}
+
+  \end{defblock}  
+    \vfill\pause
+
+    \begin{exblock}[Exterior algebra of a Lie-Rinehart algebra]
+      $G = \Lambda^\bullet \mathfrak{L}$ for a Lie-Rinehart algebra $(A,\mathfrak{L},\rho)$ with $\lbrace\cdot,\cdot\rbrace$ the Schouten-Nijenhuis bracket extending the Lie bracket on $E$.
     \end{exblock}
@@
 \note[itemize]{
-  \item To generalize the above geometric structures, we introduce the algebraic counterparts of  "multivector fields " and  "differential forms with Cartan calculus. " 
-  \item  A  Lie-Rinehart algebra  $(A,E)$ consists of a commutative associative algebra $A$ (think of $A=C^\infty(M)$) and an $A$-module $E$ (think of $E=\mathfrak X(M)$, the vector fields) which is also a Lie algebra, together with an *anchor* map $\rho: E \to \mathop{\mathrm{Der}}(A)$ (derivations of $A$) satisfying a Leibniz rule: $[X, aY] = a[X,Y] + (\rho(X)a),Y$.
-This abstractly encodes the notion of derivations of $A$ with an $A$-linear Lie bracket.
-  \item Example: If $A=C^\infty(M)$, then $E=\Gamma(TM)$ (the module of vector fields) with the identity anchor $\rho(X)=X$ is a Lie-Rinehart algebra. 
-  \item   In fact, Lie-Rinehart algebras are algebraic analogues of Lie algebroids (and every Lie algebroid gives a Lie-Rinehart algebra).}
-%-----------------------------------------------------------+
-
-%-----------------------------------------------------------+
-\begin{frame}{Gerstenhaber Algebras}
-  \emph{A graded algebra that captures the structure of exterior algebra of multivector fields.}
+  \item  The bracket $\{\blank,\blank\}$ could also be reinterpreted as a degree $-1$ bracket on the desuspended $\Z$-graded vector space $G$, coincides with the definition of $1$-Poisson algebra of \cite{Cattaneo2006b}.
+  \item The Schouten--Nijenhuis bracket is the unique graded Lie bracket satisfying the following properties:
+\begin{itemize}
+	\item It restricts to the given Lie bracket on $\Lambda_A^1 \mathfrak{L} = \mathfrak{L}$;
+	\item It vanishes on $A = \Lambda_A^0 \mathfrak{L}$;
+	\item It satisfies the graded Leibniz rule with respect to the wedge product.
+\end{itemize}
 %
-  \begin{defblock}[Gerstenhaber Algebra]
-    A triple $(\mathcal{G}, \wedge, [\cdot,\cdot])$ where
-    \begin{itemize}
-      \item $\mathcal{G} = \bigoplus_{i\in\mathbb{Z}} \mathcal{G}^i$ is a $\mathbb{Z}$-graded vector space,
-      \item $\wedge: \mathcal{G}^p \times \mathcal{G}^q \to \mathcal{G}^{p+q}$ is a graded-commutative, associative product (degree $0$ operation),
-      \item $[\cdot,\cdot]: \mathcal{G}^p \times \mathcal{G}^q \to \mathcal{G}^{p+q-1}$ is a bracket of degree $-1$, making $\mathcal{G}$ into a graded Lie algebra,
-      \item Compatibility (Leibniz rule): The bracket is a derivation of the product:
-        \[
-          [x, y\wedge z] = [x,y]\wedge z + (-1)^{(\deg x -1)\deg y} y\wedge [x,z]
-        \]
-        for homogeneous $x,y,z$.
-    \end{itemize}
-
-    \begin{exblock}%{Example}
-      If $(A,E)$ is a Lie-Rinehart algebra, the exterior algebra of $E$ (with a degree shift) carries a natural Gerstenhaber structure.
-    \end{exblock}
-
-    \begin{exblock}%{Example}
-      Take $\mathcal{G} = \Lambda^\bullet E$ (the exterior wedge algebra of $E$ treated as a graded space of multivectors).
-The wedge product is the usual wedge of multivectors, and the bracket is the Schouten-Nijenhuis bracket extending the Lie bracket on $E$ to all multivectors.
-This $(\Lambda E,\wedge,[\cdot,\cdot]_{SN})$ is a Gerstenhaber algebra, prototypical in geometry (for $E=\mathfrak X(M)$ one recovers the standard Gerstenhaber algebra of multivector fields on $M$).
-    \end{exblock}
-
-\end{frame}
-\note[itemize]{
-  \item  A Gerstenhaber algebra is a graded algebra that captures the structure of exterior algebra of multivector fields. 
-  \item Compatibility (Leibniz rule): The bracket is a derivation of the product: $[x, y\wedge z] = [x,y]\wedge z + (-1)^{(\deg x -1)\deg y} y\wedge [x,z]$ for homogeneous $x,y,z$.
-This is the defining Gerstenhaber identity, generalizing the fact that the Lie bracket of vector fields satisfies a Leibniz rule with respect to wedge of forms or functions.
+Explicitly, for homogeneous elements $x_1, \dots, x_m, y_1, \dots, y_n \in \mathfrak{L}$ and $f \in A$, it is given by
+\begin{align*}
+	[x_1 \wedge \cdots \wedge x_m,\; y_1 \wedge \cdots \wedge y_n] 
+	&= \sum_{i,j} (-1)^{i+j} [x_i, y_j] \wedge x_1 \wedge \cdots \widehat{x_i} \cdots \wedge x_m \wedge y_1 \wedge \cdots \widehat{y_j} \cdots \wedge y_n~.
+\end{align*}
 }
@@
   %
-  \begin{defblock}[Gerstenhaber Module]
-    A Gerstenhaber module over a Gerstenhaber algebra $(\mathcal{G}, \wedge, [\cdot,\cdot])$ is a graded module $\mathcal{M} = \bigoplus_{i\in\mathbb{Z}} \mathcal{M}^i$ together with an action
-    \[
-      \iota: \mathcal{G}^p \times \mathcal{M}^q \to \mathcal{M}^{q - p}
-    \]
-    satisfying:
-    \begin{itemize}
-      \item $\iota$ is $A$-linear in the second argument,
-      \item **Compatibility:** For homogeneous $x,y\in \mathcal{G}$ and $m\in \mathcal{M}$,
-        \[
-          \iota_{[x,y]} m = \iota_x (\iota_y m) - (-1)^{(\deg x -1)(\deg y -1)} \iota_y (\iota_x m).
-        \]
+  \begin{quote}
+    \centering
+    \emph{... generalize the structure of (Grassmann) algebra of differential forms...}
+  \end{quote}
+  %
+  \begin{defblock}[Gerstenhaber Module ~~{\small( over a Gers. Alg. $G$ )}]
+    A \underline{graded vector space} $V$ equipped with a \emph{Gerstenhaber algebra structure} \\ on $G\oplus V^{\mathrm{rev}}$ such that:
+    \begin{itemize}[label=$\triangleright$]
+      \item $G \hookrightarrow G\oplus V^{\mathrm{rev}}$ is a  Gerstenhaber subalgebra,
+      \item Both brackets and associative multiplication vanish when restricted to $V^{\rev}$
     \end{itemize}
+  \end{defblock}
+  \vfill\pause
 
-\begin{itemize}
-  \item $G$-module $M$ with contraction $\iota_X$ of degree $-\deg X$.
-  \item Induced Lie derivative $L_X = [d,\iota_X]$ when $d$ is defined.
-\end{itemize}
+  \begin{exblock}[Chevalley--Eilenberg Algebra]
+    The Chevalley--Eilenberg algebra for the Lie-Rinehart algebra $(A,\mathfrak{L},\rho)$:
+    $$
+    \CE(\mathfrak{L}) := \left((\Lambda_A^\bullet \mathfrak{L})^*\right)^{\rev}$$
+
+    carries a canonical structure of Gerstenhaber module over $\Lambda_A^\bullet \mathfrak{L}$. 
+  \end{exblock}
+
 \end{frame}
 \note[itemize]{
-  \item Gerstenhaber Module extends the idea of a multivector acting on forms by contraction. 
-  \item Concretely, for each element $X\in G^p$, we have a degree $-p$ operator $i_X: M^\ast \to M^{\ast-p}$ (interpreted as interior product by $X$) satisfying a compatible set of identities (graded derivations, etc.).
-  \item We also typically get an induced Lie derivative action $L_X$ of degree 0 defined by $L_X := [D,;i_X]$ once a differential $D$ is present (see below).
-We won’t detail the full set of axioms here, but essentially a Gerstenhaber module gives an algebraic version of the pair of operations $(i_X, L_X)$ acting on a  "forms " module, with $i$ being antiderivations and $L$ Lie derivations.
-  \item (The literature sometimes refers to this structure as a  "TTN (Tsygan-Tamarkin-Nest) calculus " .)}
+  \item  meta-concept: given a type of algebraic structure $\Gamma$ (e.g., associative, Poisson, Gerstenhaber, or Lie algebra) and a $\Gamma$-algebra $A$, the data of a module structure over $A$ can often be encoded as a $\mathbb{k}$-vector space $M$ together with a $\Gamma$-structure on $A \oplus M$, which:
+	\begin{itemize}
+		\item the inclusion $A \hookrightarrow A \oplus M$ is a $\Gamma$-algebra morphism,
+		\item squares to zero, i.e., the structure is trivial when restricting everything to $M$.
+	\end{itemize}
+  \item The two grading reversals from in the example cancel out, i.e.
+we have a Gerstenhaber algebra structure on $\Lambda\mathfrak{L}\oplus(\Lambda\mathfrak{L})^*$.
+However, if one omits both reversals, the formulas and gradings one obtains become inconsistent with the literature.
+  \item The algebra $\CE^\bullet(\mathfrak{L})$ is canonically endowed with the wedge product
+  \item $*$ stands for the $A$-linear dual. $\Hom_A(\Lambda_A^k \mathfrak{L}, A)$.
+  \item $\rev$ indicates the reversal of the grading, i.e., $(V^{\rev})^k = V^{-k}$.  
+}
 %-----------------------------------------------------------+
@@
   %
+  \begin{quote}
+    \centering
+    \emph{... generalize the structure of (the de Rham) algebra ...}
+  \end{quote}
+  %
   \begin{defblock}[Batalin-Vilkovisky Module]
-    A Batalin-Vilkovisky module (BV-module) over a Gerstenhaber algebra $(\mathcal{G}, \wedge, [\cdot,\cdot])$ is a Gerstenhaber module $(\mathcal{M}, \iota)$ together with a differential $d: \mathcal{M}^i \to \mathcal{M}^{i+1}$ (i.e.
-$d^2=0$) satisfying the Cartan identity:
-    \[
-      L_x := [d, \iota_x] = d \circ \iota_x + (-1)^{\deg x -1} \iota_x \circ d
-    \]
-    for all homogeneous $x\in \mathcal{G}$, where $L_x$ is the Lie derivative induced by the Gerstenhaber module structure.
+    Is a \underline{graded vector space} $V$ together with
+    \begin{itemize}[label=$\triangleright$]
+      \item a differential $\d: V^i \to V^{i+1}$ (i.e. $d^2=0$),
+      \item a Gerstenhaber module structure over a Gerstenhaber algebra $(G, \wedge, \lbrace\cdot,\cdot\rbrace)$,
+    \end{itemize}
+    Compatibility wrt the Lie algebra action $\Lie:G\action V$: 
+    $$
+      \Lie_x = [\iota_x, \d]~, \qquad \forall x \in G~.
+    $$
   \end{defblock}
+  \vfill\pause
+
+    \begin{exblock}[Chevalley--Eilenberg Algebra]
+    The Chevalley--Eilenberg algebra  $\CE(\mathfrak{L})$
+    carries a canonical differential
+\begin{align*}
+	\dCE(\alpha)&(x_1 \wedge \dotsb \wedge x_{k+1})
+  \qquad\qquad\qquad {\tiny(
+  \forall \alpha \in \CE^k(\mathfrak{L})~, x_1, \dotsc, x_{k+1} \in \mathfrak{L})}
+  \\
+  =&~\phantom{+} \sum_{i=1}^{k+1} (-1)^{i+1} \rho(x_i)\big(\alpha(x_1 \wedge \dotsb \widehat{x_i} \dotsb \wedge x_{k+1})\big) \\
+	&~+ \sum_{1 \leq i < j \leq k+1} (-1)^{i+j} \alpha\big(\lbrace x_i, x_j\rbrace \wedge x_1 \wedge \dotsb \widehat{x_i} \dotsb \widehat{x_j} \dotsb \wedge x_{k+1}\big)~,\\
+  &~.
+\end{align*}
+  \end{exblock}
 
@@
 \note[itemize]{
-  \item Batalin-Vilkovisky Modules (BV-Modules): A BV-module is a Gerstenhaber module that is also equipped with a differential of degree $+1$ (like an exterior derivative) satisfying Cartan’s formula.
-  \item Formally, let $G$ be a Gerstenhaber algebra and $(M,d)$ a cochain complex (so $d: M^i \to M^{i+1}$ with $d^2=0$).
-We say $M$ is a BV-module over $G$ if $M$ is a Gerstenhaber $G$-module and, for all $X\in G$, we have the Cartan identity $L_X = [d,; i_X]$ (and automatically $[L_X, i_Y] = i_{[X,Y]}$, etc.)  .
-  \item In other words, $M$ carries an action of $G$ by contraction $i_X$ and Lie derivative $L_X$ such that together with the differential $d$ they satisfy the standard graded commutation relations of Cartan calculus.
-\item We often call $d$ the BV differential.}
+  \item usually $\d$ is called \emph{BV differential}.
+  \item The algebra $\CE^\bullet(\mathfrak{L})$ is canonically endowed with the wedge product and a differential $\dCE \colon \CE^k(\mathfrak{L}) \to \CE^{k+1}(\mathfrak{L})$.
+The notation $\widehat{X_i}$ indicates omission of the $i$-th term from the wedge product.
+
+}
 %-----------------------------------------------------------+
@@
 \begin{frame}{Abstract Cartan Calculus}
+  %
+  \begin{quote}
+    \centering
+    \emph{BV-module $(V,\d)$ over $(G,\wedge,\lbrace\cdot,\cdot\rbrace)$ encode a full Cartan calculus}
+  \end{quote}
+  %
+  \vfill\pause
+  \begin{denotblock}
     \begin{itemize}
-  \item A Gerstenhaber module $M$ with differential $d$.
-  \item Cartan identity: $L_X = [d,\iota_X]$.
-  \item Encodes full algebraic Cartan calculus.
+      \item $\d$ the degree $1$ differential on $V$;
+	    \item $\iota$ the associative algebra action\footnote{$\iota_{x\wedge y}=\iota_x\iota_y~, \qquad \forall x,y\in G$.} of $(G,\wedge)$ on $V$;
+  	  \item $\Lie$ the Lie algebra action\footnote{$\Lie_{x\wedge y}=\iota_x\Lie_y + (-1)^{|y|}\Lie_x \iota_y~, \qquad \forall  x,y\in G$.} of $(G,\{\blank,\blank\})$ on $V$ of degree $-1$.
     \end{itemize}   
+  \end{denotblock}
+  \vfill\pause
 
-  \begin{itemize}
-  \item $(G,M,d)$ with $G$ Gerstenhaber, $M$ BV-module, $d^2=0$.
-  \item Examples: $(\mathfrak{X}^\bullet(M),\Omega^\bullet(M), d)$.
-  \item Extends to noncommutative and algebraic settings.
-\end{itemize}
+  \begin{lemblock}[Cartan identities]
+ The operators $\d$, $\iota_x$, and $\Lie_x$ satisfy six graded commutation relations:
+	%
+  \begin{align*}
+	  \d^2                            &= 0,            &&&
+	\iota_X \iota_Y + \iota_Y \iota_X  &= 0 ~,         \\
+\iota_X \d   +	\d \iota_X      &= \Lie_X ~,    &&&
+	\d \Lie_X - \Lie_X \d          &= 0 ~,    \\
+	\Lie_X \iota_Y - \iota_Y \Lie_X    &= \iota_{[X,Y]}~,  &&&
+	\Lie_X \Lie_Y - \Lie_Y \Lie_X      &= \Lie_{[X,Y]}~. 
+\end{align*}
+	%
+  \end{lemblock}
+  \vfill\pause
+
+  \begin{exblock}[Classical Cartan Calculus]
+    \vspace{-0.5em}
+    $$ A=C^\infty(M)~,  \quad \mathfrak{L}=\X(M)~,\quad
+     G=\Lambda^\bullet \X(M)~, \quad V=\Omega^\bullet(M)~. $$
+  \end{exblock}
+  %
 \end{frame}
-\note{Example (Classical Cartan Calculus): Take $G = \Lambda^\bullet \mathfrak X(M)$ (Gerstenhaber algebra of multivector fields on a manifold) and $M=\Omega^\bullet(M)$ (the de Rham complex of differential forms).
-This is a canonical example of a BV-module  : the differential $d$ is the exterior derivative, the contraction $i_X$ is the usual insertion of a multivector $X$ into a form, and the Lie derivative $L_X$ is the usual one acting on forms.
-These satisfy $L_X = d \circ i_X + i_X \circ d$ (Cartan formula) and all other Cartan identities.
-In fact, this example exactly recovers the classical Cartan calculus on $M$ as a BV-module structure on $\Omega^\bullet(M)$, with $G$ playing the role of  "polyvector fields " .
-This justifies the abstractions: any Gerstenhaber algebra + BV-module pair can be seen as a generalized  "space of multivectors and forms " with a full Cartan calculus available .
-We emphasize that such structures exist in much more general settings, including noncommutative geometry (where $A$ is a noncommutative algebra and one considers analogues of forms and multivectors  ), but for our purposes we stick to the algebraic axioms.}
+\note[itemize]{
+  \item 	A pair $(G, V)$ consisting of a Gerstenhaber algebra and a BV module is often called a \emph{Tsygan–Tamarkin–Nest noncommutative differential calculus}~\cite[Def.~4.4]{Tsygan2004}.
+  \item Denote Gerstenhaber algebra structure on $G \oplus V^{\rev}$ by $(\star,\llbracket\blank,\blank\rrbracket)$.
+For a homogeneous element $x \in G$, denote by $\iota_x$ and $\Lie_x$ the corresponding operators on $V$.
+  \item These actions are induced by restricting the Gerstenhaber structure $(\star,\llbracket\blank,\blank\rrbracket)$ on $G \oplus V^{\rev}$ to $G \otimes V^{\rev} \subset (G \oplus V^{\rev})^{\otimes 2}$.
+ \item The associative action $\iota$ is defined by
+	\[
+	\morphism{\iota}{G \otimes V^{\rev}}{V^{\rev}}{(x,\alpha)}{\iota_x \alpha := x \star \alpha},
+	\]
+	and satisfies
+	\[
+	\iota_{x \wedge y} \alpha = \iota_x \iota_y \alpha \quad \text{and} \quad \iota_x \alpha = (-1)^{|x||\alpha|} \alpha \star x.
+	\]
+
+	\item The Lie action $\Lie$ is defined by
+	\[
+	\morphism{\Lie}{G \otimes V^{\rev}}{V^{\rev}[-1]}{(x,\alpha)}{\Lie_x \alpha := \llbracket x, \alpha \rrbracket},
+	\]
+	and satisfies
+	\[
+	\Lie_{\{x,y\}} \alpha = \Lie_x \Lie_y \alpha + (-1)^{(|x|-1)(|y|-1)} \Lie_y \Lie_x \alpha,
+	\]
+	as well as the graded antisymmetry identity
+	\[
+	\Lie_x \alpha = -(-1)^{|x||\alpha|} \llbracket \alpha, x \rrbracket.
+	\]
+ \item The compatibility between $\star$ and $\llbracket\blank,\blank\rrbracket$ in $G \oplus V^{\rev}$ implies the following \emph{mixed Leibniz rules} (see \cite[Def.~2.1]{Kowalzig2015}):
+  \begin{align}
+	  \iota_{\{x,y\}} \alpha &= \Lie_x \iota_y \alpha - (-1)^{(|x|-1)|y|} \iota_y \Lie_x \alpha, \\
+	  \Lie_{x \wedge y} \alpha &= \iota_x \Lie_y \alpha + (-1)^{|x||y|} \iota_y \Lie_x \alpha. \label{eq:mixedleib}
+  \end{align}
+  \item The use of the reverse grading on $V$ in the definition ensures that for any homogeneous $x \in G^k$, the operators $\iota_x$ and $\Lie_x$ have degrees $-k$ and $1-k$, respectively, when viewed as endomorphisms of $V$.
+}
 %-----------------------------------------------------------+

### 2025-10-22 bv-triples-Rogers-generalized.tex
Observables section - complete

@@
-%- HandOut Flag -----------------------------------------------------------------------------------------
+%- HandOut Flag ----------------------
 \makeatletter
@@
 
+%- Bibliography (Biber) ----------------------------------------------------------------------------------
+\usepackage[backend=biber,style=alphabetic,maxnames=2]{biblatex}
+\bibliography{bibfile.bib}
+
 %===========================================================%
@@
 
-\begin{frame}{Hamiltonian Pairs}
+%-----------------------------------------------------------%
+\begin{frame}[fragile]{Abstract Hamiltonian Pairs}
+  \begin{quote}
+    \emph{Rogers construction naturally generalizes to a purely algebraic setting.}
+  \end{quote}
+  \vfill\pause
+
+  Data:
   \begin{itemize}
-  \item Data: $G$, $M$ BV-module, $c \in M$ closed.
-  \item Pair $(X,m)$ with $\iota_X c = d m$.
-  \item Generalizes $(X_f, f)$ in symplectic geometry.
+    \item $G = (G,\wedge,\lbrace \cdot, \cdot \rbrace)$ a Gerstenhaber algebra;
+    \item $V = (V,\d,\iota,\Lie)$ a BV-module over $G$;
+    \item $\omega \in V^{k{+}1}$ a fixed cocycle, i.e. $\d \omega = 0$, for $k\geq 1$.
   \end{itemize}
+  \vfill\pause
+
+  \begin{defblock}[Hamiltonian Pairs]
+    Elements of the graded vector space:
+	  $$
+		\Ham^0(V, \omega) := \left\{ (\alpha, X) \in V^{k-1} \oplus G^1 \mid \iota_X \omega = -\d\alpha \right\},
+    $$
+  \end{defblock}
+  \vfill\pause
+
+  \begin{remblock}[$\Ham^0(V, \omega)$ can also be viewed as the fibered product \( V^{k-1} \times_{V^k} G^1 \)]
+     over the following pullback in the category of vector spaces:
+	\begin{displaymath}
+		\begin{tikzcd}
+			\Ham^0(V, \omega) \arrow[r] \arrow[d] \ar[dr,"\lrcorner",very near start,phantom]& G^1 \ar[d,"\iota_{\blank}\omega"] \\
+			V^{k-1} \arrow[r, "-\d"] & V^{k}
+		\end{tikzcd}
+	\end{displaymath}
+  \end{remblock}
 \end{frame}
-\note{Given an algebraic Cartan calculus as above, we can now construct the $L_\infty$-algebra of observables in complete generality.
-The construction mirrors the one Rogers gave on manifolds, but now in purely algebraic terms.
+\note[itemize]{
+  \item The construction of the Roger's $L_\infty$-algebra  can be carried out for any BV-module equipped with a fixed $k+1$-cocycle $\omega$, i.e., for which $\d \omega = 0 $ with respect to the differential $\d$, since being a BV-module provides the structure of a complete Cartan calculus, which is all we need.
+}
+%-----------------------------------------------------------%
 
-- **Data:** Let $G$ be a Gerstenhaber algebra, $M$ a BV-module over $G$ with differential $d$, and let $c \in M^k$ be a fixed *cocycle*, meaning $d c = 0$. 
-Think of $c$ as the algebraic analog of a closed multisymplectic form (indeed in geometry $c$ could be $\omega$, which is closed by assumption).
-We also assume $c$ is *nondegenerate* in the sense that it induces the relevant pairings (this is automatic in the geometric case and can be treated as a cocycle condition in the algebraic case; for simplicity, we proceed assuming $c$ behaves like a  "volume form " or  "top form " to contract with).
-- **Hamiltonian Pairs:** We define a **Hamiltonian pair** as a pair $(X, m)$ with $X \in G$ (a multivector) and $m \in M$ (an element of the module) such that $X$ and $m$ are related by the cocycle $c$ via:
+%-----------------------------------------------------------%
+\begin{frame}{Abstract {$L_\infty$}-algebra of Observables}
 
-    $i_X(c) = d m$.
+\begin{defblock}[{$L_\infty$}-algebra of Observables]
+  The graded vector space $\Ham(V, \omega)$  given by
+  $$
+  \Ham(V, \omega)^i := \begin{cases}
+    V^{k-1 + i} & i \leq -1, \\
+    \Ham^0(V, \omega) & i = 0,\\
+    0 & i \geq 1~;
+  \end{cases} 
+  $$
+  with degree $(2-j)$ multibrackets $l_j\colon \Ham^{\otimes j}(V, \omega) \to \Ham(V, \omega)[2-j]$, given by:
 
-    In other words, $m$ is an element whose BV-differential equals the contraction of $c$ with $X$.
-This is directly analogous to the condition $i_{X_f}\omega = d f$ in the geometric case (here $X$ plays the role of $X_f$ and $m$ plays the role of the observable like $f$ or $\alpha$).
-We denote by $\mathsf{Ham}(G,M;c)$ the set of all Hamiltonian pairs.
-In graded terms, one typically considers homogeneous $X$ and $m$ of complementary degrees summing to $k-1$ (so that $i_X c$ has the same degree as $d m$).
+	\begin{itemize}
+		\item $
+			      l_1(\alpha) = \begin{cases}
+				      \d\alpha      & \text{if } i < -1, \\
+				      (\d\alpha, 0) & \text{if } i = -1, \\
+				      0             & \text{if } i = 0;
+			      \end{cases} $\\
+		\item $
+        l_2\big( (\alpha_1, X_1), (\alpha_2, X_2) \big) = \big( \iota_{X_1} \iota_{X_2} \omega, \{X_1, X_2\} \big);
+		      $\\
+		\item $
+          l_{j\geq 3}\big( (\alpha_1, X_1), \dots, (\alpha_j, X_j) \big) = -\iota_{X_1} \dots \iota_{X_j} \omega;
+		      $\\
+		\item All multibrackets of arity greater than or equal to $2$ vanish when evaluated on at least one degree nonzero element.
+	\end{itemize}
+\end{defblock}
+%
 
-    **Intuition:** A Hamiltonian pair $(X,m)$ means that $m$ is an *observable* whose  "derived bracket " with the cocycle $c$ yields $X$.
-If $c$ is nondegenerate, $X$ is uniquely determined by $m$ (just as a symplectic form gives a unique $X_f$ for each $f$), so we can think of $m$ as the *observable element* and $X$ as its *Hamiltonian generator*.
-However, in singular or degenerate cases, there could be multiple $X$ for a given $m$ or vice versa, hence it is safer to keep the pair.
-(In the construction we actually consider an appropriate quotient to identify pairs that give the same physical observable; more formally $\mathsf{Ham}(G,M;c)$ can be constructed as a fiber product $G \times_{M} M$ via the maps $X \mapsto i_X c$ and $m \mapsto d m$ .)}
+\end{frame}
+\note[itemize]{
+    \item 	The verification that the above definition yields an honest $L_\infty$-algebra can be directly adapted from~\cite[Thm.
+5.2]{rogers2012linfty} noticing that their proof is purely algebraic in nature and relies only on the Cartan calculus axioms.
+}
+%-----------------------------------------------------------%
 
-\begin{frame}{The Space and the Multibrackets}
-\begin{itemize}
-  \item Graded space $\mathcal{O}(G,M;c)$.
-  \item Brackets $\ell_k$ built from $d$, $\iota_X$, $L_X$, $[\cdot,\cdot]$.
-  \item $\ell_1 = d$, $\ell_2 = $ Lie + derived terms, $\ell_3 = i_{X_1}i_{X_2}i_{X_3}(c)$.
-\end{itemize}
+%-----------------------------------------------------------%
+\begin{frame}[fragile]{Abstract {$L_\infty$}-algebra of Observables (examples)}
+
+  \begin{exblock}[Observables $L_\infty$-algebra associated with a Lie--Rinehart algebra]
+    Let $(A, \mathfrak{L})$ be a Lie--Rinehart algebra, $\omega \in \CE(\mathfrak{L})^{k+1}$ a cocycle.
+    \\
+    We get an $L_\infty$-structure on the complex
+	\begin{displaymath}
+		\begin{tikzcd}[]
+			A \arrow[r] &
+			\mathfrak{L}^* \arrow[r] &
+			\cdots \arrow[r] &
+			(\Lambda^{k-2} \mathfrak{L})^* \arrow[r] &
+			(\Lambda^{k-1} \mathfrak{L})^* \times_{(\Lambda^k \mathfrak{L})^*} \mathfrak{L}
+		\end{tikzcd}~.
+	\end{displaymath}
+\end{exblock}
+  \vfill\pause
+
+\begin{exblock} 
+	When 
+   $$ A=C^\infty(M)~, \qquad  \mathfrak{L}=\mathfrak{X}(M)$$
+   we retrieve the Roger's construction (given in the context of closed differential forms).
+\end{exblock}
+
 \end{frame}
-\note{- \textbf{Graded observables space:} We assemble the observables into a graded vector space as follows.
-
-\[
-\mathcal{O}(G,M;c)\;=\;\bigoplus_{j\ge 0}\mathcal{O}^j,
-\]
-
-where:
-
-- $\mathcal{O}^0$ (degree~0 part) is the space of Hamiltonian pairs $(X,m)$ as above (with $i_X c = d m$).
-- For higher degrees $j>0$, roughly speaking $\mathcal{O}^j$ consists of elements of $M$ of degree $(k-1+j)$ (or related shifts) corresponding to forms of lower degree than $c$.
-In fact, in Rogers' original construction for an $n$-plectic manifold, the $L_\infty$-algebra of observables was an $n$-term complex concentrated in degrees $0,1,\dots,n-1$.
-Here $k=n+1$ (degree of $c$), so one can show $\mathcal{O}(G,M;c)$ is concentrated in degrees $0$ up to $n-1$ (i.e.
-$0$ up to $k-2$).
-Degree~0 are Hamiltonian $(n-1)$-forms (with vector fields), degree~1 would be Hamiltonian $(n-2)$-forms, ..., up to degree $n-1$ corresponding to Hamiltonian $0$-forms (basic observables).
-We will not need the explicit formula for each degree in this talk; the key is that this graded space includes all would-be observables and their "Hamiltonian partners."}
-
-\begin{frame}{Examples}
-\begin{itemize}
-  \item Classical: $G=\mathfrak{X}^\bullet(M)$, $M=\Omega^\bullet(M)$, $c=\omega$.
-  \item Recovers Rogers’ multisymplectic $L_\infty$.
-  \item Other contexts: algebraic, noncommutative, etc.
-\end{itemize}
-\end{frame}
-\note{- **$L_{\infty}$-Algebra Structure:** **Theorem A** (Miti-Ryvkin 2025) states that under the above setup, $\mathcal{O}(G,M;c)$ carries a natural structure of an $L_\infty$-algebra (homotopy Lie algebra) whose brackets are defined using the data of the Gerstenhaber algebra $G$, the BV-module operations, and the cocycle $c$ .
-Concretely, the multilinear $L_\infty$ operations $\ell_r: \mathcal{O}^{\otimes r} \to \mathcal{O}$ (of degree $2-r$) are given by formulas analogous to those in the multisymplectic manifold case :
-    - The unary bracket $\ell_1$ (degree $+1$ map) is essentially induced by the BV differential $d$ on the observable part (it maps a degree~1 element to degree~0 by $\ell_1(m) = (X,d m)$ or something similar, and is zero on degree~0 pairs in the fully nondegenerate case).
-    - The binary bracket $\ell_2((X_1,m_1), (X_2,m_2))$ has a result in degree~0 and is given by
-
-        \[
-        \ell_2((X_1,m_1),(X_2,m_2)) \;=\; \big([X_1,X_2],\; L_{X_1}m_2 * (-1)^{|X_1|\cdot|X_2|}L_{X_2}m_1\big),
-        \]
-
-        which in the simplest case recovers the Poisson bracket structure (when $m$’s are functions, $L_{X_1}m_2 = X_1(m_2)$).
-The precise formula involves appropriate Koszul signs for graded elements .
-
-    - A tertiary bracket $\ell_3((X_1,m_1),(X_2,m_2),(X_3,m_3))$ can be defined using the cocycle $c$: essentially one can take $i_{X_1}i_{X_2}i_{X_3}(c)$ (which is an element of $M$) as part of the output (this corresponds to evaluating the 3-form on three vector fields to get a number or top-form), ensuring that the Jacobi identity holds up to homotopy.
-    - Higher brackets $\ell_r$ for $r>3$ may be zero or determined similarly by $c$ if its degree is larger.
-In fact, for an $(n+1)$-form $c$, all brackets $\ell_r$ with $r> n$ will vanish (so the $L_\infty$ is  "finite " or $n$-term) .
-
-    The upshot is that **all these brackets are built out of the operations $[\cdot,\cdot]$ in $G$, $i_X$, $L_X$, $d$, and contraction with $c$**, mimicking the standard formulas in coordinates.
-It is nontrivial but true that these operations satisfy the required homotopy Jacobi identities.
-The verification is essentially a translation of Rogers’ original proof to this abstract setting - since Rogers’ proof was  "purely algebraic in nature, " it adapts directly here .
-We have thus constructed an **$L_\infty$-algebra of observables** $\mathcal{O}(G,M;c)$ associated to any BV-module with a cocycle.
-This is the main result of the first part of the talk.
-
-    Example (Geometric Case): If we take $G = \Lambda^\bullet \mathfrak X(M)$, $M = \Omega^\bullet(M)$ (so classical Cartan calculus on a manifold), and $c = \omega$ an $n$-plectic form, then $\mathcal{O}(G,M;c)$ precisely recovers Rogers’ $L_\infty$-algebra of observables on $(M,\omega)$  .
-In degree 0, $\mathcal{O}^0$ consists of Hamiltonian $(n!-!1)$-forms (with their Hamiltonian vector fields), which are exactly Rogers’ observables.
-The brackets $\ell_r$ coincide with those defined by Rogers (up to sign conventions), and one can check the $L_\infty$ identities by the same calculations in Cartan calculus .
-This generality shows the power of the BV-module approach: any example of a Gerstenhaber algebra + cocycle yields such an $L_\infty$.
-For instance, one could even take noncommutative analogues (with a suitable cyclic cocycle playing the role of $c$) to get  "$L_\infty$-observables " in noncommutative geometry  , although we won’t explore that in this talk.}
+\note[itemize]{
+    \item b
+}
+%-----------------------------------------------------------%
 
@@
 
-\begin{frame}{Conclusion / Summary}
-\begin{itemize}
-  \item Algebraic formalism for $L_\infty$ observables via BV-modules.
-  \item Generalizes Rogers' result.
-  \item Enables reduction via constraint triples.
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Outlook}
-\begin{itemize}
-  \item Homotopy momentum maps.
-  \item Operadic reformulation.
-  \item Applications to field theory.
-\end{itemize}
-\end{frame}
+%===========================================================%
 

### 2025-10-22 bv-triples-reduction.tex
Observables section - complete

@@
 \checkpoint
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%	
+\subsection{Regular reduction} 
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%	
+\begin{frame}{Regular reduction in symplectic geometry}
+
+	\textbf{\color{UniGreen}Symplectic reduction:}~~
+	\\ 
+	{\it \small
+	Procedure associating to any (suitably regular) pair of symplectic manifold and Hamiltonian action another symplectic manifold of smaller dimension.}
+	\vfill
+
+	\pause
+
+	\begin{center}
+		\includegraphics[width=.5\textwidth]{Pictures/Reduction}	
+	\end{center}
+
+	\textbf{\color{UniGreen}In mechanics:}~~
+				\\
+			{\it \small
+				it embodies the process of restricting the dynamics of the system to the level sets of the conserved quantities pertaining to the symmetry group.		
+			}
+			\\[.2em]
+			\color{gray}\small( e.g. restricting to studying a point-like particle in a central potential by studying it in radial coordinates)
+
+\end{frame}
+\note[itemize]{
+	\item  \emph{(Credits to \href{https://math.gmu.edu/~cblacke/}{Casey Blacker} for the notes and to \href{https://arxiv.org/abs/1206.3302}{Christian Lessig} for the picture. See acknowledgements.}
+	\item  In classical mechanics symmetry reduction plays an important role. Mathematically, this is usually phrased in terms of Marsden-Weinstein reduction
+	\item {Symplectic Reduction} takes two inputs:
+	\\ 1. Hamiltonian $G$-space $(M,\omega,{\color{orange}G},{\color{blue}\mu})$
+	\\ 2. parameter ${\color{blue}\phi}\in\g^*$
+	\item The \emph{reduced space} is $M_\phi:={\color{blue}\mu^{-1}(\phi)}{\color{orange}/G_\phi}$.
+	\item (Marsden--Weinstein '74, Meyer '73) THM:\\
+		If $\mu^{-1}(\phi)\subset M$ is smooth and $G_\phi\curvearrowright \mu^{-1}(\phi)$ is free and proper, then there is a \textbf{unique symplectic form} $\omega_\phi\in\Omega^2(M_\phi)$ such that $\pi^*\omega_\phi = i^*\omega$.
+
+	\item Heuristic Approach to Reduction:
+	\\1. describe $G\curvearrowright M$ in terms of $\omega$ 	\hspace{1cm}
+	({\color{green}moment map $\mu$})
+	\\2. identify a distinguished reduced space \hspace{1cm}
+	({\color{green}reduction at $\mu=0$})
+	\\3. use the ambiguity in 1.\ to obtain a family of reduced spaces \hspace{1cm}
+	({\color{green}reduction at $\mu-\phi=0$, i.e.\ reduction at $\mu=\phi$}
+	\\
+	{\tiny Note: If $G_\phi\neq G$, then $\mu-\phi:M\to\g^*$ is not a moment map for either $G\curvearrowright M$ or $G_\phi\curvearrowright M$.}
+
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}{Reminder: momentum maps in symplectic geometry}\label{frame:symplecticmomaps}
+	Consider $\theta:G\curvearrowright M$ symplectic,~~ $\underline{\cdot}:\mathfrak{g}\to \mathfrak{X}(M)$ infinitesimal action.
+	\vfill
+
+	\begin{columns}[T]
+		\setlength{\belowdisplayskip}{5pt}
+		\begin{column}{.50\linewidth}
+			%
+			\centering \it
+			\onslide<2->{
+				\begin{defblock}[Equivariant moment map]
+					Smooth map $$\mu:M\to \mathfrak{g}^\ast$$
+					such that:
+					\begin{itemize}
+						\item[i.] $d\langle \mu,\xi\rangle = -\iota_{\underline{\xi}}\omega$ 
+						~\qquad, $\forall \xi \in \mathfrak{g}$
+						\item[ii.] $\mu \circ \theta_g = Ad_g^\ast \circ \mu$
+						 \qquad\small, $\forall g \in G$
+					\end{itemize}
+				\end{defblock}
+			}
+		\end{column}	
+		%
+		\onslide<2->{\vrule{}}
+		%
+		\begin{column}{.50\linewidth}
+			\onslide<3->{			
+				\begin{defblock}[Comoment map]
+					Linear map $$\widetilde{\mu}: \mathfrak{g}\to C^\infty(M,\omega)$$
+					such that:
+					\begin{itemize}
+						\item[i.] $d\widetilde{\mu}(\xi) = -\iota_{\underline{\xi}}\omega$ 
+						\qquad~\small, $\forall \xi \in \mathfrak{g}$
+						\item[ii.] $\widetilde{\mu}([\xi,\eta]) = \lbrace\widetilde{\mu}(\xi),\widetilde{\mu}(\eta)\rbrace$ \small, $\forall \xi,\eta \in \mathfrak{g}$
+					\end{itemize}
+				\end{defblock}
+			}
+		\end{column}	
+	\end{columns}	
+	%
+	\pause
+	\vspace{1em}
+	%
+	\begin{columns}[]
+		\setlength{\belowdisplayskip}{5pt}
+		\begin{column}{.40\linewidth}
+			%
+			\centering \it
+			\onslide<5->{
+				\begin{upshotblocktitle}[Duality]
+					\begin{displaymath}
+						\mu(x) : \mathfrak{\xi} \mapsto \widetilde{\mu}(\xi)\big\vert_x
+					\end{displaymath}
+					%
+					\emph{
+					\small
+					"duality wrt. the currying operation"					
+					}
+				\end{upshotblocktitle}
+			}
+		\end{column}	
+		%
+		%
+		\begin{column}{.60\linewidth}
+			\onslide<4->{			
+				\begin{upshotblocktitle}[$\widetilde{\mu}$ as a lift]
+					\begin{displaymath}
+						\begin{tikzcd}[ampersand replacement = \&]
+						 \& C^\infty(M,\omega) \ar[d,"\vHam"]
+						 \\
+						 \mathfrak{g} \ar[ur,dashed,sloped,"\widetilde{\mu}"]\ar[r,"\underline{\cdot}"'] \& \mathfrak{X}(M)
+						\end{tikzcd}
+					\end{displaymath}
+					%
+					\emph{
+					\small
+					"it is a lift (in the Lie category) of the infinitesimal action by the assigment of hamiltonian v.fields."					
+					}
+				\end{upshotblocktitle}
+			}
+		\end{column}	
+	\end{columns}		
+\end{frame}
+\note[itemize]{
+		\item Moment maps are instrumental to the proper formalization of reduction in symplectic geometry.
+		\item consider an action preserving the symplectic form.
+		\item[-] $\langle \cdot, \cdot \rangle$ is the natural pairing of $\mathfrak{g}$ and $\mathfrak{g}^\ast$.
+			\item[-] $\theta_g$ is the diffeomorphism associated to $g\in G$ via $\theta:G\curvearrowright M$
+			\item[-] $Ad^\ast_g$ is the coadjoint action $G\curvearrowright \mathfrak{g}^\ast$
+		\item The moment map can be reexpressed as a comomentum map.
+		\item Observe that ii. on the left always implies ii. on the right. The converse is trure only if $G$ is connected.
+		\item $G\curvearrowright M$ is said "Hamiltonian" (see slide \ref{frame:gisthamaction} in appendix) iff $\exists$ comoment map $\widetilde{\mu}$.
+		\item \emph{moment map: Describe ${\color{orange}G\curvearrowright M}$ in terms of $\color{blue}C^\infty(M)\to\X(M)$.}
+		\begin{center}
+		\begin{tikzpicture}[scale=1.5]
+			\node[orange] (A) at (0,0) {$\g$};
+			\node[gray] (A1) at (0,-.3) {$\xi$};
+			\node[blue] (B) at (1,1) {$C^\infty(M)$};
+			\node[gray] (B2) at (1.55,1) {$f$};
+			\node[orange] (C) at (1,0) {$\X(M)$};
+			\node[gray] (C1) at (1,-.3) {$\underline\xi$};
+			\node[gray] (C2) at (1.55,0) {$X_f$};
+
+			\path[->,blue,dashed] (A) edge node[above left] {$\langle\mu,\cdot\,\rangle$} (B);
+			\path[->,orange] (A) edge (C);
+			\path[->] (B) edge (C);
+			\path[|->,gray] (A1) edge (C1);
+			\path[|->,gray] (B2) edge (C2);
+
+			\begin{scope}[xshift=3cm]
+				\node at (-.32,.8) {as Lie algebras};
+				\node at (-.13,.2) {i.e., {\color{blue}$\mu_\xi$} generates {\color{orange}$\underline\xi$}};
+			\end{scope}
+		\end{tikzpicture}
+
+			\footnotesize		(\emph{moment map:} ${\color{blue}\mu:M\to\g^*}$, 
+		 \emph{Hamiltonian $G$-space:} 	$(M,\omega,G,\mu)$)
+		\end{center}
+		\item
+		 $\alpha\mapsto X_\alpha$ is a homomorphism of Leibniz algebras:
+		$$\d\{\alpha,\beta\} = \d\L_{X_\alpha}\beta = \L_{X_\alpha}\iota_{X_\beta}\omega = \iota_{[X_\alpha,X_\beta]}\omega ~{\color{black!80} \implies}~
+		X_{\{\alpha,\beta\}} = [X_\alpha,X_\beta]$$
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}[fragile]{Marsden-Weinstein-Meyer reduction}
+	\begin{thmblock}[Marsden-Weinstein reduction \cite{MarsdenWeinstein74}]
+		\vspace{-.4em}\hspace{-1em}
+		\begin{tabular}{l p{14cm}}
+			Given: & $(M,\omega)$ symplectic
+			\\
+			& $\color{orange}G\curvearrowright M$ symplectic with equivariant momap. $\mu:M\to \mathfrak{g}^*$
+			\\[.2em]
+			Assume: & ${\color{blue}\phi} \in \mathfrak{g}^*$ regular value of $\mu$ 
+			\qquad\quad \footnotesize \textcolor{gray}{($\Rightarrow$ $\mu^{-1}(\phi)\hookrightarrow M$ smooth embedding)}
+			\\
+			& $G_\phi\curvearrowright \mu^{-1}(\phi)$ free and proper
+			\quad \footnotesize \textcolor{gray}{($\Rightarrow$ $\mu^{-1}(\phi)/G_\phi$ smooth manifold)}
+			\\[.4em]
+			Then: & \textbf{$\exists!$ symplectic structure} $\omega_\phi$ in $M_\phi:={\color{blue}\mu^{-1}(\phi)}{\color{orange}/G_\phi}$ \\
+			& s.t. $\pi^\ast \omega_\phi = j^\ast \omega$ 
+			\qquad {\footnotesize with $j:\mu^{-1}(\phi) \hookrightarrow M$ and $\pi:\mu^{-1}(\phi)\twoheadrightarrow M_\mu$}
+		\end{tabular}
+		\vspace{-.4em}
+	\end{thmblock}
+	%
+	\vfill
+	\begin{center}
+	\begin{tikzpicture}[scale=2]
+		\node[blue] (A) at (0,0) {$\mu^{-1}(\phi)$};
+		\node[gray] (A1) at (0,.3) {$i^*\omega$};
+		\node[gray] (A2) at (-.6,0) {$\pi^*\omega_\phi$};
+		\node[blue] (B) at (1,0) {$M$};
+		\node[gray] (B1) at (1,.3) {$\omega$};
+		\node[orange] (C) at (0,-.8) {$M_\phi$};
+		\node[gray] (C2) at (-.6,-.8) {$\omega_\phi$};
+
+		\path[right hook->,blue] (A) edge node[above] {$i$} (B);
+		\path[orange,->] (A) edge node[left] {$\pi$} (C);
+		\begin{scope}[xshift=-1.8cm]
+			\node[blue] at (0,0) {\small restrict to $\{\mu=\phi\}$};
+			\node[orange] at (.15,-.4) {\small quotient by $G_\phi$};
+		\end{scope}
+	\end{tikzpicture}
+	\end{center}
+	\pause
+	\vfill
+	\centering
+	The action of $G$ on $\mu^{-1}(0)$ is free and proper $\Rightarrow$ $0$ is reg. val. of $\mu$
+
+\end{frame}
+\note[itemize]{
+ \item 
+	Let $(M,\omega)$ symplectic, $G\circlearrowright M$ be a Lie group action\pause and $\mu:M\to \mathfrak g^*$ such that: 
+	\item  $\mu$ is a momentum, i.e. the infinitesimal action $\xi\mapsto \underline\xi:\mathfrak g\to \mathfrak X(M)$ of $G$ satisfies $X_{\langle\mu,\xi\rangle}=\underline \xi$. 
+	\item $\mu$ is $G$-equivariant, i.e. $\mu(gm)=Ad^*_g\mu(m)$ 
+	\item Then $\exists!$ symplectic form $\omega_r$ on $M_r=\frac{\mu^{-1}(0)}{G}$ such that $\pi^*\omega_r=i^*\omega$.
+%% https://q.uiver.app/#q=WzAsMyxbMCwwLCJNIl0sWzMsMCwiXFxtdV57LTF9KDApIl0sWzYsMCwiTV9yIl0sWzEsMCwiaVxcXFwgXFxzdWJzdGFja3tpbmNsdXNpb25+b2Z+c3Vic3BhY2V9IiwyLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoiaG9vayIsInNpZGUiOiJib3R0b20ifX19XSxbMSwyLCJcXHBpXFxcXCBcXHN1YnN0YWNre3F1b3RpZW50fmJ5fnJlbGF0aW9ufSJdXQ==
+%\[\begin{tikzcd}
+%	M &&& {\mu^{-1}(0)} &&& {M_r}
+%	\arrow["\begin{array}{c} i\\ \substack{inclusion~of~subspace} \end{array}"', hook', from=1-4, to=1-1]
+%	\arrow["\begin{array}{c} \pi\\ \substack{quotient~by~relation} \end{array}", two heads, from=1-4, to=1-7]
+%\end{tikzcd}\]
+
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\subsection{Singular reduction}
+\begin{frame}{Symplectic singular reduction schemes}
+	\begin{block}{The gist of singular reduction}
+		 \begin{itemize}
+			 \item[-] when $\mu$ is singular (i.e. $\mu^{-1}(0)$ is not a mfd.), the (geometrically) reduced space may not exist.
+			 \item[-] a \emph{singular reduction scheme} is a procedure to construct a "reduced" algebra of observable out of the given data
+			 \item[-] such that it corresponds to the algebra of observable of the reduced manifold in the regular case.
+		 \end{itemize}
+	\end{block}
+	 %
+	 \pause
+	 \vfill
+	 %
+	\begin{thmblock}[Sniatycki-Weinstein reduction \cite{SniatyckiWeinstein83}]
+		\vspace{-.4em}\hspace{-1em}
+		\begin{tabular}{l p{14cm}}
+			Given: & $(M,\omega)$ symplectic
+			\\
+			& $G\curvearrowright M$ symplectic with equivariant momap. $\mu:M\to \mathfrak{g}^*$
+			\\[.4em]
+			Then: & 
+			$\displaystyle \left[\sfrac{C^\infty(M)}{I_\mu}\right]^G$
+			admits a Poisson algebra structure 
+			\footnote{$I_\mu$ = associative ideal generated by $\widetilde{\mu}(\g)$}			
+			\\
+			& it agrees with the M--W reduction in the regular case.		
+		\end{tabular}
+		\vspace{-.4em}
+	\end{thmblock}
+ \end{frame}
+\note[itemize]{
+ \item Let $(M,\omega,G,\mu)$ be a symplectic Hamiltonian $G$-space.
+ \item The \emph{momentum ideal} is the associative ideal $I_\mu\subset C^\infty(M)$ generated by the momenta $\mu_{\xi}$ for any $\xi\in \mathfrak{g}$.
+		Namely
+		\[
+			I_\mu 
+			= 
+			\Big\langle \mu_\xi \Big\rangle_{\xi \in \mathfrak{g}}^{\text{\tiny asso.}} 
+			=
+			\left\{
+				\left.
+					\sum_{i=1}^n f_i ~ \mu_{\xi_i}
+				\right|~
+					f_i \in C^\infty(M),~ \xi_i\in \mathfrak{g},~  1 \leq i \leq n
+			\right\}
+		\]
+
+ \item The \emph{\'Sniatycki--Weinstein reduction} is the Poisson algebra
+		\[
+			\left(C^\infty(M)/I_\mu\right)^G.
+		\]
+
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\subsection{Constraints Algebras}
+\begin{frame}[fragile]{Attempting algebraic reduction naively}
+When the action is not 'free and proper', we can try to mimic this directly using the function algebras:
+% https://q.uiver.app/#q=WzAsNixbMCwwLCJNIl0sWzEsMCwiXFxtdV57LTF9KDApPVMiXSxbMywwLCJNX3IiXSxbMCwxLCJDXlxcaW5mdHkoTSkiXSxbMSwxLCJDXntcXGluZnR5fShTKT1cXGZyYWN7Q157XFxpbmZ0eX0oTSl9e0lfe1N9fSJdLFszLDEsIkNee1xcaW5mdHl9KE1fcik9Q15cXGluZnR5KFMpXkciXSxbMSwyLCJcXHN1YnN0YWNre3F1b3RpZW50fSIsMCx7InN0eWxlIjp7ImhlYWQiOnsibmFtZSI6ImVwaSJ9fX1dLFszLDQsIlxcc3Vic3RhY2t7cXVvdGllbnR9IiwwLHsic3R5bGUiOnsiaGVhZCI6eyJuYW1lIjoiZXBpIn19fV0sWzAsMSwiXFxzdWJzdGFja3tyZXN0cmljdGlvbn0iLDAseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dLFs0LDUsIlxcc3Vic3RhY2t7cmVzdHJpY3Rpb259IiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoic3F1aWdnbHkifX19XV0=
+\[\begin{tikzcd}
+	M & {\mu^{-1}(0)=S} && {M_r} \\
+	{C^\infty(M)} & {C^{\infty}(S):=\frac{C^{\infty}(M)}{I_{S}}} && {C^{\infty}(M_r)=C^\infty(S)^G}
+	\arrow["{\substack{restriction}}", squiggly, from=1-1, to=1-2]
+	\arrow["{\substack{quotient}}", two heads, from=1-2, to=1-4]
+	\arrow["{\substack{quotient}}", two heads, from=2-1, to=2-2]
+	\arrow["{\substack{restriction}}", squiggly, from=2-2, to=2-4]
+\end{tikzcd}\]
+
+where $I_S=\{f\in C^{\infty}(M)~|~f|_S=0\}$.
+\pause 
+\vfill
+Equivalently:
+
+% https://q.uiver.app/#q=WzAsMyxbMCwwLCJDXlxcaW5mdHkoTSkiXSxbMiwwLCJOX1M9XFx7Zn58fiBmXFxpbiBDXlxcaW5mdHkoTSl8X1N+fkdcXG1hdGhybXstaW52YXJpYW50fVxcfSJdLFs0LDAsIlxcZnJhY3tOX1N9e0lfU30iXSxbMCwxLCJcXHN1YnN0YWNre3Jlc3RyaWN0aW9ufSIsMCx7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6InNxdWlnZ2x5In19fV0sWzEsMiwiXFxzdWJzdGFja3txdW90aWVudH0iLDAseyJzdHlsZSI6eyJoZWFkIjp7Im5hbWUiOiJlcGkifX19XV0=
+\[\small\begin{tikzcd}
+	{C^\infty(M)} && {N_S=\{f~|~ f\in C^\infty(M)|_S~~G\mathrm{-invariant}\}} && {\frac{N_S}{I_S}}
+	\arrow["{\substack{restriction}}", squiggly, from=1-1, to=1-3]
+	\arrow["{\substack{quotient}}", two heads, from=1-3, to=1-5]
+\end{tikzcd}\]
+\pause
+\vfill
+
+\begin{alertblock}{Problem}
+	$C^\infty(S)^G=\frac{N_S}{I_S}$ is not a Poisson algebra in general.
+\end{alertblock}
+(when constraints not first class, cf. Dirac reduction)
+\end{frame}
+\note[itemize]{
+	\item \emph{(Credits to \href{https://www.ryvkin.eu/}{Leonid Ryvkin} for the tex code of this slide.)}
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}{Constraint Algebras} 
+	\begin{block}{Idea:}
+	    \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
+			\item[-] Both regular/geometric and singular/algebraic reduction are 2-steps procedures (1. restrict 2. quotient).
+			\item[-] Let's work in a category where all data needed for the reduction are bundled together in a suitable categorical objects. {\tiny (To avoid pathologies arising from these steps)}
+	    \end{itemize}
+	\end{block}
+	\pause
+	\vfill
+	\begin{defblock}[Constraint algebra triples \cite{Dippell2023}]
+		A (strong embedded) constraint algebra $\mathcal A$ is given by a triple $(\mathcal A_T, \mathcal A_N, \mathcal A_0)$, where
+		\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
+			\item[•] $\mathcal A_T$ is an algebra \emph{("total space")}
+			\item[•] $\mathcal A_N\subset \mathcal A_T$ a subalgebra  \emph{("normal space")}
+			\item[•] $\mathcal A_0\subset \mathcal A_N$ a two-sided ideal in $\mathcal A_T$ \emph{("zero space")}
+		\end{itemize}
+	\end{defblock}
+	\vfill
+	\pause
+	\begin{exblock}
+		Let $S$ be a closed set. Algebraically, we describe $C^\infty(S)$ by $\frac{C^\infty(M)}{I_S}$.
+		\\ 
+		We can think of it as the constraint triple:
+		$$
+			\mathcal A=(\mathcal A_T,\mathcal A_N,\mathcal A_0)=(C^\infty(M),C^\infty(M), I_S)
+		$$
+	\end{exblock}
+
+\end{frame}
+\note[itemize]{
+	\item  triples of the type (algebra , subalgebra, ideal).
+	\item After \cite{Dippell2023} we call such triples { \bf constraint triples} and their parts \emph{total space, normal space, zero space}.
+	\item It is a (strong) constraint algebra if $\mathcal A_0\subset \mathcal A_N\subset \mathcal A_T$ subalgebras and $\mathcal A_0\subset \mathcal A_T$ ideal.
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}{Other approaches to singular reduction}
+ 	Many singular reduction schemes adhere to this pattern!
+ 	\vfill
+ 	\pause
+\begin{table}[]
+	\begin{tabular}{l|l|l||l}
+		algebra $\mathcal{A}_T$ & subalgebra $\mathcal{A}_N$ & ideal $\mathcal{A}_0$ & comment \\
+		\hline
+
+		$C^\infty(M)$&      $N_S$     &   $I_S$   &  $\substack{S=\mu^{-1}(0),~ I_S=\{f~|~f|_S=0\}}$ \\
+			&&&  $\substack{N_S= \{ f | gf-f\in I_S \forall g\in G\}}$ \\
+	& & & \color{red} not Poisson \\ 
+	\hline	\pause
+	$C^\infty(M)$&   $F_S$         &   $I_S$   &  $\substack{F_S=\{f~|~\{f,I_S\}\subset I_S\}}$ \\
+	& & & \color{red} if $I_S\subset F_S$\\
+	\hline \pause
+
+	$C^\infty(M)$&   $C^\infty(M)^G$         &   $(I_S)^G$   &  $\substack{C^\infty(M)^G=\{f~|~gf=f\forall g\in G\}}$ \\
+	\hline \pause
+		$C^\infty(M)$&   $C^\infty(M)^G$         &   $(I_\mu)^G$   & $\substack{I_\mu=\{\sum_{i=1}^k f_i\langle \mu,\xi_i\rangle|~f_i\in C^\infty(M), \xi_i\in \mathfrak g\}}$\\
+		\hline \pause
+	$C^\infty(M)$&      $N_\mu$     &   $I_\mu$   & $\substack{N_\mu= \{ f | gf-f\in I_\mu \forall g\in G\}}$ \footnote{When $G$ connected $N_\mu=N(I_\mu):=\{f~|~\{f,I_\mu\}\subset I_\mu\}$.}\\
+	\hline
+
+	\end{tabular}\pause
+\end{table}
+	\vfill
+	{\bf Remarks }names in order: 'naive' , Dirac, Sniatycki, Arms-Cushman-Gotay, Sniatycki-Weinstein.
+
+\end{frame}
+\note[itemize]{
+	\item \emph{(Credits to \href{https://www.ryvkin.eu/}{Leonid Ryvkin} for the tex code of this slide.)}
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%------------------------------------------------------------------------------------------------
 

### 2025-10-23 bv-triples-main.tex
Background complete. ToninusThem updated.
Observables section - complete
Reduction Section almost done.

@@
 \renewcommand{\Ham}{\mathrm{Ham}}
-\newcommand{\Der}{\mathrm{Der}}
 \usepackage{enumitem}
@@
 	\checkpoint	
-	%\input{bv-triples-Rogers-generalized}
+	\input{bv-triples-Rogers-generalized}
 %-----------------------------------------------------------%
@@
 	\checkpoint	
-	%\input{bv-triples-reduction}
+	\input{bv-triples-reduction}
 %-----------------------------------------------------------%
@@
 
+%-------------------------------------------------------+
+\begin{frame}{Conclusion / Summary}
+\begin{itemize}
+  \item Algebraic formalism for $L_\infty$ observables via BV-modules.
+  \item Generalizes Rogers' result.
+  \item Enables reduction via constraint triples.
+\end{itemize}
+\end{frame}
+%-------------------------------------------------------+
+
+%-------------------------------------------------------+
+\begin{frame}{Outlook}
+\begin{itemize}
+  \item Homotopy momentum maps.
+  \item Operadic reformulation.
+  \item Applications to field theory.
+\end{itemize}
+\end{frame}
+%-------------------------------------------------------+
+
+%-------------------------------------------------------+
+% APPENDIX
+%-------------------------------------------------------+
+%-------------------------------------------------------+
+\appendix
+%-------------------------------------------------------+
+%-------------------------------------------------------+
+\section{Complementary Material}
+	\input{bv-triples-complementary-material}
 %------------------------------------------------------------------------------------------------
-% APPENDIX
+
 %------------------------------------------------------------------------------------------------
-\appendix
+\section{References \& Aknowledgments}
 %------------------------------------------------------------------------------------------------
-\section{Complementary Material}
-	%\input{bv-triples-complementary-material}
-	%\input{bv-triples-aknowledgements}
-%------------------------------------------------------------------------------------------------
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}[t,allowframebreaks]{Aknowledgments}
+	\begin{itemize}
+		\item MW reduction as "restriction to level sets", C. Lessig,
+			\href{https://arxiv.org/abs/1206.3302}{arXiv:1206.3302}
+		\item Several tex code snippets and slides in appendix are due to \href{https://www.ryvkin.eu/}{Leonid Ryvkin}.
+		\item Some tex code snippets are due to \href{https://math.gmu.edu/~cblacke/}{Casey Blacker}.
+
+	\end{itemize}
+\end{frame}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+% https://en.wikibooks.org/wiki/LaTeX/Bibliographies_with_biblatex_and_biber
+\begin{frame}[t,allowframebreaks]{Bibliography}
+	%\nocite{*}
+	\printbibliography
+\end{frame}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
 

### 2025-10-23 bv-triples-reduction.tex
Reduction Section almost done.

@@
 	{\it \small
-	Procedure associating to any (suitably regular) pair of symplectic manifold and Hamiltonian action another symplectic manifold of smaller dimension.}
+	Procedure associating to any (suitably regular) pair of \textbf{symplectic manifold} and \textbf{Hamiltonian action} another symplectic manifold of smaller dimension.}
 	\vfill
@@
 %- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\begin{frame}{Reminder: momentum maps in symplectic geometry}\label{frame:symplecticmomaps}
-	Consider $\theta:G\curvearrowright M$ symplectic,~~ $\underline{\cdot}:\mathfrak{g}\to \mathfrak{X}(M)$ infinitesimal action.
-	\vfill
+\begin{frame}[fragile]{Marsden-Weinstein-Meyer reduction}
+	Consider: \quad $(M,\omega)$ symplectic,\quad $\theta:G\curvearrowright M$ $G$-action,\quad $\underline{\cdot}:\mathfrak{g}\to \mathfrak{X}(M)$ $\g$-action.
+	\vfill\pause
 
-	\begin{columns}[T]
-		\setlength{\belowdisplayskip}{5pt}
-		\begin{column}{.50\linewidth}
-			%
-			\centering \it
-			\onslide<2->{
 	\begin{defblock}[Equivariant moment map]
-					Smooth map $$\mu:M\to \mathfrak{g}^\ast$$
-					such that:
-					\begin{itemize}
-						\item[i.] $d\langle \mu,\xi\rangle = -\iota_{\underline{\xi}}\omega$ 
-						~\qquad, $\forall \xi \in \mathfrak{g}$
-						\item[ii.] $\mu \circ \theta_g = Ad_g^\ast \circ \mu$
-						 \qquad\small, $\forall g \in G$
-					\end{itemize}
+		Smooth map $\quad\mu:M\to \mathfrak{g}^\ast\quad$ such that:
+
+		\quad {\it i)} $\d\langle \mu,\xi\rangle = -\iota_{\underline{\xi}}\omega$,
+		\qquad {\it ii)}  $\mu \circ \theta_g = Ad_g^\ast \circ \mu$,
+		\qquad $\forall \xi \in \mathfrak{g},~ \forall g \in G$.
 	\end{defblock}
-			}
-		\end{column}	
-		%
-		\onslide<2->{\vrule{}}
-		%
-		\begin{column}{.50\linewidth}
-			\onslide<3->{			
-				\begin{defblock}[Comoment map]
-					Linear map $$\widetilde{\mu}: \mathfrak{g}\to C^\infty(M,\omega)$$
-					such that:
-					\begin{itemize}
-						\item[i.] $d\widetilde{\mu}(\xi) = -\iota_{\underline{\xi}}\omega$ 
-						\qquad~\small, $\forall \xi \in \mathfrak{g}$
-						\item[ii.] $\widetilde{\mu}([\xi,\eta]) = \lbrace\widetilde{\mu}(\xi),\widetilde{\mu}(\eta)\rbrace$ \small, $\forall \xi,\eta \in \mathfrak{g}$
-					\end{itemize}
-				\end{defblock}
-			}
-		\end{column}	
-	\end{columns}	
-	%
-	\pause
-	\vspace{1em}
-	%
-	\begin{columns}[]
-		\setlength{\belowdisplayskip}{5pt}
-		\begin{column}{.40\linewidth}
-			%
-			\centering \it
-			\onslide<5->{
-				\begin{upshotblocktitle}[Duality]
-					\begin{displaymath}
-						\mu(x) : \mathfrak{\xi} \mapsto \widetilde{\mu}(\xi)\big\vert_x
-					\end{displaymath}
-					%
-					\emph{
-					\small
-					"duality wrt. the currying operation"					
-					}
-				\end{upshotblocktitle}
-			}
-		\end{column}	
-		%
-		%
-		\begin{column}{.60\linewidth}
-			\onslide<4->{			
-				\begin{upshotblocktitle}[$\widetilde{\mu}$ as a lift]
-					\begin{displaymath}
-						\begin{tikzcd}[ampersand replacement = \&]
-						 \& C^\infty(M,\omega) \ar[d,"\vHam"]
-						 \\
-						 \mathfrak{g} \ar[ur,dashed,sloped,"\widetilde{\mu}"]\ar[r,"\underline{\cdot}"'] \& \mathfrak{X}(M)
-						\end{tikzcd}
-					\end{displaymath}
-					%
-					\emph{
-					\small
-					"it is a lift (in the Lie category) of the infinitesimal action by the assigment of hamiltonian v.fields."					
-					}
-				\end{upshotblocktitle}
-			}
-		\end{column}	
-	\end{columns}		
-\end{frame}
-\note[itemize]{
-		\item Moment maps are instrumental to the proper formalization of reduction in symplectic geometry.
-		\item consider an action preserving the symplectic form.
-		\item[-] $\langle \cdot, \cdot \rangle$ is the natural pairing of $\mathfrak{g}$ and $\mathfrak{g}^\ast$.
-			\item[-] $\theta_g$ is the diffeomorphism associated to $g\in G$ via $\theta:G\curvearrowright M$
-			\item[-] $Ad^\ast_g$ is the coadjoint action $G\curvearrowright \mathfrak{g}^\ast$
-		\item The moment map can be reexpressed as a comomentum map.
-		\item Observe that ii. on the left always implies ii. on the right. The converse is trure only if $G$ is connected.
-		\item $G\curvearrowright M$ is said "Hamiltonian" (see slide \ref{frame:gisthamaction} in appendix) iff $\exists$ comoment map $\widetilde{\mu}$.
-		\item \emph{moment map: Describe ${\color{orange}G\curvearrowright M}$ in terms of $\color{blue}C^\infty(M)\to\X(M)$.}
-		\begin{center}
-		\begin{tikzpicture}[scale=1.5]
-			\node[orange] (A) at (0,0) {$\g$};
-			\node[gray] (A1) at (0,-.3) {$\xi$};
-			\node[blue] (B) at (1,1) {$C^\infty(M)$};
-			\node[gray] (B2) at (1.55,1) {$f$};
-			\node[orange] (C) at (1,0) {$\X(M)$};
-			\node[gray] (C1) at (1,-.3) {$\underline\xi$};
-			\node[gray] (C2) at (1.55,0) {$X_f$};
+	\vfill\pause
 
-			\path[->,blue,dashed] (A) edge node[above left] {$\langle\mu,\cdot\,\rangle$} (B);
-			\path[->,orange] (A) edge (C);
-			\path[->] (B) edge (C);
-			\path[|->,gray] (A1) edge (C1);
-			\path[|->,gray] (B2) edge (C2);
-
-			\begin{scope}[xshift=3cm]
-				\node at (-.32,.8) {as Lie algebras};
-				\node at (-.13,.2) {i.e., {\color{blue}$\mu_\xi$} generates {\color{orange}$\underline\xi$}};
-			\end{scope}
-		\end{tikzpicture}
-
-			\footnotesize		(\emph{moment map:} ${\color{blue}\mu:M\to\g^*}$, 
-		 \emph{Hamiltonian $G$-space:} 	$(M,\omega,G,\mu)$)
-		\end{center}
-		\item
-		 $\alpha\mapsto X_\alpha$ is a homomorphism of Leibniz algebras:
-		$$\d\{\alpha,\beta\} = \d\L_{X_\alpha}\beta = \L_{X_\alpha}\iota_{X_\beta}\omega = \iota_{[X_\alpha,X_\beta]}\omega ~{\color{black!80} \implies}~
-		X_{\{\alpha,\beta\}} = [X_\alpha,X_\beta]$$
-}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\begin{frame}[fragile]{Marsden-Weinstein-Meyer reduction}
 	\begin{thmblock}[Marsden-Weinstein reduction \cite{MarsdenWeinstein74}]
@@
 		\begin{tabular}{l p{14cm}}
-			Given: & $(M,\omega)$ symplectic
-			\\
-			& $\color{orange}G\curvearrowright M$ symplectic with equivariant momap. $\mu:M\to \mathfrak{g}^*$
+			Given: &   $\mu:M\to \mathfrak{g}^*$ equivariant moment map for $\color{orange}G\curvearrowright M$ $G$
 			\\[.2em]
@@
 	\end{center}
-	\pause
-	\vfill
-	\centering
-	The action of $G$ on $\mu^{-1}(0)$ is free and proper $\Rightarrow$ $0$ is reg. val. of $\mu$
 
@@
 %\end{tikzcd}\]
+	\item 	The action of $G$ on $\mu^{-1}(0)$ is free and proper $\Rightarrow$ $0$ is reg. val. of $\mu$
 
@@
 			admits a Poisson algebra structure 
-			\footnote{$I_\mu$ = associative ideal generated by $\widetilde{\mu}(\g)$}			
+			\footnote{$I_\mu$ = associative ideal generated by $\check{\mu}(\g)$ with $\check{\mu}(\xi):=\langle\mu,\xi\rangle$ the comomentum map.}			
 			\\
@@
 %- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\begin{frame}{Other approaches to singular reduction}
- 	Many singular reduction schemes adhere to this pattern!
+\begin{frame}{Constraint Gerstenhaber-Modules}
+
+%
+\begin{defblock}[Constraint Gerstenhaber algebra {(\cite[Def. 2.25]{dippelkern})}]
+	A constraint algebra $G=\triple{G}$ equipped with a constraint bilinear map
+	\begin{displaymath}
+		\{ \blank, \blank \} \colon G[1] \otimes G[1] \to G[1]
+	\end{displaymath}
+	such that $G_\Total$ is a Gerstenhaber algebra. 
+\end{defblock}
+\pause\vfill
+%
+
+ \begin{remblock}[$G$ can be seen as a triple of Gerstenhaber subalgebras]\label{rk:constraintgerst-as-triple}
+	 $G_\Null \subseteq G_\Wobs \subseteq (G_\Total, \wedge,\lbrace\blank,\blank\rbrace)$ such that $G_\Null$ is a Gerstenhaber ideal in $G_\Wobs$. 
+\end{remblock}
+\pause\vfill
+%
+
+\begin{defblock}[Constraint Gerstenhaber module]\label{def:constraintgerstmodule}
+	A constraint vector space $V=\triple{V}$ endowed with a constraint Gerstenhaber algebra structure on the space $G \oplus V^\rev$ such that the multiplication and the bracket are trivial when restricted to $V^\rev$.
+\end{defblock}
 \vfill
- 	\pause
-\begin{table}[]
-	\begin{tabular}{l|l|l||l}
-		algebra $\mathcal{A}_T$ & subalgebra $\mathcal{A}_N$ & ideal $\mathcal{A}_0$ & comment \\
-		\hline
-
-		$C^\infty(M)$&      $N_S$     &   $I_S$   &  $\substack{S=\mu^{-1}(0),~ I_S=\{f~|~f|_S=0\}}$ \\
-			&&&  $\substack{N_S= \{ f | gf-f\in I_S \forall g\in G\}}$ \\
-	& & & \color{red} not Poisson \\ 
-	\hline	\pause
-	$C^\infty(M)$&   $F_S$         &   $I_S$   &  $\substack{F_S=\{f~|~\{f,I_S\}\subset I_S\}}$ \\
-	& & & \color{red} if $I_S\subset F_S$\\
-	\hline \pause
-
-	$C^\infty(M)$&   $C^\infty(M)^G$         &   $(I_S)^G$   &  $\substack{C^\infty(M)^G=\{f~|~gf=f\forall g\in G\}}$ \\
-	\hline \pause
-		$C^\infty(M)$&   $C^\infty(M)^G$         &   $(I_\mu)^G$   & $\substack{I_\mu=\{\sum_{i=1}^k f_i\langle \mu,\xi_i\rangle|~f_i\in C^\infty(M), \xi_i\in \mathfrak g\}}$\\
-		\hline \pause
-	$C^\infty(M)$&      $N_\mu$     &   $I_\mu$   & $\substack{N_\mu= \{ f | gf-f\in I_\mu \forall g\in G\}}$ \footnote{When $G$ connected $N_\mu=N(I_\mu):=\{f~|~\{f,I_\mu\}\subset I_\mu\}$.}\\
-	\hline
-
-	\end{tabular}\pause
-\end{table}
-	\vfill
-	{\bf Remarks }names in order: 'naive' , Dirac, Sniatycki, Arms-Cushman-Gotay, Sniatycki-Weinstein.
 
@@
 \note[itemize]{
-	\item \emph{(Credits to \href{https://www.ryvkin.eu/}{Leonid Ryvkin} for the tex code of this slide.)}
+	\item  We have seen how the notion of BV-modules can be understood as a Cartan calculus. In this section, we will adapt this notion to the setting of constraint algebras and modules.
+	\item Details: constraint morphisms, tensor products, strongness.
+	\item the following four equations hold:
+	%
+	\begin{align*}
+		\{ G_\Wobs, G_\Wobs \} &\subseteq G_\Wobs~,&& G_\Wobs \wedge G_\Wobs \subseteq G_\Wobs~, \\
+		\{ G_\Null, G_\Wobs \} &\subseteq G_\Null~,&& G_\Wobs \wedge G_\Null \subseteq G_\Null ~.
+	\end{align*}
+	For a strong Gerstenhaber algebra, we would also need to check $G_\Null \wedge G_\Total \subseteq G_\Null$ as the only additional condition.
+	\item Since every constraint Gerstenhaber algebra is, in particular, a graded constraint algebra and a graded constraint Lie algebra, we know that ${G}_{\red}$ carries the structures of a graded algebra and a graded Lie algebra.
+Moreover, it is easy to see that the graded Leibniz rule on ${G}$
+induces a graded Leibniz rule on ${G}_{\red}$, showing that ${G}_{\red}$ forms itself a Gerstenhaber algebra.
+	\item An \emph{(embedded, $\mathbb Z$-graded) constraint vector space} $V$ is given by a triple $V=(V_\Total,V_\Wobs,V_\Null)$, where $V_\Total$ is a $\mathbb Z$-graded vector space and $V_\Null\subset V_\Wobs\subset V_\Total$ are subspaces.
+A \emph{morphism} $f:V\to V'$ of constraint vector spaces is a linear map $f:V_\Total\to V'_\Total$ such that $f(V_\Wobs)\subset V'_\Wobs$ and $f(V_\Null)\subset V'_\Null$.
 }
@@
 
-%------------------------------------------------------------------------------------------------
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}{Constraint Cartan calculus}
+%
+\begin{defblock}[Constraint BV-module]\label{def:constraintbv}
+	A Gerstenhaber module $V=\triple{V}$ endowed with a constraint degree $1$ homomorphism
+	$$
+		\d \colon V \to V[1]~,
+	$$
+	such that $(V_\Total, \d_\Total)$ is a BV-module over $G_\Total$.
+\end{defblock}
+\pause\vfill
+%
 
-\begin{frame}{Constraint Triples}
-\begin{itemize}
-  \item Triple $(A, A_C, \overline{A})$ with inclusion/projection.
-  \item $A_C$ encodes constraints, $\overline{A} = A/I$ reduced algebra.
-  \item Adapted to Gerstenhaber and BV-module settings.
-\end{itemize}
+\begin{remblock}[Constraint Cartan calculus]
+	The con. BV-module structure implies the existence of constraint morphisms
+	$$ \iota: G\otimes V^{\rev} \to V^{\rev}, \d: V \to V[1] \text{ and } \Lie: G\otimes V^{\rev} \to V^{\rev}[-1] $$ satisfying six commutation rules as before.
+\end{remblock}
+\vfill
+
 \end{frame}
+\note[itemize]{
+	\item 
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
 
-\begin{frame}{Constraint BV-Modules}
-\begin{itemize}
-  \item Triples $(G, G_C, \overline{G})$, $(M, M_C, \overline{M})$.
-  \item Structures compatible with Cartan calculus.
-  \item Closed cocycle triple $c = (c, c_C, \overline{c})$.
-\end{itemize}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}[shrink]{Constraint $L_\infty$ Algebra Associated with a constraint BV-module}
+	%
+	\begin{defblock}[Constraint $L_\infty$-algebras] 
+	A constraint vector space $L=\triple{L}$  equipped with a collection of constraint multilinear maps
+	\begin{displaymath}
+		l_j \colon L^{\otimes j} \to L[2-j]
+	\end{displaymath}
+	such that $(L_\Total, (l_j)_\Total)$ is an $L_\infty$-algebra.
+	\end{defblock}
+	\pause\vfill
+	%
+
+	Let $V$ a cons. BV-module over a cons. Gerst. algebra $G$,  $\omega\in V_\Wobs^{k+1}$ a cocycle.
+	\begin{defblock}[Constraint vector space of Hamiltonian pairs]\label{def:constraint-algebraicham0}
+		The	 constraint graded vector space:
+		$$
+		\Ham^0(V, \omega) := 
+		\colvec{
+			\big\{ (\alpha, X) \in V^{k-1}_\Total \oplus G_\Total^1 \mid \iota_X \omega = -\d\alpha \big\}
+			\\
+			\Ham^0(V, \omega) \cap \big(V_\Wobs \oplus G_\Wobs\big)
+			\\
+			\Ham^0(V, \omega) \cap \big( V_\Null \oplus G_\Null \big)
+		}
+		~.
+		$$
+	\end{defblock}
+	\pause\vfill
+	%
+
+	\begin{defthmblock}[Constraint $L_\infty$-algebra of observables]
+		The \emph{constraint $\Z$-graded vector space}
+  		$$
+  		\Ham(V, \omega)^i := 
+		\begin{cases}
+    		V^{k-1 + i} & i \leq -1, \\
+    		\Ham^0(V, \omega) & i = 0,\\
+    		0 & i \geq 1~;
+  		\end{cases} 
+  		$$
+	endowed with the family of cons. multilinear maps \( l_j \colon \Ham^{\otimes j}(V, \omega) \to \Ham(V, \omega)[2-j] \) defined via cons. multicontractions with $\omega$.
+	\end{defthmblock}
+
 \end{frame}
+\note[itemize]{
+	\item  Building on the chosen embedded constraint setting, one can further define constraint $L_\infty$-algebras in close analogy with the classical case.
+	\item 	Since we work in the embedded setting, a constraint $L_\infty$-algebra $L$ as per \autoref{def:constraintlinfty} is given by a sequence of $L_\infty$-subalgebras $L_\Null \subseteq L_\Wobs \subseteq (L_\Total,(l_j)_\Total)$ such that $L_\Null$ is in particular an $L_\infty$-ideal  in $L_\Wobs$ in the following sense:
+	\begin{displaymath}
+		l_j\big(L_\Null, L_\Wobs,\dots, L_\Wobs\big)
+		\subseteq L_\Null~, \quad \forall j \geq 1~.
+	\end{displaymath}
+	Therefore, is assured that the $L_\infty$-algebra structure on $L_\Total$ induces a well-defined $L_\infty$-algebra structure on the reduced space $\red(L) := L_\Wobs / L_\Null$ (compare with \autoref{rk:constraintalgebras-as-triples}).
+	\item 	The space of Hamiltonian pairs can be interpreted as the fibered product \( V^{k-1} \times_{V^k} G^1 \) in the category of constraint vector spaces. 
+	This perspective yields, in particular, three pullback diagrams, one for each component of the constraint vector space described.
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
 
-\begin{frame}{Constraint $L_\infty$ Algebra Associated with…}
-\begin{itemize}
-  \item Construct observables $\mathcal{O} = (\mathcal{O}, \mathcal{O}_C, \overline{\mathcal{O}})$.
-  \item Each component carries an $L_\infty$ structure.
-  \item Brackets compatible with inclusions/projections.
-\end{itemize}
-\end{frame}
-
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
 \begin{frame}{Reduction Functor}
@@
 \end{frame}
+\note[itemize]{
+	\item  
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
 
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
 \begin{frame}{Recovering Old Results}
@@
 \end{frame}
+\note[itemize]{
+	\item  This framework provides a unified approach to understanding various geometric and algebraic structures.
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
 

### 2025-10-23 bv-triples-Rogers-generalized.tex
Slides complete.

@@
 %- D0cum3nt ----------------------------------------------------------------------------------------------
-%\documentclass[beamer,10pt]{standalone}   
-\documentclass[beamer,10pt,handout]{standalone}  \Handouttrue
+\documentclass[beamer,10pt]{standalone}   
+%\documentclass[beamer,10pt,handout]{standalone}  \Handouttrue
 
@@
 
-	\begin{itemize}
+	\begin{itemize}[label=$\cdot$]
 		\item $
@@
 %===========================================================%
-
-We now turn to the second main part: **reduction** of the $L_\infty$-algebra of observables in the presence of constraints or symmetries.
-In symplectic geometry, reduction is accomplished by the Marsden-Weinstein quotient: one restricts to the zero level set of a momentum map and then quotients by the symmetry group.
-Algebraically, this corresponds to first imposing ideal relations (for the constraints) and then modding out by gauge symmetries.
-The **constraint triple** formalism packages these two steps (subobject and quotient) in a single algebraic structure .
-
-- **Constraint Triples:** A **constraint triple** (or **coisotropic triple**) in general consists of:
-    1. An algebra (or other structure) $A$ representing the full system’s observables.
-    2. A subalgebra $C \subset A$ representing the *constraints* (for example, functions vanishing on a certain submanifold, or first-class constraint algebra in Dirac’s theory).
-    3. A quotient (factor) algebra $\overline{A} = A/ I$ for some ideal $I$ related to $C$, representing the *reduced* algebra of observables after constraints are imposed and quotiented.
-
-    These are equipped with structure maps (inclusions and projections) satisfying compatibility conditions (e.g.
-$I$ is the ideal of relations defining $C$) .
-Intuitively, one has $C$ as the "constraint algebra" (functions that vanish on the constraint surface) and $\overline{A}$ as the algebra of functions on the quotient of that constraint surface by symmetries.
-Dippel, Esposito & Waldmann formalized this in the context of Poisson algebras and deformation quantization , showing that many reduction procedures can be understood as functors on such triples.
-
-    We adopt this idea in our setting: we will consider **constraint Gerstenhaber algebras** and **constraint BV-modules**, which are triples $(G, G_C, \overline{G})$ and $(M, M_C, \overline{M})$ capturing the full, constraint, and reduced parts of our algebraic Cartan calculus .
-All the structure (brackets, differentials, etc.) is assumed to exist on each part and to be compatible.
-For instance, a *constraint Gerstenhaber algebra* means $G$ is a Gerstenhaber algebra, $G_C \subset G$ a subalgebra (constraints), and $\overline{G} = G/G_C$ (some quotient) such that the wedge and bracket operations map triples to triples (roughly $[![G, G]!]$ sends $G_C$ to $G_C$ and induces well-defined operations on the quotient) .
-Similarly, a *constraint BV-module* $(M, M_C, \overline{M})$ has $M_C$ a submodule (the  "constraints on forms ") and $\overline{M}=M/M_C$ the quotient module, with differential $d$ and contractions $i_X$ etc.
-respecting the triples (so that, e.g., $d(M_C)\subseteq M_C$ and induces a differential on $\overline{M}$) .
-This is a bit of structure to keep track of, but conceptually it means we have *Cartan calculus not just on one algebra, but simultaneously on a sub- and a quotient algebra*.
-
-    - **Origin in Geometry:** If one has a manifold $M$ with a coisotropic submanifold $C\subset M$ (the constraint surface) and a group $G$ acting with gauge orbits, one can form a *constraint manifold* in the sense of Dippel-Kern 2025 .
-The algebra of smooth functions on a constraint manifold is exactly a constraint triple $(A, C, \overline{A})$ in which $C$ are the functions vanishing on the constraint surface and $\overline{A}$ functions on the quotient (when nice).
-Likewise, vector fields tangent to $C$ etc.
-form a constraint Lie-Rinehart algebra, and so on.
-Indeed, it has been shown that a **constraint Lie-Rinehart algebra** naturally induces a constraint Gerstenhaber algebra and constraint BV-module structures .
-So this framework is not lacking examples - it generalizes classical constrained Hamiltonian systems.
-- **Constraint $L_\infty$ of Observables:** Once we have constraint versions of $G$ and $M$ **and** a *constraint cocycle* $c = (c, c_C, \overline{c})$ (meaning $c$ lies in $M$, $c_C$ in $M_C$ and $\overline{c}$ is its class in $\overline{M}$, with each closed under their respective differentials), we can perform the same construction as before *in the category of constraint complexes*.
-That is, we define the **constraint Hamiltonian pairs** as triples $((X, X_C, \overline{X}), (m, m_C, \overline{m}))$ such that $i_X(c) = d m$, $i_{X_C}(c_C) = d m_C$ and these are compatible/projection of the first (so $\overline{X}$ and $\overline{m}$ are the images of $X,m$, etc.) .
-All such triples form a constraint graded space of observables.
-**Theorem C** asserts that this constraint observables space carries a **constraint $L_\infty$-algebra** structure .
-By  "constraint $L_\infty$-algebra, " we mean an $L_\infty$ whose underlying structure is also a triple $(L, L_C, \overline{L})$: there are brackets $\ell_r$ on each of $L, L_C, \overline{L}$, and the inclusion/projection maps intertwine these (so that $L_C$ is an $L_\infty$-subalgebra and $\overline{L}$ the quotient $L_\infty$) .
-The brackets are defined using the same formulas as in the unconstrained case, applied levelwise to $(G, M, c)$, $(G_C, M_C, c_C)$ and inducing $(\overline{G}, \overline{M}, \overline{c})$ .
-The $L_\infty$ identities hold simultaneously on each level by the same reasoning as before, thanks to the compatibility of the constraint data.
-- **Reduction Functor:** Once we have a constraint $L_\infty$-algebra of observables, *reducing it* means passing to the **quotient part** of the constraint triple.
-In categorical terms, there is a forgetful functor sending a constraint object $(X, X_C, \overline{X})$ to the quotient $\overline{X}$.
-When we apply this to the constraint $L_\infty$ of observables, we obtain an $L_\infty$-algebra on $\overline{L}$, which we interpret as the **reduced $L_\infty$-algebra of observables** of the constrained system.
-Intuitively, this $\overline{L}$ encodes observables that are invariant under the symmetry and defined on the constraint surface (since we mod out those that vanish or differ by constraint terms) .
-By construction, all the $L_\infty$ brackets descend to $\overline{L}$, so the homotopy Lie structure is well-defined on the quotient.
-This algebra $\overline{L}$ is the algebraic analog of the Poisson algebra of the reduced phase space in classical reduction, but here it can handle the homotopy brackets arising from a multisymplectic form and even if no nice manifold quotient exists (e.g.
-in singular cases).
-- **Recovery of Known Results:** Our general reduction scheme, when applied to the **geometric case** of a multisymplectic manifold with a group action, reproduces the results of our earlier work (Blacker-Miti-Ryvkin, SIGMA 2024) .
-In that work, we constructed a reduced $L_\infty$ of observables by more ad-hoc means; now we see it fits into the constraint triple framework.
-Specifically, given a Lie group $G$ acting on an $n$-plectic manifold $(M,\omega)$ with a covariant momentum map $\mu$ , one can form the constraint triple:
-    - $A = $ observables $L_\infty$ on $(M,\omega)$,
-    - $A_C = $ those observables that vanish on the constraint (e.g. forms pulled back by $\mu$ setting to zero, etc.),
-    - $\overline{A} = $ observables on the reduced space (when $0$ level set mod $G$ is nice, these correspond to forms on the quotient).
-
-    Our formalism shows that $\overline{A}$ inherits an $L_\infty$-algebra structure automatically .
-No assumptions of regularity or freeness are needed in the algebraic approach - even if the quotient is singular, $\overline{A}$ is well-defined as a homotopy algebra.
-This extends the multisymplectic reduction of Blacker 2021 (which assumed regularity) to a far more general context .
-Moreover, within our algebraic setting we identify an object called the **residue defect**, which measures the slight difference between naive and actual reduction in the homotopy context.
-In the earlier work, this residue term appeared somewhat mysteriously to satisfy the homotopy Jacobi identities; here we can interpret it cleanly as arising from the constraint differential and the failure of a certain exactness on the constraint submodule.
-Our framework **clarifies the role of the  "residue defect "**: it is an intrinsic part of the constraint $L_\infty$ structure that vanishes under appropriate conditions (like when the momentum map level is regular) .
-
-- **Summary of Main Results:** We can summarize the main technical results (theorems) as follows:
-    - **Theorem A:** *Given any Gerstenhaber algebra $G$ with a BV-module $M$ and a closed element $c\in M$, the graded space of Hamiltonian pairs $\mathcal{O}(G,M;c)$ admits an $L_\infty$-algebra structure (observables algebra), defined by the multilinear maps derived from Cartan calculus.*
-    - **Theorem B:** *If $(A,E)$ is a **constraint** Lie-Rinehart algebra (constraint version of derivations over a constraint algebra $A$), then one naturally obtains a constraint Gerstenhaber algebra and a constraint BV-module $(G, M)$ out of it.
-(In short, classical constraint manifolds yield constraint Cartan calculus algebraically.)
-    - **Theorem C:** *Given a constraint Gerstenhaber algebra and BV-module with a constraint cocycle $c$, one can construct a **constraint** $L_\infty$-algebra of observables.
-Moreover, its **reduced part** $\overline{\mathcal{O}}$ (the quotient level) is an $L_\infty$-algebra that describes the observables of the reduced system.*
-
-    As an application, Theorem C applied to multisymplectic manifolds with symmetries recovers the reduced $L_\infty$ in  and explains the extra terms (residue defect) in a categorical way .
-
-## **Conclusion and Outlook**
-
-We have developed a **purely algebraic toolkit** for constructing and reducing $L_\infty$-algebras of observables, extending concepts from symplectic geometry to multisymplectic and even noncommutative settings .
-This framework shows the power of combining homotopy algebra (for observables) with constraint category theory (for reduction).
-It provides a unified perspective where classical geometric reduction is just one instance of an algebraic functor acting on $L_\infty$-algebras .
-
-Some directions for further research include:
-
-- **Homotopy Momentum Maps:** Relating our constraint $L_\infty$-reduction to the notion of *homotopy momentum maps* (which appear in alternative higher reduction approaches, e.g.
-the work of Callies-Frégier-Rogers-Zambon on $L_\infty$-moment maps .
-It would be interesting to connect the **Leibniz-algebra-valued momentum maps** used here  with homotopy moment maps in an $L_\infty$-context.
-- **Operadic Formulation:** The constraint triple constructions hint at an operadic or higher-categorical organization.
-One could aim to describe the entire process (Cartan calculus + constraints + $L_\infty$) in terms of operads or properads encoding these algebraic relations .
-This might streamline proofs and allow further generalizations (e.g.
-to quantum or $A_\infty$ settings).
-- **Applications to Field Theory:** Ultimately, multisymplectic forms arise in classical field theory (e.g.
-the 2-form in mechanics vs.
-a 3-form in 2-dimensional field theory).
-Our algebraic observables $L_\infty$ could serve as a foundation for understanding *higher Poisson brackets* on the phase space of fields and their reduction under symmetries.
-Recent works on polysymplectic and polycontact reduction provide complementary geometric approaches; linking those with our algebraic method is a promising avenue.
-
-**References:** *(Selected key references in context)* Rogers (2012) for the original multisymplectic $L_\infty$-algebra construction; Dippel-Esposito-Waldmann (2019) for constraint (coisotropic) triples in Poisson algebra setting; Blacker-Miti-Ryvkin (2024) for algebraic multisymplectic reduction; and our work Miti-Ryvkin (2025) (Differential Geom.
-Appl.) which this talk is based on, for full details and proofs.
-The methods presented exemplify how **pure algebraic techniques can not only recover but also enlighten classical geometric results** in higher symplectic geometry, broadening the scope to singular and noncommutative realms.

### 2025-10-23 bv-triples-intro.tex
Slides complete.

@@
 		            \node[draw=orange!40,anchor=base,text width=5cm] (s1)
-		            {...};
+		            {The procedure to reduce the dimensions of Phase Space (e.g. of the space of measurable quantities) in presence of constraints or symmetries.};
 			}
@@
 		            \node[draw=blue!40,anchor=base, text width=5cm] (s2)
-		            {...};
+		            {Higher analogue of DGLie algebras where Jacobi holds up to homotopies.};
 			}
@@
 	            \node[draw=green!40,anchor=base,text width=5cm] (s3)
-	            {...};
+	            {Algebraic object encoding measurable quantities of a mechanical system.};
 	         }
@@
 	            \node[draw=red!40,anchor=base,text width=5cm] (s4)
-	            {...};
+	            {Algebraic object encoding Cartan Calculus.};
 	           }	
@@
 	\begin{block}{Based on:}
-		 \emph{ \small
-			 M. , Ryvkin;
-			\textbf{Multisymplectic observable reduction using constraint triples}; 
-			\href{https://arxiv.org/abs/2506.00234}{arXiv:2506.00234}.
-		 }.
-
+		\fullcite{ShortMiti2025}
 	\end{block}
@@
 \begin{frame}[fragile]{Scope / Goals}
-	\begin{block}{Upshots:}
+	\begin{upshotblocktitle}
 		\begin{itemize}
@@
 		\end{itemize}
-	\end{block}
+	\end{upshotblocktitle}
 	\pause \vfill
 
-	\begin{block}{Claim:}
+	\begin{claimblocktitle}
 		To any given BV-module over a Gerstenhaber algebra together with a chosen closed element (a "cocycle") in the module, we can define:
@@
 		\end{itemize}
-	\end{block}
+	\end{claimblocktitle}
 	\pause \vfill
 
-	\begin{block}{Applications:}
-		\begin{itemize}
-			\item[$\bullet$] A more conceptual picture for the algebraic reduction of the observables $L_\infty$-algebra in presence of constraints / symmetries.
-		\end{itemize}
-	\end{block}
+	\begin{outlookblock}[Applications]
+		A more conceptual picture for the algebraic reduction of the observables $L_\infty$-algebra in presence of constraints / symmetries.
+	\end{outlookblock}
 	\vfill

### 2025-10-23 bv-triples-main.tex
Slides complete.

--- 2025-10-21 bv-triples-main.tex
@@
 \title{Construction and Reduction of the $L_\infty$ Algebra of Observables Associated with a BV-Module} 
-\subtitle{\href{https://www.mat.uniroma2.it/~ricerca/algebr/page-AREA_files/page-AREA-2_files/talks.html}{- ARTS - Algebra and Representation Theory Seminar in Roma "Tor Vergata"}}
+\subtitle{}
 \author[AMM]{
-	\href{https://www.antoniomiti.it/}{Antonio Michele Miti}
-	{\small joint work w/ Leonid Ryvkin}
+	\href{https://www.antoniomiti.it/}{Antonio Michele Miti} \\
+	{(\small joint work w/ \href{https://www.ryvkin.eu}{Leonid Ryvkin})}
 }
@@
 {
+
 	{\vskip 1ex}
+	\href{https://www.mat.uniroma2.it/~ricerca/algebr/page-AREA_files/page-AREA-2_files/talks.html}{- ARTS - Algebra and Representation Theory Seminar in Roma "Tor Vergata"}
+	\\
 	Universit\'a di Roma - Tor Vergata, October 2025
@@
 %+----------------------------------------------------------+
-	\checkpoint	
 	\input{bv-triples-background}
@@
 %+----------------------------------------------------------+
-	\checkpoint	
-	%\input{bv-triples-Rogers-generalized}
+	\input{bv-triples-Rogers-generalized}
 %-----------------------------------------------------------%
@@
 %+----------------------------------------------------------+
-	\checkpoint	
-	%\input{bv-triples-reduction}
+	\input{bv-triples-reduction}
 %-----------------------------------------------------------%
@@
 	\addtocounter{framenumber}{-1}
-		\begin{frame}{Conclusion:}
-			\vfill
+		\begin{frame}{Conclusions}
+			\begin{upshotblocktitle}[Algebraic formalism for $L_\infty$ observables]
+				We generalized Rogers' construction to constraint BV-modules.
+			\end{upshotblocktitle}
+			\vfill\pause
+
+			\begin{upshotblocktitle}[Recovered previous reduction procedures]
+				 Emploied this machinery to provide a conceptual framework for algebraic multisymplectic reduction of observables via constraint triples 
+				 \smallskip
+
+				 \fullcite{Blacker-M-Ryvkin-2024}\nocite{Blacker-M-Ryvkin-2024}
+			\end{upshotblocktitle}
+			\vfill\pause
+
+			\begin{outlookblock}[An operadic reformulation]
+				Rather than defining suitable constraint triples "by hand", it could be interesting to provide a systematic treatment, e.g. within the language of operads.
+			\end{outlookblock}
+			\vfill\pause
+
 		  	\centering 
-		  \onslide<2->{\Huge\color{red} 
+		  	{\Huge\color{red} 
 		  	\emph{Thank you for your attention!}\normalsize \color{black}}
@@
 		\note[itemize]{
-			\item
+			\item 				The constraint triples formalism provides a powerful tool to treat singular geometric (and algebraic) settings. 
 		}
@@
 
+%-------------------------------------------------------+
+% APPENDIX
+%-------------------------------------------------------+
+%-------------------------------------------------------+
+\appendix
+%-------------------------------------------------------+
+%-------------------------------------------------------+
+\section{Complementary Material}
+	\input{bv-triples-complementary-material}
 %------------------------------------------------------------------------------------------------
-% APPENDIX
+
 %------------------------------------------------------------------------------------------------
-\appendix
+\section{References \& Aknowledgements}
 %------------------------------------------------------------------------------------------------
-\section{Complementary Material}
-	%\input{bv-triples-complementary-material}
-	%\input{bv-triples-aknowledgements}
-%------------------------------------------------------------------------------------------------
+	\input{bv-triples-acknowledgements}
 

### 2025-10-23 bv-triples-reduction.tex
Slides complete.

@@
 	\begin{defblock}[Constraint $L_\infty$-algebras] 
-	A constraint vector space $L=\triple{L}$  equipped with a collection of constraint multilinear maps
-	\begin{displaymath}
-		l_j \colon L^{\otimes j} \to L[2-j]
-	\end{displaymath}
+	A constraint vector space $L=\triple{L}$  equipped with \\
+	a collection of constraint multilinear maps $l_j \colon L^{\otimes j} \to L[2-j]$\\
 	such that $(L_\Total, (l_j)_\Total)$ is an $L_\infty$-algebra.
@@
 	\begin{defblock}[Constraint vector space of Hamiltonian pairs]\label{def:constraint-algebraicham0}
-		The	 constraint graded vector space:
+		The	 \emph{constraint ungraded vector space}:
 		$$
@@
 \begin{frame}{Reduction Functor}
-\begin{itemize}
-  \item Quotient part $\overline{\mathcal{O}}$ inherits $L_\infty$ structure.
-  \item Encodes reduced observables algebra.
-  \item No need for regular quotient at geometric level.
-\end{itemize}
+
+	\begin{remblock}[Reduction functor]\label{rk:red-functor}
+		The very purpose of introducing categories of constraint objects is to assume the existence of a corresponding \emph{reduction functor} $\red$ that assigns to each constraint object its reduced counterpart.
+	\end{remblock}
+	\vfill\pause
+
+	\begin{exblock}[Constraint associative algebras]
+	A constraint associative algebra is equivalently given by a triple $A = \triple{A}$, where $A_\Wobs \subset A_\Total$ is a subalgebra, and $A_\Null \subset A_\Wobs$ is a (two-sided) ideal. i.e.:
+		$$
+			\red: \textbf{ConAlg} \to \textbf{Alg}~, \quad \mathcal A \mapsto \red(\mathcal A) := \mathcal A_\Wobs / \mathcal A_\Null~,
+		$$
+	\end{exblock}
+	\vfill\pause
+
+	\begin{upshotblocktitle}[Reduction functor for the $L_\infty$-algebra of observables]
+		The $\Null$ part of $\Ham(V, \omega)$ is an $L_\infty$-ideal in the $\Wobs$ part. 
+		\\
+		Thus, the reduction functor applied to the constraint $L_\infty$-algebra of observables space gives a honest $L_\infty$-algebra.
+	\end{upshotblocktitle}
+
 \end{frame}
 \note[itemize]{
-	\item  
-}
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+	\item  	The reduction functor $\red$ assigns to each object $V$ the quotient vector space $\red(V) := V_\Wobs/V_\Null$, and to each morphism $f: V \to V'$ the induced map $\red(f): V_\Wobs/V_\Null \to V'_\Wobs/V'_\Null$.
 
-%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
-\begin{frame}{Recovering Old Results}
-\begin{itemize}
-  \item Applies to multisymplectic reduction (Blacker-Miti-Ryvkin 2024).
-  \item Explains residue defect in homotopy Jacobi identity.
-  \item Matches geometric reduction under regularity.
-\end{itemize}
-\end{frame}
-\note[itemize]{
-	\item  This framework provides a unified approach to understanding various geometric and algebraic structures.
 }

### 2025-10-24 bv-triples-background.tex
Reduction Section almost done.
Slides complete.
Presentation done.

@@
 %-----------------------------------------------------------+
+\subsection{Lie--Rinehart Algebras}
+%-----------------------------------------------------------+
+
+%-----------------------------------------------------------+
 \begin{frame}{Lie-Rinehart Algebras}
@@
       \item $\mathfrak{L}$ is an $A$-module and a Lie algebra,
-      \item there is an anchor map $\rho: \mathfrak{L} \to \mathrm{Der}(A)$ satisfying the Leibniz rule:
+      \item $\rho: \mathfrak{L} \to \mathrm{Der}(A)$ is an $A$-linear maps satisfying the Leibniz rule:
 
@@
     \item Let ${A}$ be a commutative  algebra over a field $\mathbb{k}$.
-  Denote by $\X(A)=\Der_{\mathbb{k}}(A)$ its Lie algebra of derivations, which naturally forms an $A$-submodule of $\End(A)$ with the action $A\action \End(A)$ given by postmultiplying with the element of $A$.
+  Denote by $\X(A)=\Der_{\mathbb{k}}(A)$ its Lie algebra of derivations, which naturally forms an $A$-submodule of $\End(A)$ with the action $A\curvearrowright \End(A)$ given by postmultiplying with the element of $A$.
   \item In the context of differential geometry, a primary example is when $A = C^\infty(M)$, the algebra of smooth functions on a smooth manifold $M$.
@@
 }
+%-----------------------------------------------------------+
+
+%-----------------------------------------------------------+
+\subsection{Gerstenhaber Algebras and Modules}
 %-----------------------------------------------------------+
@@
 		\item $\wedge : G \otimes G \to G$ is a graded commutative, associative product;
-		\item $\{\blank,\blank\} :G[1]\otimes G[1]\to G[1]$ is a graded Lie bracket,
+		\item $\{\cdot,\cdot\} :G[1]\otimes G[1]\to G[1]$ is a graded Lie bracket,
   \end{itemize}
@@
 \note[itemize]{
-  \item  The bracket $\{\blank,\blank\}$ could also be reinterpreted as a degree $-1$ bracket on the desuspended $\Z$-graded vector space $G$, coincides with the definition of $1$-Poisson algebra of \cite{Cattaneo2006b}.
+  \item  The bracket $\{\cdot,\cdot\}$ could also be reinterpreted as a degree $-1$ bracket on the desuspended $\Z$-graded vector space $G$, coincides with the definition of $1$-Poisson algebra of \cite{Cattaneo2006b}.
   \item The Schouten--Nijenhuis bracket is the unique graded Lie bracket satisfying the following properties:
@@
     $$
-    \CE(\mathfrak{L}) := \left((\Lambda_A^\bullet \mathfrak{L})^*\right)^{\rev}$$
+    \CE(\mathfrak{L}) := \left((\Lambda_A^\bullet \mathfrak{L})^*\right)^{\rev}
+    $$ 
+    \smallskip
 
@@
 %-----------------------------------------------------------+
+\subsection{Cartan Calculus}
+%-----------------------------------------------------------+
+
+%-----------------------------------------------------------+
 \begin{frame}{BV-Modules}
@@
     \end{itemize}
-    Compatibility wrt the Lie algebra action $\Lie:G\action V$: 
+    Compatibility wrt the Lie algebra action $\Lie:G\curvearrowright V$: 
     $$
@@
     \centering
-    \emph{BV-module $(V,\d)$ over $(G,\wedge,\lbrace\cdot,\cdot\rbrace)$ encode a full Cartan calculus}
+    \emph{a BV-module $(V,\d)$ over $(G,\wedge,\lbrace\cdot,\cdot\rbrace)$ encodes a full Cartan calculus}
   \end{quote}
@@
 	    \item $\iota$ the associative algebra action\footnote{$\iota_{x\wedge y}=\iota_x\iota_y~, \qquad \forall x,y\in G$.} of $(G,\wedge)$ on $V$;
-  	  \item $\Lie$ the Lie algebra action\footnote{$\Lie_{x\wedge y}=\iota_x\Lie_y + (-1)^{|y|}\Lie_x \iota_y~, \qquad \forall  x,y\in G$.} of $(G,\{\blank,\blank\})$ on $V$ of degree $-1$.
+  	  \item $\Lie$ the Lie algebra action
+      of $(G,\{\cdot,\cdot\})$ on $V$ of degree $-1$.
     \end{itemize}   
@@
   \begin{lemblock}[Cartan identities]
- The operators $\d$, $\iota_x$, and $\Lie_x$ satisfy six graded commutation relations:
+ The operators $\d$, $\iota_x$, and $\Lie_x$ satisfy six\footnote{There's also: $\Lie_{x\wedge y}=\iota_x\Lie_y + (-1)^{|y|}\Lie_x \iota_y~, \qquad \forall  x,y\in G$.}  graded commutation relations:
 	%
@@
   \item 	A pair $(G, V)$ consisting of a Gerstenhaber algebra and a BV module is often called a \emph{Tsygan–Tamarkin–Nest noncommutative differential calculus}~\cite[Def.~4.4]{Tsygan2004}.
-  \item Denote Gerstenhaber algebra structure on $G \oplus V^{\rev}$ by $(\star,\llbracket\blank,\blank\rrbracket)$.
+  \item Denote Gerstenhaber algebra structure on $G \oplus V^{\rev}$ by $(\star,\llbracket\cdot,\cdot\rrbracket)$.
 For a homogeneous element $x \in G$, denote by $\iota_x$ and $\Lie_x$ the corresponding operators on $V$.
-  \item These actions are induced by restricting the Gerstenhaber structure $(\star,\llbracket\blank,\blank\rrbracket)$ on $G \oplus V^{\rev}$ to $G \otimes V^{\rev} \subset (G \oplus V^{\rev})^{\otimes 2}$.
+  \item These actions are induced by restricting the Gerstenhaber structure $(\star,\llbracket\cdot,\cdot\rrbracket)$ on $G \oplus V^{\rev}$ to $G \otimes V^{\rev} \subset (G \oplus V^{\rev})^{\otimes 2}$.
  \item The associative action $\iota$ is defined by
@@
 	\]
- \item The compatibility between $\star$ and $\llbracket\blank,\blank\rrbracket$ in $G \oplus V^{\rev}$ implies the following \emph{mixed Leibniz rules} (see \cite[Def.~2.1]{Kowalzig2015}):
+ \item The compatibility between $\star$ and $\llbracket\cdot,\cdot\rrbracket$ in $G \oplus V^{\rev}$ implies the following \emph{mixed Leibniz rules} (see \cite[Def.~2.1]{Kowalzig2015}):
   \begin{align}

### 2025-10-24 bv-triples-intro.tex
Presentation done.

@@
 		            \node[draw=orange!40,anchor=base,text width=5cm] (s1)
-		            {The procedure to reduce the dimensions of Phase Space (e.g. of the space of measurable quantities) in presence of constraints or symmetries.};
+		            {The procedure to reduce the dimensions of a Phase Space (or the space of obsevables) in presence of constraints or symmetries.};
 			}

### 2025-10-24 bv-triples-main.tex
Corrected problem with flags
Presentation done.

@@
 %- HandOut Flag -----------------------------------------------------------------------------------------
-	\newif\ifHandout
+	\newif\ifHandout\Handoutfalse
 	\Handouttrue  %uncomment for the printable version
@@
 	{\vskip 1ex}
-	\href{https://www.mat.uniroma2.it/~ricerca/algebr/page-AREA_files/page-AREA-2_files/talks.html}{- ARTS - Algebra and Representation Theory Seminar in Roma "Tor Vergata"}
+	\href{https://www.mat.uniroma2.it/~ricerca/algebr/page-AREA_files/page-AREA-2_files/talks.html}{- ARTS - Algebra and Representation Theory Seminar}
 	\\
@@
 	\titlepage
+	% Handout watermark
 	\ifHandout
@@
 	\fi
+	% European Commission	
+		\tikz[overlay,remember picture]
+		{
+	    	%	\node at ($(current page.west)+(1.5,0)$) [rotate=90] {\Huge\textcolor{gray}{\today}};
+	    	\node[        
+	    		text width = 3.5cm
+			]
+	        		at ($(current page.south west)+(2.0,2.0)$) [rotate=0] {
+
+					\href{https://dipartimenti.unicatt.it/dmf-home?rdeLocaleAttr=it}{\includegraphics[width=\textwidth]{./Logos/Eu-h2020}}
+
+	        		};
+		}
 	\end{frame}
@@
 
-			\begin{upshotblocktitle}[Recovered previous reduction procedures]
+			\begin{claimblocktitle}[Recovered previous reduction procedures]
 				 Emploied this machinery to provide a conceptual framework for algebraic multisymplectic reduction of observables via constraint triples 
@@
 				 \fullcite{Blacker-M-Ryvkin-2024}\nocite{Blacker-M-Ryvkin-2024}
-			\end{upshotblocktitle}
+			\end{claimblocktitle}
 			\vfill\pause

### 2025-10-24 bv-triples-reduction.tex
Presentation done.

@@
 %- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+\begin{frame}{A plethora of approaches to singular reduction}
+ 	Many singular reduction schemes adhere to this pattern!
+ 	\vfill
+ 	\pause
+\begin{table}[]
+	\begin{tabular}{l|l|l||l}
+		algebra $\mathcal{A}_T$ & subalgebra $\mathcal{A}_N$ & ideal $\mathcal{A}_0$ & comment \\
+		\hline
+
+		$C^\infty(M)$&      $N_S$     &   $I_S$   &  $\substack{S=\mu^{-1}(0),~ I_S=\{f~|~f|_S=0\}}$ \\
+			&&&  $\substack{N_S= \{ f | gf-f\in I_S \forall g\in G\}}$ \\
+	& & & \color{red} not Poisson \\ 
+	\hline	\pause
+	$C^\infty(M)$&   $F_S$         &   $I_S$   &  $\substack{F_S=\{f~|~\{f,I_S\}\subset I_S\}}$ \\
+	& & & \color{red} if $I_S\subset F_S$\\
+	\hline \pause
+
+	$C^\infty(M)$&   $C^\infty(M)^G$         &   $(I_S)^G$   &  $\substack{C^\infty(M)^G=\{f~|~gf=f\forall g\in G\}}$ \\
+	\hline \pause
+		$C^\infty(M)$&   $C^\infty(M)^G$         &   $(I_\mu)^G$   & $\substack{I_\mu=\{\sum_{i=1}^k f_i\langle \mu,\xi_i\rangle|~f_i\in C^\infty(M), \xi_i\in \mathfrak g\}}$\\
+		\hline \pause
+	$C^\infty(M)$&      $N_\mu$     &   $I_\mu$   & $\substack{N_\mu= \{ f | gf-f\in I_\mu \forall g\in G\}}$ \footnote{When $G$ connected $N_\mu=N(I_\mu):=\{f~|~\{f,I_\mu\}\subset I_\mu\}$.}\\
+	\hline
+
+	\end{tabular}\pause
+\end{table}
+	\vfill
+	{\bf Remarks }names in order: 'naive' , Dirac, Sniatycki, Arms-Cushman-Gotay, Sniatycki-Weinstein.
+
+\end{frame}
+\note[itemize]{
+	\item \emph{(Credits to \href{https://www.ryvkin.eu/}{Leonid Ryvkin} for the tex code of this slide.)}
+}
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
+
+%- . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - . - .%
 \begin{frame}{Constraint Gerstenhaber-Modules}
@@
 	\begin{displaymath}
-		\{ \blank, \blank \} \colon G[1] \otimes G[1] \to G[1]
+		\{ \cdot, \cdot \} \colon G[1] \otimes G[1] \to G[1]
 	\end{displaymath}
@@
  \begin{remblock}[$G$ can be seen as a triple of Gerstenhaber subalgebras]\label{rk:constraintgerst-as-triple}
-	 $G_\Null \subseteq G_\Wobs \subseteq (G_\Total, \wedge,\lbrace\blank,\blank\rbrace)$ such that $G_\Null$ is a Gerstenhaber ideal in $G_\Wobs$. 
+	 $G_\Null \subseteq G_\Wobs \subseteq (G_\Total, \wedge,\lbrace\cdot,\cdot\rbrace)$ such that $G_\Null$ is a Gerstenhaber ideal in $G_\Wobs$. 
 \end{remblock}
